---
title: "ABFM Naive Levy Elasticity Models"
author: "MVH & AWM"
date: "July 19, 2024"
format: 
  html:
    embed-resources: true
    theme: minty
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 200px
---

```{r setup}
#| output: FALSE

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(modelsummary)
library(tidyverse)
library(kableExtra)
library(glue)
library(DT)
library(flextable)

set_flextable_defaults(theme_fun = theme_vanilla, 
                       padding = 2,
                       line_spacing = 1,
                       big.mark = ",",
                       )

options(DT.options = list())

set_summ_defaults(digits = 2, pvals = FALSE, robust = "HC5")

```

# Data Description

Our data ("panel_data.csv") is generated on line 187 of the "helper_recode_variables.R" file, which queries, filters, and manipulates variables from the PTAXSIM DB. It is the same data we have been using since February EXCEPT for the models we ran in April, where we used "grouped" taxing agencies.

SSAs are excluded from our sample.

Chicago is included in our sample.


# Naive Model

```{r}
#| label: load_paneldata_duplicate
#| output: false


df <- read_csv("panel_data.csv") |>  # 10,374 observations before filtering
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()
# 10,181 obs

df_panel <- pdata.frame(df, index = c("agency_num", "year"))
# is.pbalanced(df_panel)

# Balance the panel -> now 9758 obs
df_panel <- make.pbalanced(df_panel)
# is.pbalanced(df_panel)       # 9,758 obs after balancing


# Subset: schools and munis - 4,250
school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO") %>%
 make.pbalanced("shared.individuals")
# is.pbalanced(school_muni)


# All schools: 2,380 obs.
schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY") %>% 
  make.pbalanced(balance.type = "shared.individuals" )
#is.pbalanced(schools)

# Elementary schools: 1,938 obs.
ele <- subset(df_panel, minor_type == "ELEMENTARY") %>% 
  make.pbalanced(balance.type = "shared.individuals" )


# Secondary Schools: 442 obs.
sec <- subset(df_panel, minor_type == "SECONDARY") %>% 
  make.pbalanced(balance.type = "shared.individuals" )



# All munis: 1853 obs.
muni_subset  <- subset(df_panel, minor_type == "MUNI") %>% 
  make.pbalanced(balance.type = "shared.individuals" )
# is.pbalanced(munis)


# HR Munis: 1,253 obs. --> 1,190 after balancing
muni_hr <- subset(df_panel, (minor_type == "MUNI" | clean_name == "Cicero")  & home_rule_ind == 1) %>% 
  make.pbalanced(balance.type = "shared.individuals" )
# is.pbalanced(muni_hr)


# NHR munis: 685 obs. --> 612 after balancing
muni_nhr <- subset(df_panel, (minor_type == "MUNI" | clean_name == "Cicero")& home_rule_ind == 0) %>% 
  make.pbalanced(balance.type = "shared.individuals")

colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")
  
```


## All Agencies

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

Merriman, July 20 - "It might be interesting to run a regression with all non-home-rule agencies that are not municipalities or schools." -- **See Model Below!**

> "Other Agencies" include taxing agencies that are NOT Schools or Municipalities.


```{r twfe_all_naive}

all_agencies_naive <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = df_panel)

hr_others <- subset(df_panel, home_rule_ind == 1 & (minor_type != "MUNI" & major_type != "SCHOOL")) %>% make.pbalanced("shared.individuals")


nhr_others <- subset(df_panel, home_rule_ind == 0 & (minor_type != "MUNI" & major_type != "SCHOOL")) %>%  make.pbalanced("shared.individuals")

naive_hr_others <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = hr_others)

naive_nhr_others <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = nhr_others)


all_agencies_summ_table <- 
  export_summs(all_agencies_naive, naive_hr_others, naive_nhr_others,
               model.names = c("All Agencies", "Other HR Agencies", "Other NHR Agencies"),
                                robust = "HC5",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))



all_agencies_summ_table

```

## Municipalities

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

```{r twfe_muni_naive}


naive_mod_munis <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)


naive_mod_muni_hr <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = muni_hr)

naive_mod_muni_nhr <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = muni_nhr)


muni_summ_table <- 
  export_summs(naive_mod_munis, naive_mod_muni_hr, naive_mod_muni_nhr,
               model.names = c("All Municipalities", "HR Municipalities", "NHR Municipalities"),
                                robust = "HC3",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_summ_table <- set_caption(muni_summ_table, "Municipalities, Dependant Variable: ln(levy)")

muni_summ_table

```

## Schools

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

There are five types of school taxing agencies: elementary, secondary, community colleges, miscellaneous, and unified. Elementary school districts make up the overwhelming majority of these taxing agencies.

```{r school_distr}

school_summary <- df |>
  filter(major_type == "SCHOOL") |>
  filter(year == 2021) |>
  group_by(minor_type) |>
  rename("School Type" = minor_type) |>
  summarize(n = n())

bar_colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")

ggplot(school_summary, aes(x = `School Type`, y = n, fill = `School Type`)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = bar_colors) +
  ylim(0, 125) +
  theme_minimal() +
  labs(title = "School Agencies by Type (2021)",
       x = "Type of School",
       y = "n") +
  theme(legend.position = "none") +
  geom_text(aes(label = n), vjust = -0.5, size = 3)

```

The community college, miscellaneous, and unified observations are omitted from the "Elementary & Secondary Schools" regression model.

```{r twfe_school_naive}
#| tbl-cap: "Schools by Type, Dependent Variable: ln(levy)"


school_naive <- plm(log_levy ~ log_av,
                        model = "within",
                         effect = "twoways",
                         data = schools)

ele_naive <- plm(log_levy ~ log_av,
                            model = "within",
                            effect = "twoways",
                            data = ele)

sec_naive <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = sec)

# no_other_school_subset <- subset(df_panel, major_type == "SCHOOL" 
#                        & minor_type != c("COMM COLL", "MISC", "UNIFIED"))
# 
# naive_mod_no_misc_school <- plm(log_levy ~ log_av,
#                                model = "within",
#                                effect = "twoways",
#                                data = no_other_school_subset)

school_summ_table <- export_summs(school_naive, ele_naive, sec_naive,
             model.names = c("Elementary & Secondary", "Elementary", "Secondary"),
             robust = "HC5",
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#school_table <- set_caption(school_summ_table, "Schools by Type, Dependent Variable: ln(levy)")

school_summ_table

```

The "Elementary & Secondary Schools" model excludes "misc", community colleges, and unified school districts.



## Municipalities & Schools

Since our focus is on municipalities and schools, I reran the model while only retaining those agency types.

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::


```{r twfe_schools_munis_naive}

# 4488 obs, balanced
muni_school_subset <- subset(df_panel, major_type == "SCHOOL" | minor_type == "MUNI" | agency_name == "TOWN CICERO") %>%
 make.pbalanced("shared.individuals")
#is.pbalanced(muni_school_subset)

# 1219 --> 1156 after balancing
muni_school_hr <- subset(muni_school_subset, home_rule_ind == 1) %>%
 make.pbalanced("shared.individuals")
#is.pbalanced(muni_school_hr)

# 3269 --> 3213 after balancing
muni_school_nhr <- subset(muni_school_subset, home_rule_ind == 0)  %>%
make.pbalanced("shared.individuals")
#is.pbalanced(muni_school_nhr)    
   

naive_muni_school <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_subset)

naive_muni_school_hr <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_hr)

naive_muni_school_nhr <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_nhr)

muni_school_table <- export_summs(naive_muni_school, naive_muni_school_hr, naive_muni_school_nhr,
             model.names = c("Municipalities & Schools", "Municipalities & Schools (HR)", "Municipalities & Schools (NHR)"),
             robust = "HC3",
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_school_table <- set_caption(muni_school_table, "Schools & Municipalities, Dependant Variable: ln(levy)")

muni_school_table

```


