---
title: "Levy Elasticity"
subtitle: "April 2024 Update"
author: "MVH & AWM"
format: 
  html:
    theme: lumen
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left-body
---

# Model Decision

ln(levy) = ln(av) + lag(ln(av)) + lag(ln(av), 2) + lag(ln(av)\^2)

Plain language: regress the log of the levy on the log of av, two lags of the log of av, and a lagged binomial of logged av.

# Outstanding Question

-   Our results are robust to Chicago's inclusion/exclusion from the model. Which goes into the appendix?

(Michael thinks Chicago inflates our standard errors and thus including it in our data is unsporting.)

# Model Discussion

## Variables

\[Mention grouping and how we'll move forward calling them municipalities or something.\]

### Independent Variable

ln(levy)

### Dependent Variables

ln(av) - natural log of the muni's levy. Used to reflect the tax base in lieu of EAV because it shows greater variation, lacks the EQ factor, doesn't include exemptions, \[Alea add stuff\].

lag(ln(av)) - it is likely that policy makers

lag(ln(av)\^2)

Two reasons:

1\) We hypothesize that the levy's responsiveness to the tax base's size is non-linear because \[of diminishing marginal returns\].

2)  Exploratory data analysis (visualizations) further suggested diminishing marginal returns in responsiveness to the tax base.

We *did not* try throwing this variable into the model first to see what happened second.

We *did* use a notepad, colored pens, and some pre-calc to verify where the exponent needed to go vis-a-vi the ln() operator.

## To (2W) Fixed or Not Fixed Effects

During an earlier iteration of our research design, we argued that two-way fixed effects were inappropriate given our use of a reassessment as the exogenous shock allowing us make a causal argument. Our current model neither makes a causal argument nor uses reassessment as a shock. Thus, the question is moot and we can use forward

# Data Discussion

We are using the "gm_for_pivots.csv" file made in "models.qmd".

Creation of the data set can be replicated with the whatever.qmd file.

# Models

```{r setup, output = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = TRUE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(prediction)


set_summ_defaults(digits = 2, robust = "HC5")

gm <- read.csv("gm_for_pivots.csv")

gm_nochi <- read.csv("gm_nochi_for_pivots.csv")

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year"))

nochi_pd <- pdata.frame(gm_nochi, 
                        index = c("uniqueid", "year"))
```

## Basic Models (e.g., ln(levy) \~ ln(av) + e)

```{r basic_w_Chi}

basic1_1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic1_2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic1_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(basic1_1, basic1_2, basic1_3)

modnames <- list("No AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

basic_table <- set_caption(ht, "Dependent Variable: ln(levy)")

print(basic_table)
```

```{r basic_wo_Chi}

basic1_nochi <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

basic2_nochi <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

basic3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(basic1_nochi, basic2_nochi, basic3_nochi)

modnames <- list("No AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

basic_table_nochi <- set_caption(ht, "Dependent Variable: ln(levy) (Excludes Chicago)")

print(basic_table_nochi)
```

## Reassessment Lag Dummy Variable

```{r reassess_lag_table}

relag1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

relag2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

relag3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(relag1, relag2, relag3)

modnames <- list("0 AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_lag_table <- set_caption(ht, "Dependent Variable: ln(levy); Interactions w/ lag(reassess_year)")

print(reassess_lag_table)
```

```{r reassess_lag_table_nochi}

relag1_nochi <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

relag2_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

relag3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(relag1_nochi, relag2_nochi, relag3_nochi)

modnames <- list("0 AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_lag_table_nochi <- set_caption(ht, "Dependent Variable: ln(levy); Interactions w/ lag(reassess_year) (Excludes Chicago)")

print(reassess_lag_table_nochi)
```

Let's try playing adding regular reassessment_year!

```{r reassess_table_1}

reass1_1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass1_2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass1_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(reass1_1, reass1_2, reass1_3)

modnames <- list("0 AV Lag", "1 AV Lag", "2 AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_table_1 <- set_caption(ht, "Dependent Variable: ln(levy)")

print(reassess_table_1)

```

```{r reassess_table_1_nochi}

reass1_1_nochi <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass1_2_nochi <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass1_3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(reass1_1_nochi, reass1_2_nochi, reass1_3_nochi)

modnames <- list("0 AV Lag", "1 AV Lag", "2 AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            "AIC" = "AIC",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_table_1_nochi <- set_caption(ht, "Dependent Variable: ln(levy) (Excludes Chicago)")

print(reassess_table_1_nochi)
```

Crazy LSAT mix-and-match time!

```{r reassess_table_LSAT}

reass2_1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_2 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(reass2_1, reass2_2, reass2_3, reass2_4)

modnames <- list("Standard Model (2 AV Lags)", "ln(AV)", "1st AV Lag", "2nd AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_table_LSAT <- set_caption(ht, "Dependent Variable: ln(levy); Interactions w/ Reassessment Year")

print(reassess_table_LSAT)

```

```{r reassess_table_LSAT_nochi}

reass2_1_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass2_2_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass2_3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass2_4_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(reass2_1_nochi, reass2_2_nochi, reass2_3_nochi, reass2_4_nochi)

modnames <- list("Standard Model (2 AV Lags)", "ln(AV)", "1st AV Lag", "2nd AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_table_LSAT_nochi <- set_caption(ht, "Dependent Variable: ln(levy); Interactions w/ Reassessment Year (Excludes Chicago)")

print(reassess_table_LSAT_nochi)
```

## Polynomial Models

```{r polymodels}

poly1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly2 <- plm(log_levy ~ log_av + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(poly1, poly2, poly3, poly4)

modnames <- list("Standard Model (2 AV Lags)", "No Lag", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-statistic" = "statistic",
                            "p-value" = "p.value"))

poly_table <- set_caption(ht, "Dependent Variable: ln(levy)")

print(poly_table)
```

```{r polymodels_nochi}

poly1_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

poly2_nochi <- plm(log_levy ~ log_av + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

poly3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

poly4_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(poly1_nochi, poly2_nochi, poly3_nochi, poly4_nochi)

modnames <- list("Standard Model (2 AV Lags)", "No Lag", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-statistic" = "statistic",
                            "p-value" = "p.value"))

poly_table_nochi <- set_caption(ht, "Dependent Variable: ln(levy) (Excludes Chicago)")

print(poly_table_nochi)

```

# Goodness of Fit

## Plot Model Residuals

The best model appears to use 1 lag of ln(av) and the binomial lag(ln(av)\^2).

```{r}

best_mod <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

best_mod_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

###TIDYVERSE CANNOT BE LOADED FOR THE NEXT TWO COMMANDS

pred_best <- prediction(best_mod, data = gm_pd)

pred_best_nochi <- prediction(best_mod_nochi, data = nochi_pd)

library(tidyverse)

pred_best <- pred_best %>%
  mutate(resid = log_levy - fitted)

pred_best %>%
  ggplot(aes(x = log_levy, y = resid), alpha = .5) +
  geom_point() +
  labs(
    title = "Best Model Residuals"
  )

pred_best_nochi <- pred_best_nochi %>%
  mutate(resid = log_levy - fitted)

pred_best_nochi %>%
  ggplot(aes(x = log_levy, y = resid), alpha = .5) +
  geom_point() +
  labs(
    title = "Best Model Residuals (Excludes Chicago)"
  )

```
