---
title: "Data Exploration--Revised RD"
author: "AWM * MVH"
format: html
editor: visual
code-fold: true
toc: true
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(DBI)

library(ptaxsim)
#library(sf)
library(stars)
#library(glue)
library(lmtest)
library(huxtable) # for summ() and regression output formatting
# Create the DB connection with the default name expected by PTAXSIM functions
library(jtools)
library(plm) #for fixed effects
library(modelsummary)
library(dplyr)

ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2021.0.4.db")
#set_summ_defaults(digits = 2, pvals = FALSE, robust = "HC3" )


# Data notes for pct_res: 
# muni av and eav are calculated from the pin data table in ptaxsim. It is BEFORE exemptions and includes any EAV that is above the frozen TIF EAV, frozen EAV, and EAV outside of TIF tax codes.
# percentages for land use are also before exemptions and do not consider any EAV that would go to a TIF increment

#groupies <- readxl::read_excel("./grouped_munis_manual_entry.xlsx")

muni_agency_names <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT DISTINCT agency_num, agency_name, minor_type
  FROM agency_info
  WHERE minor_type = 'MUNI'
  OR agency_num = '020060000'
  "
  ) %>% 
  mutate(first6 = str_sub(agency_num,1,6),
        # first5 = str_sub(agency_num,1,5)
         ) %>%
  select(-minor_type)

```

```{r message = FALSE, warning = FALSE}
source("helper_recode_variables.R")
```

```{r}

library(dplyr)

all_agencies <- recoded_data

```

# Hypothesis 1

[**Hypothesis 1: Levy is inelastic to the taxbase for non-HR taxing agencies (capped funds)**]{.underline}

- H0: Capped extensions increase at the maximum rate possible (Leviathan theory? Idk)

- H1: They do not tax as much as possible, they ain\'t greedy, they only ask for what the \"need\"

  - taxing agencies do not tax at the maximum amount (aka descriptive stats on who is or isn\'t taxing at the maximum amount possible.)

  - Levy is inelastic to the taxbase (cuz duh, they have no power over it and can\'t respond to eav changes over time without shooting themselves in the foot for future years of taxation.)

- Levy increases the max amount (for non -- HR capped funds)

- Explanation: Show that the yearly percent change for capped funds is close to or equal to the lesser of inflation or 5%.

```{r}
nonHR_munis <- panel_data %>% 
  filter(minor_type == "MUNI" & home_rule_ind == 0 & total_final_levy > 0)



# agency_data3 <- nonHR_munis %>% 
#   filter(!agency_num %in% dropped_munis) %>%
#   filter(!agency_num %in% exclude_hr_change) %>%
#   filter(total_final_levy > 0) %>%
#   mutate( 
#          total_non_cap_ext = ifelse(!is.na(total_non_cap_ext) & total_non_cap_ext > 0,
#                                     as.numeric(total_non_cap_ext), NA), # value that matches Clerk Office PDF for Levy.
#          total_capped_ext = total_ext - total_non_cap_ext) %>%
#   mutate( 
#     log_eav = log(cty_total_eav), # eav within Cook AND neighboring counties.
#     log_levy = log(total_capped_ext),
#     log_levy2 = log(total_non_cap_ext)    
# 
#     )

endpoints <- nonHR_munis %>% filter(year == 2021)

nonHR_munis %>% 
  group_by(agency_name)  %>%
  ggplot() + 
  geom_line(aes(x=year, y = total_non_cap_ext, group = agency_name, color = Triad)) +
  geom_text(data = (endpoints), aes(x=year, y = total_non_cap_ext, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()+
    labs(title = "Non-Homerule Municipalities: Non-Capped Funds", 
         caption = "Non-Capped Funds include revenue collected to pay 
         for expenditures related to bonds, pensions, etc.
         PTELL do not apply to non-capped funds.")


nonHR_munis %>% 
  group_by(agency_name)  %>%
  filter(minor_type == "MUNI" & agency_name != "CITY OF CHICAGO") %>% 
  ggplot() + 
  geom_line(aes(x=year, y = total_capped_ext, group = agency_name, color = Triad)) +
  geom_text(data = (endpoints  %>%  filter(minor_type == "MUNI" & agency_name != "CITY OF CHICAGO")), aes(x=year, y = total_capped_ext, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()+
    labs(title = "Non-Homerule Municipalities: Capped Funds")



nonHR_munis %>% 
  filter(capped_pct_change < .5) %>%
  group_by(agency_name)  %>%
  ggplot() + 
  geom_line(aes(x=year, y = capped_pct_change, group = agency_name, color = Triad)) +
#  geom_text(data = (endpoints  %>%  filter(minor_type == "MUNI" & agency_name != "CITY OF CHICAGO")), aes(x=year, y = total_capped_ext, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()+
    labs(title = "Non-Homerule Municipalities: Capped Funds Pct Change")
  
```


```{r}
library(dplyr)

library(openxlsx)

groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))

grouped_nonhr_manual <- recoded_data %>% 
     filter(home_rule_ind == 0) %>%

  left_join(groupies2,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP" # | major_type == "MISCELLANEOUS"
          & minor_type != "MISC"
          # minor_type == "MUNI" | agency_name == "TOWN CICERO"
           ) %>%
  arrange(grouped_label, year) %>%
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_non_cap_ext =sum(total_non_cap_ext, na.rm=TRUE),
            total_capped_ext = sum(total_capped_ext, na.rm=TRUE),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
            total_non_cap_ext_4log =sum(total_non_cap_ext, na.rm=TRUE)+1,
            total_capped_ext_4log = sum(total_capped_ext, na.rm=TRUE)+1,
            total_final_levy_4log = sum(total_final_levy, na.rm=TRUE)+1,
            cty_total_eav = first(cty_total_eav), 
            av = sum(av, na.rm=TRUE),
            minor_type = first(minor_type),
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
           # home_rule_ind = first(home_rule_ind)
            ) %>% 
    left_join(muni_agency_names) %>% 
    mutate(
      log_eav = log(cty_total_eav),
      log_capped = log(total_capped_ext_4log),
      log_noncapped = log(total_non_cap_ext_4log),
      log_levy = log(total_final_levy_4log),
     bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(agency_name, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(agency_name, "_", home_rule_ind, "_", bundled, "_", first(lim_rate)),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(agency_name, year, everything()) %>% arrange(agency_name, year)


 grouped_nonhr_manual %>% 
  ungroup() %>%
   group_by(year, home_rule_ind) %>%
  summarize(count = n())

```
```{r}
library(dplyr)
# turn it into panel data!
# two way fixed effects will be used for agency and year.
panel_data <-pdata.frame(grouped_nonhr_manual, index = c("agency_name", "year"))



# need to detach dplyr because conflict w/ plm lag command
detach("package:dplyr", unload = TRUE)

panel_data$lag_totallevy <- plm::lag(panel_data$total_final_levy, 1)
panel_data$lag_capped <- plm::lag(panel_data$total_capped_ext, 1)
panel_data$lag_non_capped <- plm::lag(panel_data$total_non_cap_ext, 1)

panel_data$lag_cty_total_eav <- plm::lag(panel_data$cty_total_eav, 1)
panel_data$lag_av <- plm::lag(panel_data$av, 1)


panel_data$eav_lag1 <- plm::lag(panel_data$cty_total_eav, 1)
panel_data$eav_lag2 <- plm::lag(panel_data$cty_total_eav, 2)
panel_data$eav_lag3 <- plm::lag(panel_data$cty_total_eav, 3)
panel_data$eav_lag4 <- plm::lag(panel_data$cty_total_eav, 4)

panel_data$reassess_lag1 <- plm::lag(panel_data$reassess_year, 1)
panel_data$reassess_lag2 <- plm::lag(panel_data$reassess_year, 2)

#boss said leave redundant code.


library(dplyr)

panel_data <- panel_data %>% 
  
  mutate(eav_pct_change = ((cty_total_eav - lag_cty_total_eav)/ lag_cty_total_eav)*100,
         tfl_pct_change = ((total_final_levy - lag_totallevy) / lag_totallevy) *100,
         capped_pct_change = ((total_capped_ext - lag_capped) / lag_capped ) * 100,
         noncapped_pct_change = ((total_non_cap_ext - lag_non_capped) / lag_non_capped) * 100,
         av_pct_change = ((av - lag_av) / lag_av) * 100,
         av_increase = ifelse(av_pct_change > 0, "AV increased", 
                              ifelse(av_pct_change == 0, "No Change", "AV Increase")),
         up_down  = ifelse(eav_pct_change > 0, "increased", "decreased"))  %>%
  
  mutate(# eav_pct_change = ifelse(is.na(eav_pct_change), 0, eav_pct_change),
         home_rule_ind = as.factor(home_rule_ind),
         #minor_type = as.factor(minor_type),
         #major_type = as.factor(major_type),
         first6 = as.factor(first6))

detach("package:dplyr", unload = TRUE)

panel_data$lag_eav_pct_change1 <- plm::lag(panel_data$eav_pct_change, 1)
panel_data$lag_eav_pct_change2 <- plm::lag(panel_data$eav_pct_change, 2)

panel_data$lag_av_pct_change1 <- plm::lag(panel_data$av_pct_change, 1)
panel_data$lag_av_pct_change2 <- plm::lag(panel_data$av_pct_change, 2)

```

```{r}
library(dplyr)
# nonHR_munis <- grouped_nonhr_manual %>% 
#   filter(minor_type == "MUNI" & home_rule_ind == 0 & total_final_levy > 0)
# 


# agency_data3 <- nonHR_munis %>% 
#   filter(!agency_num %in% dropped_munis) %>%
#   filter(!agency_num %in% exclude_hr_change) %>%
#   filter(total_final_levy > 0) %>%
#   mutate( 
#          total_non_cap_ext = ifelse(!is.na(total_non_cap_ext) & total_non_cap_ext > 0,
#                                     as.numeric(total_non_cap_ext), NA), # value that matches Clerk Office PDF for Levy.
#          total_capped_ext = total_ext - total_non_cap_ext) %>%
#   mutate( 
#     log_eav = log(cty_total_eav), # eav within Cook AND neighboring counties.
#     log_levy = log(total_capped_ext),
#     log_levy2 = log(total_non_cap_ext)    
# 
#     )

endpoints <- grouped_nonhr_manual %>% filter(year == 2020)

grouped_nonhr_manual %>% 
 # ungroup() %>%
  group_by(agency_name)  %>%
  ggplot() + 
  geom_line(aes(x=year, y = total_non_cap_ext, group = agency_name, color = Triad, alpha = .5)) +
  geom_text(data = (endpoints), aes(x=year, y = total_non_cap_ext, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()+
    labs(title = "Non-Homerule Municipalities: Non-Capped Funds", 
         caption = "Non-Capped Funds include revenue collected to pay 
         for expenditures related to bonds, pensions, etc.
         PTELL do not apply to non-capped funds.")


grouped_nonhr_manual %>% 
  filter(year != 2021) %>%
  group_by(agency_name)  %>%
  #filter(minor_type == "MUNI" & agency_name != "CITY OF CHICAGO") %>% 
  ggplot() + 
  geom_line(aes(x=year, y = total_capped_ext, group = agency_name, color = Triad, alpha = .5)) +
  geom_text(data = (endpoints), aes(x=year, y = total_capped_ext, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()+
    labs(title = "Non-Homerule Municipalities: Capped Funds")




# panel_data %>% 
#   filter(total_capped_ext > 1) %>% 
#   filter(minor_type == "MUNI") %>%
#   filter(capped_pct_change >= -50 & capped_pct_change < 50) %>%
#   filter(year != 2021)


panel_data %>% 
  filter(minor_type == "MUNI") %>%
  filter(capped_pct_change >= -50 & capped_pct_change < 50) %>%
  filter(year != 2021) %>%
  ggplot() + 
  geom_line(aes(x=year, y = capped_pct_change, group = agency_name, color = Triad, alpha = .5)) +
 # geom_text(data = endpoints, aes(x=year, y = capped_pct_change, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()


panel_data %>% 
  filter(minor_type == "MUNI") %>%
  filter(capped_pct_change >= -20 & capped_pct_change < 20) %>%
  filter(year != 2021) %>%
  ggplot() + 
  geom_line(aes(x=year, y = capped_pct_change, group = agency_name, color = Triad, alpha = .5)) +
 # geom_text(data = endpoints, aes(x=year, y = capped_pct_change, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()

panel_data %>% 
  filter(minor_type == "MUNI") %>%
 filter(tfl_pct_change >= -20 & tfl_pct_change < 20) %>%
  filter(year != 2021) %>%
  ggplot() + 
  geom_line(aes(x=year, y = tfl_pct_change, group = agency_name, color = Triad, alpha = .5)) +
 # geom_text(data = endpoints, aes(x=year, y = capped_pct_change, label = agency_name), size = 2, hjust = .8, vjust=-1.5, check_overlap = TRUE)+
  theme_bw()+
    labs(title = "Non-Homerule Municipalities: Total Final Levy Pct Change")
```



```{r}
panel_data %>% filter(agency_name != "VILLAGE OF FORD HEIGHTS" & minor_type == "MUNI") %>%
  ggplot() + geom_point(aes(x=capped_pct_change, y= lim_rate))

panel_data %>% filter(lim_rate > 5)

panel_data %>% 
  filter(minor_type == "MUNI" ) %>%
  filter(capped_pct_change > 500 | !is.finite(capped_pct_change)
         ) %>%
  select(agency_name, capped_pct_change, everything())

```

```{r}
HR_munis <- panel_data %>% 
  filter(minor_type == "MUNI" & home_rule_ind == 0 & total_final_levy > 0)

```

# Hypothesis II

[**Hypothesis II: HR agencies have a non-zero elasticity in relation to the tax base.**]{.underline}

- *Alea\'s phrasing: HR taxing agencies do not defensively tax as much as possible every year. They are able to be flexible and elastic or whatever*

- H1a: Elasticity is greater than zero (based on theory of needing more revenue for more services and services are related to taxable base)
- H1b: Elasticity is different than nonHRagencies

Want: HR regression, DV = summed total final levy for grouped agencies

levy= B0\*EAV+B1\*(EAV\*AssessmentYear)

Dummy for reassessment year. Maybe do the lagged reassessment year too



# Grouped by grouped_label from CSV

Uses manually coded labels that combine both methods of grouping taxing agencies:

Non homerule taxing agencies are grouped if they are "Connected Agencies" (i.e. they share first 6 digits, and lim_rate). The lim_rate is kept as the first(lim_rate) and the total_final_rate should be the sum(total_final_rate) of the grouped agencies.

```{r}
library(dplyr)

library(openxlsx)

groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))
                                                                        

```

```{r}
library(dplyr)

table(recoded_data$reassess_year, recoded_data$minor_type)

grouped_manual <- recoded_data %>% 
  left_join(groupies2,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP"  | major_type == "MISCELLANEOUS" &
           minor_type != "MISC"
          # minor_type == "MUNI" | agency_name == "TOWN CICERO"
           ) %>%
 # filter(minor_type != "SSA") %>% 
  # filter(home_rule_ind == 1) %>%
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE)+1,
            total_ext = sum(total_ext, na.rm=TRUE),
            total_non_cap_ext = sum(total_non_cap_ext, na.rm=TRUE),
            total_final_rate = sum(total_final_rate, na.rm=TRUE),
            cty_total_eav = first(cty_total_eav), 
            av = sum(av, na.rm=TRUE),
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
           # home_rule_ind = first(home_rule_ind)
            ) %>% 
    left_join(muni_agency_names) %>% 
    #select(-c(Column1, `Most recent reassessed`)) %>% 
    mutate(
      log_eav = log(cty_total_eav),
      log_levy = log(total_final_levy),
     bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, agency_name, everything())

write_csv(grouped_manual, "grouped_attempt 12-14-2023.csv")

 grouped_manual %>% 
  ungroup() %>%
   group_by(year, home_rule_ind) %>%

  #filter(year == 2021) %>%
  summarize(count = n()) %>%
   pivot_wider(names_from = "home_rule_ind", values_from = "count") %>%
   rename(NonHR=`0`, HR = `1`)
```

39 nonHR and 65 HR if only majortype munis is included.

```{r}

# 1552 obs
grouped_manual_has16 <- grouped_manual %>%  
  ungroup() %>%
 # filter(year == 2021) %>%
  #arrange(home_rule_ind) %>%
  group_by(agency_name, home_rule_ind) %>%
  distinct() %>%
  mutate(count = n()) %>%
  filter(count == 16) %>% ungroup()


grouped_manual_has16 %>% ggplot() + 
  geom_line(aes(x=year,y=total_final_levy, group = agency_name, alpha = .5, color = home_rule_ind)) + 
  theme_classic()


grouped_manual_has16 %>% ggplot() + 
  geom_line(aes(x=year,y=total_final_levy, group = agency_name, alpha = .5, color = home_rule_ind)) + 
  facet_wrap(~home_rule_ind) +
  theme_classic() 

grouped_manual_has16 %>% ggplot() + 
  geom_point(aes(x=year, y=total_final_levy,# color = home_rule_ind, 
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = agency_name, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, # 
                  group = home_rule_ind,
                 # group = grouped_w_hr_ind, 
                  color = home_rule_ind), se=FALSE, size = 2) + 
  theme_classic()

grouped_manual_has16 %>% ggplot() + 
  geom_point(aes(x=year, y=total_final_levy,# color = home_rule_ind, 
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = agency_name, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, # 
                  group = home_rule_ind,
                 # group = grouped_w_hr_ind, 
                  color = home_rule_ind), se=FALSE, size = 2) + 
  facet_wrap(~home_rule_ind) +
  theme_classic()
```

```{r}

detach("package:dplyr", unload = TRUE)

grouped_munis <- pdata.frame(grouped_manual_has16, index = c("agency_name", "year")) 

table(grouped_munis$year)
grouped_munis <- make.pbalanced(grouped_munis)
is.pbalanced(grouped_munis)
table(grouped_munis$year)

grouped_munis$eav_lag1  <- plm::lag(grouped_munis$log_eav, 1)
grouped_munis$av_lag  <- plm::lag(grouped_munis$av, 1)

grouped_munis$eav_lag2  <- plm::lag(grouped_munis$log_eav, 2)

grouped_munis$cty_eav_lag  <- plm::lag(grouped_munis$cty_total_eav, 1)

# 
# grouped_munis$reassess_lag1 <- plm::lag(grouped_munis$reassess_year, 1)
# grouped_munis$reassess_lag2 <- plm::lag(grouped_munis$reassess_year, 2)
# 
# 
# grouped_munis$reassess_lead1 <- plm::lead(grouped_munis$reassess_year, 1)
# grouped_munis$reassess_lead2 <- plm::lead(grouped_munis$reassess_year, 2)
        
library(dplyr)
grouped_munis <- grouped_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag),
         av_change = av - av_lag,
         av_pct_change = (av-av_lag)/av_lag
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

# All Agencies-Agency & Year FE"
grouped_model<- plm(log(total_final_levy) ~ log(cty_total_eav), 
                   # index = c("grouped_w_hr_ind", "year"), 
                    model = "within", 
                    effect= "twoways",                    
                    data = grouped_munis)






grouped_cleannames_withHRind <- plm(log(total_final_levy) ~ log(cty_total_eav)+ log(cty_total_eav):home_rule_ind, 
                        #  index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind)

grouped_cleannames_withHRind_lagged <- plm(log(total_final_levy) ~ log(cty_total_eav)+ log(cty_total_eav):home_rule_ind + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2), 
                          #index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind_lagged)

grouped_cleannames_lag <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
                          #index = c("grouped_w_hr_ind", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)

grouped_cleannames_lag2 <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2)+log(cty_total_eav):home_rule_ind + lag(log(cty_total_eav),1):home_rule_ind  + lag(log(cty_total_eav),2):home_rule_ind ,
#                          index = c("uniqueid", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)
#summary(grouped_cleannames_lag2)


model_names <- c(grouped_model = "Grouped manually, Summed Levies", 
                 grouped_cleannames_lag = "with Lags",
                 grouped_cleannames_withHRind = "with HR Indicator",
                 grouped_cleannames_withHRind_lagged = "HR indacator with Lags",
                grouped_cleannames_lag2 = "HR interact with both Lags") # has Chicago


# plot(grouped_model)


export_summs(grouped_model, grouped_cleannames_lag,  grouped_cleannames_withHRind, grouped_cleannames_withHRind_lagged, grouped_cleannames_lag2, robust = "HC3",  model.names = model_names, statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))



```

## Seperating hr and nonhr

```{r}
 
library(dplyr)

homerule_minortype_munis <- recoded_data %>% filter(minor_type == "MUNI" | agency_name == "TOWN OF CICERO") %>%
 # grouped_manual %>% 
  filter(home_rule_ind == 1 & total_final_levy > 0)

homerule_minortype_munis <- pdata.frame(homerule_minortype_munis, index = c("agency_name", "year"))

homerule_minortype_munis <- make.pconsecutive(homerule_minortype_munis)

detach("package:dplyr", unload = TRUE)

homerule_minortype_munis$eav_lag1  <- plm::lag(homerule_minortype_munis$log_eav, 1)
homerule_minortype_munis$eav_lag2  <- plm::lag(homerule_minortype_munis$log_eav, 2)
homerule_minortype_munis$cty_eav_lag  <- plm::lag(homerule_minortype_munis$cty_total_eav, 1)
homerule_minortype_munis$av_lag  <- plm::lag(homerule_minortype_munis$av, 1)
#homerule_minortype_munis$av_lag  <- plm::lag(homerule_minortype_munis$av, 1)

        
library(dplyr)
homerule_minortype_munis <- homerule_minortype_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

hr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
                          #  index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = homerule_minortype_munis)


hr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

hr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(cty_total_eav)  + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

hr_muni_minor <- plm(log(total_final_levy)  ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2) + up_down*log(cty_total_eav),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

# summary(hr_muni_minor)
model_names = c("Homerule Government Taxing Agencies")

export_summs(hr_muni_minor_simple, #hr_muni_minor_simple0,  
             hr_muni_minor_lags,             hr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}
 
library(dplyr)

nonhr_munis <- grouped_manual %>% 
  filter(home_rule_ind == 0) %>% select(agency_name, year, everything())

nonhr_munis <- pdata.frame(nonhr_munis, index = c("agency_name", "year"))

nonhr_munis <- make.pconsecutive(nonhr_munis)

detach("package:dplyr", unload = TRUE)

nonhr_munis$eav_lag1  <- plm::lag(nonhr_munis$log_eav, 1)
nonhr_munis$eav_lag2  <- plm::lag(nonhr_munis$log_eav, 2)

nonhr_munis$cty_eav_lag <- plm::lag(nonhr_munis$cty_total_eav, 1)
        
library(dplyr)
nonhr_munis <- nonhr_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

nonhr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
                           # index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = nonhr_munis)


nonhr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
           #  index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

nonhr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(cty_total_eav)  + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

nonhr_muni_minor <- plm(log(total_final_levy)  ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2) + up_down*log(cty_total_eav),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

# summary(hr_muni_minor)
# summary(hr_muni_minor)
model_names = c("Non-HR Government Taxing Agencies")

export_summs(nonhr_muni_minor_simple, # nonhr_muni_minor_simple0, 
             nonhr_muni_minor_lags, 
                      nonhr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

# Percent change

```{r}
# nonhr_munis

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "twoways",                    
                    data = nonhr_munis) %>% summary()

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "individual",                    
                    data = nonhr_munis) %>% summary()

# nonhr_munis

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "twoways",                    
                    data = homerule_minortype_munis) %>% summary()

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "individual",                    
                    data = homerule_minortype_munis) %>% summary()
```

```{r levy-indexed, error=TRUE}
library(dplyr)
library(tidyverse)

indexed_munis <- grouped_nonhr_manual %>%
#  mutate(year = as.factor(year)) %>%
  ungroup() %>%
  filter(minor_type == "MUNI") %>%
 # filter(!agency_num %in% dropped_munis & !agency_num %in% exclude_hr_change ) %>% 
  mutate(year = as.character(year),
         agency_name = as.character(agency_name)) %>% 
  group_by(agency_name) %>% 
  summarize(     # Index values to 2006
    year=year,
    
    eav_idx = cty_total_eav / (cty_total_eav[year == "2006"] ),
    levy_idx = total_final_levy / (total_final_levy[year == "2006"]),
    av_idx = av / (av[year == 2006]),
    Triad = Triad,
    home_rule_ind = home_rule_ind
  )   

indexed_munis %>% 
  ggplot(aes(x=year, y = levy_idx, group = agency_name, label = agency_name, color = as.factor(home_rule_ind))) + 
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() + 
  theme_classic()+
 # geom_text(size = 2, vjust=-1.5)+
 # facet_wrap(~home_rule_ind)+
  labs(title = "Non-HR Municipalities:Total Final Levy Indexed to 2006")


indexed_munis %>% ggplot() + 
  geom_line(aes(x=year, y = levy_idx, group = agency_name, color = Triad), alpha=.5, linetype = "dashed") +
  geom_point(aes(x=year, y = levy_idx), alpha = .1) + 
  theme_classic()+
  facet_wrap(~Triad)+
    labs(title = "Non-HR Municipalities:Total Final Levy Indexed to 2006")



indexed_munis %>% ggplot() + geom_line(aes(x=year, y = av_idx, group = agency_name, color = as.factor(home_rule_ind)))  +
  facet_wrap(~Triad) + 
  theme(legend.position = "bottom") +
  labs(title = "Non-HR Municipalities: AV Indexed to 2006" )

indexed_munis %>% ggplot() + geom_line(aes(x=year, y = levy_idx, group = agency_name, color = Triad)) +  facet_wrap(~Triad) + 
  labs(title = "Non-HR Municipalities: Total Final Levy Indexed to 2006")

#minortype_munis %>% write_csv("minortype_munis.csv")
```

# Schools

```{r error=TRUE}
library(dplyr)

schools <- recoded_data %>%
  filter(major_type == "SCHOOL") %>%
  group_by(agency_name) %>%
  mutate(year_count = n()) %>%
  ungroup() %>% 
  filter(year_count >10)

schools <- pdata.frame(schools, index = c("agency_name", "year"))


is.pbalanced(schools)
schools <- plm::make.pbalanced(schools )

detach("package:dplyr", unload = TRUE)


# based on major_type == Schools. Groups all schools together. 

school_mod_major_simple <- plm(log(total_final_levy) ~ log(cty_total_eav),
                               index = c("agency_name", "year"),
                  model = "within",  effect= "twoways", data = schools)

school_mod_major <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
                        index = c("agency_name", "year"),
                  model = "within",  effect= "twoways", data = schools)


school_mod_secondary_simple <- plm(log(total_final_levy) ~ log(cty_total_eav),
                        subset = minor_type == "SECONDARY",
                        index = c("agency_name", "year"), model = "within",
                        effect= "twoways", data = schools)

school_mod_secondary <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
                        subset = minor_type == "SECONDARY",
                        index = c("agency_name", "year"), model = "within",
                        effect= "twoways", data = schools)

# doesn't exist every year
# school_mod_unified <- plm(log(total_final_levy) ~ log(cty_total_eav)+ lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
#                         subset = minor_type == "UNIFIED",
#                         index = c("agency_name", "year"),
#                         model = "within",
#                         effect= "twoways", data = schools)

school_mod_elementary <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
                             subset = minor_type == "ELEMENTARY",
                             index = c("agency_name", "year"),
                             model = "within",
                             effect= "twoways", data = schools)

school_mod_elementary_simple <- plm(log(total_final_levy) ~ log(cty_total_eav),
                             subset = minor_type == "ELEMENTARY",
                             index = c("agency_name", "year"), model = "within",
                             effect= "twoways", data = schools)

# doesn't exist every year
# school_mod_comcol <- plm(log(total_final_levy) ~ log(cty_total_eav)  + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
#                          index = c("agency_name", "year"),
#                          subset = minor_type == "COMM COLL", model = "within",
#                          effect= "twoways", data = schools)

# ## table with more school types
# model_names = c("All Schools", "All Schools", "Secondary", "Elementary", "Elementary",
#                 "Com. Colleges", "Unified" )
# export_summs(school_mod_major_simple, school_mod_major,
#              school_mod_secondary,
#              school_mod_elementary_simple, school_mod_elementary,
#              #school_mod_comcol, school_mod_unified,
#              model.names = model_names, robust=TRUE, statistics = c(N = "nobs", adjR2 = "adj.r.squared"))

model_names = c("All Schools", "All Schools", "Secondary", "Secondary", "Elementary", "Elementary")

export_summs(school_mod_major_simple, school_mod_major,
             school_mod_secondary_simple,
             school_mod_secondary,
             school_mod_elementary_simple, school_mod_elementary,

             model.names = model_names, robust=TRUE, statistics = c(N = "nobs", adjR2 = "adj.r.squared"))
```
