---
title: "Descriptive Stats for Levy Project Data"
format: 
  html:
    df-print: paged
    code-fold: true
    tbl-cap-location: margin
    toc: true
    toc-location: left
---


```{r setup, warning=FALSE, message=FALSE, output = FALSE}
library(modelsummary)
library(tidyverse)
library(janitor)
library(dplyr)
```


```{r}
#| label: tryFMVdata

df <- read_csv("panel_data.csv")   ## 10,374

df <- df |> filter(!minor_type %in% c("BOND", "UNIFIED", "COMM COLL", "COOK", "MISC", "MOSQUITO") ) # 9,864 obs



df <- df |> filter(year > 2009)  |>   ## 7539 obs

  mutate(tfl_pct_change = if_else(is.na(tfl_pct_change) |
                                    is.infinite(tfl_pct_change),
                                  0, tfl_pct_change) )


df <- df |> 
  select(-c(muni_name, muni_num, agency_w_hr, first6_w_hr, log_eav:reassess_lag2, 
            lag_eav_pct_change1:lag_av_pct_change2)) %>%
  mutate_at(c("home_rule_ind"), as.character)
```


```{r}
#| label: tbl-agencies-eachyear
#| tbl-cap: Count of each agency type that  existed during each tax year. 

df %>% ungroup () |> 
  group_by(year, minor_type) %>% 
  filter((major_type == "MUNICIPALITY/TOWNSHIP" & minor_type != "MISC") | major_type == "SCHOOL" | major_type == "MISCELLANEOUS") %>% 
  summarize(count = n()) %>%
  pivot_wider(names_from = year, values_from = count) %>% 
  flextable::flextable()
```


```{r}
#| label: tbl-majortypeagencies-in2022-notpaneldata
#| tbl-cap: "2022 snapshot of agencies that existed. Not from balanced panel data. Agencies such as park, library, are within the MUNI/TOWNSHIP major_type."


datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, data = df %>% filter(year==2022), output = "flextable")
```


```{r}
#| label: tbl-minortypeagencies-in2022-notpaneldata
#| tbl-cap: "2022 snapshot of agencies that existed. Not from balanced panel data. Agencies such as park, library, etc will be combined with their larger municipality taxing agency."

datasummary_crosstab(minor_type~home_rule_ind, data = df %>%filter(year==2022),  statistic = 1~1+N, output = "flextable")

```


# Descriptive Stats

```{r eval=FALSE}
datasummary_skim(df)
datasummary_skim(df, type  = "categorical")
```

```{r}
after2009 <- df %>% filter(year > 2009) 
df <- after2009

groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
         # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))

grouped_manual <- df %>% 
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
         # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         lim_rate = ifelse(is.na(lim_rate), "NA", lim_rate)) |>
  left_join(groupies2,
            by = c("agency_name", "agency_num")
  ) %>% 
  filter((major_type == "MUNICIPALITY/TOWNSHIP"  
         & minor_type != "MISC") |  major_type == "MISCELLANEOUS"
  ) %>% 
  group_by(year, grouped_label, home_rule_ind) %>% 
  summarize(agency_name = first(agency_name),
            types = paste(list(unique(minor_type)), sep = ", "),

            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
            cty_cook_eav = first(cty_cook_eav),
            cty_total_eav = first(cty_total_eav), 
            av = first(av), ## mistake fixed: was sum, now is first()
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            rate = sum(total_final_rate, na.rm=TRUE),
            connected_count = n(),
            lim_rate = mean(as.numeric(lim_rate), na.rm=TRUE),
            clean_name = first(clean_name)
  ) %>%
  mutate(
    conn_agency = ifelse(connected_count > 1, 1, 0),
    log_eav = log(cty_total_eav),
    log_levy = log(total_final_levy),
    log_av =  log(av),
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
    panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, panel_id, everything()) %>% ungroup() 


schools <- df %>% 
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
         home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         lim_rate = ifelse(is.na(lim_rate), "NA", lim_rate)) |>
  
  filter(major_type == "SCHOOL") %>%
  mutate(grouped_label = agency_name) %>%
  group_by(year, grouped_label, home_rule_ind) %>% 
  summarize(agency_name = first(agency_name),
            types = paste(list(unique(minor_type)), sep = ", "),

            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
            cty_total_eav = first(cty_total_eav), 
            cty_cook_eav = first(cty_cook_eav),
            av = first(av), 
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            rate = sum(total_final_rate, na.rm=TRUE), 
            connected_count = n(),
            lim_rate = sum(as.numeric(lim_rate), na.rm=TRUE),
            clean_name = first(clean_name)
            
  ) %>%
  mutate(
    conn_agency = ifelse(connected_count > 1, 1, 0),      
    log_eav = log(cty_total_eav),
    log_levy = log(total_final_levy),
    log_av =  log(av),
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
    panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = "School") %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, panel_id, everything()) %>% ungroup() 


# 94 non-HR and 76 HR in 2021, 93 non-HR and 77 HR in 2022

grouped_manual %>%  
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
 
schools %>%  
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())


```

```{r}
grouped_manual <- rbind(grouped_manual, schools) %>% 
  arrange(uniqueid, year)

table(grouped_manual$town)


pop2 <- readxl::read_xlsx("Necessary_Files/populationcounts_cookcountyil.xlsx")

pop2 <- pop2 %>% 
  mutate(Name = case_when(
    Name == "Forest View" ~ "Forestview",
    Name == "East Hazel Crest" ~ "East Hazelcrest",
    Name == "Hazel Crest" ~ "Hazelcrest",
    Name == "McCook" ~ "Mc Cook",
    Name == "Mount Prospect" ~ "Mt Prospect",
    Name == "Northlake" ~ "North Lake",
    TRUE~as.character(Name)
  )
  )
grouped_manual <- grouped_manual %>% 
  filter(year > 2009) %>%
  left_join(pop2, by = c("clean_name" = "Name")) 

grouped_manual <- grouped_manual %>% 
  mutate(ext_percap = case_when(
    year < 2015 ~ round(total_final_levy/pop2010),
    year >= 2015 ~ round(total_final_levy/pop2020)),
    
    taxbase_percap = case_when(
      year < 2015 ~ round(cty_cook_eav/pop2010),
      year >= 2015 ~ round(cty_cook_eav/pop2020)),
    
    tax_rate = round(total_final_levy / cty_cook_eav, digits=4) # tax rate that would come from agency_dt instead of manually calculated from PIN level.
  )

library(plm)

df_panel <- grouped_manual %>% 
  ungroup() %>% 
  arrange(uniqueid, year) %>%
  pdata.frame(index = c("uniqueid", "year"))

df_panel %>% 
  group_by(uniqueid, year) %>% 
  summarize(count = n()) %>%  
  filter(count > 1)
```

```{r}
#| label: tbl-agencies-eachyear_paneldata
#| tbl-cap: Count of each agency type that  existed during each tax year. 

df_panel %>% ungroup() %>% group_by(year,town) %>% summarize(count = n()) %>%
  pivot_wider(names_from = year, values_from = count) %>% flextable::flextable()
```

## Table 1: Name and Number of Taxing Agencies



```{r}
#| label: tbl-majortypeagencies-in2022-paneldata
#| tbl-cap: "2022 snapshot of agencies that existed. From panel data. Agencies such as park, library, are within the MUNI/TOWNSHIP major_type."


datasummary_crosstab(town ~home_rule_ind, statistic = 1~1+N, 
                     data = df_panel %>% filter(year==2022), output = "flextable")
```


## Table 2: Levy and Levy Growth

### Per Capita

```{r}
#| label: tbl-levyperperson
#| tbl-cap: "Growth in the levy per person from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022. Only Municipalities have population counts, so only they are included in the per capita tables."

# agency level growth:
levy_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           !is.na(ext_percap)         ) %>% 
  select(year, clean_name, ext_percap) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
               values_from = "ext_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  arrange(desc(pct_growth))  

levy_table %>% DT::datatable(
  rownames = FALSE,
  options = list(
    dom = 't',
    scrollX = TRUE, # Enable horizontal scrolling
    columnDefs = list(
      list(targets = 1:2
      ),
      list(targets = 1:2, width = '50px')
    )
  ))
```

```{r}
levy_table %>% 
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  geom_vline(aes(xintercept = mean(pct_growth, na.rm=TRUE), color = "Mean"))+ 
  geom_vline(aes(xintercept = median(pct_growth, na.rm=TRUE), color = "Median")) + 
  theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", 
       title = "Distribution of Growth Rates", subtitle = "Levy per Capita from 2010 to 2022", 
       caption = "Median value/capita in 2022 = $645. 
       Mean value/capita = $1139.")
```


```{r}
#| label: tbl-levyperpersonmedian
#| tbl-cap: "Median levy per person from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022."


levy_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Levy per Capita` = median(`2010`, na.rm=TRUE),
    `2010 Mean Levy per Capita` = mean(`2010`, na.rm=TRUE),

    `2010 Levy StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Levy per Capita` = median(`2022`, na.rm=TRUE),
    `2022 Mean Levy per Capita` = mean(`2022`, na.rm=TRUE),

    `2022 Levy StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Growth of Levy per Capita` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Levy per Capita` = round(mean(pct_growth, na.rm=TRUE), digits = 2),

    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE)),
    `# of Agencies` = n()
  ) |>
  mutate(across(where(is.numeric), round, digits = 1)) %>%
  
  pivot_longer(cols = c(`2010 Median Levy per Capita`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE)

```


### Total Levy



```{r}
#| label: tbl-extgrowth
#| tbl-cap: "**Growth in total levy** from 2010 to 2022. Uses summed `total_final_levy` for grouped munis and townships."

df_panel %>% 
  filter(year == 2010 | year == 2022 ) %>% 
  filter(!is.na(total_final_levy)) %>%
  select(year, uniqueid, total_final_levy) %>% 
  pivot_wider( id_cols = "uniqueid", names_from = "year", 
               values_from = "total_final_levy") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  arrange(desc(pct_growth)) %>% 
  DT::datatable(rownames = FALSE)
```


```{r}
df_panel %>% 
  filter((year == 2010 | year == 2022) ) %>% 
  select(year, uniqueid, total_final_levy) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "total_final_levy") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", 
       title = "Distribution of Growth Rates",
       subtitle = "Summed Levy per Grouped Agency, 2010 to 2022")

```


```{r}
#| label: tbl-levygrowth_summed_median
#| tbl-cap: "Median levy from 2010 to 2022."



df_panel %>% 
  filter((year == 2010 | year == 2022) ) %>% 
  select(year, uniqueid, total_final_levy) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "total_final_levy") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  ungroup() %>%
  summarize(
    `2010 Median Levy` = median(`2010`, na.rm=TRUE),
    `2010 Mean Levy` = mean(`2010`, na.rm=TRUE),
    `2010 Levy StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Levy` = median(`2022`, na.rm=TRUE),   
    `2022 Mean Levy` = mean(`2022`, na.rm=TRUE),
    `2022 Levy StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Growth of Levy` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Levy` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE)),
    `# of Agencies` = n()
  ) |>
  mutate(across(where(is.numeric), round, digits = 1)) %>%
  
  pivot_longer(cols = c(`2010 Median Levy`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE)

```



## Table 3: Tax Base and Tax Base Growth

### Per Capita
```{r}
#| label: tbl-table3
#| tbl-cap-location: top
#| tbl-cap: "Tax Base Summary Statistics (per capita), 2010 and 2022. Median change  calculated from agency level change and then locating the median value of growth. For muni taxing agencies that share taxing jurisdiction (have the same tax base EAV) with municipality taxing agencies, then the "

# agency level growth:
taxbase_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           !is.na(taxbase_percap )
         ) %>% 
  select(year, clean_name, taxbase_percap) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
               values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  arrange(desc(pct_growth)) 

taxbase_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Tax Base per Capita` = median(`2010`, na.rm=TRUE),
    `2010 Mean Tax Base per Capita` = mean(`2010`, na.rm=TRUE),
    `2010 Tax Base StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Tax Base per Capita` = median(`2022`, na.rm=TRUE),
    `2022 Median Tax Base per Capita` = mean(`2022`, na.rm=TRUE),
    `2022 Tax Base StdDv` = round(sd(`2022`, na.rm=TRUE)),
    `Median Growth of Tax Base per Capita` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Tax Base per Capita` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
    
  ) |>
  mutate(across(where(is.numeric), round)) %>%
  
  pivot_longer(cols = c(`2010 Median Tax Base per Capita`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE)

```

```{r}
taxbase_table %>% 
  ggplot() + geom_histogram(aes(x=pct_growth)) + theme_classic() + labs(x = "Growth %", y = "Agency Count", title = "Tax Base per Capita (in EAV) Growth, 2010 to 2022")
```

```{r} 
#| label: tbl-taxbasegrowth-percap
#| tbl-cap: "Growth in the **tax base per capita** from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022."

df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  filter(!is.na(clean_name)) %>%
  select(year, clean_name, taxbase_percap) %>% 
  pivot_wider(id_cols = "clean_name", names_from = "year", 
              values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```



### Tax Base (in EAV) Growth

```{r}
#| label: tbl-taxbasegrowth
#| tbl-cap: "**Growth in the tax base** from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2020."

df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  select(year, uniqueid, cty_cook_eav) %>% 
  pivot_wider(id_cols = "uniqueid", names_from = "year", 
              values_from = "cty_cook_eav") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  mutate(across(where(is.numeric), round, digits = 2)) %>%

  arrange(desc(pct_growth)) %>% 
  DT::datatable(rownames = FALSE)
```


```{r}
df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  filter(town == "Muni" ) %>% 
  select(year, uniqueid, cty_cook_eav) %>% 
  pivot_wider(id_cols = "uniqueid", names_from = "year", 
              values_from = "cty_cook_eav") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  ungroup() %>%
  summarize(
    `2010 Median Tax Base` = median(`2010`, na.rm=TRUE),
    `2010 Mean` = mean(`2010`, na.rm=TRUE),
    `2010 Tax Base StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Tax Base` = median(`2022`, na.rm=TRUE),
    `2022 Mean` = mean(`2022`, na.rm=TRUE),
    `2022 Tax Base StdDv` = round(sd(`2022`, na.rm=TRUE)),
    `Median Growth of Tax Base` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Tax Base` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
  ) |>
  mutate(across(where(is.numeric), round)) %>%
  
  pivot_longer(cols = c(`2010 Median Tax Base`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE) %>%
                DT::formatRound('value', mark = ",", digits = 0) 

```

```{r}
taxbase_table %>% 
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", 
       title = "Growth in Tax Base (in EAV), 2010 to 2022")
```


## Table 4: Tax Rate and Tax Rate Growth

```{r}
#| label: tbl-taxrate-table
#| tbl-cap: "Tax Rate Growth for Grouped Taxing Agencies, 2010 to 2022"


# agency level growth:
rate_table <- df_panel %>% 
  filter((year == 2010 | year == 2022)) %>% 
  filter(!is.na(clean_name)) %>%
  select(year, uniqueid, rate) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  mutate(across(where(is.numeric))) %>%
  arrange(desc(pct_growth)) 

rate_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Rate` = median(`2010`, na.rm=TRUE),
    `2010 Mean Rate` = mean(`2010`, na.rm=TRUE),
    `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
    `2022 Median Rate` = median(`2022`, na.rm=TRUE),
    `2022 Mean Rate` = mean(`2022`, na.rm=TRUE),
    `2022 Rate StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Rate Growth` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
    
  ) |>
  mutate(across(where(is.numeric), round, digits = 2)) %>%
  pivot_longer(cols = c(`2010 Median Rate`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  flextable::flextable(cwidth = 1.5)
```

```{r}
df_panel %>% 
  filter((year == 2010 | year == 2022)) %>% 
  filter(!is.na(clean_name)) %>%
  select(year, uniqueid, rate) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ))%>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  labs(y = "# of Agencies", x = '% Growth',
       title = "Distribution of Tax Rate Growth",
       subtitle = "Municipality Taxing Agencies, 2010 to 2022")+
  theme_classic()

```


```{r}
#| label: tbl-taxrate-table-grouped
#| tbl-cap: "Tax Rate Growth for Grouped Taxing Agencies, 2010 to 2022"


# agency level growth:
rate_table <- df_panel %>% 
  filter((year == 2010 | year == 2022)) %>% 
  select(year, uniqueid, rate) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  mutate(across(where(is.numeric))) %>%
  arrange(desc(pct_growth)) 

rate_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Rate` = median(`2010`, na.rm=TRUE),
    `2010 Mean Rate` = mean(`2010`, na.rm=TRUE),
    `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
    `2022 Median Rate` = median(`2022`, na.rm=TRUE),
    `2022 Mean Rate` = mean(`2022`, na.rm=TRUE),
    `2022 Rate StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
    
  ) |>
  pivot_longer(cols = c(`2010 Median Rate`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  flextable::flextable(cwidth = 1.5)
```

```{r}
rate_table %>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  labs(y = "# of Agencies", x = '% Growth',
       title = "Distribution of Tax Rate Growth",
       subtitle = "Grouped Taxing Agencies, 2010 to 2022")+
  theme_classic()

```


```{r}
#| label: tbl-agencylevy-taxrates-notgrouped
#| tbl-cap: "Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav. Not grouped!"

df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  select(year, agency_name, rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "rate") %>%   
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 2) ),
         `2022` = (round(`2022`, digits = 2) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

### Not Grouped

```{r}

rate_table <- df |>
  filter(!is.na(total_final_rate)) |>
  filter(year %in% c("2010", "2022")) |>
  select(year, minor_type, agency_name, total_final_rate) %>% 
  pivot_wider( id_cols = c("minor_type", "agency_name"), names_from = "year", 
              values_from = "total_final_rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  arrange(desc(pct_growth))  

rate_table  |> DT::datatable(rownames = FALSE)


rate_table |>
    ungroup() %>%
    group_by(minor_type) |>

   summarize(
            `2010 Median Rate` = round(median(`2010`, na.rm=TRUE), digits = 2),
            `2010 Mean Rate` = round(mean(`2010`, na.rm=TRUE), digits = 2),
            `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
            `2022 Median Rate` = round(median(`2022`, na.rm=TRUE), digits = 2),
            `2022 Mean Rate` = round(mean(`2022`, na.rm=TRUE), digits = 2),
            `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits =2),
            `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
            `Mean Rate Growth` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
            `StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
           `# of Agencies` = n()) |> 
  flextable::flextable()
```

```{r}
rate_table %>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  labs(y = "# of Agencies", x = '% Growth',
       title = "Distribution of Tax Rate Growth",
       subtitle = "All Taxing Agencies, 2010 to 2022")+
  theme_classic()
```

# Models

## TWFE Models 

```{r}
library(fixest)

twfe = feols(log(total_final_levy) ~ log(cty_cook_eav)  | uniqueid + year, vcov = "twoway",  data = df_panel)


twfe_lags = feols(log(total_final_levy)~ log(cty_cook_eav) + l(log(cty_cook_eav), 1) + l(log(cty_cook_eav), 2 ) | uniqueid + year, vcov = "twoway", panel.id = c("uniqueid", "year"), data = df_panel) 

etable(twfe, twfe_lags, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```


```{r}

twfe <- feols(log(total_final_levy) ~ log(cty_cook_eav) | uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year"))
  
dummies <- feols(log(total_final_levy) ~ log(cty_cook_eav) + uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year"))


side_by_side <- function(models, estimates, ...) {
    models <- rep(models, each = length(estimates))
    estimates <- rep(estimates, times = 2)
    names(models) <- names(estimates)
    modelsummary(models = models, estimate = estimates,
                 statistic = NULL, gof_omit = ".*", ...)
}

models <- list(
  twfe <- feols(log(total_final_levy) ~ log(cty_cook_eav) | uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year")),
  dummies <- feols(log(total_final_levy) ~ log(cty_cook_eav) + uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year"))) 

estimates <- c("Coef." = "estimate", "Std.Error" = "std.error")
side_by_side(models, estimates = estimates,
             coef_omit = 'uniqueid| year',
            output = "kableExtra")
```

```{r}

est1 = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year"))

est1_twowayse = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid + year , data = df_panel, panel.id = c("uniqueid", "year"), vcov = "twoway")

est2 = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid[av] + year , data = df_panel, panel.id = c("uniqueid", "year"), vcov = "twoway")

etable(est1, est1_twowayse, est2, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```

**Uses Reassess Year** Only works for Munis, maybe Towns. Schools do not have the reassess year variable.

```{r}
est1 = feols(log(total_final_levy) ~ log(av) + l(log(av), 1:2) + l(log(av))  + reassess_year + l(reassess_year, 1:2) + log(av)*l(reassess_year, 1:2) | uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year"), vcov = "twoway")

est2 = feols(log(total_final_levy) ~ log(av)  + l(log(av))* reassess_year | uniqueid + year, data = (df_panel %>% filter(town=="Muni")), panel.id = c("uniqueid", "year"),vcov = "twoway")

etable(est1, est2, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```


**Subset by Muni, Town, and Schools**

```{r}
muni = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav)) + l(log(cty_cook_eav), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni"), vcov = "twoway")

muni2 = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav)) + l(log(cty_cook_eav), 2) | uniqueid + year + home_rule_ind, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni"), vcov = "twoway")


town = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav),-1:2) + l(log(cty_cook_eav), 2)   | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Town"), vcov = "twoway")

school = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav)) + l(log(cty_cook_eav), 2)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="School"), vcov = "twoway")

 etable(muni, muni2, town, school, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```


> Schools are still always different than Towns or Municipalities




## Individual FE Models 

```{r}
library(fixest)

onefe = feols(log(total_final_levy) ~ log(cty_cook_eav)  | uniqueid,  data = df_panel)

onefe_lags = feols(log(total_final_levy)~ log(cty_cook_eav) + l(log(cty_cook_eav), 1) + l(log(cty_cook_eav), 2 ) + year | uniqueid,  panel.id = c("uniqueid", "year"), data = df_panel) 

etable(onefe, onefe_lags, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```


```{r}

est1 = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid, data = df_panel, panel.id = c("uniqueid", "year"))

est2 = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid[av], data = df_panel, panel.id = c("uniqueid", "year"))

etable(est1, est2, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```

**Uses Reassess Year** Only works for Munis, maybe Towns. Schools do not have the reassess year variable.

```{r}
est1 = feols(log(total_final_levy) ~ log(av) + l(log(av), 1:2) + l(log(av))  + reassess_year + l(reassess_year, 1:2) + log(av)*l(reassess_year, 1:2) | uniqueid, data = df_panel, panel.id = c("uniqueid", "year"))

est2 = feols(log(total_final_levy) ~ log(av)  + l(log(av))* reassess_year | uniqueid, data = (df_panel %>% filter(town=="Muni")), panel.id = c("uniqueid", "year"))

etable(est1, est2, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```


**Subset by Muni, Town, and Schools**

```{r}
muni = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav)) + l(log(cty_cook_eav), 2) | uniqueid, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni"))

muni2 = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav)) + l(log(cty_cook_eav), 2) | uniqueid + home_rule_ind, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni"))


town = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav),-1:2) + l(log(cty_cook_eav), 2)   | uniqueid, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Town"))

school = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav)) + l(log(cty_cook_eav), 2)  | uniqueid, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="School"))

 etable(muni, muni2, town, school, fitstat = c('n', 'f' , 'rmse', 'r2', 'ar2', 'war2'))
```


> Schools are still always different than Towns or Municipalities


