---
title: "Descriptive Stats for Levy Project Data"
format: 
  html:
    df-print: paged
    code-fold: true
    tbl-cap-location: margin
    toc: true
    toc-location: left
---


```{r setup, warning=FALSE, message=FALSE, output = FALSE}
library(modelsummary)
library(tidyverse)
library(janitor)
library(knitr)
library(DT)
```

> I do not trust the calculations for muni_pct_eav_taxed.  Check loop file for how it was calculated. Might just be incorrect denominator?  Other calculations seem fine. 


```{r}
#| label: tryFMVdata

df <- read_csv("panel_data.csv")   ## 10,374
df <- df |> 
  mutate(tfl_pct_change = if_else(is.na(tfl_pct_change) | 
                                    is.infinite(tfl_pct_change), 
                                  0, tfl_pct_change) )

df <- df |> 
  select(-c(muni_name, muni_num, agency_w_hr, first6_w_hr, log_eav:reassess_lag2, 
            lag_eav_pct_change1:lag_av_pct_change2)) %>%
  mutate_at(c("home_rule_ind"), as.character)

```

# Descriptive Stats

```{r}
datasummary_skim(df)
datasummary_skim(df, type  = "categorical")
```

```{r}
datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, 
                     data = df%>% filter(year==2022), 
                     title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = df%>%filter(year==2022),  
                     statistic = 1~1+N, 
                     title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r}
muni_fmv <- read_csv("Necessary_Files/ptaxsim_muni_level_2006-2022.csv")

muni_fmv <- muni_fmv |> select(-muni_pct_eav_taxed)

#muni_fmv_2006 <- muni_fmv |> filter(year == 2006)

muni_fmv_2022 <- muni_fmv |> 
  filter(year == 2022)  


datasummary_skim(muni_fmv_2022)

muni_fmv %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
muni_fmv %>% filter(year==2006)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
```


```{r}
library(plm)
df <- left_join(df, muni_fmv) 


# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
df_panel <- df %>% 
  filter( minor_type == "MUNI" | agency_name == "TOWN CICERO" | minor_type == "ELEMENTARY" | minor_type=="SECONDARY") %>% 
  pdata.frame(index = c("clean_name", "year") ) %>% 
  make.pbalanced(balance.type = "shared.individuals")


# Balance the panel -> now 9945 obs 

is.pbalanced(df_panel)

pdim(df_panel)

```
```{r}
datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, data = df_panel%>% filter(year==2022), title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel%>%filter(year==2022),  statistic = 1~1+N, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r}
df_panel %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

df_panel %>% filter(year==2006)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

#df_panel %>% 
 # filter(year==2006)%>% 
  #select(muni_fmv, muni_fmv_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary(~minor_type, data = df_panel %>% filter(year==2022), fmt = fmt_sprintf("%.0f"))
```

### Test if Fixed Effects should be used

"pooling" is equivalent to classic linear model  
"within" is like classic linear model with n-1 group dummies. (Dummies for each group and one is the comparison group.)  

```{r eval=FALSE}

# imagine that it makes "one line"for all observations instead of a line for each individual over time
g <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)
plmtest(g, effect = "twoways", type = "ghm")

gw <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)

gp <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)


summary(gp)
summary(gw)

plmtest(g)
plmtest(gw)

plmtest(naive_mod_munis, effect = "twoways", type = "ghm")
pFtest(gw, gp)
```


## Table 1: Name and Number of Taxing Agencies

```{r}
#| label: tbl-majortype-byhomerule
#| tbl-cap: "Major type taxing agencies by home rule indicator"

datasummary_crosstab(major_type~home_rule_ind, data = df_panel, 
                     # title = "Taxing Agency Types by Home Rule Indicator", 
                     output = "flextable")
```


```{r}
#| label: tbl-minortype-byhomerule
#| tbl-cap: "Minor type taxing agencies by home rule indicator"

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel, 
                    # title = "Taxing Agency Types by Home Rule Indicator", 
                     output = "flextable")
```


## Table 2: Levy and Levy Growth


```{r data_load_tbl_2}
# pop <- readxl::read_xlsx("Necessary_Files/community_cohort_inputs.xlsx") %>% 
#   select(MUNI, POP) %>% filter(!is.na(MUNI))

pop2 <- readxl::read_xlsx("Necessary_Files/populationcounts_cookcountyil.xlsx")

library(dplyr)

# pop <- pop %>% 
#   mutate(MUNI = case_when(
#     MUNI == "Forest View" ~ "Forestview",
#     MUNI == "East Hazel Crest" ~ "East Hazelcrest",
#     MUNI == "Hazel Crest" ~ "Hazelcrest",
#     MUNI == "McCook" ~ "Mc Cook",
#     MUNI == "Mount Prospect" ~ "Mt Prospect",
#     MUNI == "Northlake" ~ "North Lake",
#     TRUE~as.character(MUNI)
#   )
#   )

pop2 <- pop2 %>% 
  mutate(Name = case_when(
    Name == "Forest View" ~ "Forestview",
    Name == "East Hazel Crest" ~ "East Hazelcrest",
    Name == "Hazel Crest" ~ "Hazelcrest",
    Name == "McCook" ~ "Mc Cook",
    Name == "Mount Prospect" ~ "Mt Prospect",
    Name == "Northlake" ~ "North Lake",
    TRUE~as.character(Name)
  )
  )

df <- df %>% filter(!is.na(clean_name) ) %>% 
  left_join(pop2, by = c("clean_name" = "Name"))
                
df %>% filter(!is.na(clean_name) & is.na(pop2010) ) %>% 
  select(clean_name, pop2010, everything())

df <- df %>% 
  mutate(ext_percap = case_when(
    year < 2015 ~ round(muni_levy/pop2010),
    year >= 2015 ~ round(muni_levy/pop2020)),
    
    taxbase_percap = case_when(
      year < 2015 ~ round(cty_cook_eav/pop2010),
      year >= 2015 ~ round(cty_cook_eav/pop2020)),
    
    tax_rate = round(muni_levy / cty_cook_eav, digits=4))

```

```{r table_2}

df |>
  filter(year %in% c("2010", "2022")) |>
  group_by(year) |>
  summarize(med_per_cap_levy = median(ext_percap),
            sd_levy_per_cap = sd(ext_percap),
            med_levy_per_cap_growth = median((muni_levy/pop2020)/(muni_levy/pop2010)),
            sd_muni_per_cap_levy_growth = sd((muni_levy/pop2020)/(muni_levy/pop2010))
  ) |>
  pivot_longer(-year, names_to = "statistic", values_to = "value") |>
  pivot_wider(names_from = year, values_from = value) |>
  datatable(caption = "Summary Statistics (per capita), 2010 and 2022",
            rownames = FALSE,
            options = list(
              dom = 't',
              scrollX = TRUE, # Enable horizontal scrolling
              columnDefs = list(
                list(targets = 1:2, render = JS("function(data, type, row, meta) {
                  return type === 'display' ? data.toFixed(2) : data;
              }")),
                list(targets = 1:2, width = '50px')
              )
            ))

```


```{r}
#| label: tbl-extperperson
#| tbl-cap: "Growth in the average levy per person from 2006 to 2022. Uses 2010 population counts for 2006 and 2020 population counts for 2020."

df %>% 
  filter(year == 2006 | year == 2022 & 
           (minor_type == "MUNI" | agency_name == "TOWN CICERO") & 
           major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, ext_percap, ext_percap) %>% 
  pivot_wider( id_cols = "agency_name", names_from = "year", 
              values_from = "ext_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2006`)/`2006` * 100, digits = 1) ) ) %>%
  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 3: Tax Base and Tax Base Growth

```{r} 
#| label: tbl-taxbasegrowth
#| tbl-cap: "Growth in the tax base per capita from 2006 to 2022. Uses 2010 population counts for 2006 and 2020 population counts for 2020."

df %>% 
  filter(year == 2006 | year == 2022 & 
           (minor_type == "MUNI" | agency_name == "TOWN CICERO") & 
           major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, taxbase_percap) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", 
              values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2006`)/`2006` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 4: Tax Rate and Tax Rate Growth

```{r}
#| label: tbl-compositelevy-taxrates
#| tbl-cap: "Tax rates calculated from composite municipality levy / municipality's tax base"

df %>% 
  filter(year == 2006 | year == 2022 & 
           (minor_type == "MUNI" | agency_name == "TOWN CICERO") & 
           major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, tax_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", 
              values_from = "tax_rate") %>% 
  mutate(pct_growth = (round((`2022`-`2006`)/`2006` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

```{r}
#| label: tbl-agencylevy-taxrates
#| tbl-cap: "Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav."

df %>% 
  filter(year == 2006 | year == 2022) %>% 
  select(year, agency_name, total_final_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "total_final_rate") %>%   
  mutate(pct_growth = (round((`2022`-`2006`)/`2006` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

```{r}
#| label: tbl-descriptivestats-nochicago
#| tbl-cap: "Descriptive Stats for Taxing Agencies Outside of Chicago"

df %>% filter(year==2006) %>% 
  filter(clean_name!="Chicago") %>%
  select(ext_percap, taxbase_percap, muni_fmv_taxed, muni_eav_taxed, muni_levy, total_final_levy, total_final_rate, cty_cook_eav, muni_current_rate_avg, muni_PC_total, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary_skim(fmt = fmt_sprintf("%.0f"))


df %>% filter(year==2022) %>% 
  filter(clean_name!="Chicago") %>%
  select(ext_percap, taxbase_percap, muni_fmv_taxed, muni_eav_taxed, muni_levy, total_final_levy, total_final_rate, cty_cook_eav, muni_current_rate_avg, muni_PC_total, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary_skim(fmt = fmt_sprintf("%.0f"))
```


