---
title: "Descriptive Stats for Levy Project Data"
format: 
  html:
    df-print: paged
    code-fold: true
    tbl-cap-location: margin
    toc: true
    toc-location: left
---


```{r setup, warning=FALSE, message=FALSE, output = FALSE}
library(modelsummary)
library(tidyverse)
library(janitor)
library(dplyr)
```

> I do not trust the calculations for muni_pct_eav_taxed.  Check loop file for how it was calculated. Might just be incorrect denominator?  Other calculations seem fine. 


```{r}
#| label: tryFMVdata

df <- read_csv("panel_data.csv")   ## 10,374
df <- df |> filter(year > 2009)    ## 7923 obs
  # 
  # mutate(tfl_pct_change = if_else(is.na(tfl_pct_change) | 
  #                                   is.infinite(tfl_pct_change), 
  #                                 0, tfl_pct_change) )

df <- df |> 
  select(-c(muni_name, muni_num, agency_w_hr, first6_w_hr, log_eav:reassess_lag2, 
            lag_eav_pct_change1:lag_av_pct_change2)) %>%
  mutate_at(c("home_rule_ind"), as.character)

gm_nochi <- read.csv("gm_nochi_for_pivots.csv")
library(plm)
nochi_pd <- pdata.frame(gm_nochi, 
                        index = c("uniqueid", "year"))


```

```{r}
raw_data_joined <- read_csv("agency_raw_joined.csv")    # 17,2294 obs

## Fill in missing data for taxable EAV variables
## uses logic that EAV = levy / tax rate = EAV
raw_data_joined <- raw_data_joined %>%
  
  # drops 5332 taxing agencies (agency-year combos)
  filter(minor_type != "SSA") %>% 
  
  # fills in missing cty_cook_eav variables. 
  mutate(cty_cook_eav = ifelse(is.na(cty_cook_eav) & total_final_levy > 0, 
                               total_final_levy / (total_final_rate/100), cty_cook_eav),
         cty_total_eav = ifelse(is.na(cty_total_eav) & total_final_levy > 0 , 
                                total_final_levy / (total_final_rate/100), cty_total_eav)) %>% 
  
  # then keeps only taxing agencies that have a taxable EAV > 0
  filter(cty_total_eav > 0 )

## 11,533 obs - AWM 3/31/2024



# pulls in additional tables that exist in PTAXSIM database
# for calculating taxable AV: Taxable EAV / 
cpi <- read_csv("./Necessary_Files/cpi.csv") 

eq_factor <- read_csv("./Necessary_Files/eq_factor.csv") %>% 
  select(-eq_factor_tentative)

# Remove taxing agencies that had a levy of $0 for any year. 
# drop all occurrences of the taxing agency
# Countryside, Deer Park, Homer Glen, Norridge, Oak Brook, Schaumburg, Dixmoor (2011 only) are dropped using `dropped_munis 
dropped_munis <- c("030250000", "030270000", "030300000", "030585000", "030840000", "030890000", "031150000", "031230000")


exclude_hr_change <- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000" )


recoded_data <- raw_data_joined %>% 
  left_join(cpi, by = c("year" = "levy_year")) %>%
  left_join(eq_factor) %>%
  
  mutate(
    agency_num = as.character(agency_num),            # change variable type
    agency_num = str_pad(agency_num, 9, "left", "0"), # add missing leading zeros
    first6 = str_pad(first6, 6, "left", "0"),
    home_rule_ind = as.character(home_rule_ind),      # change reference category
    minor_type = as.factor(minor_type),
    reassess_year = as.character(reassess_year)       # change variable type
    ) %>%
  
  mutate(cty_total_eav = as.numeric(cty_total_eav),    # taxable eav in cook and neighboring counties
         cty_cook_eav = as.numeric(cty_cook_eav),      # taxable EAV in cook county only
         pct_in_Cook = cty_cook_eav / cty_total_eav,   # to identify taxing agencies that cross county lines
         total_final_levy = as.numeric(total_final_levy), 
         av = cty_cook_eav / eq_factor_final,          # backed out taxable Assessed Value of properties
         first6_w_hr = str_c(first6, "_", home_rule_ind),
         agency_w_hr = str_c(agency_num, "_", home_rule_ind)
         )



recoded_data <- recoded_data %>% 
  
  #keep only agencies greater than 90% in Cook
  filter(pct_in_Cook > 0.9) %>% 
  
  mutate(
    # Add 1 to total_final_levy to allow ln transformation.
    # we do not want to drop agencies if they have zero because we still need to group them in a later step.
    total_final_levy_4log = total_final_levy + 1,
  
    log_eav = log(cty_total_eav),       # Taxable EAV within Cook AND neighboring counties.
    log_levy = log(total_final_levy_4log),  
    log_av = log(av),
    year = as.factor(year),             # change to factor type for plm()
    agency_num = as.factor(agency_num)  # factor for plm()
    
  )

groupies <- read_csv("grouped_labels.csv") 
head(groupies)

groupies <- groupies %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         agency_num = as.factor(agency_num), 
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))

after2009 <- recoded_data %>% 
  ungroup() %>% 
  mutate(year_num = as.numeric(as.character(year)) ) %>% 
  filter(year_num > 2009) %>%
 # filter(year %in% c("2018", "2019", "2020". "2021") ) %>%   
  left_join(groupies,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP" # | major_type == "MISCELLANEOUS"
           & minor_type != "MISC"
           ) %>%  
 # filter(home_rule_ind == 1) %>% 
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE)+1,
            cty_cook_eav = first(cty_cook_eav), 
            av = first(av), ## was sum(), now first()
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind)) %>% 
   # left_join(muni_agency_names) %>% 
    #select(-c(Column1, `Most recent reassessed`)) %>% 
    mutate(
      log_av = log(av),
      log_levy = log(total_final_levy),
      bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything())

 after2009 %>%  
  ungroup() %>%
  #filter(year == 2021) %>%
  group_by(home_rule_ind, year) %>%
  summarize(count = n())

 
```

# Descriptive Stats

```{r}
df <- after2009
datasummary_skim(df)
datasummary_skim(df, type  = "categorical")
```

```{r}
# datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, 
#                      data = df%>% filter(year==2022), 
#                      title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
# 
# datasummary_crosstab(minor_type~home_rule_ind, data = df%>%filter(year==2022),  
#                      statistic = 1~1+N, 
#                      title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r eval=FALSE}
muni_fmv <- read_csv("Necessary_Files/ptaxsim_muni_level_2006-2022.csv")

muni_fmv <- muni_fmv |> select(-muni_pct_eav_taxed)

#muni_fmv_2006 <- muni_fmv |> filter(year == 2006)

muni_fmv_2022 <- muni_fmv |> 
  filter(year == 2022)  


datasummary_skim(muni_fmv_2022)

muni_fmv %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
muni_fmv %>% filter(year==2010)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
```


```{r }
library(plm)
df <- after2009 #|> mutate(year = as.numeric(year))# |> left_join(muni_fmv) 


# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
df_panel <- df %>% 
#  filter( minor_type == "MUNI" | agency_name == "TOWN CICERO" | minor_type == "ELEMENTARY" | minor_type=="SECONDARY") %>% 
  pdata.frame(index = c("uniqueid", "year") ) %>% 
  make.pbalanced(balance.type = "shared.individuals")


# Balance the panel -> now 9945 obs 

is.pbalanced(df_panel)

pdim(df_panel)

```
```{r eval=FALSE}
datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, data = df_panel%>% filter(year==2022), title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel%>%filter(year==2022),  statistic = 1~1+N, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r eval=FALSE}
df_panel %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

df_panel %>% filter(year==2010)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

#df_panel %>% 
 # filter(year==2006)%>% 
  #select(muni_fmv, muni_fmv_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary(~minor_type, data = df_panel %>% filter(year==2022), fmt = fmt_sprintf("%.0f"))
```

### Test if Fixed Effects should be used

"pooling" is equivalent to classic linear model  
"within" is like classic linear model with n-1 group dummies. (Dummies for each group and one is the comparison group.)  

```{r eval=FALSE}

# imagine that it makes "one line"for all observations instead of a line for each individual over time
g <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)
plmtest(g, effect = "twoways", type = "ghm")

gw <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)

gp <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)


summary(gp)
summary(gw)

plmtest(g)
plmtest(gw)

plmtest(naive_mod_munis, effect = "twoways", type = "ghm")
pFtest(gw, gp)
```


## Table 1: Name and Number of Taxing Agencies

```{r eval=FALSE}
#| label: tbl-majortype-byhomerule
#| tbl-cap: "Major type taxing agencies by home rule indicator"

datasummary_crosstab(major_type~home_rule_ind, data = df_panel, 
                     # title = "Taxing Agency Types by Home Rule Indicator", 
                     output = "flextable")
```


```{r eval=FALSE}
#| label: tbl-minortype-byhomerule
#| tbl-cap: "Minor type taxing agencies by home rule indicator"

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel, 
                    # title = "Taxing Agency Types by Home Rule Indicator", 
                     output = "flextable")
```


## Table 2: Levy and Levy Growth


```{r}
# pop <- readxl::read_xlsx("Necessary_Files/community_cohort_inputs.xlsx") %>% 
#   select(MUNI, POP) %>% filter(!is.na(MUNI))

pop2 <- readxl::read_xlsx("Necessary_Files/populationcounts_cookcountyil.xlsx")

library(dplyr)

# pop <- pop %>% 
#   mutate(MUNI = case_when(
#     MUNI == "Forest View" ~ "Forestview",
#     MUNI == "East Hazel Crest" ~ "East Hazelcrest",
#     MUNI == "Hazel Crest" ~ "Hazelcrest",
#     MUNI == "McCook" ~ "Mc Cook",
#     MUNI == "Mount Prospect" ~ "Mt Prospect",
#     MUNI == "Northlake" ~ "North Lake",
#     TRUE~as.character(MUNI)
#   )
#   )

pop2 <- pop2 %>% 
  mutate(Name = case_when(
    Name == "Forest View" ~ "Forestview",
    Name == "East Hazel Crest" ~ "East Hazelcrest",
    Name == "Hazel Crest" ~ "Hazelcrest",
    Name == "McCook" ~ "Mc Cook",
    Name == "Mount Prospect" ~ "Mt Prospect",
    Name == "Northlake" ~ "North Lake",
    TRUE~as.character(Name)
  )
  )

df <- df %>% # filter(!is.na(clean_name) ) %>% 
  left_join(pop2, by = c("clean_name" = "Name"))
                
df %>% filter(!is.na(clean_name) & is.na(pop2010) ) %>% 
  select(clean_name, pop2010, everything())

df <- df %>% 
  mutate(ext_percap = case_when(
    year < 2015 ~ round(muni_levy/pop2010),
    year >= 2015 ~ round(muni_levy/pop2020)),
    
    taxbase_percap = case_when(
      year < 2015 ~ round(cty_cook_eav/pop2010),
      year >= 2015 ~ round(cty_cook_eav/pop2020)),
    
    tax_rate = round(muni_levy / cty_cook_eav, digits=4))

```

```{r}
#| label: tbl-extperperson
#| tbl-cap: "Growth in the average levy per person from 2006 to 2022. Uses 2010 population counts for 2006 and 2020 population counts for 2020."

df %>% 
  filter(year == 2010 | year == 2022 
         ) %>% 
  select(year, agency_name, ext_percap, ext_percap) %>% 
  pivot_wider( id_cols = "agency_name", names_from = "year", 
              values_from = "ext_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 3: Tax Base and Tax Base Growth

```{r} 
#| label: tbl-taxbasegrowth
#| tbl-cap: "Growth in the tax base per capita from 2006 to 2022. Uses 2010 population counts for 2006 and 2020 population counts for 2020."

df %>% 
  filter(year == 2010 | year == 2022) %>% 
  select(year, agency_name, taxbase_percap) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", 
              values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 4: Tax Rate and Tax Rate Growth

```{r}
#| label: tbl-compositelevy-taxrates
#| tbl-cap: "Tax rates calculated from composite municipality levy / municipality's tax base"

df %>% 
  filter(year == 2010 | year == 2022 & 
           (minor_type == "MUNI" | agency_name == "TOWN CICERO") & 
           major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, tax_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", 
              values_from = "tax_rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2019` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

```{r}
#| label: tbl-agencylevy-taxrates
#| tbl-cap: "Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav."

df %>% 
  filter(year == 2006 | year == 2022) %>% 
  select(year, agency_name, total_final_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "total_final_rate") %>%   
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

```{r}
#| label: tbl-descriptivestats-nochicago
#| tbl-cap: "Descriptive Stats for Taxing Agencies Outside of Chicago"

df %>% filter(year==2010) %>% 
  filter(clean_name!="Chicago") %>%
  select(ext_percap, taxbase_percap, muni_fmv_taxed, muni_eav_taxed, muni_levy, total_final_levy, total_final_rate, cty_cook_eav, muni_current_rate_avg, muni_PC_total, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary_skim(fmt = fmt_sprintf("%.0f"))


df %>% filter(year==2022) %>% 
  filter(clean_name!="Chicago") %>%
  select(ext_percap, taxbase_percap, muni_fmv_taxed, muni_eav_taxed, muni_levy, total_final_levy, total_final_rate, cty_cook_eav, muni_current_rate_avg, muni_PC_total, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary_skim(fmt = fmt_sprintf("%.0f"))
```


