---
title: "Descriptive Stats for Levy Project Data"
format: 
  html:
    df-print: paged
    code-fold: true
    tbl-cap-location: top
    toc: true
    toc-location: left
---


```{r setup, warning=FALSE, message=FALSE, output = FALSE}
library(modelsummary)
library(tidyverse)
library(janitor)
library(knitr)
library(DT)
```



```{r}
#| label: tryFMVdata

df <- read_csv("panel_data.csv")   ## 10,374

df <- df |> filter(!minor_type %in% c("BOND", "UNIFIED", "COMM COLL", "COOK", "MOSQUITO", "SANITARY") ) # 9704 obs remain

df <- df |>
  mutate(tfl_pct_change = if_else(is.na(tfl_pct_change) |
                                    is.infinite(tfl_pct_change),
                                  0, tfl_pct_change) )

df <- df |> 
  select(-c(muni_name, muni_num, agency_w_hr, first6_w_hr, log_eav:reassess_lag2, 
            lag_eav_pct_change1:lag_av_pct_change2)) %>%
  mutate_at(c("home_rule_ind"), as.character) %>%
 # Code Cicero as a Municipality and not a township.
  mutate(minor_type = ifelse(agency_name == "TOWN CICERO", "MUNI", minor_type))


df <- df |> 
  group_by(agency_name) |>
  arrange(Township, clean_name) |>
  mutate(clean_name = first(clean_name),
         Township = first(Township))

# muni_names <- unique(df$clean_name)
# library(data.table)
# 
# df <- df |> mutate(
#   muni_name = ifelse(grepl(agency_name, pattern = muni_names, ignore.case=TRUE) == TRUE, muni_names, clean_name)
#   #clean_name = ifelse(agency_name %like% muni_names, muni_names, clean_name)
#  # clean_name = str_replace(agency_name, muni_names$clean_name, muni_names$clean_name, clean_name )
#   )

```

# Descriptive Stats

```{r}
datasummary_skim(df)
datasummary_skim(df, type  = "categorical")
```


```{r eval=FALSE, include = FALSE}
muni_fmv <- read_csv("Necessary_Files/ptaxsim_muni_level_2006-2022.csv")

muni_fmv <- muni_fmv |> select(-muni_pct_eav_taxed) 
## muni_pct_eav_taxed is actually the muni wide tax rate calculated from the 
## Levy / Taxed EAV. It was mislabeled in the summary file.

#muni_fmv_2006 <- muni_fmv |> filter(year == 2006)

muni_fmv_2022 <- muni_fmv |> 
  filter(year == 2022)  


datasummary_skim(muni_fmv_2022)

muni_fmv %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
muni_fmv %>% filter(year==2006)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
```


> df_panel only includes Municipality Taxing Agecncies (which should be grouped with the miscellaneous and other muni/township taxing agencies but is not in these tables) and Elementary and Secondary School Districts.


```{r}
library(plm)
#df <- left_join(df, muni_fmv) 
pop2 <- readxl::read_xlsx("Necessary_Files/populationcounts_cookcountyil.xlsx")

pop2 <- pop2 %>% 
  mutate(Name = case_when(
    Name == "Forest View" ~ "Forestview",
    Name == "East Hazel Crest" ~ "East Hazelcrest",
    Name == "Hazel Crest" ~ "Hazelcrest",
    Name == "McCook" ~ "Mc Cook",
    Name == "Mount Prospect" ~ "Mt Prospect",
    Name == "Northlake" ~ "North Lake",
    TRUE~as.character(Name)
  )
  )
df <- df %>% 
  filter(year > 2009) %>%
  left_join(pop2, by = c("clean_name" = "Name")) 

df_panel <- df %>% 
  mutate(ext_percap = case_when(
    year < 2015 ~ round(total_final_levy/pop2010),
    year >= 2015 ~ round(total_final_levy/pop2020)),
    
    taxbase_percap = case_when(
      year < 2015 ~ round(cty_cook_eav/pop2010),
      year >= 2015 ~ round(cty_cook_eav/pop2020)),
    
    tax_rate = round(total_final_levy / cty_cook_eav, digits=4) # tax rate that would come from agency_dt instead of manually calculated from PIN level.
    )

df_panel <- df_panel %>% ungroup() %>%
  filter( minor_type == "MUNI" | minor_type == "ELEMENTARY" | minor_type=="SECONDARY" | minor_type == "TOWNSHIP") %>% 
  pdata.frame(index = c("agency_name", "year") ) %>% 
  make.pbalanced(balance.type = "shared.individuals")


# Balance the panel -> now 4301 obs 

is.pbalanced(df_panel)

pdim(df_panel)

```




```{r eval=FALSE, include=FALSE}
df_panel %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

df_panel %>% filter(year==2006)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

#df_panel %>% 
 # filter(year==2006)%>% 
  #select(muni_fmv, muni_fmv_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary(~minor_type, data = df_panel %>% filter(year==2022), fmt = fmt_sprintf("%.0f"))
```

 

```{r test-fixedeffects-isneeded, eval=FALSE, include = FALSE}

### Test if Fixed Effects should be used

# "pooling" is equivalent to classic linear model  
# "within" is like classic linear model with n-1 group dummies. (Dummies for each group and one is the comparison group.) 
# 

# imagine that it makes "one line"for all observations instead of a line for each individual over time
g <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)

plmtest(g, effect = "twoways", type = "ghm")

gw <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)

gp <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)


summary(gp)
summary(gw)

plmtest(g)
plmtest(gw)

plmtest(naive_mod_munis, effect = "twoways", type = "ghm")
pFtest(gw, gp)
```


## Table 1: Name and Number of Taxing Agencies

### Filtered Panel Data

```{r}
#| label: tbl-majortype-byhomerule-filtered
#| tbl-cap: "Minor type taxing agencies by home rule indicator"

datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, data = df_panel%>% filter(year==2022), output = "flextable")
```


```{r}
#| label: tbl-minortype-byhomerulefiltered
#| tbl-cap: "Minor type taxing agencies by home rule indicator"

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel%>%filter(year==2022),  statistic = 1~1+N, output = "flextable")
```


## Table 2: Levy and Levy Growth for Municipality Taxing Agencies


```{r data_load_tbl_2}

#pop2 <- readxl::read_xlsx("Necessary_Files/populationcounts_cookcountyil.xlsx")

library(dplyr)

# 
# pop2 <- pop2 %>% 
#   mutate(Name = case_when(
#     Name == "Forest View" ~ "Forestview",
#     Name == "East Hazel Crest" ~ "East Hazelcrest",
#     Name == "Hazel Crest" ~ "Hazelcrest",
#     Name == "McCook" ~ "Mc Cook",
#     Name == "Mount Prospect" ~ "Mt Prospect",
#     Name == "Northlake" ~ "North Lake",
#     TRUE~as.character(Name)
#   )
#   )

#df <- df %>% left_join(pop2, by = c("clean_name" = "Name"))

df <- df %>% 
  mutate(ext_percap = case_when(
    year < 2015 ~ round(total_final_levy/pop2010),
    year >= 2015 ~ round(total_final_levy/pop2020)),
    
    taxbase_percap = case_when(
      year < 2015 ~ round(cty_cook_eav/pop2010),
      year >= 2015 ~ round(cty_cook_eav/pop2020)),
    
    tax_rate = round(total_final_levy / cty_cook_eav, digits=4) # tax rate that would come from agency_dt instead of manually calculated from PIN level.
    )

df_filtered <- df %>%  
  filter(!is.na(clean_name) ) %>% ## Gets rid of schools
  ungroup()

# df_filtered %>% 
#   filter(!is.na(clean_name) & is.na(pop2010) ) %>% 
#   select(clean_name, pop2010, everything())
## Homer Glen did not join and get population numbers but it gets dropped anyways 
# and is mostly outside of Cook County



```

```{r original_table, eval=FALSE, include = FALSE}
df_filtered |>
  group_by(year) |>
  summarize(
    median_levypercap = median(ext_percap, na.rm=TRUE),
    sd_levypercap = sd(ext_percap, na.rm=TRUE),
    med_levypercap_growth = median((muni_levy/pop2020) / (muni_levy/pop2010), na.rm=TRUE),
    sd_levypercap_growth = sd(((muni_levy/pop2020) / (muni_levy/pop2010)), na.rm=TRUE)
  ) |>
  filter(year %in% c("2010", "2022")) |>
  pivot_longer(c(median_levypercap:sd_levypercap_growth), names_to = "statistic", values_to = "value") |>
  pivot_wider(id_cols = c(statistic ) , names_from = year, values_from = value   ) |>
  datatable(caption = "County Wide Stats: Summary Statistics (per capita), 2010 and 2022",
            rownames = FALSE,
            options = list(
              dom = 't',
              scrollX = TRUE, # Enable horizontal scrolling
              columnDefs = list(
                list(targets = 1:2, render = JS("function(data, type, row, meta) {
                  return type === 'display' ? data.toFixed(2) : data;
              }")),
              list(targets = 1:2, width = '50px')
              )
            ))
```

### For all Municipality Taxing Agencies

```{r}
#| label: tbl-levymediangrowth
#| tbl-cap: "pct change calculated from aggregated medians instead of individual pct change."
#| eval: false
#| include: false


df_filtered |>
  filter(minor_type == "MUNI") |>
  filter(year %in% c("2010", "2022")) |>
  group_by(year) |>
  summarize("Median Per Capita Levy" = round(median(ext_percap, na.rm=TRUE)),
            "Standard Deviation" = round(sd(ext_percap, na.rm=TRUE)),
                                         "Agency Count" = n()
  )|>

  pivot_longer(-year, names_to = "statistic", values_to = "value") |>
  pivot_wider(names_from = year, values_from = value) |>
      mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) |>

  flextable::flextable()
```


```{r}
#| label: tbl-levyperperson
#| tbl-cap: "Growth in the levy per person from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022."

# agency level growth:
levy_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           (minor_type == "MUNI")
         ) %>% 
  select(year, clean_name, ext_percap) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
              values_from = "ext_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  arrange(desc(pct_growth))  

levy_table %>% DT::datatable(
  rownames = FALSE,
            options = list(
              dom = 't',
              scrollX = TRUE, # Enable horizontal scrolling
              columnDefs = list(
                list(targets = 1:2#, 
              #  render = JS("function(data, type, row, meta) {
             #     return type === 'display' ? data.toFixed(2) : data;
             # }")
              ),
              list(targets = 1:2, width = '50px')
              )
            ))
```


```{r}
#| label: tbl-levyperpersonmedian
#| tbl-cap: "Median levy per person from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2020."
#| message: false
#| warning: false



# levy_table %>% 
#   ungroup() %>%
#    summarize(
#             `2010 Levy StdDv` = round(sd(`2010`, na.rm=TRUE)),
#             `2022 Levy StdDv` = round(sd(`2022`, na.rm=TRUE))) |>
#  pivot_longer(cols = c(`2010 Levy StdDv`:`2022 Levy StdDv`),  
#               names_to = "statistic", values_to = "value") |>
#   DT::datatable(rownames = FALSE)


levy_table %>% 
  ungroup() %>%
   summarize(
            `2010 Median Levy per Capita` = median(`2010`, na.rm=TRUE),
   `2010 Levy StdDv` = (sd(`2010`, na.rm=TRUE)),
            `2022 Median Levy per Capita` = median(`2022`, na.rm=TRUE),
               `2022 Levy StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),

            `Median Growth of Levy per Capita` = round(median(pct_growth, na.rm=TRUE), digits = 2),
            `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE))

           ) |>
      mutate(across(where(is.numeric), round, digits = 1)) %>%

  pivot_longer(cols = c(`2010 Median Levy per Capita`:`Growth StdDv`),  
               names_to = "statistic", values_to = "value") |>

  DT::datatable(rownames = FALSE)

```


## Table 3: Tax Base and Tax Base Growth


### Municipalities only 

```{r}
#| label: tbl-table3
#| tbl-cap-location: top
#| tbl-cap: "Tax Base Summary Statistics (per capita), 2010 and 2022. pct change calculated from aggregated medians instead of individual pct change. ignore pct change standard deviation. "




# agency level growth:
taxbase_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           (minor_type == "MUNI")
         ) %>% 
  select(year, clean_name, cty_cook_eav) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
              values_from = "cty_cook_eav") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  arrange(desc(pct_growth)) 


taxbase_table %>% #select(year`2022`) %>% 
  ggplot() + geom_histogram(aes(x=pct_growth))

hist(taxbase_table$pct_growth)

df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           (minor_type == "MUNI")
         ) %>% 
  group_by(year) %>%
summarize(mean = mean(cty_cook_eav, na.rm=TRUE),
          median = median(cty_cook_eav, na.rm=TRUE)) 




# agency level growth:
taxbase_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           (minor_type == "MUNI")
         ) %>% 
  select(year, clean_name, taxbase_percap) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
              values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  arrange(desc(pct_growth)) 


taxbase_table %>% 
  ungroup() %>%
   summarize(
            `2010 Median Tax Base per Capita` = median(`2010`, na.rm=TRUE),
            `2010 Mean Base per Cap` = median(mean(`2010`, na.rm=TRUE)),
   `2010 Tax Base StdDv` = (sd(`2010`, na.rm=TRUE)),
            `2022 Median Tax Base per Capita` = median(`2022`, na.rm=TRUE),
               `2022 Tax Base StdDv` = round(sd(`2022`, na.rm=TRUE)),

            `Median Growth of Levy per Capita` = round(median(pct_growth, na.rm=TRUE), digits = 2),
               `2022 Mean Base per Cap` = median(mean(`2022`, na.rm=TRUE)),

            `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2)

           ) |>
      mutate(across(where(is.numeric), round)) %>%

  pivot_longer(cols = c(`2010 Median Tax Base per Capita`:`Growth StdDv`),  
               names_to = "statistic", values_to = "value") |>

  DT::datatable(rownames = FALSE)

```

```{r} 
#| label: tbl-taxbasegrowth
#| tbl-cap: "Growth in the tax base per capita from 2006 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022."

df_panel %>% 
  filter(!is.na(clean_name)) %>%
  filter(year == 2010 | year == 2022 & 
           (minor_type == "MUNI") 
 ) %>% 
  select(year, clean_name, taxbase_percap) %>% 
  pivot_wider(id_cols = "clean_name", names_from = "year", 
              values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 4: Tax Rate and Tax Rate Growth


```{r}
#| label: tbl-taxrate-table
#| tbl-cap: "Tax Rate Growth for Municipalities. 2010 to 2022"


# agency level growth:
rate_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           (minor_type == "MUNI")
         ) %>% 
  select(year, clean_name, total_final_rate) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
              values_from = "total_final_rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  mutate(across(where(is.numeric))) %>%
  arrange(desc(pct_growth)) 

rate_table %>% 
  ungroup() %>%
   summarize(
            `2010 Median Rate` = median(`2010`, na.rm=TRUE),
   `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
            `2022 Median Rate` = median(`2022`, na.rm=TRUE),
               `2022 Rate StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),

            `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
            `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2)

           ) |>
  pivot_longer(cols = c(`2010 Median Rate`:`Growth StdDv`),  
               names_to = "statistic", values_to = "value") |>
  flextable::flextable(cwidth = 1.5)
```



```{r}
#| label: tbl-agencylevy-taxrates
#| tbl-cap: "**Agency Level Tax Rate Growth.** Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav."

df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  select(year, agency_name, total_final_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "total_final_rate") %>%   
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


```{r}
#| label: tbl-agencylevy-taxrates-notbalanced
#| tbl-cap: "**Agency Level Tax Rate Growth - NOT from balanced panel.** Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav."


rate_table <- df |>
  filter(year %in% c("2010", "2022")) |>
  select(year, minor_type, agency_name, total_final_rate) %>% 
  pivot_wider( id_cols = c("minor_type", "agency_name"), names_from = "year", 
              values_from = "total_final_rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  arrange(desc(pct_growth))  

rate_table  |> DT::datatable(rownames = FALSE)
```


```{r}
#| label: tbl-minortype-agency-rategrowth-notbalanced
#| tbl-cap: "**Agency Level Tax Rate Growth - NOT from balanced panel.** Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav."


rate_table |>
    ungroup() %>%
    group_by(minor_type) |>

   summarize(
            `2010 Median Rate` = median(`2010`, na.rm=TRUE),
           `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),

            `2022 Median Rate` = median(`2022`, na.rm=TRUE),
            `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits =2),

            `Median Rate Growth` = median(pct_growth, na.rm=TRUE),
            `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
           Agencies = n()) |> flextable::flextable()
```

Note: Some municipalities may have experienced growth that appears larger due to absorbing some of the sub-taxing agencies (e.g. Health, Library, etc.)



## Models 

```{r}
library(fixest)
list <- list(
  twfe <- feols(log(total_final_levy) ~ log(cty_cook_eav) | agency_name + year, data = df_panel),
  
  dummies <- feols(log(total_final_levy) ~ log(cty_cook_eav) + agency_name + year, data = df_panel)
)

modelsummary(list,
             stars = TRUE,
             coef_omit = 'agency_name',
             )

feols(log(total_final_levy) ~ log(cty_cook_eav) | agency_name + year + minor_type, data = df_panel)


feols(log(total_final_levy) ~ log(cty_cook_eav) + lag(log(cty_cook_eav), 1) + lag(log(cty_cook_eav), 2 ) | agency_name + year, data = df_panel) 

```


```{r}
feols(log(total_final_levy) ~ log(av) + lag(log(av)) + lag(log(av)^2)  | agency_name + year, data = df_panel)

```

**Uses Reassess Year** Only works for Munis, Schools do not have the reassess year variable.

```{r}
feols(log(total_final_levy) ~ log(av) + lag(log(av)) + lag(log(av), 2) + lag(log(av)^2)  + reassess_year + lag(reassess_year, 1) + log(av)*lag(reassess_year) | agency_name + year, data = df_panel)
```


**Subset by Muni, Town, and Schools**

```{r}
feols(log(total_final_levy) ~ log(cty_cook_eav) + lag(log(cty_cook_eav)) + lag(log(cty_cook_eav), 2) | agency_name + year, data = df_panel %>% filter(minor_type=="MUNI"))
feols(log(total_final_levy) ~ log(cty_cook_eav) + lag(log(cty_cook_eav)) + lag(log(cty_cook_eav), 2) | agency_name + year + home_rule_ind, data = df_panel %>% filter(minor_type=="MUNI"))


feols(log(total_final_levy) ~ log(cty_cook_eav) + lag(log(cty_cook_eav)) + lag(log(cty_cook_eav), 2)   | agency_name + year, data = df_panel %>% filter(minor_type=="TOWNSHIP"))

feols(log(total_final_levy) ~ log(cty_cook_eav) + lag(log(cty_cook_eav)) + lag(log(cty_cook_eav), 2)  | agency_name + year, data = df_panel %>% filter(major_type=="SCHOOL"))

```


> Schools are still always different than Towns or Municipalities


