---
title: "Descriptive Stats for Levy Project Data"
format: 
  html:
    df-print: paged
---


```{r warning=FALSE, message=FALSE, output = FALSE}
library(modelsummary)
library(tidyverse)
library(janitor)
library(dplyr)
```

> I do not trust the calculations for muni_pct_eav_taxed.  Check loop file for how it was calculated. Might just be incorrect denominator?  Other calculations seem fine. 


```{r}
#| label: tryFMVdata

df <- read_csv("panel_data.csv")   ## 10,374
df <- df |> 
  mutate(tfl_pct_change = if_else(is.na(tfl_pct_change) | 
                                    is.infinite(tfl_pct_change), 
                                  0, tfl_pct_change) )

df <- df |> 
  select(-c(muni_name, muni_num, agency_w_hr, first6_w_hr, log_eav:reassess_lag2, 
            lag_eav_pct_change1:lag_av_pct_change2)) %>%
  mutate_at(c("home_rule_ind"), as.character)
```

# Descriptive Stats

```{r}
datasummary_skim(df)
datasummary_skim(df, type  = "categorical")
```

```{r}
datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, 
                     data = df%>% filter(year==2022), 
                     title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = df%>%filter(year==2022),  
                     statistic = 1~1+N, 
                     title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r}
muni_fmv <- read_csv("Necessary_Files/ptaxsim_muni_level_2006-2022.csv")

muni_fmv <- muni_fmv |> select(-muni_pct_eav_taxed)

#muni_fmv_2006 <- muni_fmv |> filter(year == 2006)

muni_fmv_2022 <- muni_fmv |> 
  filter(year == 2022)  


datasummary_skim(muni_fmv_2022)

muni_fmv %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
muni_fmv %>% filter(year==2006)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))
```


```{r}
library(plm)
df <- left_join(df, muni_fmv) 


# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
df_panel <- df %>% 
  filter( minor_type == "MUNI" | agency_name == "TOWN CICERO" | minor_type == "ELEMENTARY" | minor_type=="SECONDARY") %>% 
  pdata.frame(index = c("clean_name", "year") ) %>% 
  make.pbalanced(balance.type = "shared.individuals")


# Balance the panel -> now 9945 obs 

is.pbalanced(df_panel)

pdim(df_panel)

```
```{r}
datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, data = df_panel%>% filter(year==2022), title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel%>%filter(year==2022),  statistic = 1~1+N, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r}
df_panel %>% filter(year==2022) %>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

df_panel %>% filter(year==2006)%>% select(muni_fmv, muni_fmv_taxed, muni_eav_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% datasummary_skim(fmt = fmt_sprintf("%.0f"))

#df_panel %>% 
 # filter(year==2006)%>% 
  #select(muni_fmv, muni_fmv_taxed, muni_levy, muni_current_rate_avg, muni_PC_total, muni_eav, muni_avg_C2_bill_noexe, muni_avg_C2_bill_withexe) %>% 
  datasummary(~minor_type, data = df_panel %>% filter(year==2022), fmt = fmt_sprintf("%.0f"))
```

### Test if Fixed Effects should be used

"pooling" is equivalent to classic linear model  
"within" is like classic linear model with n-1 group dummies. (Dummies for each group and one is the comparison group.)  

```{r eval=FALSE}

# imagine that it makes "one line"for all observations instead of a line for each individual over time
g <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)
plmtest(g, effect = "twoways", type = "ghm")

gw <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)

gp <- plm(log_levy ~ log(muni_fmv_taxed),
                         model = "pooling",
                         data = muni_subset)


summary(gp)
summary(gw)

plmtest(g)
plmtest(gw)

plmtest(naive_mod_munis, effect = "twoways", type = "ghm")
pFtest(gw, gp)
```


## Table 1: Name and Number of Taxing Agencies

```{r}
datasummary_crosstab(major_type~home_rule_ind, data = df_panel, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = df_panel, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```


## Table 2: Levy and Levy Growth


```{r}
pop <- readxl::read_xlsx("Necessary_Files/community_cohort_inputs.xlsx") %>% 
  select(MUNI, POP) %>% filter(!is.na(MUNI))
library(dplyr)

pop <- pop %>% 
  mutate(MUNI = case_when(
    MUNI == "Forest View" ~ "Forestview",
    MUNI == "East Hazel Crest" ~ "East Hazelcrest",
    MUNI == "Hazel Crest" ~ "Hazelcrest",
    MUNI == "McCook" ~ "Mc Cook",
    MUNI == "Mount Prospect" ~ "Mt Prospect",
    MUNI == "Northlake" ~ "North Lake",
    TRUE~as.character(MUNI)
  )
  )

df <- df %>% filter(!is.na(clean_name) ) %>% 
  left_join(pop, by = c("clean_name" = "MUNI"))
                
df %>% filter(!is.na(clean_name) & is.na(POP) )    %>% 
  select(clean_name, POP, everything())

df<- df %>% mutate(ext_percap = round(muni_levy/POP),
                   taxbase_percap = round(cty_cook_eav/POP),
                   tax_rate = round(muni_levy / cty_cook_eav, digits=4))
```

```{r}

df %>% filter(year == 2006 | year == 2022 & (minor_type == "MUNI" | agency_name == "TOWN CICERO") & major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, ext_percap) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "ext_percap") %>% arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 3: Tax Base and Tax Base Growth

```{r}
df %>% 
  filter(year == 2006 | year == 2022 & 
           (minor_type == "MUNI" | agency_name == "TOWN CICERO") & 
           major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, taxbase_percap) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", 
              values_from = "taxbase_percap") %>% 
  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


## Table 4: Tax Rate and Tax Rate Growth

```{r}
#| label: tbl-compositelevy-taxrates
#| tbl-cap: "Tax rates calculated from composite municipality levy / municipality's tax base"

df %>% 
  filter(year == 2006 | year == 2022 & 
           (minor_type == "MUNI" | agency_name == "TOWN CICERO") & 
           major_type == "MUNICIPALITY/TOWNSHIP") %>% 
  select(year, agency_name, tax_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", 
              values_from = "tax_rate") %>% 
  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

```{r}
#| label: tbl-agencylevy-taxrates
#| tbl-cap: "Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav."

df %>% 
  filter(year == 2006 | year == 2022) %>% 
  select(year, agency_name, total_final_rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "total_final_rate") %>% arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```


