---
title: "ABFM Naive Levy Elasticity Models"
author: "Michael Van Hulle"
date: "June 11, 2024"
format: 
  html:
    embed-resources: true
    theme: minty
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 200px
---

# Changes from 6-11 Models:

1.  Balanced the panel, dropping:
    a.  579 obs. from the "panel_data.csv" file
    b.  104 obs. from schools (not accounting
2.  Only evaluate primary and secondary schools (~1-4 obs for other types)
3.  Models have been run w/o Chicago
4.  Dropped munis that change HR status
5.  Dropped munis w/ $0 levy

```{r setup}
#| output: FALSE

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(modelsummary)
library(tidyverse)
library(kableExtra)
library(glue)
library(DT)
library(flextable)

set_flextable_defaults(theme_fun = theme_vanilla, 
                       padding = 2,
                       line_spacing = 1,
                       big.mark = ",",
                       )

options(DT.options = list())

set_summ_defaults(digits = 2, pvals = FALSE, robust = "HC5")

```

# Data Description

Our data ("panel_data.csv") is generated on line 187 of the "helper_recode_variables.R" file, which queries, filters, and manipulates variables from the PTAXSIM DB. It is the same data we have been using since February EXCEPT for the models we ran in April, where we used "grouped" taxing agencies.

SSAs are excluded from our sample.

Chicago is included in our sample.

```{r}
#| label: load_paneldata
#| output: false
#| eval: false

# import 8178 observations

df <- read_csv("panel_data.csv") |>
  # First column of csv is empty?
  select(-1) |>
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()

# Convert to panel data (8178 obs)

df_panel <- pdata.frame(df, index = c("agency_num", "year"))

# Balance the panel -> now 7599 obs (lost 579)

is.pbalanced(df_panel)

# df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")

# Subset: schools and munis - 3655 obs.
# NOTE: BALANCING THE PANEL & LIMITING SCHOOL SAMPLE DROPS 194 OF THESE OBS, 
# THE DIFFERENCE FROM THE MODELS
# WE SENT MERRIMAN ON 6/11 IS IN THIS NUMBER

school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO")

# All schools: 1938 obs.

schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY")

# Elementary schools: 1751 obs.

ele <- subset(df_panel, minor_type == "ELEMENTARY")

# Secondary Schools: 187 obs.

sec <- subset(df_panel, minor_type == "SECONDARY")

# All munis: 1700 obs.

munis <- subset(df_panel, minor_type == "MUNI")

# HR Munis: 1051 obs.

muni_hr <- subset(df_panel, minor_type == "MUNI" & home_rule_ind == 1)

# NHR munis: 685 obs.

muni_nhr <- subset(df_panel, minor_type == "MUNI" & home_rule_ind == 0)

colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")
  
```

```{r}
#| label: tryFMVdata
#| 


df <- read_csv("panel_data.csv")

muni_fmv <- read_csv("Necessary_Files/ptaxsim_muni_level_2006-2022.csv") 

df <- left_join(df, muni_fmv) |>
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()

# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("agency_num", "year"))
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
# df_panel <- make.pbalanced(df_panel, balance.type = "fill")


# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
# df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")

df_panel <- pdata.frame(df, index = c("agency_num", "year"))
df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")



# Balance the panel -> now 9758 obs 

is.pbalanced(df_panel)



# Subset: schools and munis - 4250 obs.
# NOTE: BALANCING THE PANEL & LIMITING SCHOOL SAMPLE DROPS 194 OF THESE OBS, 
# THE DIFFERENCE FROM THE MODELS
# WE SENT MERRIMAN ON 6/11 IS IN THIS NUMBER

school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO")

# All schools: 2380 obs.

schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY")

# Elementary schools: 1938 obs.

ele <- subset(df_panel, minor_type == "ELEMENTARY")

# Secondary Schools: 442 obs.

sec <- subset(df_panel, minor_type == "SECONDARY")

# All munis: 1870 obs.

munis <- subset(df_panel, minor_type == "MUNI"| agency_name == "TOWN CICERO")

# HR Munis: 1202 obs.

muni_hr <- subset(df_panel,(minor_type == "MUNI" | agency_name == "TOWN CICERO")& home_rule_ind == 1)

# NHR munis: 668 obs.

muni_nhr <- subset(df_panel, (minor_type == "MUNI" | agency_name == "TOWN CICERO")& home_rule_ind == 0)

```


# Data Exploration

## AV

### Descriptive Statistics

```{r all_av_descrips}

all_av_table <- df_panel |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

print(all_av_table)

```

```{r school_av_descrips}

school_av_table <- schools |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

#print(school_table_all)

ele_av_table <- ele |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

#print(school_table_ele)

sec_av_table <- sec |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

#print(school_table_sec)

school_av_table_final <- bind_cols(school_av_table, ele_av_table, sec_av_table)

print(school_av_table_final)

```

```{r muni_av_descrips}

muni_av_table <- munis |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

#print(muni_av_table)

nhr_av_table <- muni_nhr |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

#print(nhr_av_table)

hr_av_table <- muni_hr |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(av), 
            av_max = max(av), 
            av_mean = mean(av), 
            av_med = median(av), 
            av_sd = sd(av))

#print(nhr_av_table)

muni_av_table_final <- bind_cols(muni_av_table, nhr_av_table, hr_av_table)

print(muni_av_table_final)
```

### Visualizations

```{r av_visualizations}

colors_green <- c("#059212", "#06D001", "#9BEC00", "#F3FF90")

colors_blue_red <- c("#219C90", "#FFF455", "#FFC700", "#EE4E4E")

colors_space <- c("#26355D", "#AF47D2", "#FF8F00", "#FFDB00")

colors_custom <- c("#003f5c", "#444e86", "#955196", "#dd5182", "#ff6e54", "#ffa600")

colors_2 <- c("#003f5c", "#ffa600")

# schools |>
#   mutate(year = as.numeric(year)) |>
#   ggplot() +
#   geom_line(aes(x = year, y = ))
# 
# ggplot(schools, aes(x = year, y = av, ))

# ggplot(schools, aes(x = year, y = av,  fill = `School Type`)) +
#   geom_bar(stat = "identity") +
#   scale_fill_manual(values = bar_colors) +
#   ylim(0, 125) +
#   theme_minimal() +
#   labs(title = "School Agencies by Type (2021)",
#        x = "Type of School",
#        y = "n") +
#   theme(legend.position = "none") +
#   geom_text(aes(label = n), vjust = -0.5, size = 3)

```


## FMV Naive models - for Alea's curiosity

```{r muni_fmv_descrips}

muni_fmv_table <- munis |>
  group_by(year) |>
  summarize(n = n(), 
            fmv_min = min(muni_fmv_taxed), 
            fmv_max = max(muni_fmv_taxed), 
            fmv_mean = mean(muni_fmv_taxed), 
            fmv_med = median(muni_fmv_taxed), 
            fmv_sd = sd(muni_fmv_taxed))
muni_fmv_table

nhr_fmv_table <- muni_nhr |>
  group_by(year) |>
  summarize(n = n(), 
            fmv_min = min(muni_fmv_taxed), 
            fmv_max = max(muni_fmv_taxed), 
            fmv_mean = mean(muni_fmv_taxed), 
            fmv_med = median(muni_fmv_taxed), 
            fmv_sd = sd(muni_fmv_taxed))
nhr_fmv_table

hr_fmv_table <- muni_hr |>
  group_by(year) |>
  summarize(n = n(), 
            fmv_min = min(muni_fmv_taxed), 
            fmv_max = max(muni_fmv_taxed), 
            fmv_mean = mean(muni_fmv_taxed), 
            fmv_med = median(muni_fmv_taxed), 
            fmv_sd = sd(muni_fmv_taxed))
hr_fmv_table

```

```{r}
munis %>% filter(clean_name !="Chicago") %>% ggplot() + geom_line(aes(x=year, y = muni_fmv_taxed, group = clean_name, color = Triad, alpha = .5)) + facet_wrap(~Triad)
```


```{r twfe_muni_fmv_naive}

muni_subset <- subset(df_panel, minor_type == "MUNI" | agency_name == "TOWN CICERO")



naive_mod_munis <- plm(log(levy) ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)
# summary(naive_mod_munis)

hr_subset <- subset(df_panel, home_rule_ind == 1 & (minor_type == "MUNI" | agency_name == "TOWN CICERO"))

is.pbalanced(hr_subset)
hr_subset <- make.pbalanced(hr_subset)
hr_subset |>
  group_by(year) |>
  summarize(n = n(), 
            av_min = min(muni_fmv_taxed), 
            av_max = max(muni_fmv_taxed), 
            av_mean = mean(muni_fmv_taxed), 
            av_med = median(muni_fmv_taxed), 
            av_sd = sd(muni_fmv_taxed))

nhr_subset <- subset(df_panel, home_rule_ind == 0 & (minor_type == "MUNI" | agency_name == "TOWN CICERO"))
is.pbalanced(nhr_subset)
nhr_subset <- make.pbalanced(nhr_subset)
           
naive_mod_muni_hr <- plm(log(levy) ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = hr_subset)

naive_mod_muni_nhr <- plm(log(levy) ~ log(muni_fmv_taxed),
                         model = "within",
                         effect = "twoways",
                         data = nhr_subset)


muni_summ_table <- 
  export_summs(naive_mod_munis, naive_mod_muni_hr, naive_mod_muni_nhr,
               model.names = c("All Municipalities", "HR Municipalities", "NHR Municipalities"),
                                robust = "HC3",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_summ_table <- set_caption(muni_summ_table, "Municipalities, Dependant Variable: ln(levy)")

muni_summ_table

```


## Levy

### Descriptive Statistics

```{r all_levy_descrips}

all_levy_table <- df_panel |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

all_levy_table

```

```{r school_levy_descrips}

school_levy_table <- schools |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

#print(school_table_all)

ele_levy_table <- ele |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

#print(school_table_ele)

sec_levy_table <- sec |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

#print(school_table_sec)

school_levy_table_final <- bind_cols(school_levy_table, ele_levy_table, sec_levy_table)

school_levy_table_final

```

```{r muni_levy_descrips}

muni_levy_table <- munis |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

#print(muni_levy_table)

nhr_levy_table <- muni_nhr |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

#print(nhr_levy_table)

hr_levy_table <- muni_hr |>
  group_by(year) |>
  summarize(n = n(), 
            levy_min = min(levy), 
            levy_max = max(levy), 
            levy_mean = mean(levy), 
            levy_med = median(levy), 
            levy_sd = sd(levy))

#print(nhr_levy_table)

muni_levy_table_final <- bind_cols(muni_levy_table, nhr_levy_table, hr_levy_table)

muni_levy_table_final
```

### Visualizations

```{r av_graphs}

schools |>
  mutate(year = as.numeric(year)) |>
  ggplot() +
  geom_line(aes(x = year, y = median(av), group = "minor_type", ))

```

# Naive Model

```{r}
#| label: load_paneldata_duplicate
#| output: false

# import _____ observations

df <- read_csv("panel_data.csv") |>
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()

# Convert to panel data (8178 obs)

df_panel <- pdata.frame(df, index = c("agency_num", "year"))

# Balance the panel -> now 7599 obs (lost 579)

is.pbalanced(df_panel)

# df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")

# Subset: schools and munis - 3655 obs.
# NOTE: BALANCING THE PANEL & LIMITING SCHOOL SAMPLE DROPS 194 OF THESE OBS, 
# THE DIFFERENCE FROM THE MODELS
# WE SENT MERRIMAN ON 6/11 IS IN THIS NUMBER

school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO")

# All schools: 1938 obs.

schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY")

# Elementary schools: 1751 obs.

ele <- subset(df_panel, minor_type == "ELEMENTARY")

# Secondary Schools: 187 obs.

sec <- subset(df_panel, minor_type == "SECONDARY")

# All munis: 1700 obs.

munis <- subset(df_panel, minor_type == "MUNI")

# HR Munis: 1051 obs.

muni_hr <- subset(df_panel, minor_type == "MUNI" & home_rule_ind == 1)

# NHR munis: 685 obs.

muni_nhr <- subset(df_panel, minor_type == "MUNI" & home_rule_ind == 0)

colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")
  
```

We have panel data and thus even a naive model needs to account for serial correlation of error terms and heteroskedasticity.

I considered three options:

1.  Pooled OLS model

2.  Random effects model

3.  Fixed-effects model (TWFE)

I communed with Wooldridge (2018) and am comfortable we want to use a TWFE model as our "naive" model. Here, a RE model is more efficient than a pooled OLS model because it removes some of the serial correlation in the error term that plagues time series data.

Then, for choosing between a RE and TWFE model, I selected TWFE to avoid the need to incorporate any sort of time-related control variables.

I selected HC5 as my HC-estimator because Chicago generates high-leverage observations.

## All Agencies

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

```{r twfe_all_naive}

all_agencies_naive <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = df_panel)

#summary(school_muni_naive)

# hr_all_subset <- subset(df_panel, home_rule_ind == 1)
# 
# nhr_all_subset <- subset(df_panel, home_rule_ind == 0)
# 
# naive_mod_all_hr <- plm(log_levy ~ log_av,
#                          model = "within",
#                          effect = "twoways",
#                          data = hr_all_subset)
# 
# naive_mod_all_nhr <- plm(log_levy ~ log_av,
#                          model = "within",
#                          effect = "twoways",
#                          data = nhr_all_subset)


all_agencies_summ_table <- 
  export_summs(all_agencies_naive,
               model.names = c("All Agencies"),
                                robust = "HC5",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#school_muni_summ_table <- set_caption(school_muni_summ_table, "All Agencies, Dependant Variable: ln(levy)")

print(all_agencies_summ_table)

```

## Municipalities

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

```{r twfe_muni_naive}

muni_subset <- subset(df_panel, minor_type == "MUNI" | agency_name == "TOWN CICERO")

naive_mod_munis <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)

hr_subset <- subset(df_panel, home_rule_ind == 1 & (minor_type == "MUNI" | agency_name == "TOWN CICERO"))

nhr_subset <- subset(df_panel, home_rule_ind == 0 & (minor_type == "MUNI" | agency_name == "TOWN CICERO"))

naive_mod_muni_hr <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = hr_subset)

naive_mod_muni_nhr <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = nhr_subset)


muni_summ_table <- 
  export_summs(naive_mod_munis, naive_mod_muni_hr, naive_mod_muni_nhr,
               model.names = c("All Municipalities", "HR Municipalities", "NHR Municipalities"),
                                robust = "HC3",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_summ_table <- set_caption(muni_summ_table, "Municipalities, Dependant Variable: ln(levy)")

print(muni_summ_table)

```

## Schools

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

There are five types of school taxing agencies: elementary, secondary, community colleges, miscellaneous, and unified. Elementary school districts make up the overwhelming majority of these taxing agencies.

```{r school_distr}

school_summary <- df |>
  filter(major_type == "SCHOOL") |>
  filter(year == 2021) |>
  group_by(minor_type) |>
  rename("School Type" = minor_type) |>
  summarize(n = n())

bar_colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")

ggplot(school_summary, aes(x = `School Type`, y = n, fill = `School Type`)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = bar_colors) +
  ylim(0, 125) +
  theme_minimal() +
  labs(title = "School Agencies by Type (2021)",
       x = "Type of School",
       y = "n") +
  theme(legend.position = "none") +
  geom_text(aes(label = n), vjust = -0.5, size = 3)

```

The community college, miscellaneous, and unified observations are omitted from the "Elementary & Secondary Schools" regression model.

```{r twfe_school_naive}

#school_subset <- subset(df_panel, major_type == "SCHOOL")

school_naive <- plm(log_levy ~ log_av,
                        model = "within",
                         effect = "twoways",
                         data = schools)

# ele_school_subset <- subset(df_panel, major_type == "SCHOOL" 
#                               & minor_type == "ELEMENTARY")

ele_naive <- plm(log_levy ~ log_av,
                            model = "within",
                            effect = "twoways",
                            data = ele)

#second_school_subset <- subset(df_panel, minor_type == "SECONDARY")

sec_naive <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = sec)

# no_other_school_subset <- subset(df_panel, major_type == "SCHOOL" 
#                        & minor_type != c("COMM COLL", "MISC", "UNIFIED"))
# 
# naive_mod_no_misc_school <- plm(log_levy ~ log_av,
#                                model = "within",
#                                effect = "twoways",
#                                data = no_other_school_subset)

school_summ_table <- export_summs(school_naive, ele_naive, sec_naive,
             model.names = c("Elementary & Secondary", "Elementary", "Secondary"),
             robust = "HC5",
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#school_table <- set_caption(school_summ_table, "Schools by Type, Dependant Variable: ln(levy)")

print(school_summ_table)

```

The "Elementary & Secondary Schools" model excludes "misc", community colleges, and unified school districts.

Alea and I are trying to figure out why the magnitude of log_av's coefficient plummets when secondary and elementary schools are broken out from each other. That outcome is consistent with the coefficients seen in the random effects models below used as a robustness check.

## Municipalities & Schools

Since our focus is on municipalities and schools, I reran the model while only retaining those agency types.

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

```{r twfe_schools_munis_naive}

muni_school_subset <- subset(df_panel, major_type == "SCHOOL" | minor_type == "MUNI" | agency_name == "TOWN CICERO")

muni_school_hr <- subset(muni_school_subset, home_rule_ind == 1)

muni_school_nhr <- subset(muni_school_subset, home_rule_ind == 0)

naive_muni_school <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_subset)

naive_muni_school_hr <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_hr)

naive_muni_school_nhr <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_nhr)

muni_school_table <- export_summs(naive_muni_school, naive_muni_school_hr, naive_muni_school_nhr,
             model.names = c("Municipalities & Schools", "Municipalities & Schools (HR)", "Municipalities & Schools (NHR)"),
             robust = "HC3",
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_school_table <- set_caption(muni_school_table, "Schools & Municipalities, Dependant Variable: ln(levy)")

print(muni_school_table)

```


