---
title: "Descriptive Stats for Levy Project Data"
warning: false
format:
  html:
    df-print: paged
    code-fold: true
    tbl-cap-location: margin
    toc: true
    toc-location: left
---

# Questions/Comments so I don't forget them.

- I looked at the names of minor_type = "INFRA" (it isn't a citation to something further down the document)
-- They are 22 infrastructure funds, one for each county. We probs want to call them "infrastructure" and group them with the counties?
- Did we want to filter out total_final_levy > 1 as late as line ~135?
- I think ~line 146 has the filter messing things up. I comment more on that _infra_.
- The obs we want to drop for the models would be filtered from the "munis" df with the filter: filter(!grouped_label %in% munis$grouped_label)
-- I don't know exactly how to apply that to df_panel

# Data Prep

```{r setup, warning=FALSE, message=FALSE, output = FALSE}
library(modelsummary)
library(tidyverse)
library(janitor)
library(dplyr)
library(fixest)
library(sandwich)
```


```{r}
#| label: dataprep

southtriad <- c("Berwyn", "Bloom", "Bremen", "Calumet", "Cicero", "Lemont",
                "Lyons", "Oak Park", "Orland", "Palos", "Proviso", "Rich", 
                "River Forest", "Riverside", "Stickney", "Thornton", "Worth")

northtriad <- c("Barrington", "Elk Grove","Evanston", "Hanover", "Leyden", 
                "Maine", "New Trier", "Niles", "Northfield", "Norwood Park", 
                "Palatine", "Schaumburg", "Wheeling")

df <- read_csv("panel_data.csv")   ## 10,374

df <- df |> filter(!minor_type %in% c("BOND", "UNIFIED", "COMM COLL", 
                                      "COOK", "MISC", "SANITARY", "FIRE",
                                      "MOSQUITO", "WATER") ) # 9,051 obs
# MVH & AWM obs match


df <- df |> 
  filter(year > 2009)  |>   ## 6922 obs MVH: 6922

  # Change infinite values from tfl % delta to 0
  mutate(tfl_pct_change = if_else(is.na(tfl_pct_change) |
                                    is.infinite(tfl_pct_change),
                                  0, tfl_pct_change))


df <- df |> 
  select(-c(muni_name, muni_num, agency_w_hr, first6_w_hr, 
            log_eav:reassess_lag2, 
            lag_eav_pct_change1:lag_av_pct_change2)) %>%
  mutate_at(c("home_rule_ind"), as.character)  %>%
  # Code Cicero as a Municipality and not a township.
  mutate(minor_type = ifelse(agency_name == "TOWN CICERO", "MUNI", minor_type)) %>%
  
  # Rosemont and its school district have huge jump 
  # in tax base and levy due to TIF expiring
  filter(!grepl('ROSEMONT|DISTRICT 78', agency_name)) #6883 obs. MVH & AWM match

```

```{r}
#| include: false

df %>% filter(is.na(clean_name))
df %>% filter(is.na(Triad))


```


```{r}
#| label: tbl-agencies-eachyear
#| tbl-cap: Count of each agency type that  existed during each tax year. 

df %>% ungroup () |> 
  group_by(year, minor_type) %>% 
  filter((major_type == "MUNICIPALITY/TOWNSHIP") | major_type == "SCHOOL" | major_type == "MISCELLANEOUS") %>% 
  summarize(count = n()) %>%
  pivot_wider(names_from = year, values_from = count) %>% 
  flextable::flextable()
```


```{r}
#| label: tbl-majortypeagencies-in2022-notpaneldata
#| tbl-cap: "2022 snapshot of agencies that existed. Not from balanced panel data. Agencies such as park, library, are within the MUNI/TOWNSHIP major_type."


datasummary_crosstab(major_type ~home_rule_ind, statistic = 1~1+N, data = df %>% filter(year==2022), output = "flextable")
```


```{r}
#| label: tbl-minortypeagencies-in2022-notpaneldata
#| tbl-cap: "2022 snapshot of agencies that existed. Not from balanced panel data. Agencies such as park, library, etc will be combined with their larger municipality taxing agency."

datasummary_crosstab(minor_type~home_rule_ind, data = df %>%filter(year==2022),  statistic = 1~1+N, output = "flextable")

```


# Descriptive Stats

```{r eval=FALSE}
datasummary_skim(df)
datasummary_skim(df, type  = "categorical")
```

## Grouping Values 

```{r}
after2009 <- df %>% filter(year > 2009) 
df <- after2009 # yes, I suck.

groupies2 <- read_csv("grouped_labels.csv") %>%      
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"))



munis <- df %>% 
    mutate(#agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
         home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         lim_rate = ifelse(is.na(lim_rate), "NA", lim_rate)) |>
    left_join(groupies2, by = c("agency_name", "agency_num")) %>%
  
  # HERE HERE HERE THIS IS THE KEY FILTER THAT NEEDS TO BE CHANGED

 # filter(major_type == "MUNICIPALITY/TOWNSHIP" | minor_type %in% c("LIBRARY", "PARK")) %>% 
                                                                                  # Added old MUNI filter back
 filter(minor_type =="MUNI") %>%
  

  group_by(year, grouped_label) %>% 
  arrange(agency_num) %>%
  summarize(home_rule_ind = mean(as.numeric(home_rule_ind), na.rm=TRUE),
    agency_name = first(agency_name),
            types = paste(list(unique(minor_type)), sep = ", "),

            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
                min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav),
            cty_cook_eav = first(cty_cook_eav),
            cty_total_eav = first(cty_total_eav), 
            av = first(av), ## mistake fixed: was sum, now is first()
            Triad = first(Triad), 
            agency_count = n(),  # Agencies in Grouped
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            rate = sum(total_final_rate, na.rm=TRUE),
            connected_count = n(),
            lim_rate = mean(as.numeric(lim_rate), na.rm=TRUE),
            clean_name = first(clean_name),
                   min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav)
  ) %>%
    mutate(
        dif_group_eav = max_group_eav - min_group_eav,
    conn_agency_flag = ifelse(connected_count > 1, 1, 0),
    log_eav = log(cty_total_eav),
    log_levy = log(total_final_levy),
    log_av =  log(av),
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "03", "Muni", 
                  ifelse(first2_dig == "02", "Township", "Other")),
    town = ifelse( agency_name == c("TOWN EVANSTON", "GENERAL ASSISTANCE EVANSTON",                                  "TOWN CICERO", "GENERAL ASSISTANCE CICERO"), "Muni", town),
    ) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything()) %>% ungroup() %>%
  filter(grepl("MUNI|TOWN", types))



grouped_manual <- df %>% 
    mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
         home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         lim_rate = ifelse(is.na(lim_rate), "NA", lim_rate)) |>
  
  left_join(groupies2,
            by = c("agency_name", "agency_num")) %>%
  
    filter(!grouped_label %in% munis$grouped_label) %>%
  filter((major_type == "MUNICIPALITY/TOWNSHIP"  
         & minor_type != "MISC") |  major_type == "MISCELLANEOUS") %>% # I think this is the analogous filter to remove
    arrange(agency_num) %>%

  group_by(year, grouped_label, home_rule_ind) %>% 
  summarize(agency_name = first(agency_name),
            types = paste(list(unique(minor_type)), sep = ", "), #Filtering off of this! Here goes nothing!
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
                min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav),
            cty_cook_eav = first(cty_cook_eav),
            cty_total_eav = first(cty_total_eav), 
            av = first(av), ## mistake fixed: was sum, now is first()
            Triad = first(Triad), 
            agency_count = n(),  # Agencies in Grouped
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            rate = sum(total_final_rate, na.rm=TRUE),
            connected_count = n(),
            lim_rate = mean(as.numeric(lim_rate), na.rm=TRUE),
            clean_name = first(clean_name),
            min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav)
  ) %>%
 # filter(!types %in% "MUNI") |> #AND TRY UNCOMMENTING THIS OUT!
  mutate(
        dif_group_eav = max_group_eav - min_group_eav,
    conn_agency_flag = ifelse(connected_count > 1, 1, 0),
    log_eav = log(cty_total_eav),
    log_levy = log(total_final_levy),
    log_av =  log(av),
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02", "Town", 
                  ifelse(first2_dig == "03", "Muni", "Other")),
    town = ifelse( agency_name == "TOWN CICERO", "Muni", town)) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything()) %>% ungroup() 



schools <- df %>% 
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
         home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         lim_rate = ifelse(is.na(lim_rate), "NA", lim_rate)) |>
  
  filter(major_type == "SCHOOL") %>%
  mutate(grouped_label = agency_name) %>%
  group_by(year, grouped_label, home_rule_ind) %>% 
  summarize(agency_name = first(agency_name),
            types = paste(list(unique(minor_type)), sep = ", "),

            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
            min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav),
            cty_total_eav = first(cty_total_eav), 
            cty_cook_eav = first(cty_cook_eav),
            av = first(av), 
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            rate = sum(total_final_rate, na.rm=TRUE), 
            connected_count = n(),
            lim_rate = sum(as.numeric(lim_rate), na.rm=TRUE),
            clean_name = first(clean_name),
  ) %>%
  mutate(
    dif_group_eav = max_group_eav - min_group_eav,
    conn_agency_flag = ifelse(connected_count > 1, 1, 0),      
    log_eav = log(cty_total_eav),
    log_levy = log(total_final_levy),
    log_av =  log(av),
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
    first2_dig = str_sub(agency_num, 1,2),
    town = "School") %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything()) %>% ungroup() 


grouped_manual %>%  
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
 
#139 schools
schools %>%  
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())

 
munis %>%  
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
```

```{r}
grouped_bind <- rbind(munis, schools) %>%
  filter(grouped_label != "drop") %>%
      mutate(home_rule_ind = ifelse(home_rule_ind > 0, 1, 0),
             uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled)) %>%
  arrange(uniqueid, year) %>%
   group_by(year, town, grouped_label) %>% 
  arrange(agency_num) %>%
  summarize(home_rule_ind = mean(as.numeric(home_rule_ind), na.rm=TRUE),
    agency_name = first(agency_name),
            types = paste(list(unique(types)), sep = ", "),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE),
            min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav),
            cty_cook_eav = first(cty_cook_eav),
            cty_total_eav = first(cty_total_eav), 
            av = first(av), ## mistake fixed: was sum, now is first()
            Triad = first(Triad), 
            agency_count = sum(agency_count),  # Agencies in Grouped
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            rate = sum(rate, na.rm=TRUE),
            connected_count = sum(agency_count),
            lim_rate = mean(as.numeric(lim_rate), na.rm=TRUE),
            clean_name = first(clean_name),
                   min_group_eav = min(cty_cook_eav),
            max_group_eav = max(cty_cook_eav)
  ) %>%
  mutate(
        dif_group_eav = max_group_eav - min_group_eav,
    conn_agency_flag = ifelse(connected_count > 1, 1, 0),
    log_eav = log(cty_total_eav),
    log_levy = log(total_final_levy),
    log_av =  log(av),
    bundled = ifelse(agency_count > 1, 1, 0))%>% 
  mutate(uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled)) %>%
  select(year, uniqueid, everything()) %>% ungroup() %>%
    mutate(town = ifelse(grepl("Cicero|Evanston", uniqueid), "Muni", town))


grouped_bind %>%  
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())

grouped_manual <- grouped_bind 

table(grouped_manual$town)


pop2 <- readxl::read_xlsx("Necessary_Files/populationcounts_cookcountyil.xlsx")

pop2 <- pop2 %>% 
  mutate(Name = case_when(
    Name == "Forest View" ~ "Forestview",
    Name == "East Hazel Crest" ~ "East Hazelcrest",
    Name == "Hazel Crest" ~ "Hazelcrest",
    Name == "McCook" ~ "Mc Cook",
    Name == "Mount Prospect" ~ "Mt Prospect",
    Name == "Northlake" ~ "North Lake",
    TRUE~as.character(Name)
  )
  )
grouped_manual <- grouped_manual %>% 
  filter(year > 2009) %>%
  left_join(pop2, by = c("clean_name" = "Name")) 

grouped_manual <- grouped_manual %>% 
  mutate(ext_percap = case_when(
    year < 2015 ~ round(total_final_levy/pop2010),
    year >= 2015 ~ round(total_final_levy/pop2020)),
    
    taxbase_percap = case_when(
      year < 2015 ~ round(cty_cook_eav/pop2010),
      year >= 2015 ~ round(cty_cook_eav/pop2020)),
    
    tax_rate = round(total_final_levy / cty_cook_eav, digits=4) # tax rate that would come from agency_dt instead of manually calculated from PIN level.
  )

#library(plm)

df_panel <- grouped_manual %>% 
  ungroup() %>% 
  arrange(uniqueid, year)  


write_csv(df_panel, "model_data_Sept172024.csv")

df_panel %>% 
  group_by(uniqueid, year) %>% 
  summarize(count = n()) %>%  
  filter(count > 1)

```

```{r}
#| label: tbl-agencies-eachyear_paneldata
#| tbl-cap: Count of each agency type that  existed during each tax year. 

df_panel %>% ungroup() %>% group_by(year, town) %>% 
  summarize(count = n()) %>%
  pivot_wider(names_from = year, values_from = count) %>% flextable::flextable()
```

# Presentation Tables

## Table 1: Name and Number of Taxing Agencies


```{r}
#| label: tbl-majortypeagencies-in2022-paneldata
#| tbl-cap: "2022 snapshot of agencies that existed. From panel data. Agencies such as park, library, are within the MUNI/TOWNSHIP major_type."


datasummary_crosstab(town ~home_rule_ind, statistic = 1~1+N, 
                     data = df_panel %>% filter(year==2022), output = "flextable")
```


## Table 2: Levy and Levy Growth

### Per Capita

```{r}
#| label: tbl-levyperperson
#| tbl-cap: "Growth in the levy per person from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022. Only Municipalities have population counts, so only they are included in the per capita tables."

# agency level growth:
levy_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           !is.na(ext_percap) ) %>% 
  select(year, clean_name, ext_percap) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
               values_from = "ext_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  arrange(desc(pct_growth)) %>%  
  filter(!is.na(pct_growth))
 

levy_table %>% DT::datatable(
  rownames = FALSE,
  options = list(
    dom = 't',
    scrollX = TRUE, # Enable horizontal scrolling
    columnDefs = list(
      list(targets = 1:2
      ),
      list(targets = 1:2, width = '50px')
    )
  ))
```

```{r}
levy_table %>% 
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  geom_vline(aes(xintercept = mean(pct_growth, na.rm=TRUE), color = "Mean"))+ 
  geom_vline(aes(xintercept = median(pct_growth, na.rm=TRUE), color = "Median")) + 
  theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", 
       title = "Distribution of Growth Rates", subtitle = "Levy per Capita from 2010 to 2022", 
       caption = "Median value/capita in 2022 = $645. 
       Mean value/capita = $1139.")
```


```{r}
#| label: tbl-levyperpersonmedian
#| tbl-cap: "Median levy per person from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022."


levy_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Levy per Capita` = median(`2010`, na.rm=TRUE),
    `2010 Mean Levy per Capita` = mean(`2010`, na.rm=TRUE),

    `2010 Levy StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Levy per Capita` = median(`2022`, na.rm=TRUE),
    `2022 Mean Levy per Capita` = mean(`2022`, na.rm=TRUE),

    `2022 Levy StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Growth of Levy per Capita` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Levy per Capita` = round(mean(pct_growth, na.rm=TRUE), digits = 2),

    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE)),
    `# of Agencies` = n()
  ) |>
  mutate(across(where(is.numeric), round, digits = 1)) %>%
  
  pivot_longer(cols = c(`2010 Median Levy per Capita`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE)

```


### Total Levy



```{r}
#| label: tbl-extgrowth
#| tbl-cap: "**Growth in total levy** from 2010 to 2022. Uses summed `total_final_levy` for grouped munis and townships."

levy_table <- df_panel %>% 
  filter(year == 2010 | year == 2022 ) %>% 
  filter(!is.na(total_final_levy)) %>%
  select(year, uniqueid, total_final_levy) %>% 
  pivot_wider( id_cols = "uniqueid", names_from = "year", 
               values_from = "total_final_levy") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  arrange(desc(pct_growth)) %>% 
    filter(!is.na(pct_growth))

levy_table %>%
  DT::datatable(rownames = FALSE)
```


```{r}
df_panel %>% 
  filter((year == 2010 | year == 2022) ) %>% 
  select(year, uniqueid, total_final_levy) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "total_final_levy") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
    filter(!is.na(pct_growth)) %>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", 
       title = "Distribution of Growth Rates",
       subtitle = "Summed Levy per Grouped Agency, 2010 to 2022")

```


```{r}
#| label: tbl-levygrowth_summed_median
#| tbl-cap: "Median levy from 2010 to 2022."



df_panel %>% 
  filter((year == 2010 | year == 2022) ) %>% 
  select(year, uniqueid, total_final_levy) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "total_final_levy") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
    filter(!is.na(pct_growth)) %>%

  ungroup() %>%
  summarize(
    `2010 Median Levy` = median(`2010`, na.rm=TRUE),
    `2010 Mean Levy` = mean(`2010`, na.rm=TRUE),
    `2010 Levy StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Levy` = median(`2022`, na.rm=TRUE),   
    `2022 Mean Levy` = mean(`2022`, na.rm=TRUE),
    `2022 Levy StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Growth of Levy` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Levy` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE)),
    `# of Agencies` = n()
  ) |>
  mutate(across(where(is.numeric), round, digits = 1)) %>%
  
  pivot_longer(cols = c(`2010 Median Levy`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE)

```

### Levy CAGR

```{r}
current_year <- 2022

df_panel <- df_panel %>% mutate(uniqueid = as.character(uniqueid),
                                year = as.character(year))

levysumms <- df_panel %>% group_by(year) %>% summarize(total_final_levy = sum(total_final_levy, na.rm=TRUE))
# function for calculating the CAGR
calc_cagr <- function(df, n) {
  df <- levysumms %>%
     arrange(year) %>%
   # group_by(uniqueid) %>%
    mutate(cagr = ((`total_final_levy` / lag(`total_final_levy`, n)) ^ (1 / n)) - 1)

  return(df)
}

# 2011 to 2022 is 12 years of data
cagr_12 <- calc_cagr(levysumms, 12) %>% 
    filter(year == as.numeric(as.character(current_year))) %>%
  summarize(cagr_12 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_10 <- calc_cagr(levysumms, 10) %>% 
    filter(year == as.numeric(as.character(current_year))) %>%
  summarize(cagr_10 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_5 <- calc_cagr(levysumms, 5) %>% 
  filter(year == as.numeric(as.character(current_year))) %>%
  summarize(cagr_5 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_3 <- calc_cagr(levysumms, 3) %>% 
  filter(year == current_year) %>%
  summarize(cagr_3 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_2 <- calc_cagr(levysumms, 2) %>% 
  filter(year == current_year) %>%
  summarize(cagr_2 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_1 <- calc_cagr(levysumms, 1) %>% 
  filter(year == current_year) %>%
  summarize(cagr_1 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

# update variables so cagr_24 becomes cagr_25
CAGR_levies <- data.frame(cagr_1, cagr_2, cagr_3, cagr_5, cagr_10, cagr_12 ) %>% 
  #select(-c(uniqueid.1, uniqueid.2, uniqueid.3, uniqueid.4, uniqueid.5 )) %>% 
  rename(#"Unique ID" = uniqueid, 
         "1 Year CAGR" = cagr_1, "2 Year CAGR" = cagr_2, "3 Year CAGR" = cagr_3, "5 Year CAGR" = cagr_5, "10 Year CAGR" = cagr_10, "12 Year CAGR" = cagr_12)


CAGR_levies %>%   
  DT::datatable(rownames = FALSE) 

```



## Table 3: Tax Base and Tax Base Growth

### Per Capita
```{r}
#| label: tbl-table3
#| tbl-cap-location: top
#| tbl-cap: "Tax Base Summary Statistics (per capita), 2010 and 2022. Median change  calculated from agency level change and then locating the median value of growth. For muni taxing agencies that share taxing jurisdiction (have the same tax base EAV) with municipality taxing agencies, then the "

# agency level growth:
taxbase_table <- df_panel %>% 
  filter((year == 2010 | year == 2022) & 
           !is.na(taxbase_percap )
         ) %>% 
  select(year, clean_name, taxbase_percap) %>% 
  pivot_wider( id_cols = c("clean_name"), names_from = "year", 
               values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
    filter(!is.na(pct_growth)) %>%

  arrange(desc(pct_growth)) 

taxbase_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Tax Base per Capita` = median(`2010`, na.rm=TRUE),
    `2010 Mean Tax Base per Capita` = mean(`2010`, na.rm=TRUE),
    `2010 Tax Base StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Tax Base per Capita` = median(`2022`, na.rm=TRUE),
    `2022 Median Tax Base per Capita` = mean(`2022`, na.rm=TRUE),
    `2022 Tax Base StdDv` = round(sd(`2022`, na.rm=TRUE)),
    `Median Growth of Tax Base per Capita` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Tax Base per Capita` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
    
  ) |>
  mutate(across(where(is.numeric), round)) %>%
  
  pivot_longer(cols = c(`2010 Median Tax Base per Capita`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE)

```

```{r}
taxbase_table %>% 
  ggplot() + geom_histogram(aes(x=pct_growth)) + theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", title = "Tax Base per Capita (in EAV) Growth, 2010 to 2022")
```

```{r} 
#| label: tbl-taxbasegrowth-percap
#| tbl-cap: "Growth in the **tax base per capita** from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2022."

df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  filter(!is.na(clean_name)) %>%
  select(year, clean_name, taxbase_percap) %>% 
  pivot_wider(id_cols = "clean_name", names_from = "year", 
              values_from = "taxbase_percap") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  filter(!is.na(pct_growth)) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```



### Tax Base (in EAV) Growth

```{r}
#| label: tbl-taxbasegrowth
#| tbl-cap: "**Growth in the tax base** from 2010 to 2022. Uses 2010 population counts for 2010 and 2020 population counts for 2020."

taxbase_table <- df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  select(year, uniqueid, cty_cook_eav) %>% 
  pivot_wider(id_cols = "uniqueid", names_from = "year", 
              values_from = "cty_cook_eav") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  mutate(across(where(is.numeric), round, digits = 2)) %>%  
  filter(!is.na(pct_growth))


taxbase_table %>%
  arrange(desc(pct_growth)) %>% 
  DT::datatable(rownames = FALSE)


```


```{r}
df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
 # filter(town == "Muni" ) %>% 
  select(year, uniqueid, cty_cook_eav) %>% 
  pivot_wider(id_cols = "uniqueid", names_from = "year", 
              values_from = "cty_cook_eav") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  filter(!is.na(pct_growth)) %>%

  ungroup() %>%
  summarize(
    `2010 Median Tax Base` = median(`2010`, na.rm=TRUE),
    `2010 Mean` = mean(`2010`, na.rm=TRUE),
    `2010 Tax Base StdDv` = (sd(`2010`, na.rm=TRUE)),
    `2022 Median Tax Base` = median(`2022`, na.rm=TRUE),
    `2022 Mean` = mean(`2022`, na.rm=TRUE),
    `2022 Tax Base StdDv` = round(sd(`2022`, na.rm=TRUE)),
    `Median Growth of Tax Base` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Growth of Tax Base` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
  ) |>
  mutate(across(where(is.numeric), round)) %>%
  
  pivot_longer(cols = c(`2010 Median Tax Base`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  
  DT::datatable(rownames = FALSE) %>%
                DT::formatRound('value', mark = ",", digits = 0) 

```

```{r}
taxbase_table %>% 
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + theme_classic() + 
  labs(x = "Growth %", y = "Agency Count", 
       title = "Growth in Tax Base (in EAV), 2010 to 2022")
```

### CAGR 

First year is 2011, last year is 2022.

```{r}
current_year <- 2022
taxbasessums <- df_panel %>% group_by(year) %>% 
  summarize(cty_cook_eav = sum(cty_cook_eav, na.rm=TRUE))

# function for calculating the CAGR
calc_cagr <- function(df, n) {
  df <- taxbasessums %>%
     arrange(year) %>%
  #  group_by(uniqueid) %>%
    mutate(cagr = ((`cty_cook_eav` / lag(`cty_cook_eav`, n)) ^ (1 / n)) - 1)

  return(df)
}

# 2011 to 2022 is 12 years of data
cagr_12 <- calc_cagr(taxbasessums, 12) %>% 
    filter(year == as.numeric(as.character(current_year))) %>%
  summarize(cagr_12 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_10 <- calc_cagr(taxbasessums, 10) %>% 
    filter(year == as.numeric(as.character(current_year))) %>%
  summarize(cagr_10 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_5 <- calc_cagr(taxbasessums, 5) %>% 
  filter(year == as.numeric(as.character(current_year))) %>%
  summarize(cagr_5 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_3 <- calc_cagr(taxbasessums, 3) %>% 
  filter(year == current_year) %>%
  summarize(cagr_3 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_2 <- calc_cagr(taxbasessums, 2) %>% 
  filter(year == current_year) %>%
  summarize(cagr_2 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

cagr_1 <- calc_cagr(taxbasessums, 1) %>% 
  filter(year == current_year) %>%
  summarize(cagr_1 = case_when(year == current_year ~ round(sum(cagr*100, na.rm = TRUE), 2)))

# update variables so cagr_24 becomes cagr_25
CAGR_taxbase <- data.frame(cagr_1, cagr_2, cagr_3, cagr_5, cagr_10, cagr_12 ) %>% 
 # select(-c(uniqueid.1, uniqueid.2, uniqueid.3, uniqueid.4, uniqueid.5 )) %>% 
  rename(#"Unique ID" = uniqueid, 
         "1 Year CAGR" = cagr_1, "2 Year CAGR" = cagr_2, "3 Year CAGR" = cagr_3, "5 Year CAGR" = cagr_5, "10 Year CAGR" = cagr_10, "12 Year CAGR" = cagr_12)


CAGR_taxbase%>%   
  DT::datatable(rownames = FALSE) 

```


## Table 4: Tax Rate and Tax Rate Growth

```{r}
#| label: tbl-taxrate-table
#| tbl-cap: "Tax Rate Growth for Grouped Taxing Agencies, 2010 to 2022"


# agency level growth:
rate_table <- df_panel %>% 
  filter((year == 2010 | year == 2022)) %>% 
  filter(!is.na(clean_name)) %>%
  select(year, uniqueid, rate) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  mutate(across(where(is.numeric))) %>%
  arrange(desc(pct_growth)) %>%  
  filter(!is.na(pct_growth))


rate_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Rate` = median(`2010`, na.rm=TRUE),
    `2010 Mean Rate` = mean(`2010`, na.rm=TRUE),
    `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
    `2022 Median Rate` = median(`2022`, na.rm=TRUE),
    `2022 Mean Rate` = mean(`2022`, na.rm=TRUE),
    `2022 Rate StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Mean Rate Growth` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
    
  ) |>
  mutate(across(where(is.numeric), round, digits = 2)) %>%
  pivot_longer(cols = c(`2010 Median Rate`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  flextable::flextable(cwidth = 1.5)
```

```{r}
df_panel %>% 
  filter((year == 2010 | year == 2022)) %>% 
  filter(!is.na(clean_name)) %>%
  select(year, uniqueid, rate) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ))%>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  labs(y = "# of Agencies", x = '% Growth',
       title = "Distribution of Tax Rate Growth",
       subtitle = "Municipality Taxing Agencies, 2010 to 2022")+
  theme_classic()

```


```{r}
#| label: tbl-taxrate-table-grouped
#| tbl-cap: "Tax Rate Growth for Grouped Taxing Agencies, 2010 to 2022"


# agency level growth:
rate_table <- df_panel %>% 
  filter((year == 2010 | year == 2022)) %>% 
  select(year, uniqueid, rate) %>% 
  pivot_wider( id_cols = c("uniqueid"), names_from = "year", 
               values_from = "rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) )) %>%
  mutate(across(where(is.numeric))) %>%
  arrange(desc(pct_growth)) 

rate_table %>% 
  ungroup() %>%
  summarize(
    `2010 Median Rate` = median(`2010`, na.rm=TRUE),
    `2010 Mean Rate` = mean(`2010`, na.rm=TRUE),
    `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
    `2022 Median Rate` = median(`2022`, na.rm=TRUE),
    `2022 Mean Rate` = mean(`2022`, na.rm=TRUE),
    `2022 Rate StdDv` = round(sd(`2022`, na.rm=TRUE), digits = 2),
    `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
    `Growth StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
    `# of Agencies` = n()
    
  ) |>
  pivot_longer(cols = c(`2010 Median Rate`:`# of Agencies`),  
               names_to = "statistic", values_to = "value") |>
  flextable::flextable(cwidth = 1.5)
```

```{r}
rate_table %>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  labs(y = "# of Agencies", x = '% Growth',
       title = "Distribution of Tax Rate Growth",
       subtitle = "Grouped Taxing Agencies, 2010 to 2022")+
  theme_classic()

```


```{r}
#| label: tbl-agencylevy-taxrates-notgrouped
#| tbl-cap: "Tax rates shown come from the `total_final_rate` variable within PTAXSIM's internal `agency` data table. It comes from the total_final_levy / cty_cook_eav. Not grouped!"

df_panel %>% 
  filter(year == 2010 | year == 2022) %>% 
  select(year, agency_name, rate) %>% 
  pivot_wider(id_cols = "agency_name", names_from = "year", values_from = "rate") %>%   
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 2) ),
         `2022` = (round(`2022`, digits = 2) ) ) %>%

  arrange(desc(`2022`)) %>% 
  DT::datatable(rownames = FALSE)
```

### Not Grouped

```{r}

rate_table <- df |>
  filter(!is.na(total_final_rate)) |>
  filter(year %in% c("2010", "2022")) |>
  select(year, minor_type, agency_name, total_final_rate) %>% 
  pivot_wider( id_cols = c("minor_type", "agency_name"), names_from = "year", 
              values_from = "total_final_rate") %>% 
  mutate(pct_growth = (round((`2022`-`2010`)/`2010` * 100, digits = 1) ) ) %>%
  arrange(desc(pct_growth))  

rate_table  |> DT::datatable(rownames = FALSE)


rate_table |>
    ungroup() %>%
    group_by(minor_type) |>

   summarize(
            `2010 Median Rate` = round(median(`2010`, na.rm=TRUE), digits = 2),
            `2010 Mean Rate` = round(mean(`2010`, na.rm=TRUE), digits = 2),
            `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits = 2),
            `2022 Median Rate` = round(median(`2022`, na.rm=TRUE), digits = 2),
            `2022 Mean Rate` = round(mean(`2022`, na.rm=TRUE), digits = 2),
            `2010 Rate StdDv` = round(sd(`2010`, na.rm=TRUE), digits =2),
            `Median Rate Growth` = round(median(pct_growth, na.rm=TRUE), digits = 2),
            `Mean Rate Growth` = round(mean(pct_growth, na.rm=TRUE), digits = 2),
            `StdDv` = round(sd(pct_growth, na.rm=TRUE), digits = 2),
           `# of Agencies` = n()) |> 
  flextable::flextable()
```

```{r}
rate_table %>%
  ggplot() + 
  geom_histogram(aes(x=pct_growth)) + 
  labs(y = "# of Agencies", x = '% Growth',
       title = "Distribution of Tax Rate Growth",
       subtitle = "All Taxing Agencies, 2010 to 2022")+
  theme_classic()
```

# Models


A is given assessment year's taxed AV and B is the next year's taxed AV.

alpha = ( square root (B/A ) ) - 1

*Changed 9/23 by MVH. Should be:*

r = cube_root(B/A) - 1

```{r merriman_model_w_triads}

df_temp <- read_csv("model_data_Sept212024.csv") %>% 
  ungroup() %>%
  group_by(uniqueid) %>% 
  arrange(year)%>% 
  mutate(rate = ifelse(reassess_year == 1 & !is.na(lead(av,3)), (lead(av, 3) / av)^(1/3) - 1, NA)) %>%
  select(year, reassess_year, uniqueid, grouped_label, av, cty_cook_eav, agency_count, rate, everything()) %>% 
  arrange(uniqueid, year) %>%
  fill(rate, .direction = "down") %>%
  mutate(av_true = av*(1+rate), .before = av)
  
  
```

```{r triad_merriman_data_expl}

df_temp |>
  filter(is.na(rate)) |>
  group_by(year) |>
  summarize(n = n())

df_temp |>
  filter(year != "2010") |>
  filter(is.na(rate)) |>
  select(agency_name) |>
  distinct()

df_temp |>
  filter(year == "2011") |>
  filter(is.na(rate)) |>
  summarize()

df_temp |>
  filter(year == "2012") |>
  filter(is.na(rate)) |>
  summarize()

df_temp |>
  filter(is.na(rate)) |>
  group_by(year) |>
  summarize(sum(av), n = n())

df_temp_2 <- df_temp |>
  mutate(av_true = ifelse(is.na(av_true) & reassess_year == "1" & !is.na(av), av, av_true))

df_temp_2 |>
  filter(is.na(av_true)) |>
  group_by(year, triad_name) |>
  summarize(n = n())

df_mmm <- df_temp_2 |>
  filter(year >= 2012)

df_mmm <- panel(df_mmm, panel.id = c("uniqueid", "year"))

```
```{r merriman_models-withlogs}



mods_nw <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) + log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                ),
  
  "EAV" = feols(log(total_final_levy) ~ log_eav + log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                ),
  
    "EAV Interact" = feols(log(total_final_levy) ~ log_eav + log(av_true) + log_eav*log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                )
  )

modelsummary::modelsummary(
  mods_nw,
  output = "flextable",
 #gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

mods_iid <- list(
  
  "AV (iid)" = feols(log(total_final_levy) ~ log(av) + log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                ),
  
  "AV Interact (iid)" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                ),
  
  "EAV (iid)" = feols(log(total_final_levy) ~ log_eav + log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                ),
  
    "EAV Interact (iid)" = feols(log(total_final_levy) ~ log_eav + log(av_true) + log_eav*log(av_true) | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                )
  )


modelsummary::modelsummary(
  mods_iid,
  output = "flextable",
 #gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

```{r merriman_models}



mods_1 <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) + av_true | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + av_true + log(av)*av_true | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                ),
  
  "EAV" = feols(log(total_final_levy) ~ log_eav + av_true | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                ),
  
    "EAV Interact" = feols(log(total_final_levy) ~ log_eav + av_true + log_eav*av_true | uniqueid + year,
               data = df_mmm,
               vcov = "newey_west",
               panel.id = c("uniqueid", "year")
                )
  )

modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

mods_iid <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) + av_true | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + av_true + log(av)*av_true | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                ),
  
  "EAV" = feols(log(total_final_levy) ~ log_eav + av_true | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                ),
  
    "EAV Interact" = feols(log(total_final_levy) ~ log_eav + av_true + log_eav*av_true | uniqueid + year,
               data = df_mmm,
               vcov = "iid",
               panel.id = c("uniqueid", "year")
                )
  )


modelsummary::modelsummary(
  mods_iid,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

```{r visualizing_mm_data}

df_mmm |>
  ggplot(aes(x = log(av), y = log(av_true))) +
  geom_point() +
  geom_abline() +
  theme_classic()


```

- vcov options in modelsummary: robust, classical, HC3, bootstrap
- vcov options in feols(): newey_west, hc1, etc.

- gof_omit options in modelsummary: 

-gof_map to exclude specific goodness of fit measures   
- gof_omit to exclude specific measures.   

-vcov options: HC, HC0, HC1(aka Stata's), HC2, HC3(robust, R default in plm package), HC4, HC5, HAC, and more.

```{r}
df_panel <- read_csv("model_data_Sept212024.csv")
```

## Trying to deal with reassessment cycles

> Wait until info for school taxing agencies with their triad is collected. Less observations in these tables due to many agencies not having a triad associated with them until manually merged in.

```{r eval=FALSE}
library(fixest)

models <- list(
  twfe = feols(log(total_final_levy) ~ log(av) + triad_name + reassess_year | uniqueid + year, panel.id = c("uniqueid", "year"), vcov = "newey_west",  data = df_panel),

triadbyyear_fe = feols(log(total_final_levy) ~ log(av) + l(log(av), 1) + l(log(av), 2 ) | uniqueid + year^triad_name,vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),

triad_dummy = feols(log(total_final_levy) ~ log(av) + l(log(av), 1) + l(log(av), 2 ) + triad_name | triad_name + uniqueid + year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),

twfe_lags = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | uniqueid + year^triad_name, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel) )

modelsummary(
  models,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)
```


## TWFE Models 

```{r}
library(fixest)

models <- list(
  "Plain TWFE" = feols(log(total_final_levy) ~ log(av)  | uniqueid + year,  data = df_panel, vcov = "newey_west", panel.id = c("uniqueid", "year")),
  
        "TWFE - year^reassess" = feols(log(total_final_levy) ~ log(av)  | uniqueid + year^reassess_year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),
      
      "TWFE - year^lagreassess" = feols(log(total_final_levy) ~ log(av)  | uniqueid + year^l(reassess_year,1),vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),
      
  "TWFE w/ AV Lags" = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | uniqueid + year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),


 "TWFE - interaction" = feols(log(total_final_levy)~ log(av) + l(log(av),1)*reassess_year + l(log(av),1)
   +i(reassess_year, l(log(av)) )
   | uniqueid + year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),

     "TWFE - Agency Type" = feols(log(total_final_levy)~ log(av) + l(log(av), 1:2) + i(town, log(av)) | uniqueid + year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel)
  
  )


modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)

# year coefficients
fixef(models$`Plain TWFE`)[[2]]
fixef(models$`TWFE - Agency Type`)[[2]]



```

```{r}
models <- list(
  twfe_slopes = feols(log(total_final_levy) ~ log(av) + reassess_year | uniqueid + year, vcov = "newey_west",  panel.id = c("uniqueid", "year"), data = df_panel),

  year_reassess_fe = feols(log(total_final_levy) ~ log(av) + l(log(av), 1) + l(log(av), 2 ) | uniqueid + year^reassess_year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),

  triad_dummy = feols(log(total_final_levy) ~ log(av) + log(av)*triad_name | uniqueid + year, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel),

  id_yearTriad_fe = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | uniqueid + year^triad_name, vcov = "newey_west", panel.id = c("uniqueid", "year"), data = df_panel) 
)

modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)

```


```{r}
#| warning: false
#| message: false


models <- list(
  est1 = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid + year, data = df_panel, panel.id = c("uniqueid", "year")),
  
  est_twowayse = feols(log(total_final_levy) ~ log(av)  + l(log(av), 1:2)  | uniqueid + year , data = df_panel, panel.id = c("uniqueid", "year"), vcov = "twoway"),
  
    est_twoway_nwse = feols(log(total_final_levy) ~ log(av)  + l(log(av), 1:2)  | uniqueid + year , data = df_panel, panel.id = c("uniqueid", "year"), vcov = "newey_west")
  )

modelsummary(
  models,
  output = "flextable",
 # gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)
```


### Main Models 

```{r}
#| label: tbl-AllAgencies-leads
#| tbl-cap: "All taxing agencies remaining in sample with agency and year fixed effects."
#| warning: false
#| message: false

models <- list(
  
    'All Agencies Remaining' = feols(log(total_final_levy) ~ log(av) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel, vcov = "newey_west"),
  

  'All Agencies Remaining - Leads' = feols(log(total_final_levy) ~ log(av) + f(log(av), 1:2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel, vcov = "newey_west"),
  
  'All Agencies Remaining - Leads +' = feols(log(total_final_levy) ~ log(av) + f(log(av), 1:2)*reassess_year*triad_name | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel, vcov = "newey_west")
  
  

                 )

modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)

```



```{r}
#| label: tbl-AllAgencies
#| tbl-cap: "All taxing agencies remaining in sample with agency and year fixed effects."
#| warning: false
#| message: false

models <- list(
  
    'All Agencies Remaining' = feols(log(total_final_levy) ~ log(av) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel, vcov = "newey_west"),
  

  'All Agencies Remaining - Lags' = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel, vcov = "newey_west")
  

                 )

modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)

```


**Subset by Muni, Town, and Schools**

```{r}
#| label: tbl-uniqueidyearFE
#| tbl-cap: "UniqueID and year fixed effects."



models <- list(
  
  Munis = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), 
                data = df_panel %>% filter(town=="Muni"), vcov = "newey_west"
                ),
  
   'Homerule Muni' = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni" & home_rule_ind==1), vcov = "newey_west"
                      ),
  
     'Non-HR Muni' = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni" & home_rule_ind==0), vcov = "newey_west"
                     ),
  
  # Township = feols(log(total_final_levy) ~ log(av) + l(log(av), 1:2)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Township"), vcov = "newey_west"
  #              ),
   # Other = feols(log(total_final_levy) ~ log(av) + l(log(av), 1:2)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Other"), vcov = "newey_west"
   #             ),

  Schools = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid + year, panel.id = c("uniqueid", "year"),  vcov = "newey_west", 
                 data = df_panel %>% filter(town=="School"))
  )

modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)

```

```{r}
#| label: tbl-uniqueidyearHrandnonHR
#| tbl-cap: "UniqueID and year fixed effects."


models <- list(
  
  Munis = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), 
                data = df_panel %>% filter(town=="Muni"), vcov = "newey_west"
                ),
  
   'Homerule Muni' = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter((town=="Muni" | town == "Other") & home_rule_ind==1), vcov = "newey_west"
                      ),
  
     'Non-HR Muni' = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter((town=="Muni" | town == "Other") & home_rule_ind==0), vcov = "newey_west"
                     ),
  
  # Township = feols(log(total_final_levy) ~ log(av) + l(log(av), 1:2)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Township"), vcov = "newey_west"
  #              ),

  Schools = feols(log(total_final_levy) ~ log(av) + l(log(av)) + l(log(av), 2)  | uniqueid + year, panel.id = c("uniqueid", "year"),  vcov = "newey_west", 
                 data = df_panel %>% filter(town=="School"))
  )

modelsummary(
  models,
  output = "flextable",
 # gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

```{r}
#| label: tbl-uniqueidyearFE-noLags
#| tbl-cap: "**Log(Levy)~Log(AV):** UniqueID and Year fixed effects."


models <- list(
  Munis = feols(log(total_final_levy) ~ log(av)  | uniqueid + year, panel.id = c("uniqueid", "year"), 
                data = df_panel %>% filter(town=="Muni" & year > 2011), vcov = "newey_west"
                ),
  
   'Homerule Muni' = feols(log(total_final_levy) ~ log(av)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni" & home_rule_ind==1 & year > 2011), vcov = "newey_west"
                      ),
  
     'Non-HR Muni' = feols(log(total_final_levy) ~ log(av)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Muni" & home_rule_ind==0  & year > 2011), vcov = "newey_west"
                     ),
 

  # Township = feols(log(total_final_levy) ~ log(av)  | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Township" & year > 2011), vcov = "newey_west"
  #              ),
     # Other = feols(log(total_final_levy) ~ log(av) | uniqueid + year, panel.id = c("uniqueid", "year"), data = df_panel %>% filter(town=="Other" & year > 2011), vcov = "newey_west"
     #           ),

  Schools = feols(log(total_final_levy) ~ log(av) | uniqueid + year, panel.id = c("uniqueid", "year"),  vcov = "newey_west", 
                 data = df_panel %>% filter(town=="School" & year > 2011))
  )

modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)

```


> Schools are still always different than Towns or Municipalities




