---
title: "ABFM Naive Levy Elasticity Models"
author: "MVH & AWM"
date: "July 19, 2024"
format: 
  html:
    embed-resources: true
    theme: minty
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 200px
---

```{r setup}
#| output: FALSE

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(modelsummary)
library(tidyverse)
library(kableExtra)
library(glue)
library(DT)
library(flextable)

set_flextable_defaults(theme_fun = theme_vanilla, 
                       padding = 2,
                       line_spacing = 1,
                       big.mark = ",",
                       )

options(DT.options = list())

set_summ_defaults(digits = 2, pvals = FALSE, robust = "HC5")

```

# Data Description

Our data ("panel_data.csv") is generated on line 187 of the "helper_recode_variables.R" file, which queries, filters, and manipulates variables from the PTAXSIM DB. It is the same data we have been using since February EXCEPT for the models we ran in April, where we used "grouped" taxing agencies.

SSAs are excluded from our sample.

Chicago is included in our sample.

```{r}
#| label: load_paneldata
#| output: false
#| eval: false

# import 8178 observations

df <- read_csv("panel_data.csv") |>
  # First column of csv is empty?
  select(-1) |>
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()

# Convert to panel data (8178 obs)

df_panel <- pdata.frame(df, index = c("agency_num", "year"))

# Balance the panel -> now 7599 obs (lost 579)

is.pbalanced(df_panel)

# df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")

# Subset: schools and munis - 3655 obs.
# NOTE: BALANCING THE PANEL & LIMITING SCHOOL SAMPLE DROPS 194 OF THESE OBS, 
# THE DIFFERENCE FROM THE MODELS
# WE SENT MERRIMAN ON 6/11 IS IN THIS NUMBER

school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO")

# All schools: 1938 obs.

schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY")

# Elementary schools: 1751 obs.

ele <- subset(df_panel, minor_type == "ELEMENTARY")

# Secondary Schools: 187 obs.

sec <- subset(df_panel, minor_type == "SECONDARY")

# All munis: 1700 obs.

munis <- subset(df_panel, minor_type == "MUNI")

# HR Munis: 1051 obs.

muni_hr <- subset(df_panel, minor_type == "MUNI" & home_rule_ind == 1)

# NHR munis: 685 obs.

muni_nhr <- subset(df_panel, minor_type == "MUNI" & home_rule_ind == 0)

colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")
  
```

```{r}
#| label: tryFMVdata
#| output: false


df <- read_csv("panel_data.csv")

muni_fmv <- read_csv("Necessary_Files/ptaxsim_muni_level_2006-2022.csv") 

df <- left_join(df, muni_fmv) |>
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()

# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("agency_num", "year"))
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
# df_panel <- make.pbalanced(df_panel, balance.type = "fill")


# Convert to panel data (10,181 obs)
# df_panel <- pdata.frame(df, index = c("clean_name", "year"))
# df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")

df_panel <- pdata.frame(df, index = c("agency_num", "year"))
df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")



# Balance the panel -> now 9758 obs 

#is.pbalanced(df_panel)



# Subset: schools and munis - 4250 obs.
# NOTE: BALANCING THE PANEL & LIMITING SCHOOL SAMPLE DROPS 194 OF THESE OBS, 
# THE DIFFERENCE FROM THE MODELS
# WE SENT MERRIMAN ON 6/11 IS IN THIS NUMBER

school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO")

# All schools: 2380 obs.

schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY")

# Elementary schools: 1938 obs.

ele <- subset(df_panel, minor_type == "ELEMENTARY")

# Secondary Schools: 442 obs.

sec <- subset(df_panel, minor_type == "SECONDARY")

# All munis: 1870 obs.

munis <- subset(df_panel, minor_type == "MUNI"| agency_name == "TOWN CICERO")

# HR Munis: 1202 obs.

muni_hr <- subset(df_panel,(minor_type == "MUNI" | agency_name == "TOWN CICERO")& home_rule_ind == 1)

# NHR munis: 668 obs.

muni_nhr <- subset(df_panel, (minor_type == "MUNI" | agency_name == "TOWN CICERO")& home_rule_ind == 0)

```

# Naive Model

```{r}
#| label: load_paneldata_duplicate
#| output: false

# import 10,181 observations

df <- read_csv("panel_data.csv") |>
  # Rename select variables
  rename(levy = total_final_levy) |>
  # Filter out zero levies
  filter(levy > 0) |>
  # Convert to data frame
  as.data.frame()

# Convert to panel data (10,181 obs)

df_panel <- pdata.frame(df, index = c("agency_num", "year"))

# Balance the panel -> now 9758 obs

#is.pbalanced(df_panel)

df_panel <- make.pbalanced(df_panel, balance.type = "shared.individuals")
#is.pbalanced(df_panel)

# Subset: schools and munis - 3655 obs.
# NOTE: BALANCING THE PANEL & LIMITING SCHOOL SAMPLE DROPS 194 OF THESE OBS, 
# THE DIFFERENCE FROM THE MODELS
# WE SENT MERRIMAN ON 6/11 IS IN THIS NUMBER

school_muni <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY" | minor_type == "MUNI" | agency_name == "TOWN CICERO")
#is.pbalanced(school_muni)

# All schools: 1938 obs.

schools <- subset(df_panel, minor_type == "ELEMENTARY" | minor_type == "SECONDARY")
#is.pbalanced(schools)

# Elementary schools: 1751 obs.

ele <- subset(df_panel, minor_type == "ELEMENTARY")

# Secondary Schools: 187 obs.

sec <- subset(df_panel, minor_type == "SECONDARY")

# All munis: 1700 obs.

munis <- subset(df_panel, minor_type == "MUNI")
#is.pbalanced(munis)

# HR Munis: 1051 obs.

muni_hr <- subset(df_panel, (minor_type == "MUNI" | clean_name == "Cicero")  & home_rule_ind == 1)
#is.pbalanced(muni_hr)

# NHR munis: 685 obs.

muni_nhr <- subset(df_panel, (minor_type == "MUNI" | clean_name == "Cicero")& home_rule_ind == 0)

colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")
  
```


## All Agencies

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

```{r twfe_all_naive}

all_agencies_naive <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = df_panel)
#summary(school_muni_naive)

# hr_all_subset <- subset(df_panel, home_rule_ind == 1)
# 
# nhr_all_subset <- subset(df_panel, home_rule_ind == 0)
# 
# naive_mod_all_hr <- plm(log_levy ~ log_av,
#                          model = "within",
#                          effect = "twoways",
#                          data = hr_all_subset)
# 
# naive_mod_all_nhr <- plm(log_levy ~ log_av,
#                          model = "within",
#                          effect = "twoways",
#                          data = nhr_all_subset)


all_agencies_summ_table <- 
  export_summs(all_agencies_naive,
               model.names = c("All Agencies"),
                                robust = "HC5",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#school_muni_summ_table <- set_caption(school_muni_summ_table, "All Agencies, Dependant Variable: ln(levy)")

all_agencies_summ_table

```

## Municipalities

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

```{r twfe_muni_naive}

muni_subset <- subset(df_panel, minor_type == "MUNI" | agency_name == "TOWN CICERO")
muni_subset<- make.pbalanced(muni_subset)

#is.pbalanced(muni_subset)

naive_mod_munis <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = muni_subset)

hr_subset <- subset(df_panel, home_rule_ind == 1 & (minor_type == "MUNI" | agency_name == "TOWN CICERO"))
hr_subset<- make.pbalanced(hr_subset)
#is.pbalanced(hr_subset)

nhr_subset <- subset(df_panel, home_rule_ind == 0 & (minor_type == "MUNI" | agency_name == "TOWN CICERO"))
nhr_subset<- make.pbalanced(nhr_subset)
#is.pbalanced(nhr_subset)

naive_mod_muni_hr <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = hr_subset)

naive_mod_muni_nhr <- plm(log_levy ~ log_av,
                         model = "within",
                         effect = "twoways",
                         data = nhr_subset)


muni_summ_table <- 
  export_summs(naive_mod_munis, naive_mod_muni_hr, naive_mod_muni_nhr,
               model.names = c("All Municipalities", "HR Municipalities", "NHR Municipalities"),
                                robust = "HC3",
                                statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_summ_table <- set_caption(muni_summ_table, "Municipalities, Dependant Variable: ln(levy)")

muni_summ_table

```

## Schools

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::

There are five types of school taxing agencies: elementary, secondary, community colleges, miscellaneous, and unified. Elementary school districts make up the overwhelming majority of these taxing agencies.

```{r school_distr}

school_summary <- df |>
  filter(major_type == "SCHOOL") |>
  filter(year == 2021) |>
  group_by(minor_type) |>
  rename("School Type" = minor_type) |>
  summarize(n = n())

bar_colors <- c("#264653", "#2a9d8f", "#e9c46a", "#f4a261", "#e76f51")

ggplot(school_summary, aes(x = `School Type`, y = n, fill = `School Type`)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = bar_colors) +
  ylim(0, 125) +
  theme_minimal() +
  labs(title = "School Agencies by Type (2021)",
       x = "Type of School",
       y = "n") +
  theme(legend.position = "none") +
  geom_text(aes(label = n), vjust = -0.5, size = 3)

```

The community college, miscellaneous, and unified observations are omitted from the "Elementary & Secondary Schools" regression model.

```{r twfe_school_naive}

#school_subset <- subset(df_panel, major_type == "SCHOOL")

school_naive <- plm(log_levy ~ log_av,
                        model = "within",
                         effect = "twoways",
                         data = schools)

# ele_school_subset <- subset(df_panel, major_type == "SCHOOL" 
#                               & minor_type == "ELEMENTARY")

ele_naive <- plm(log_levy ~ log_av,
                            model = "within",
                            effect = "twoways",
                            data = ele)

#second_school_subset <- subset(df_panel, minor_type == "SECONDARY")

sec_naive <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = sec)

# no_other_school_subset <- subset(df_panel, major_type == "SCHOOL" 
#                        & minor_type != c("COMM COLL", "MISC", "UNIFIED"))
# 
# naive_mod_no_misc_school <- plm(log_levy ~ log_av,
#                                model = "within",
#                                effect = "twoways",
#                                data = no_other_school_subset)

school_summ_table <- export_summs(school_naive, ele_naive, sec_naive,
             model.names = c("Elementary & Secondary", "Elementary", "Secondary"),
             robust = "HC5",
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#school_table <- set_caption(school_summ_table, "Schools by Type, Dependant Variable: ln(levy)")

school_summ_table

```

The "Elementary & Secondary Schools" model excludes "misc", community colleges, and unified school districts.



## Municipalities & Schools

Since our focus is on municipalities and schools, I reran the model while only retaining those agency types.

::: callout-note
All models include time and agency fixed effects and use HC5 heteroskedasticity-consistent standard errors.
:::


```{r twfe_schools_munis_naive}

muni_school_subset <- subset(df_panel, major_type == "SCHOOL" | minor_type == "MUNI" | agency_name == "TOWN CICERO")
#is.pbalanced(muni_school_subset)

muni_school_hr <- subset(muni_school_subset, home_rule_ind == 1)   # 1219
#is.pbalanced(muni_school_hr)
muni_school_hr <- make.pbalanced(muni_school_hr, "shared.individuals")     ## 1156
#is.pbalanced(muni_school_hr)

muni_school_nhr <- subset(muni_school_subset, home_rule_ind == 0)  # 3269
#is.pbalanced(muni_school_nhr)    
muni_school_nhr <- make.pbalanced(muni_school_nhr, "shared.individuals")   # 3213 
#is.pbalanced(muni_school_nhr)    

naive_muni_school <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_subset)

naive_muni_school_hr <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_hr)

naive_muni_school_nhr <- plm(log_levy ~ log_av,
                               model = "within",
                               effect = "twoways",
                               data = muni_school_nhr)

muni_school_table <- export_summs(naive_muni_school, naive_muni_school_hr, naive_muni_school_nhr,
             model.names = c("Municipalities & Schools", "Municipalities & Schools (HR)", "Municipalities & Schools (NHR)"),
             robust = "HC3",
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

#muni_school_table <- set_caption(muni_school_table, "Schools & Municipalities, Dependant Variable: ln(levy)")

muni_school_table

```


