---
title: "Revenue Elasticity for Cook County Municipalities"
author: "AWM & MVH"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float: yes
    df_print: paged
    code_folding: hide
subtitle: Using total_final_levy
---

```{r setup, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(DBI)
#library(data.table)
#library(ggspatial)
#library(gstat)
#library(here)
#library(httr)
#library(jsonlite)
library(ptaxsim)
#library(sf)
library(stars)
#library(glue)
library(lmtest)
library(huxtable) # for summ() and regression output formatting
# Create the DB connection with the default name expected by PTAXSIM functions
library(jtools)
library(plm) #for fixed effects
library(modelsummary)
library(dplyr)

#ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2022.0.0.db")
#set_summ_defaults(digits = 2, pvals = FALSE, robust = "HC3" )


# Data notes for pct_res: 
# muni av and eav are calculated from the pin data table in ptaxsim. It is BEFORE exemptions and includes any EAV that is above the frozen TIF EAV, frozen EAV, and EAV outside of TIF tax codes.
# percentages for land use are also before exemptions and do not consider any EAV that would go to a TIF increment

#groupies <- readxl::read_excel("./grouped_munis_manual_entry.xlsx")

# muni_agency_names <- DBI::dbGetQuery(
#   ptaxsim_db_conn,
#   "SELECT DISTINCT agency_num, agency_name, minor_type
#   FROM agency_info
#   WHERE minor_type = 'MUNI'
#   OR agency_num = '020060000'
#   "
#   ) %>% 
#   mutate(first6 = str_sub(agency_num,1,6),
#         # first5 = str_sub(agency_num,1,5)
#          ) %>%
#   select(-minor_type)

```

From agency.R code in ptaxsim Gitlab "The levy of each jurisdiction is reported by the Cook County Clerk's Office. URL here: <https://www.cookcountyclerkil.gov/service/tax-extension-and-rates>


# Data Gathering and Cleaning



## Manipulated Variables

```{r message = FALSE, warning = FALSE}
source("helper_recode_variables.R")
```

```{r}

library(dplyr)

all_agencies <- recoded_data

```


# Models for All Taxing Agencies

Includes schools, and miscellaneous taxing agencies all together. Only for comparison. Excludes SSAs and Cook County taxing agencies.

```{r}
table(all_agencies$major_type)

detach("package:dplyr", unload = TRUE)

all_m1_simple<- plm(log(total_final_levy_4log) ~ log(cty_total_eav), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = all_agencies)
#summary(all_m1_simple)

all_m1_lags<- plm(log(total_final_levy_4log) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = all_agencies)

# 
# model_names <- c( all_m1_simple = "All Agencies FE, Naive Levy Requested", 
#                   all_m1_lags = "With Lagged EAV"
#                  # all_m1 = "Leads & Lags"
#                   )
# 
# export_summs(all_m1_simple, all_m1_lags,# all_m1, #, all_m1_all_vars, 
#              robust = "HC3",  model.names = model_names, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))


```
```{r AV-version, include = FALSE}


av_simple<- plm(log(total_final_levy_4log) ~ log(av), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = all_agencies)
#summary(all_m1_simple)

av_lags<- plm(log(total_final_levy_4log) ~ log(av) + lag(log(av), 1) + lag(log(av),2), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = all_agencies)


model_names <- c( av_simple = "All Agencies FE, Naive Levy Requested", 
                  av_lags = "With Lagged EAV"
                 # all_m1 = "Leads & Lags"
                  )

export_summs(av_simple, av_lags,# all_m1, #, all_m1_all_vars, 
             robust = "HC3",  model.names = model_names, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))


```

```{r}

m1 <- plm(log(total_final_levy_4log) ~ log(cty_total_eav), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = panel_data)


m2<- plm(log(total_final_levy_4log) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = panel_data)
  
  
m3<-  plm(log(total_final_levy_4log) ~ log(cty_total_eav)*up_down, 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = panel_data)


m4 <- plm(log(summed_levy_first6) ~ log(cty_total_eav)*up_down  + lag(log(cty_total_eav), 1)*up_down + lag(log(cty_total_eav),2)*up_down, 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = governments_panel) 


```


__With Homerule Indicator & log(EAV) Interaction__

```{r}
all_agencies <- panel_data 



all_m1_simple<- plm(log(total_final_levy_4log) ~ log(cty_total_eav) + home_rule_ind:log(cty_total_eav), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = all_agencies)


all_m1_lags<- plm(log(total_final_levy_4log) ~ log(cty_total_eav)  + home_rule_ind + home_rule_ind:log(cty_total_eav) +  lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
             index = c("agency_name", "year"), 
             model = "within", effect = "twoways",                    
             data = all_agencies)


all_m1<- plm(log(total_final_levy_4log) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
             index = c("agency_name", "year"),
             model = "within", effect= "twoways",
             data = all_agencies)

model_names <- c(m1 = "ALL gencies ", 
                m2= "ALL agencies with lags",
                m3 = "Asymmetric Model",
                all_m1_simple = "All Agencies FE, with Interaction", 
                all_m1_lags = "and Add in Lagged EAV",
                m4 = "Governments Panel"

                  )

export_summs(m1, m2, m3, all_m1_simple, all_m1_lags, m4, model.names = model_names,
             statistics = c(N = "nobs",adj.R2 = "adj.r.squared", R2 = "r.squared"))
```

# Grouped by grouped_label from CSV

Uses manually coded labels that combine both methods of grouping taxing agencies: 

taxing agencies that could be grouped by either the first 6 digits of their  shared tax base (EAV equal during a tax year)

```{r}
library(dplyr)

library(openxlsx)
groupies2 <- read.xlsx("grouped_agencies_28Nov2023.xlsx") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
                                                                        
         first6 = as.character(first6)) #add missing leading zeros


groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))
                                                                        

```

```{r}
library(dplyr)

table(recoded_data$reassess_year, recoded_data$minor_type)

grouped_manual <- recoded_data %>% 
  left_join(groupies2,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP" # | major_type == "MISCELLANEOUS"
           & minor_type != "MISC"
           ) %>%
  filter(minor_type != "SSA") %>% 
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE)+1,
            cty_total_eav = first(cty_total_eav), 
            av = sum(av, na.rm=TRUE),
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind)) %>% 
    left_join(muni_agency_names) %>% 
    #select(-c(Column1, `Most recent reassessed`)) %>% 
    mutate(
      log_eav = log(cty_total_eav),
      log_levy = log(total_final_levy),
      bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything())



 grouped_manual %>%  # 236 nonHR and 68 HR
  ungroup() %>%
  filter(year == 2021) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
```

72 nonHR and 65 HR if only majortype munis is included. 

```{r}

# 1552 obs
grouped_manual_has16 <- grouped_manual %>%  # 124 nonHR and 69 HR
  ungroup() %>%
 # filter(year == 2021) %>%
  arrange(home_rule_ind) %>%
  group_by(uniqueid) %>%
  distinct() %>%
  mutate(count = n()) %>%
  filter(count == 16) %>% ungroup()


grouped_manual_has16 %>% ggplot() + 
  geom_line(aes(x=year,y=total_final_levy, group = uniqueid, alpha = .5, color = home_rule_ind)) + 
  theme_classic()


grouped_manual_has16 %>% ggplot() + 
  geom_line(aes(x=year,y=total_final_levy, group = uniqueid, alpha = .5, color = home_rule_ind)) + 
  facet_wrap(~home_rule_ind) +
  theme_classic() 

grouped_manual_has16 %>% ggplot() + 
  geom_point(aes(x=year, y=total_final_levy,# color = home_rule_ind, 
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = uniqueid, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, # 
                  group = home_rule_ind,
                 # group = grouped_w_hr_ind, 
                  color = home_rule_ind), se=FALSE, size = 2) + 
  theme_classic()

grouped_manual_has16 %>% ggplot() + 
  geom_point(aes(x=year, y=total_final_levy,# color = home_rule_ind, 
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = uniqueid, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, # 
                  group = home_rule_ind,
                 # group = grouped_w_hr_ind, 
                  color = home_rule_ind), se=FALSE, size = 2) + 
  facet_wrap(~home_rule_ind) +
  theme_classic()
```


```{r}

detach("package:dplyr", unload = TRUE)

grouped_munis <- pdata.frame(grouped_manual_has16, index = c("uniqueid", "year")) 

table(grouped_munis$year)
grouped_munis <- make.pbalanced(grouped_munis)
is.pbalanced(grouped_munis)
table(grouped_munis$year)

grouped_munis$eav_lag1  <- plm::lag(grouped_munis$log_eav, 1)
grouped_munis$av_lag  <- plm::lag(grouped_munis$av, 1)

grouped_munis$eav_lag2  <- plm::lag(grouped_munis$log_eav, 2)

grouped_munis$cty_eav_lag  <- plm::lag(grouped_munis$cty_total_eav, 1)

# 
# grouped_munis$reassess_lag1 <- plm::lag(grouped_munis$reassess_year, 1)
# grouped_munis$reassess_lag2 <- plm::lag(grouped_munis$reassess_year, 2)
# 
# 
# grouped_munis$reassess_lead1 <- plm::lead(grouped_munis$reassess_year, 1)
# grouped_munis$reassess_lead2 <- plm::lead(grouped_munis$reassess_year, 2)
        
library(dplyr)
grouped_munis <- grouped_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag),
         av_change = av - av_lag,
         av_pct_change = (av-av_lag)/av_lag
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

# All Agencies-Agency & Year FE"
grouped_model<- plm(log(total_final_levy) ~ log(cty_total_eav), 
                   # index = c("grouped_w_hr_ind", "year"), 
                    model = "within", 
                    effect= "twoways",                    
                    data = grouped_munis)






grouped_cleannames_withHRind <- plm(log(total_final_levy) ~ log(cty_total_eav)+ log(cty_total_eav):home_rule_ind, 
                        #  index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind)

grouped_cleannames_withHRind_lagged <- plm(log(total_final_levy) ~ log(cty_total_eav)+ log(cty_total_eav):home_rule_ind + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2), 
                          #index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind_lagged)

grouped_cleannames_lag <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
                          #index = c("grouped_w_hr_ind", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)

grouped_cleannames_lag2 <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2)+log(cty_total_eav):home_rule_ind + lag(log(cty_total_eav),1):home_rule_ind  + lag(log(cty_total_eav),2):home_rule_ind ,
#                          index = c("uniqueid", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)
#summary(grouped_cleannames_lag2)


model_names <- c(grouped_model = "Grouped manually, Summed Levies", 
                 grouped_cleannames_lag = "with Lags",
                 grouped_cleannames_withHRind = "with HR Indicator",
                 grouped_cleannames_withHRind_lagged = "HR indacator with Lags",
                grouped_cleannames_lag2 = "HR interact with both Lags") # has Chicago


# plot(grouped_model)


export_summs(grouped_model, grouped_cleannames_lag,  grouped_cleannames_withHRind, grouped_cleannames_withHRind_lagged, grouped_cleannames_lag2, robust = "HC3",  model.names = model_names, statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))



```

When using the grouped_labels csv to identify agencies that should be grouped, then there are 124 nonHR and 69 HR grouped taxing districts.

## Homerule Taxing Agencies
```{r}
 
library(dplyr)

homerule_minortype_munis <- grouped_manual %>% 
  filter(home_rule_ind == 1)

homerule_minortype_munis <- pdata.frame(homerule_minortype_munis, index = c("agency_name", "year"))

homerule_minortype_munis <- make.pconsecutive(homerule_minortype_munis)

detach("package:dplyr", unload = TRUE)

homerule_minortype_munis$eav_lag1  <- plm::lag(homerule_minortype_munis$log_eav, 1)
homerule_minortype_munis$eav_lag2  <- plm::lag(homerule_minortype_munis$log_eav, 2)
homerule_minortype_munis$cty_eav_lag  <- plm::lag(homerule_minortype_munis$cty_total_eav, 1)
#homerule_minortype_munis$av_lag  <- plm::lag(homerule_minortype_munis$av, 1)

        
library(dplyr)
homerule_minortype_munis <- homerule_minortype_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

hr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
                          #  index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = homerule_minortype_munis)


hr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

hr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(cty_total_eav)  + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

hr_muni_minor <- plm(log(total_final_levy)  ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2) + up_down*log(cty_total_eav),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

# summary(hr_muni_minor)
model_names = c("Homerule Government Taxing Agencies")

export_summs(hr_muni_minor_simple, #hr_muni_minor_simple0,  
             hr_muni_minor_lags,             hr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}
 
library(dplyr)

nonhr_munis <- grouped_manual %>% 
  filter(home_rule_ind == 0) %>% select(uniqueid, year, everything())

nonhr_munis <- pdata.frame(nonhr_munis, index = c("agency_name", "year"))

nonhr_munis <- make.pconsecutive(nonhr_munis)

detach("package:dplyr", unload = TRUE)

nonhr_munis$eav_lag1  <- plm::lag(nonhr_munis$log_eav, 1)
nonhr_munis$eav_lag2  <- plm::lag(nonhr_munis$log_eav, 2)

nonhr_munis$cty_eav_lag <- plm::lag(nonhr_munis$cty_total_eav, 1)
        
library(dplyr)
nonhr_munis <- nonhr_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

nonhr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
                           # index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = nonhr_munis)


nonhr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
           #  index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

nonhr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(cty_total_eav)  + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

nonhr_muni_minor <- plm(log(total_final_levy)  ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2) + up_down*log(cty_total_eav),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

# summary(hr_muni_minor)
# summary(hr_muni_minor)
model_names = c("Non-HR Government Taxing Agencies")

export_summs(nonhr_muni_minor_simple, # nonhr_muni_minor_simple0, 
             nonhr_muni_minor_lags, 
                      nonhr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```


# Percent change

```{r}
# nonhr_munis

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "between", 
                    effect= "individual",                    
                    data = nonhr_munis) %>% summary()

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "twoways",                    
                    data = nonhr_munis) %>% summary()

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "time",                    
                    data = nonhr_munis) %>% summary()
```


# Other Crap

## Indexed 
```{r levy-indexed, error=TRUE}
library(dplyr)
library(tidyverse)

indexed_munis <- grouped_manual_has16 %>%
#  mutate(year = as.factor(year)) %>%
  ungroup() %>%
 # filter(minor_type == "MUNI") %>%
 # filter(!agency_num %in% dropped_munis & !agency_num %in% exclude_hr_change ) %>% 
  mutate(year = as.character(year),
         agency_name = as.character(agency_name)) %>% 
  group_by(uniqueid) %>% 
  summarize(     # Index values to 2006
    year=year,
    
    eav_idx = cty_total_eav / (cty_total_eav[year == "2006"] ),
    levy_idx = total_final_levy / (total_final_levy[year == "2006"]),
    av_idx = av / (av[year == 2006]),
    Triad = Triad,
    home_rule_ind = home_rule_ind
  )   

indexed_munis %>% 
  ggplot(aes(x=year, y = levy_idx, group = uniqueid, label = uniqueid, color = as.factor(home_rule_ind))) + 
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() + 
  theme_classic()+
 # geom_text(size = 2, vjust=-1.5)+
  facet_wrap(~home_rule_ind)+
  labs(title = "Municipalities:Total Final Levy Indexed to 2006")


indexed_munis %>% ggplot() + 
  geom_line(aes(x=year, y = levy_idx, group = uniqueid, color = Triad), alpha=.5, linetype = "dashed") +
  geom_point(aes(x=year, y = levy_idx), alpha = .1) + 
  theme_classic()+
  facet_wrap(~Triad)+
    labs(title = "Municipalities:Total Final Levy Indexed to 2006")


# indexed_munis %>% ggplot() + geom_line(aes(x=year, y = eav_idx, group = uniqueid, color = as.factor(home_rule_ind)))  +
#   facet_wrap(~home_rule_ind) + 
#   labs(title = "Municipalities: Taxable EAV Indexed to 2006" )
# 

indexed_munis %>% ggplot() + geom_line(aes(x=year, y = av_idx, group = uniqueid, color = as.factor(home_rule_ind)))  +
  facet_wrap(~Triad) + 
  theme(legend.position = "bottom") +
  labs(title = "Municipalities: AV Indexed to 2006" )

indexed_munis %>% ggplot() + geom_line(aes(x=year, y = levy_idx, group = uniqueid, color = Triad)) +  facet_wrap(~Triad) + 
  labs(title = "Municipalities: Total Final Levy Indexed to 2006")

#minortype_munis %>% write_csv("minortype_munis.csv")
```

```{r levy-indexed-schools, error=TRUE}
library(dplyr)

indexed_schools <- recoded_data %>% ungroup() %>%
    filter(major_type == "SCHOOL" ) %>%
 # select( agency_name, year, #total_non_cap_ext, total_capped_ext, 
 #         cty_cook_eav, total_final_levy, home_rule_ind, Triad) %>%
  group_by(agency_name) %>% 
  mutate(years = n()) %>%
  filter(years == 16) %>%
  arrange(year) %>%
    summarize(# Index values to 2006
    eav_idx = cty_cook_eav / cty_cook_eav[year == 2006] ,
    levy_idx = total_final_levy / total_final_levy[year == 2006] ,
    av_idx = av / av[year == 2006],
  #  cappedext_idx = total_capped_ext / total_capped_ext[year == 2006] ,
  #  noncappedext_idx = total_non_cap_ext / total_non_cap_ext[year == 2006] ,
    year = year, home_rule_ind = home_rule_ind,  Triad = Triad) 

indexed_schools %>% ggplot(aes(x=year, y = levy_idx, group = agency_name, label = agency_name)) + 
    geom_line(alpha=.5, linetype = "dashed") +
  geom_point(alpha = .2) + 
  theme_classic()+
  labs(title = "Schools: Total Final Levy Indexed to 2006")


indexed_schools %>% ggplot() + 
  geom_line(aes(x=year, y = eav_idx, group = agency_name), alpha = .3)  +  theme_classic()+

  labs(title = "Schools: Taxable EAV Indexed to 2006" )

indexed_schools %>% ggplot() + 
  geom_line(aes(x=year, y = av_idx, group = agency_name), alpha = .3)  +  theme_classic()+

  labs(title = "Schools: Taxable AV Indexed to 2006" )
```



```{r townships, eval=FALSE, include=FALSE}
## ## Townships   
township_names <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT DISTINCT agency_num, agency_name, minor_type
  FROM agency_info
  WHERE minor_type = 'TOWNSHIP'
  "
  ) %>% 
  mutate(first6 = str_sub(agency_num,1,6),
        # first5 = str_sub(agency_num,1,5)
         ) %>%
  select(-minor_type)

township_names_andEAVs <- recoded_data %>%
  filter(minor_type == "TOWNSHIP") %>%
  select(township_name = agency_name, cty_total_eav)


recoded_data %>% 
  filter(year == 2021) %>%
  dplyr::group_by(as.character(cty_total_eav)) %>%
  dplyr::summarize(repeat_eavs = n()) %>% filter(repeat_eavs > 1) 


township_panel <- recoded_data %>% #filter(year == 2021) %>% 
                      
  left_join(township_names_andEAVs) %>% 
  dplyr::group_by(township_name, year, cty_total_eav) %>%
  dplyr::summarize(grouped_levy = sum(total_final_levy)) %>% filter(!is.na(township_name)) %>%
    mutate( 
    log_eav = log(cty_total_eav),
    log_levy = log(grouped_levy)
    )

panel_data <-pdata.frame(township_panel, index = c("township_name", "year"))
panel_data


townships <- plm(log_levy ~ log(cty_total_eav), 
         #    index = c("agency_name", "year"), 
             model = "within", effect = "twoways",  
             data = panel_data)
summary(townships)

```


## Major Munis

All major type taxing agencies together. 
uses government_panel.

```{r}
library(dplyr)
major_munis <-  governments_panel %>%
  mutate(reassess_year = as.factor(reassess_year))

major_munis <- pdata.frame(governments_panel, index = c("agency_num", "year")) 


detach("package:dplyr", unload = TRUE)

major_munis$reassess_lag1 <- plm::lag(major_munis$reassess_year, 1)
major_munis$reassess_lag2 <- plm::lag(major_munis$reassess_year, 2)

major_munis_naive <- plm(log_levy ~ log(cty_total_eav), 
             index = c("agency_num", "year"), 
             model = "within", effect= "twoways",                    
             data = major_munis)

## individual observations ## 
major_munis_mod <- plm(log_levy ~  log(cty_total_eav)+ lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2), 
             index = c("agency_num", "year"), 
             model = "within", effect= "twoways",                    
             data = major_munis)

major_munis_mod_morevars <- plm(log_levy ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2)*reassess_year + reassess_lag1 + reassess_lag2  + log(cty_total_eav):home_rule_ind +lag(log(cty_total_eav),2):home_rule_ind, 
             index = c("agency_num", "year"), 
             model = "within", effect= "twoways",                    
             data = major_munis)

export_summs(major_munis_naive, major_munis_mod, major_munis_mod_morevars, 
             statistics = c(N = "nobs", R2 = "r.squared"))
```

> Including variables like reassess_year and Triad can only be done with the grouped taxing agencies that have municipality names. The reassessment and triad variables are part of the clean_names file that is merged to the agency name and number (for municipalities only). Otherwise the panel drops a lot of observations since those variables are NAs. 

```{r}
library(dplyr)

## homerule taxing agencies only
homerule_majortype_munis <- governments_panel %>% 
  mutate(year = as.factor(year)) %>%
  filter(home_rule_ind==1 # Homerule only
 ) %>%
   select(year, agency_name, agency_num, major_type, minor_type, 
         cty_total_eav, cty_total_eav, total_final_levy, log_eav, log_levy,
     Triad, reassess_year, home_rule_ind )

major_munis <- pdata.frame(homerule_majortype_munis, index = c("agency_name", "year"))


detach("package:dplyr", unload = TRUE)

major_munis$eav_lag1  <- plm::lag(major_munis$log_eav, 1)
major_munis$eav_lag2  <- plm::lag(major_munis$log_eav, 2)

major_munis$reassess_lag1 <- plm::lag(major_munis$reassess_year, 1)
major_munis$reassess_lag2 <- plm::lag(major_munis$reassess_year, 2)



major_munis_naive <- plm(log_levy ~ log(cty_total_eav), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = major_munis)


hr_muni_major <- plm(log_levy ~ log(cty_total_eav) + lag(log(cty_total_eav),2)+ lag(log(cty_total_eav),1), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = major_munis)
#summary(hr_muni_major)
```


```{r}
library(dplyr)
nonhr_muni_major <- governments_panel %>% 
  mutate(year = as.factor(year)) %>%
  filter(home_rule_ind==0 # Homerule only
 ) %>%
  select(year, agency_name, agency_num, major_type, minor_type, 
         cty_total_eav, cty_total_eav, total_final_levy, log_eav, log_levy,
     Triad, reassess_year, home_rule_ind )

major_munis <- pdata.frame(nonhr_muni_major, index = c("agency_num", "year"))


detach("package:dplyr", unload = TRUE)

major_munis$eav_lag1  <- plm::lag(major_munis$log_eav, 1)
major_munis$eav_lag2  <- plm::lag(major_munis$log_eav, 2)

major_munis$reassess_lag1 <- plm::lag(major_munis$reassess_year, 1)
major_munis$reassess_lag2 <- plm::lag(major_munis$reassess_year, 2)


nonhr_muni_maj <- plm(log_levy ~ log(cty_total_eav) +lag(log(cty_total_eav),2) + lag(log(cty_total_eav),1), 
             index = c("agency_name", "year"), 
             model = "within", effect= "twoways",                    
             data = major_munis)
#summary(nonhr_muni_maj)
```


majortype: Uses all taxing agencies that have a major_type == "MUNI/TOWNSHIP". Includes many more taxing agencies than just the 134 muni taxing agencies.  Split into homerule and nonhomerule. 

Municipality models (minorType) use the 134 municipality taxing agencies from 2006-2021. Split into home rule and non homerule.


```{r}
model_names <- c("All Agencies", "All Major Muni Agencies", "Homerule Muni (MajorType)", "Non-homerule Muni (Major Type)"
                 )
# coefs <- c("","") # to make names nicer

export_summs(all_m1, major_munis_mod, hr_muni_major, nonhr_muni_maj, model.names = model_names, statistics = c(N = "nobs", R2 = "r.squared"))
#export_summs(m1, m2, m3, model.names = model_names, scale=TRUE, robust = "HC1")
```



## More graphs

```{r}
library(dplyr)

cor.test(recoded_data$total_max_levy, recoded_data$total_final_levy)

recoded_data %>% 
  filter(total_final_levy > total_max_levy) %>%  # 2593 obs when filtered
  group_by(minor_type, year) %>% 
  summarize(n = n()) %>% 
  pivot_wider(names_from = "year", values_from = "n")
  
recoded_data %>% 
  filter(total_final_levy < total_max_levy) %>%  # 666 obs when filtered
  group_by(minor_type, year) %>% 
  summarize(n = n()) %>% 
  pivot_wider(names_from = "year", values_from = "n")
```


```{r eval = FALSE}
raw_data_joined %>% # 13,000+ obs ask for the maximum levy amount
  filter(total_final_levy == total_max_levy)

raw_data_joined %>% # 666 obs ask for less than the maximum levy amount 
  filter(total_final_levy < total_max_levy) 

raw_data_joined %>%  # 4 have reduced levys larger than max levys. Not worrying about due to small number of them.
  filter(total_reduced_levy > total_max_levy)

raw_data_joined %>% 
  filter(total_ext > total_max_levy) # 5828 obs collect more than their maximum levy amount 
# maximum levy determined by limit rate * EAV 

raw_data_joined %>% # 7473 obs have  extensions smaller than their maximum levy
  filter(total_ext < total_max_levy) 


raw_data_joined %>% 
  filter(total_reduced_levy == 0 | is.na(total_reduced_levy))

```



```{r}
panel_data %>% ggplot()+
  geom_point(aes(x=log(cty_total_eav), y=log(total_final_levy), col=major_type, alpha=.1)) +
  ggtitle("Logged EAV vs Logged Levy for ALL agencies and all years")
```

### Graphs for Munis only


```{r}
library(dplyr)
#adds cicero, drops chicago
agency_data %>% 
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
         & (minor_type == "MUNI" | agency_num =="020060000")) %>%
  ggplot(aes(x=log(cty_total_eav), y=log(total_final_levy), color=agency_num, group = agency_num))+
  geom_point(alpha=.5) +
theme(legend.position = "none")+
    labs(title = "Logged Values All Years: Municipality EAV & Requested Levy")


agency_data %>% 
  filter(year == 2021) %>%
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) ) %>%
   filter(minor_type == "MUNI" | agency_num == "020060000" | agency_name == "TOWN CICERO") %>%
  ggplot(aes(x=cty_total_eav, y=total_final_levy, col=Triad, label = clean_name))+
  theme_classic()+
  geom_point()+ 
  geom_text(size = 2, vjust=-1.5)+
  labs(title = "2021 levy:eav", caption = "Drops Chicago")



agency_data %>%
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
         & (minor_type == "MUNI" | agency_num =="020060000")) %>%
  filter(Triad == "South")%>%
  ggplot(aes(x=year, 
             y= cty_total_eav, 
             group = agency_num,
            # color = Triad
          # color = reassess_year
               )  )+
  geom_line(alpha = .1)+ 
  theme_classic() + 
  labs(title = "South triad municipalities: \n Homerule & non-Homerule Together", caption = "Drops Chicago")
```

> Reminder that none of these are the bundled levies!

```{r}
agency_data %>% 
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
         & (minor_type == "MUNI" | agency_num =="020060000")) %>%
  ggplot(aes(x=cty_total_eav, y=total_final_levy, group = agency_num, color = Triad))+
  geom_point(alpha=.5) +
theme(legend.position = "none")+
    labs(title = "Muni EAV & Levy Values, All Years")




agency_data %>% 
  filter((minor_type == "MUNI" | agency_num =="020060000") & Triad == "South" & home_rule_ind == 0) %>%
  ggplot(aes(x=year, y=total_final_levy, group = agency_num))+
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() + 
  theme_classic() + 
  geom_vline(aes(xintercept= "2008" ))+
    geom_vline(aes(xintercept= "2011"))+
    geom_vline(aes(xintercept = "2014"))+
    geom_vline(aes(xintercept= "2017"))+
    geom_vline(aes(xintercept = "2020"))+
theme(legend.position = "none")+
    labs(title = "Non-homerule South Triad: Muni Levy Values All Years",
         cation = "vertical lines are for reassessment years. Levy values apear on tax bills 1 year after the reassessment year. ")


agency_data %>% 
  filter((minor_type == "MUNI" | agency_num =="020060000")) %>%
    filter(Triad == "South" & home_rule_ind == 1) %>%
  ggplot(aes(x=(year), y=total_final_levy, group = agency_name))+
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() +   theme_classic() + 
    geom_vline(aes(xintercept= "2008" ))+
    geom_vline(aes(xintercept= "2011"))+
    geom_vline(aes(xintercept = "2014"))+
    geom_vline(aes(xintercept= "2017"))+
    geom_vline(aes(xintercept = "2020"))+
theme(legend.position = "none")+
    labs(title = "Homerule South Triad: Muni Levy Values All Years",  cation = "vertical lines are for reassessment years. Levy values apear on tax bills 1 year after the reassessment year. ")

agency_data %>% 
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
         & (minor_type == "MUNI" | agency_num =="020060000")) %>%
  filter(Triad == "North" & home_rule_ind ==1) %>%
  ggplot(aes(x=year, y=total_final_levy, group = agency_name))+
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() +   theme_classic() +
      geom_vline(aes(xintercept= "2007" ))+
    geom_vline(aes(xintercept= "2010"))+
    geom_vline(aes(xintercept = "2013"))+
    geom_vline(aes(xintercept= "2016"))+
    geom_vline(aes(xintercept = "2019"))+
theme(legend.position = "none")+
    labs(title = "Homerule North Triad: Muni Levy Values All Years")

agency_data %>% 
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
         & (minor_type == "MUNI" | agency_num =="020060000")) %>%
  filter(Triad == "North" & home_rule_ind ==0) %>%
  ggplot(aes(x=year, y=total_final_levy, group = agency_name))+
  geom_line(alpha=.5, linetype = "dashed") +
        geom_vline(aes(xintercept= "2007" ))+
    geom_vline(aes(xintercept= "2010"))+
    geom_vline(aes(xintercept = "2013"))+
    geom_vline(aes(xintercept= "2016"))+
    geom_vline(aes(xintercept = "2019"))+
  geom_point() +   theme_classic() +
theme(legend.position = "none")+
    labs(title = "Non-homerule North Triad: Muni Levy Values All Years")



```


```{r error=TRUE}
agency_data %>% 
  filter(#!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
       #  & 
           (minor_type == "MUNI" | agency_num =="020060000") & Triad == "South" & home_rule_ind == 0) %>%
  ggplot(aes(x=year, y=total_final_levy, group = agency_num, color = Township))+
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point( )+
  theme_classic() + 
    geom_vline(aes(xintercept = "2008")) +
    geom_vline(aes(xintercept = "2011")) +
    geom_vline(aes(xintercept = "2014")) +
    geom_vline(aes(xintercept = "2017")) +
    geom_vline(aes(xintercept = "2020")) +
theme(legend.position = "none") +
    labs(title = "Non-homerule South Triad: Muni Levy Values All Years")


agency_data %>% 
  filter((minor_type == "MUNI" | agency_num =="020060000") & Triad == "South" & home_rule_ind == 0) %>%
  ggplot(aes(x=year, y=total_final_levy, group = agency_num, color = Township))+
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() + 
  theme_classic() + 
    geom_vline(aes(xintercept= "2008" ))+
    geom_vline(aes(xintercept= "2011"))+
    geom_vline(aes(xintercept = "2014"))+
    geom_vline(aes(xintercept= "2017"))+
    geom_vline(aes(xintercept = "2020"))+

theme(legend.position = "none")+
    labs(title = "Non-homerule South Triad: Muni Levy Values All Years")



agency_data %>% 
  filter(!(agency_num %in% c("030210000", "030210001", "030210002" ) ) 
         & (minor_type == "MUNI" | agency_num =="020060000")) %>%
  filter(Triad == "North" & home_rule_ind ==0) %>%
  ggplot(aes(x=year, y=total_final_levy, group = agency_name, color = Township))+
  geom_line(alpha=.5, linetype = "dashed") +
        geom_vline(aes(xintercept = "2007"))+
    geom_vline(aes(xintercept = "2010"))+
    geom_vline(aes(xintercept = "2013"))+
    geom_vline(aes(xintercept = "2016"))+
    geom_vline(aes(xintercept = "2019"))+
  geom_point() +   theme_classic() +
theme(legend.position = "none")+
    labs(title = "Non-homerule North Triad: Muni Levy Values All Years")

```

