---
title: "Data Exploration for Revised RD"
format: html
editor: visual
---

# New Research Design

1.  Demonstrate lack of variation for non-HR municipalities.

2.  Calculate cross-elasticity of the levy and the tax base.

    A.  Homerule Munis

    B.  Schools

Goals: Assemble needed data and balance panel data.

# Lack of Variation in non-HR Munis

First step is to demonstrate a lack of variation in non-HR Munis. Let's
create the necessary dataframe and generate some descriptive statistics.

## Generate DF

1.  Load tidyverse.
2.  Read in agency_raw_joined.csv from data generating helper file.

```{r, message = FALSE}

library(tidyverse)

agency_df <- read_csv("agency_raw_joined.csv")
```

### Clean data 1: Run Helper File

```{r, include = FALSE}

source("helper_recode_variables.R")
```

(Is there a good way to show the helper file worked?)

## Clean data 2: Group by "first_six" or EAV?

Want to isolate data on the non-HR municipalities.

```{r}

NHR_munis <- governments_panel %>%
  filter(home_rule_ind == 0)
```

### Group_by first6

```{r}
governments_panel %>%
  group_by(first6) %>%
  filter(year == "2021") %>%
  arrange(agency_num) %>%
  summarize(agency_name = first(agency_name), 
            agency_num = first(agency_num), 
            muni_av = max(muni_av), 
            muni_eav = max(muni_eav), 
            sum_tfl =  sum(total_final_levy, na.rm = T), 
            sum_tfr = sum(total_final_rate, na.rm = T), 
            sum_tml = sum(total_max_levy, na.rm = T), 
            reassess_year = first(reassess_year),
            n=n())


NHR_munis_bundled_f6 <- governments_panel %>%
  group_by(first6, year) %>%
  arrange(agency_num) %>%
  mutate(n = n()) %>%
  summarize(agency_name = first(agency_name), agency_num 
            = first(agency_num), muni_av = max(muni_av), 
            muni_eav = max(muni_eav), sum_tfl = 
              sum(total_final_levy, na.rm = T), sum_tfr = 
              sum(total_final_rate, na.rm = T), sum_tml = 
              sum(total_max_levy, na.rm = T), 
            reassess_year = first(reassess_year), first(n))
```

Check nonHR governments.

```{r}

NHR_munis_bundled %>%
  group_by(agency_name) %>%
  mutate(n = n()) %>%
  filter(n != 16) %>%
#  select(agency_name, agency_num, n) %>%
  group_by(year) %>%
  summarize(num_missing = n())
```
