---
title: "Data Validation"
author: "MVH"
format: html
editor: visual
---

## Load Packages/Read in Data

```{r, message = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(lmtest)
library(huxtable)
library(modelsummary)

df <- read_csv("agency_raw_joined.csv")
```

Note: We'll load plm when we need it so it doesn't have to fail to play
nice with tidyverse.

## Make DF with relevant variables

Thus, per Alea's "Codebook for Cook County Taxing Agency Data.docx**"**
we need:

-   year

-   agency_num

-   home_rule_ind

-   cty_cook_eav: amount of EAV within CC

-   lim_rate: rate that limits the growth in extensions on existing
    property

-   total_levy: amt requested by agency

-   total_max_levy: for HR = 1, amount requested; HR = 0, after PTELL
    limits

-   total_reduced_levy: amount of levy requested that is subject to
    PTELL limitations

-   total_non_cap_ext: amount that is requested that is not subject to
    PTELL reductions

```{r}

df <- df %>%
  select(year, agency_num, home_rule_ind, cty_cook_eav, lim_rate, 
         total_levy, total_max_levy, total_reduced_levy,
         total_non_cap_ext)
```

We also need to merge in that pesky clean names file. *If I were petty,
I'd rename the file to something rude and not just create a csv.*

```{r, eval = FALSE}

names <- read_csv("muni_shortnames.csv")

names <- names %>%
  select(agency_number, agency_name) %>%
  rename(agency_num = agency_number) %>%
  mutate(agency_num = as.character(agency_num))

df <- left_join(df, names, by = "agency_num")
```

\^\^\^\^\^Let's just come back to this item, I suppose.

## Checking Missingness

I *think* Alea said it would be helpful for me to check if any values
are missing (or something like that), so let's do that!

First, *total_levy [should equal]{.underline}* *total_reduced_levy +
total_non_cap_ext*.

```{r}

df <- df %>%
  mutate(calc_levy = total_reduced_levy + total_non_cap_ext,
         levy_dif = calc_levy - total_levy)
```

How many have values where levy_dif != 0? levy_dif \> 0 when the sum of
total_reduced_levy and total_non_cap_ext are greater than total_levy.

```{r}

options(scipen=999)

df %>%
  filter(levy_dif != 0) %>%
  arrange(desc(levy_dif)) %>%
  mutate(agency_num = as.character(agency_num)) %>%
  group_by(agency_num) %>%
  summarize(n = n()) %>%
  distinct() %>%
  arrange(desc(n)) %>%
  group_by(n) %>%
  reframe(n, count = n()) %>%
  distinct() %>%
  arrange(desc(count)) %>%
  ggplot(aes(x = n, y = count)) +
  geom_col() +
  scale_x_continuous(breaks = seq(0, 16, 1))

df_2 <- df %>%
  arrange(desc(levy_dif)) %>%
  filter(levy_dif != 0) %>%
  group_by(agency_num) %>%
  reframe(agency_num, mean_levy_dif = mean(levy_dif)) %>%
  distinct() %>% #fucking reframe
  arrange(mean_levy_dif)
  
df_2 %>%  
  ggplot(aes(mean_levy_dif)) +
  geom_histogram()
```

Let's dig in on mean_levy_dif...

```{r}

library(summarytools)

dfSummary(df_2$mean_levy_dif)
```

*THIS DID NOT WORK BECAUSE IT DIDN'T KNOW HOW TO HANDLE NAs*

Drive/PhD/Repositories/Levy_Elasticity/Levy_Elasticity').
