---
title: "Data Exploration--Revised RD"
author: "MVH & AWM"
format: html
---

# Municipalities

## Setup

1.  Load packages/global options

```{r, message = FALSE, warning = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(DBI)
library(ptaxsim)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(plm)
library(modelsummary)

# Stata uses HC1 as its default standard errors 
# set_summ_defaults(digits = 2, pvals = FALSE, robust = "HC3")

```

2.  Open PTAXSIM DB connection

```{r mvh-setup, message = FALSE, eval=FALSE, include = FALSE}

ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "G:/My Drive/PhD/Cook County Property Taxes/Data Analysis/Working Directory/ptaxsim.db")

```

```{r awm-setup, message=FALSE, include = FALSE}

ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2022.0.0.db")
```

3.  Query PTAXSIM DB for minor_type == "muni" and Cicero names

<!--# Check necessity of final two lines of this chunk!! -->

```{r}

agency <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT *
  FROM agency
  "
  ) 

hr_agency <- agency %>% 
  select(-c(cty_dupage_eav:cty_livingston_eav)) %>%  # drop extra columns of eav in other counties
  filter(home_rule_ind == 1)

muni_agency_names <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT DISTINCT agency_num, agency_name, minor_type
  FROM agency_info
  WHERE minor_type = 'MUNI'"
  ) %>% 
  mutate(first6 = str_sub(agency_num,1,6)) %>%
  select(-minor_type)
```

```{r, message = FALSE, warning = FALSE}

source("helper_recode_variables.R")
```

```{r}

library(dplyr)

all_agencies <- recoded_data

```

# Grouped by grouped_label from CSV

Uses manually coded labels that combine both methods of grouping taxing agencies:

taxing agencies that could be grouped by either the first 6 digits of their shared tax base (EAV equal during a tax year)

```{r}
library(dplyr)

library(openxlsx)

groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))
                                                                        

```

```{r}
library(dplyr)

table(recoded_data$reassess_year, recoded_data$minor_type)

grouped_manual <- recoded_data %>% 
  left_join(groupies2,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP" # | major_type == "MISCELLANEOUS"
           & minor_type != "MISC"
           ) %>%
  filter(minor_type != "SSA") %>% 
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE)+1,
            cty_total_eav = first(cty_total_eav), 
            av = first(av), ## mistake fixed: was sum, now is first()
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind)) %>% 
    left_join(muni_agency_names) %>% 
    mutate(
      log_eav = log(cty_total_eav),
      log_levy = log(total_final_levy),
      log_av =  log(av),
      bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything())


# 94 non-HR and 76 HR in 2021, 93 non-HR and 77 HR in 2022

 grouped_manual %>%  
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
```

72 nonHR and 65 HR if only majortype munis is included.

```{r}
# 1552 obs
# 2278 - 3/31/2024    and 2916 if not filtering for count == 17
grouped_manual_has17 <- grouped_manual %>% 
  ungroup() %>%
  arrange(home_rule_ind) %>%
  group_by(uniqueid) %>%
  distinct() %>%
  mutate(count = n()) %>%
  filter(count == 17) %>% 
  ungroup()
```

```{r eval=FALSE}
datasummary_crosstab(~home_rule_ind, data = grouped_manual, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")

datasummary_crosstab(minor_type~home_rule_ind, data = grouped_manual_has17, title = "Taxing Agency Types by Home Rule Indicator", output = "flextable")
```

```{r}
chicago_obs <- grouped_manual_has17 %>% filter(grouped_label == "Chicago")


grouped_manual_has17 %>% 
  filter(grouped_label != "Chicago") %>%
  ggplot() + 
  geom_line(aes(x=year,y=total_final_levy, group = uniqueid, alpha = .5, color = home_rule_ind)) + 
  theme_classic()



grouped_manual_has17 %>%     
  filter(grouped_label != "Chicago") %>%
ggplot() + 

  geom_line(aes(x=year,y=total_final_levy, group = uniqueid, alpha = .5, color = home_rule_ind)) + 
  facet_wrap(~home_rule_ind) +
  theme_classic() 

grouped_manual_has17 %>%  
    filter(grouped_label != "Chicago") %>%
ggplot() +
  geom_point(aes(x=year, y=total_final_levy,# color = home_rule_ind, 
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = uniqueid, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, # 
                  group = home_rule_ind,
                 # group = grouped_w_hr_ind, 
                  color = home_rule_ind), se=FALSE, size = 2) + 
  theme_classic()

grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
ggplot() + 
  geom_point(aes(x=year, y=total_final_levy,# color = home_rule_ind, 
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = uniqueid, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, # 
                  group = home_rule_ind,
                 # group = grouped_w_hr_ind, 
                  color = home_rule_ind), se=FALSE, size = 2) + 
  facet_wrap(~home_rule_ind) +
  theme_classic()
```

```{r}
grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=total_final_levy,
                 alpha = .1)) +
  geom_line(aes(x=year, y = total_final_levy, group = grouped_label, alpha = .1)) +
  geom_smooth(aes(x=year, y=total_final_levy, 
                  group = grouped_label
                  ), se=FALSE, size = 1, method = "lm") + 
  theme_classic()+
  facet_wrap(~Triad)

grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=av,
                 alpha = .1)) +
  geom_line(aes(x=year, y = av, group = grouped_label, alpha = .1)) +
  geom_smooth(aes(x=year, y=av, 
                  group = grouped_label
                  ), se=FALSE, size = 1, method = "lm") + 
  theme_classic()+
  facet_wrap(~Triad)

grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=(total_final_levy/av),
                 alpha = .1)) +
  geom_line(aes(x=year, y = (total_final_levy/av), group = grouped_label, alpha = .1)) +
  geom_smooth(aes(x=year, y=(total_final_levy/av), 
                  group = grouped_label
                  ), se=FALSE, size = 1, method = "lm") + 
  theme_classic()+
  facet_wrap(~Triad)




grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=(log(total_final_levy)/log(av)),
                 alpha = .1)) +
  geom_line(aes(x=year, y = (log(total_final_levy)/log(av)), group = grouped_label, alpha = .1)) +
  geom_smooth(aes(x=year, y = (log(total_final_levy)/log(av)), 
                  group = grouped_label
                  ), se=FALSE, size = 1, method = "lm") + 
  theme_classic()+
  facet_wrap(~Triad)


```

```{r}
#| layout-ncol: 2
#| column: page


grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=(log(total_final_levy)/log(av)),
                 alpha = .1)) +
  geom_line(aes(x=year, y = (log(total_final_levy)/log(av)), group = grouped_label, alpha = .1)) +
  geom_smooth(aes(x=year, y = (log(total_final_levy)/log(av)), 
                  group = grouped_label
                  ), se=FALSE, size = 1, method = "lm"
              ) + 
  theme_classic()+
  facet_wrap(~Triad)

grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=(log(total_final_levy)/log(av)),
                 alpha = .1)) +
  geom_line(aes(x=year, y = (log(total_final_levy)/log(av)), group = grouped_label, alpha = .1)) +
  geom_smooth(aes(x=year, y = (log(total_final_levy)/log(av)), 
                  group = grouped_label
                  ), se=FALSE, size = 1,# method = "lm"
              ) + 
  theme_classic()+
  facet_wrap(~Triad)

grouped_manual_has17 %>% 
    filter(grouped_label != "Chicago") %>%
  filter(home_rule_ind == 1) %>%
ggplot() + 
  geom_point(aes(x=year, y=(log(total_final_levy)/log(av)),
                 alpha = .1)) +
  geom_line(aes(x=year, y = (log(total_final_levy)/log(av)), group = grouped_label, alpha = .1)) +
  
  geom_smooth(aes(x=year, y = (log(total_final_levy)/log(av)) , 
                  group = Triad
                  ), size = 2,# method = "lm"
              ) + 
  theme_classic()
```

```{r}

grouped_manual_has17 %>% 
    filter(home_rule_ind == 1) %>%

  filter(grouped_label != "Chicago") %>%
  ggplot() + 
  geom_point(aes(x= total_final_levy, y=av)) + 
  theme_classic() +
  facet_wrap(~year)

grouped_manual_has17 %>% 
    filter(home_rule_ind == 1) %>%

  filter(grouped_label != "Chicago") %>%
  ggplot() + 
  geom_point(aes(x= av, y=total_final_levy, color = Triad)) + 
  theme_classic() +
  facet_wrap(~year)

```

```{r}
# 
# grouped_manual_has17 %>% 
#   filter(grouped_label != "Chicago") %>%
#   filter(home_rule_ind == 1) %>%
#   ggplot() + 
#   geom_point(aes(x= av, y=total_final_levy)) + 
#   theme_classic() +
#   facet_wrap(~grouped_label, scales = "free")

grouped_manual_has17 %>% 
  filter(grouped_label != "Chicago") %>% 
  filter(Triad == "North") %>%
  filter(home_rule_ind == 1) %>%
  ggplot() + 
  geom_point(aes(x= av, y=total_final_levy)) + 
  theme_classic() +
  facet_wrap(~grouped_label, scales = "free")

grouped_manual_has17 %>% 
  filter(grouped_label != "Chicago") %>% 
  filter(Triad == "South") %>%
  filter(home_rule_ind == 1) %>%
  ggplot() + 
  geom_point(aes(x= av, y=total_final_levy)) + 
  theme_classic() +
  facet_wrap(~grouped_label, scales = "free" )
```

```{r include = FALSE}
# grouped_manual_has17 %>% 
#   filter(grouped_label != "Chicago") %>%
#   filter(home_rule_ind == 1) %>%
#   ggplot() + 
#   geom_point(aes(x= log_av, y=log_levy)) + 
#   theme_classic() +
#   facet_wrap(~grouped_label, scales = "free")

grouped_manual_has17 %>% 
  filter(grouped_label != "Chicago") %>% 
  filter(Triad == "North") %>%
  filter(home_rule_ind == 1) %>%
  ggplot() + 
  geom_point(aes(x= log_av, y=log_levy)) + 
  theme_classic() +
  facet_wrap(~grouped_label, scales = "free")

grouped_manual_has17 %>% 
  filter(grouped_label != "Chicago") %>% 
  filter(Triad == "South") %>%
  filter(home_rule_ind == 1) %>%
  ggplot() + 
  geom_point(aes(x= log_av, y=log_levy)) + 
  theme_classic() +
  facet_wrap(~grouped_label, scales = "free" )
```

## Models

### HR and Non-HR In Same Model

```{r}
detach("package:dplyr", unload = TRUE)

grouped_munis <- pdata.frame(grouped_manual_has17, index = c("uniqueid", "year")) 

table(grouped_munis$year)
grouped_munis <- make.pbalanced(grouped_munis)
is.pbalanced(grouped_munis)
table(grouped_munis$year)

grouped_munis$eav_lag1  <- plm::lag(grouped_munis$log_eav, 1)
grouped_munis$av_lag1  <- plm::lag(log(grouped_munis$av), 1)

grouped_munis$eav_lag2  <- plm::lag(grouped_munis$log_eav, 2)
grouped_munis$av_lag2  <- plm::lag(log(grouped_munis$av), 2)

grouped_munis$cty_eav_lag  <- plm::lag(grouped_munis$cty_total_eav, 1)
grouped_munis$av_lag_notlogged  <- plm::lag(grouped_munis$av, 1)


# 
# grouped_munis$reassess_lag1 <- plm::lag(grouped_munis$reassess_year, 1)
# grouped_munis$reassess_lag2 <- plm::lag(grouped_munis$reassess_year, 2)
# 
# 
# grouped_munis$reassess_lead1 <- plm::lead(grouped_munis$reassess_year, 1)
# grouped_munis$reassess_lead2 <- plm::lead(grouped_munis$reassess_year, 2)
```

#### EAV Models

```{r}
library(dplyr)
grouped_munis <- grouped_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag),
         av_change = av - av_lag_notlogged,
         av_pct_change = (av-av_lag_notlogged)/av_lag_notlogged
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

# All Agencies-Agency & Year FE"
grouped_model<- plm(log(total_final_levy) ~ log(cty_total_eav), 
                   # index = c("grouped_w_hr_ind", "year"), 
                    model = "within", 
                    effect= "twoways",                    
                    data = grouped_munis)






grouped_cleannames_withHRind <- plm(log(total_final_levy) ~ log(cty_total_eav)+ log(cty_total_eav):home_rule_ind, 
                        #  index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind)

grouped_cleannames_withHRind_lagged <- plm(log(total_final_levy) ~ log(cty_total_eav)+ log(cty_total_eav):home_rule_ind + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2), 
                          #index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind_lagged)

grouped_cleannames_lag <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
                          #index = c("grouped_w_hr_ind", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)

grouped_cleannames_lag2 <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2)+log(cty_total_eav):home_rule_ind + lag(log(cty_total_eav),1):home_rule_ind  + lag(log(cty_total_eav),2):home_rule_ind ,
#                          index = c("uniqueid", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)
#summary(grouped_cleannames_lag2)


model_names <- c(grouped_model = "Grouped manually, Summed Levies", 
                 grouped_cleannames_lag = "with Lags",
                 grouped_cleannames_withHRind = "with HR Indicator",
                 grouped_cleannames_withHRind_lagged = "HR indacator with Lags",
                grouped_cleannames_lag2 = "HR interact with both Lags") # has Chicago


# plot(grouped_model)


export_summs(grouped_model, grouped_cleannames_lag,  grouped_cleannames_withHRind, grouped_cleannames_withHRind_lagged, grouped_cleannames_lag2, robust = "HC3",  model.names = model_names, statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))



```

When using the grouped_labels csv to identify agencies that should be grouped, then there are 124 nonHR and 69 HR grouped taxing districts.

#### AV Models

```{r}
library(dplyr)
grouped_munis <- grouped_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag),
         
         av_change = av - av_lag_notlogged,
         av_pct_change = (av-av_lag1)/av_lag1
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

# All Agencies-Agency & Year FE"
grouped_model<- plm(log(total_final_levy) ~ log(av), 
                   # index = c("grouped_w_hr_ind", "year"), 
                    model = "within", 
                    effect= "twoways",                    
                    data = grouped_munis)






grouped_cleannames_withHRind <- plm(log(total_final_levy) ~ log(av)+ log(av):home_rule_ind, 
                        #  index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind)

grouped_cleannames_withHRind_lagged <- plm(log(total_final_levy) ~ log(av)+ log(av):home_rule_ind + lag(log(av),1) + lag(log(av),2), 
                          #index = c("grouped_w_hr_ind", "year"), 
                          model = "within", 
                          effect= "twoways",                    
                          data = grouped_munis)

#summary(grouped_cleannames_withHRind_lagged)

grouped_cleannames_lag <- plm(log(total_final_levy) ~ log(av) + lag(log(av),1) + lag(log(av),2),
                          #index = c("grouped_w_hr_ind", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)

grouped_cleannames_lag2 <- plm(log(total_final_levy) ~ log(av) + lag(log(av),1) + lag(log(av),2)+log(av):home_rule_ind + lag(log(av),1):home_rule_ind  + lag(log(av),2):home_rule_ind ,
#                          index = c("uniqueid", "year"), 
                              model = "within", 
                              effect= "twoways",                    
                              data = grouped_munis)
#summary(grouped_cleannames_lag2)


model_names <- c(grouped_model = "Grouped manually, Summed Levies", 
                 grouped_cleannames_lag = "with Lags",
                 grouped_cleannames_withHRind = "with HR Indicator",
                 grouped_cleannames_withHRind_lagged = "HR indacator with Lags",
                grouped_cleannames_lag2 = "HR interact with both Lags") # has Chicago


# plot(grouped_model)


export_summs(grouped_model, grouped_cleannames_lag,  grouped_cleannames_withHRind, grouped_cleannames_withHRind_lagged, grouped_cleannames_lag2, robust = "HC3",  model.names = model_names, statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))



```

### Seperating hr and nonhr

#### EAV Models

```{r}
 
library(dplyr)

homerule_minortype_munis <- grouped_manual %>% 
  filter(home_rule_ind == 1)

homerule_minortype_munis <- pdata.frame(homerule_minortype_munis, index = c("agency_name", "year"))

homerule_minortype_munis <- make.pconsecutive(homerule_minortype_munis)

detach("package:dplyr", unload = TRUE)

homerule_minortype_munis$eav_lag1  <- plm::lag(homerule_minortype_munis$log_eav, 1)
homerule_minortype_munis$eav_lag2  <- plm::lag(homerule_minortype_munis$log_eav, 2)
homerule_minortype_munis$av_lag1  <- plm::lag(log(homerule_minortype_munis$av), 1)


homerule_minortype_munis$cty_eav_lag  <- plm::lag(homerule_minortype_munis$cty_total_eav, 1)
homerule_minortype_munis$av_lag_notlogged  <- plm::lag(homerule_minortype_munis$av, 1)

        
library(dplyr)
homerule_minortype_munis <- homerule_minortype_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
        
         av_change = av - av_lag_notlogged,
         av_pct_change = (av-av_lag1)/av_lag1,
         
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

hr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
                          #  index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = homerule_minortype_munis)


hr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

hr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(cty_total_eav)  + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

hr_muni_minor <- plm(log(total_final_levy)  ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2) + up_down*log(cty_total_eav),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

# summary(hr_muni_minor)
model_names = c("Homerule Government Taxing Agencies")

export_summs(hr_muni_minor_simple, #hr_muni_minor_simple0,  
             hr_muni_minor_lags,             hr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}
 
library(dplyr)

nonhr_munis <- grouped_manual %>% 
  filter(home_rule_ind == 0) %>% select(uniqueid, year, everything())

nonhr_munis <- pdata.frame(nonhr_munis, index = c("agency_name", "year"))

nonhr_munis <- make.pconsecutive(nonhr_munis)

detach("package:dplyr", unload = TRUE)

nonhr_munis$eav_lag1  <- plm::lag(nonhr_munis$log_eav, 1)
nonhr_munis$eav_lag2  <- plm::lag(nonhr_munis$log_eav, 2)

nonhr_munis$cty_eav_lag <- plm::lag(nonhr_munis$cty_total_eav, 1)
        
library(dplyr)
nonhr_munis <- nonhr_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

nonhr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
                           # index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = nonhr_munis)


nonhr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(cty_total_eav), 
           #  index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

nonhr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(cty_total_eav)  + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

nonhr_muni_minor <- plm(log(total_final_levy)  ~ log(cty_total_eav) + lag(log(cty_total_eav),1) + lag(log(cty_total_eav),2) + up_down*log(cty_total_eav),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

# summary(hr_muni_minor)
# summary(hr_muni_minor)
model_names = c("Non-HR Government Taxing Agencies")

export_summs(nonhr_muni_minor_simple, # nonhr_muni_minor_simple0, 
             nonhr_muni_minor_lags, 
                      nonhr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

#### AV Models

```{r}
 
library(dplyr)

homerule_minortype_munis <- grouped_manual %>% 
  filter(home_rule_ind == 1)

homerule_minortype_munis <- pdata.frame(homerule_minortype_munis, index = c("agency_name", "year"))

homerule_minortype_munis <- make.pconsecutive(homerule_minortype_munis)

detach("package:dplyr", unload = TRUE)

homerule_minortype_munis$eav_lag1  <- plm::lag(homerule_minortype_munis$log_eav, 1)
homerule_minortype_munis$eav_lag2  <- plm::lag(homerule_minortype_munis$log_eav, 2)
homerule_minortype_munis$av_lag1  <- plm::lag(log(homerule_minortype_munis$av), 1)


homerule_minortype_munis$cty_eav_lag  <- plm::lag(homerule_minortype_munis$cty_total_eav, 1)
homerule_minortype_munis$av_lag_notlogged  <- plm::lag(homerule_minortype_munis$av, 1)

        
library(dplyr)
homerule_minortype_munis <- homerule_minortype_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
        
         av_change = av - av_lag_notlogged,
         av_pct_change = (av-av_lag1)/av_lag1,
         
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

hr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(av), 
                          #  index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = homerule_minortype_munis)


hr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(av), 
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

hr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(av)  + lag(log(av),1) + lag(log(av),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

hr_muni_minor <- plm(log(total_final_levy)  ~ log(av) + lag(log(av),1) + lag(log(av),2) + up_down*log(av),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = homerule_minortype_munis)

# summary(hr_muni_minor)
model_names = c("Homerule Government Taxing Agencies")

export_summs(hr_muni_minor_simple, #hr_muni_minor_simple0,  
             hr_muni_minor_lags,             hr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}
 
library(dplyr)

nonhr_munis <- grouped_manual %>% 
  filter(home_rule_ind == 0) %>% select(uniqueid, year, everything())

nonhr_munis <- pdata.frame(nonhr_munis, index = c("agency_name", "year"))

nonhr_munis <- make.pconsecutive(nonhr_munis)

detach("package:dplyr", unload = TRUE)

nonhr_munis$eav_lag1  <- plm::lag(nonhr_munis$log_eav, 1)
nonhr_munis$eav_lag2  <- plm::lag(nonhr_munis$log_eav, 2)


nonhr_munis$av_lag1  <- plm::lag(log(nonhr_munis$av), 1)

nonhr_munis$cty_eav_lag <- plm::lag(nonhr_munis$cty_total_eav, 1)
nonhr_munis$av_lag_notlogged  <- plm::lag(nonhr_munis$av, 1)

library(dplyr)
nonhr_munis <- nonhr_munis %>% 
  mutate(yearly_change = log_eav-eav_lag1,
         yearly_chang_perc =(log_eav-eav_lag1)/eav_lag1,
         
         av_change = av - av_lag_notlogged,
         av_pct_change = (av-av_lag1)/av_lag1,
         
         eav_change = cty_total_eav - cty_eav_lag,
         eav_change_pct = ((cty_total_eav - cty_eav_lag)/cty_eav_lag)
       ) %>%
  mutate(up_down  = ifelse(eav_change > 0, "increased", "decreased"))


detach("package:dplyr", unload = TRUE)

nonhr_muni_minor_simple0 <- plm(log(total_final_levy)  ~ log(av), 
                           # index = c("label_hr", "year"), 
                            model = "within", effect= "twoways",                    
                            data = nonhr_munis)


nonhr_muni_minor_simple <- plm(log(total_final_levy)  ~ log(av), 
           #  index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

## These two should be the same! Shows how subsetting works in plm command.
# summary(hr_muni_minor_simple0)
# summary(hr_muni_minor_simple)

nonhr_muni_minor_lags <- plm(log(total_final_levy)  ~ log(av)  + lag(log(av),1) + lag(log(av),2),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

nonhr_muni_minor <- plm(log(total_final_levy)  ~ log(av) + lag(log(av),1) + lag(log(av),2) + up_down*log(av),
            # index = c("label_hr", "year"), 
             model = "within", effect= "twoways",                    
             data = nonhr_munis)

# summary(hr_muni_minor)
# summary(hr_muni_minor)
model_names = c("Non-HR Government Taxing Agencies")

export_summs(nonhr_muni_minor_simple, # nonhr_muni_minor_simple0, 
             nonhr_muni_minor_lags, 
                      nonhr_muni_minor, 

             robust = "HC3",  model.names = model_names, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

# Percent change

```{r}
# nonhr_munis

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "twoways",                    
                    data = nonhr_munis) %>% summary()

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "individual",                    
                    data = nonhr_munis) %>% summary()

# nonhr_munis

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "twoways",                    
                    data = homerule_minortype_munis) %>% summary()

plm(log(total_final_levy) ~ log(cty_total_eav), #*year + log(cty_total_eav)*up_down, 
                    model = "within", 
                    effect= "individual",                    
                    data = homerule_minortype_munis) %>% summary()
```

```{r levy-indexed, error=TRUE}
library(dplyr)
library(tidyverse)

indexed_munis <- grouped_manual_has17 %>%
#  mutate(year = as.factor(year)) %>%
  ungroup() %>%
 # filter(minor_type == "MUNI") %>%
 # filter(!agency_num %in% dropped_munis & !agency_num %in% exclude_hr_change ) %>% 
  mutate(year = as.character(year),
         agency_name = as.character(agency_name)) %>% 
  group_by(uniqueid) %>% 
  summarize(     # Index values to 2006
    year=year,
    
    eav_idx = cty_total_eav / (cty_total_eav[year == "2006"] ),
    levy_idx = total_final_levy / (total_final_levy[year == "2006"]),
    av_idx = av / (av[year == 2006]),
    Triad = Triad,
    home_rule_ind = home_rule_ind
  )   

indexed_munis %>% 
  ggplot(aes(x=year, y = levy_idx, group = uniqueid, label = uniqueid, color = as.factor(home_rule_ind))) + 
  geom_line(alpha=.5, linetype = "dashed") +
  geom_point() + 
  theme_classic()+
 # geom_text(size = 2, vjust=-1.5)+
  facet_wrap(~home_rule_ind)+
  labs(title = "Municipalities:Total Final Levy Indexed to 2006")


indexed_munis %>% ggplot() + 
  geom_line(aes(x=year, y = levy_idx, group = uniqueid, color = Triad), alpha=.5, linetype = "dashed") +
  geom_point(aes(x=year, y = levy_idx), alpha = .1) + 
  theme_classic()+
  facet_wrap(~Triad)+
    labs(title = "Municipalities:Total Final Levy Indexed to 2006")



indexed_munis %>% ggplot() + geom_line(aes(x=year, y = av_idx, group = uniqueid, color = as.factor(home_rule_ind)))  +
  facet_wrap(~Triad) + 
  theme(legend.position = "bottom") +
  labs(title = "Municipalities: AV Indexed to 2006" )

indexed_munis %>% ggplot() + geom_line(aes(x=year, y = levy_idx, group = uniqueid, color = Triad)) +  facet_wrap(~Triad) + 
  labs(title = "Municipalities: Total Final Levy Indexed to 2006")

#minortype_munis %>% write_csv("minortype_munis.csv")
```

# Schools

```{r error=TRUE}
library(dplyr)

schools <- recoded_data %>%
  filter(major_type == "SCHOOL") %>%
  group_by(agency_name) %>%
  mutate(year_count = n()) %>%
  ungroup() %>% 
  filter(year_count >10)

schools <- pdata.frame(schools, index = c("agency_name", "year"))


is.pbalanced(schools)
schools <- plm::make.pbalanced(schools )

detach("package:dplyr", unload = TRUE)


# based on major_type == Schools. Groups all schools together. 

school_mod_major_simple <- plm(log(total_final_levy) ~ log(cty_total_eav),
                               index = c("agency_name", "year"),
                  model = "within",  effect= "twoways", data = schools)

school_mod_major <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
                        index = c("agency_name", "year"),
                  model = "within",  effect= "twoways", data = schools)


school_mod_secondary_simple <- plm(log(total_final_levy) ~ log(cty_total_eav),
                        subset = minor_type == "SECONDARY",
                        index = c("agency_name", "year"), model = "within",
                        effect= "twoways", data = schools)

school_mod_secondary <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
                        subset = minor_type == "SECONDARY",
                        index = c("agency_name", "year"), model = "within",
                        effect= "twoways", data = schools)

# doesn't exist every year
# school_mod_unified <- plm(log(total_final_levy) ~ log(cty_total_eav)+ lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
#                         subset = minor_type == "UNIFIED",
#                         index = c("agency_name", "year"),
#                         model = "within",
#                         effect= "twoways", data = schools)

school_mod_elementary <- plm(log(total_final_levy) ~ log(cty_total_eav) + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
                             subset = minor_type == "ELEMENTARY",
                             index = c("agency_name", "year"),
                             model = "within",
                             effect= "twoways", data = schools)

school_mod_elementary_simple <- plm(log(total_final_levy) ~ log(cty_total_eav),
                             subset = minor_type == "ELEMENTARY",
                             index = c("agency_name", "year"), model = "within",
                             effect= "twoways", data = schools)

# doesn't exist every year
# school_mod_comcol <- plm(log(total_final_levy) ~ log(cty_total_eav)  + lag(log(cty_total_eav), 1) + lag(log(cty_total_eav),2),
#                          index = c("agency_name", "year"),
#                          subset = minor_type == "COMM COLL", model = "within",
#                          effect= "twoways", data = schools)

# ## table with more school types
# model_names = c("All Schools", "All Schools", "Secondary", "Elementary", "Elementary",
#                 "Com. Colleges", "Unified" )
# export_summs(school_mod_major_simple, school_mod_major,
#              school_mod_secondary,
#              school_mod_elementary_simple, school_mod_elementary,
#              #school_mod_comcol, school_mod_unified,
#              model.names = model_names, robust=TRUE, statistics = c(N = "nobs", adjR2 = "adj.r.squared"))

model_names = c("All Schools", "All Schools", "Secondary", "Secondary", "Elementary", "Elementary")

export_summs(school_mod_major_simple, school_mod_major,
             school_mod_secondary_simple,
             school_mod_secondary,
             school_mod_elementary_simple, school_mod_elementary,

             model.names = model_names, robust=TRUE, statistics = c(N = "nobs", adjR2 = "adj.r.squared"))
```

#### AV Models


```{r}
library(dplyr)

schools <- recoded_data %>%
  filter(major_type == "SCHOOL") %>% 
  filter(av>0 & total_final_levy> 0 ) %>%
  mutate(years_existed = n(), .groups = agency_name)

schools <- pdata.frame(schools, index = c("agency_name", "year"))


is.pbalanced(schools)
schools <- plm::make.pbalanced(schools )

detach("package:dplyr", unload = TRUE)


# based on major_type == Schools. Groups all schools together. 

school_mod_major_simple <- plm(log(total_final_levy) ~ log(av),
                               index = c("agency_name", "year"),
                  model = "within",  effect= "twoways", data = schools)

school_mod_major <- plm(log(total_final_levy) ~ log(av) + lag(log(av), 1) + lag(log(av),2),
                        index = c("agency_name", "year"),
                  model = "within",  effect= "twoways", data = schools)


school_mod_secondary_simple <- plm(log(total_final_levy) ~ log(av),
                        subset = minor_type == "SECONDARY",
                        index = c("agency_name", "year"), model = "within",
                        effect= "twoways", data = schools)

school_mod_secondary <- plm(log(total_final_levy) ~ log(av) + lag(log(av), 1) + lag(log(av),2),
                        subset = minor_type == "SECONDARY",
                        index = c("agency_name", "year"), model = "within",
                        effect= "twoways", data = schools)

# doesn't exist every year
# school_mod_unified <- plm(log(total_final_levy) ~ log(av)+ lag(log(av), 1) + lag(log(av),2),
#                         subset = minor_type == "UNIFIED",
#                         index = c("agency_name", "year"),
#                         model = "within",
#                         effect= "twoways", data = schools)

school_mod_elementary <- plm(log(total_final_levy) ~ log(av) + lag(log(av), 1) + lag(log(av),2),
                             subset = minor_type == "ELEMENTARY",
                             index = c("agency_name", "year"),
                             model = "within",
                             effect= "twoways", data = schools)

school_mod_elementary_simple <- plm(log(total_final_levy) ~ log(av),
                             subset = minor_type == "ELEMENTARY",
                             index = c("agency_name", "year"), model = "within",
                             effect= "twoways", data = schools)


model_names = c("All Schools", "All Schools", "Secondary", "Secondary", "Elementary", "Elementary")

export_summs(school_mod_major_simple, school_mod_major,
             school_mod_secondary_simple,
             school_mod_secondary,
             school_mod_elementary_simple, school_mod_elementary,

             model.names = model_names, robust=TRUE, statistics = c(N = "nobs", adjR2 = "adj.r.squared"))
```
