---
title: "Levy Elasticity Paper Tables"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    theme: cosmo
execute:
  echo: true
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(htmltools)
library(fs)
library(tidyverse)
library(haven)
library(gt)
library(fixest)
library(modelsummary)

# Tables are created by scripts/descriptive_stats_22_lags_cluster_updated.R
# after running the model script locally.
#table_dir <- fs::path("results", "tables")
table_dir <- fs::path("results", "tables_corrected_clustered")

include_table <- function(file) {
  table_path <- fs::path(table_dir, file)

  if (!fs::file_exists(table_path)) {
    htmltools::HTML(
      paste0(
        "<p><strong>Missing table:</strong> <code>",
        htmltools::htmlEscape(as.character(table_path)),
        "</code></p>"
      )
    )
  } else {
    htmltools::includeHTML(table_path)
  }
}
```

This page displays the HTML tables created by the replication script. Before rendering the site, run:

```{r}
#| eval: false
source("scripts/descriptive_stats_22_lags_cluster_updated.R")
quarto::quarto_render()
```

```{r}
# ================================================================
# 1. READ + MERGE DATA
# ================================================================

message(Sys.Date())
message(format(Sys.time(), "%H:%M:%S"))

safe_se <- function(model, term) {
  out <- tryCatch(fixest::se(model)[[term]], error = function(e) NA_real_)
  if (is.null(out)) NA_real_ else out
}

safe_coef <- function(model, term) {
  out <- tryCatch(stats::coef(model)[[term]], error = function(e) NA_real_)
  if (is.null(out)) NA_real_ else out
}

term_stats <- function(model, term = "d_eav", label = NULL) {
  est <- safe_coef(model, term)
  se  <- safe_se(model, term)
  tibble(
    model = label %||% deparse(substitute(model)),
    N = tryCatch(stats::nobs(model), error = function(e) NA_integer_),
    estimate = est,
    std_error = se,
    upper_bound = est + 1.645 * se,
    p_value = tryCatch(2 * pnorm(abs(est / se), lower.tail = FALSE), error = function(e) NA_real_)
  )
}
safe_first_stage_f <- function(model) {
  # fixest exposes several IV fit statistics, but names differ across versions.
  out <- tryCatch(fixest::fitstat(model, "ivf1"), error = function(e) NULL)
  if (is.null(out)) return(NA_real_)
  as.numeric(unlist(out))[1]
}


# file DM used:  #"NTA_data_2024_10_14.csv"
# email shows that he had questions about this file and then michael sent one for 10_16
main_df <- read_csv("NTA_data_2024_10_14.csv")

# main_df |> distinct(agency_group)
#415 distinct agency_groups in the 10_14 file.

# File MVH sent him:
# main_df <- read_csv("NTA_data_2024_10_16.csv") |>
#   arrange(type)


# Most recent file AWM had on her computer:
# main_df <- read_csv("NTA_data_2024_11_08.csv") |>
# arrange(type)


agency_lookup <- read_dta("Necessary_Files/fips_all_agency_name.dta")

# anti_join(main_df, agency_lookup)

main_df <- main_df |>
  left_join(agency_lookup, by = "agency_group")
# 7470 observations before dropping NAs
# 7416 after dropping NAs
# Stata listed unmatched rows and dropped merge==1 rows.
# In dplyr terms: drop observations from master that did not match.
main_df <- main_df |>
  filter(!is.na(fipsid))

census_df <- read_dta("Necessary_Files/census_data.dta")

# 3,509 observations didn't have the census data and get dropped unless missing data is filled in between census years.
#anti_join(main_df, census_df)

main_df <- main_df |>
  left_join(census_df, by = c("fipsid", "year"))

# ================================================================
# 2. MERGE EQUALIZATION FACTORS + CLEAN NUMERIC FIELDS
# ================================================================

# Stata used a .dta called eq_factor after previously creating it from CSV.
# Adjust extension if your stored file is actually .csv.

eq_factor_path_dta <- file.path("eq_factor.dta")
eq_factor_path_csv <- file.path("Necessary_Files/eq_factor.csv")

eq_factor <- if (file.exists(eq_factor_path_dta)) {
  read_dta(eq_factor_path_dta)
} else if (file.exists(eq_factor_path_csv)) {
  read_csv(eq_factor_path_csv, show_col_types = FALSE)
} else {
  stop("Could not find eq_factor.dta or eq_factor.csv in post nta folder.")
}

main_df <- main_df |>
  left_join(eq_factor, by = "year")

string_num_vars <- c("assess_year_eav",  "assess_year_av", "av_true", "rate_smooth", "total_final_levy")

main_df <- main_df |>
  mutate(
    across(
      any_of(string_num_vars),
      ~ readr::parse_number(as.character(.x), na = c("NA", "", ".")),
      .names = "n_{.col}"
    )
  )

vcov_uid <- ~n_uniqueid


# ================================================================
# 3. PANEL SETUP + CONSTRUCTED VARIABLES
# ================================================================

main_df <- main_df |>
  mutate(
    n_agency_group = as.integer(factor(agency_group)),
    n_uniqueid     = as.integer(factor(uniqueid))
  ) |>
  arrange(n_agency_group, year) |>
  filter(!is.na(n_agency_group)) |>
  group_by(n_agency_group) |>
  arrange(year, .by_group = TRUE) |>
  mutate(
    lag_av = lag(av, 1),
    lag2_av = lag(av, 2),
    lag3_av = lag(av, 3),
    lead1_av = lead(av, 1),
    lead2_av = lead(av, 2),
    lead3_av = lead(av, 3),
    lag_eq_factor_final = lag(eq_factor_final, 1),
    lag2_eq_factor_final = lag(eq_factor_final, 2),
    lag3_eq_factor_final = lag(eq_factor_final, 3),
    lag_reassess_year = lag(reassess_year, 1),
    lag2_reassess_year = lag(reassess_year, 2)
  ) |>
  ungroup() |>
  filter(year >= 2008)

main_df <- main_df |>
  mutate(
    t = case_when(
      reassess_year == 1 ~ 1,
      lag_reassess_year == 1 ~ 2,
      lag2_reassess_year == 1 ~ 3,
    ),
    r = case_when(
      t == 1 ~ ((lead3_av / av)^(1 / 3)) - 1,
      t == 2 ~ ((lead2_av / lag_av)^(1 / 3)) - 1,
      t == 3 ~ ((lead1_av / lag2_av)^(1 / 3)) - 1,
      TRUE ~ 0
    ),
    EstV = case_when(
      t == 1 ~ av,
      t == 2 ~ lag_av * (1 + r),
      t == 3 ~ lag2_av * (1 + r)^2,
      TRUE ~ 0
    ),
    ln_EstV = log(EstV),
    d_av = 100 * log(av / lag_av)) |>
  group_by(n_agency_group) |>
  mutate(
    d_eav = 100 * log((av * eq_factor_final) / (lag_av * lag(eq_factor_final))),
    d_levy = 100 * log(total_final_levy / lag(total_final_levy)),
    d_total_ig_revenue = 100 * log(total_ig_revenue / lag(total_ig_revenue)),
    d_enrollment = 100 * log(enrollment / lag(enrollment)),
    has_ig_data = if_else(is.na(d_total_ig_revenue), 0, 1),
    type_2 = case_when(
      type == "Muni" & home_rule_ind == 1 ~ "HR_muni",

      ## Added this row below!!
      type == "Muni" & home_rule_ind == 0 ~ "NonHR_muni",
      TRUE ~ as.character(type)
    )
  ) |> ungroup()



reg_df <- main_df |>
  filter(year > 2008)


reg_df <- reg_df |>
  mutate(
    # Keep municipal types separate in by-type models.
    type_2 = case_when(
      type == "Muni" & home_rule_ind == 1 ~ "HR_muni",
      type == "Muni" & home_rule_ind == 0 ~ "NonHR_muni",
      TRUE ~ as.character(type)
    ),
    # Use a non-missing home-rule flag for year-by-home-rule fixed effects.
    home_rule_for_fe = replace_na(as.integer(home_rule_ind), 0L)
  )


gov_types <- c("Other", "Township", "HR_muni", "NonHR_muni", "School")
gov_types_B <- c("HR_muni", "NonHR_muni", "School")
minor_types <- c("ELEMENTARY", "SECONDARY")

gof_omit = "IC|Log|Adj|RMSE"
```



# Main paper tables


## Table 1. Distribution of Percentage Changes in Levies and EAV

```{r tbl1}
# summarize d_levy and d_eav by type
## Table 1. Distribution of Percentage Changes in Levies and EAV

table1 <- reg_df |>
  filter(year >= 2009) |>
  mutate(
    agency_type = case_when(
      type == "Muni" ~ "All Munis",
      type == "School" ~ "Schools",
      type == "Township" ~ "Townships",
      type == "Other" ~ "Other Districts"
    )
  ) |>
  select(agency_type, d_levy, d_eav) |>
  pivot_longer(
    cols = c(d_levy, d_eav),
    names_to = "stat",
    values_to = "value"
  ) |>
  group_by(agency_type, stat) |>
  summarize(
    N = sum(!is.na(value)),
    p5 = quantile(value, .05, na.rm = TRUE),
    p25 = quantile(value, .25, na.rm = TRUE),
    p50 = quantile(value, .50, na.rm = TRUE),
    p75 = quantile(value, .75, na.rm = TRUE),
    p95 = quantile(value, .95, na.rm = TRUE),
    .groups = "drop"
  )

table1 |>
  gt() |>
  fmt_number(
    columns = c(p5, p25, p50, p75, p95),
    decimals = 1
  ) |>
  tab_header(
    title = md("**Table 1. Distribution of Percentage Changes in Levies and EAV**")
  )
```


## Table 2. All agencies OLS

```{r}
#| label: tbl-02-ols-all
#| results: asis
include_table("v22_table_02_OLS_all_agencies.html")
```

## Table 2. OLS upper-bound summary

```{r}
#| label: tbl-02-ols-upper
#| results: asis
include_table("v22_table_02_OLS_all_agencies_upper_bounds.html")
```

## Table 3. All agencies IV

```{r}
#| label: tbl-03-iv-all
#| results: asis
include_table("v22_table_03_IV_all_agencies.html")
```

## Table 3. IV upper-bound summary

```{r}
all_iv_3 <- feols(d_levy ~ 1 | year^home_rule_for_fe + n_uniqueid | d_eav ~ reassess_year,
  data = reg_df, cluster = vcov_uid)
modelsummary(all_iv_3, gof_omit = gof_omit, stars = TRUE)
extra_stats <-  term_stats(all_iv_3, "fit_d_eav", "M3") |>
                                   mutate(first_stage_F =  safe_first_stage_f(all_iv_3))

extra_stats
```

```{r}
#| label: tbl-03-iv-upper
#| results: asis
include_table("v22_table_03_IV_all_agencies_upper_bounds.html")
```

## Table 4. OLS by agency type


```{r}
d <- reg_df |> filter(type_2 %in% gov_types)

m1 <- feols(d_levy ~ d_eav, data = d, cluster = vcov_uid)
m2 <- feols(d_levy ~ d_eav | year, data = d, cluster = vcov_uid)
m3 <- feols(d_levy ~ d_eav | year + n_uniqueid, data = d, cluster = vcov_uid, split = ~type_2)


modelsummary(m3, gof_omit = gof_omit, stars = TRUE)

# extra_stats <-  term_stats(m3, "d_eav", "M3") |>
#                                    mutate(first_stage_F =  safe_first_stage_f(m3))
# 
# extra_stats

mods <- as.list(m3)
extra_stats <- purrr::imap_dfr(
  mods,
  ~ term_stats(.x, "d_eav", .y) |>
      mutate(
        first_stage_F = safe_first_stage_f(.x)
      )
)

extra_stats <-  term_stats(m3, "d_eav") |>
                                   mutate(first_stage_F =  safe_first_stage_f(m3))

extra_stats
```

```{r}
agency_label <- function(x) {
  recode(as.character(x),
    HR_muni = "Home-rule municipalities",
    NonHR_muni = "Non-home-rule municipalities",
    Muni = "All Munis",
    Other = "Other",
    Township = "Townships",
    School = "Schools",
    .default = as.character(x)
  )
}

gov_types <- c("Other", "Township", "HR_muni", "NonHR_muni", "School")
gov_types_B <- c("HR_muni", "NonHR_muni", "School")
minor_types <- c("ELEMENTARY", "SECONDARY")

run_type_v22 <- function(df, gov, iv = FALSE) {
  d <- df |> filter(type_2 == gov)
  if (!iv) {
    m1 <- feols(d_levy ~ d_eav, data = d, cluster = vcov_uid)
    m2 <- feols(d_levy ~ d_eav | year, data = d, cluster = vcov_uid)
    m3 <- feols(d_levy ~ d_eav | year + n_uniqueid, data = d, cluster = vcov_uid)
    return(list(m1 = m1, m2 = m2, m3 = m3))
  }
  m1 <- feols(d_levy ~ 1 | 0 | d_eav ~ reassess_year, data = d, cluster = vcov_uid)
  m2 <- feols(d_levy ~ 1 | year | d_eav ~ reassess_year, data = d, cluster = vcov_uid)
  m3 <- feols(d_levy ~ 1 | year + n_uniqueid | d_eav ~ reassess_year, data = d, cluster = vcov_uid)
  list(m1 = m1, m2 = m2, m3 = m3)
}


make_by_type_summary <- function(models_A, iv = FALSE) {
  term <- if (iv) "fit_d_eav" else "d_eav"
  rows <- list()
  for (spec in paste0("m", 1:3)) {
    rows[[spec]] <- map_dfr(gov_types, function(gov) {
      term_stats(models_A[[gov]][[spec]], term, gov) |>
        transmute(row = spec, agency = model, N, upper_bound, estimate, p_value)
    })
  }
bind_rows(rows) |>
    mutate(
      agency = agency_label(agency),
      row = recode(row,
        m1 = "No controls",
        m2 = "Year FE",
        m3 = "Year + unit FE"
    ))
}

ols_type_A <- setNames(map(gov_types, ~ run_type_v22(reg_df, .x, iv = FALSE)), gov_types)
iv_type_A <- setNames(map(gov_types, ~ run_type_v22(reg_df, .x, iv = TRUE)), gov_types)

ols_by_type_summary <- make_by_type_summary(ols_type_A, iv = FALSE)

ols_by_type_summary |> filter(row == "Year + unit FE")
iv_by_type_summary <- make_by_type_summary(iv_type_A, iv = TRUE)


```

```{r}
m1 <- feols(d_levy ~ 1 | 0 | d_eav ~ reassess_year, data = d, cluster = vcov_uid)
m2 <- feols(d_levy ~ 1 | year | d_eav ~ reassess_year, data = d, cluster = vcov_uid)
m3 <- feols(d_levy ~ 1 | year + n_uniqueid | d_eav ~ reassess_year, data = d, cluster = vcov_uid)

iv_mods <-   list(m1 = m1, m2 = m2, m3 = m3)


```

```{r}
#| label: tbl-04-ols-type
#| results: asis
include_table("v22_table_04_OLS_by_type_upper_bounds.html")
```

## Table 5. IV by agency type

```{r}
save_df_table <- function(df, file_stub, title = NULL, digits = 3) {
  out_file <- file.path(output_dir, paste0(file_stub, ".html"))
  df_out <- df |>
    mutate(across(where(is.numeric), ~ round(.x, digits)))

  html <- knitr::kable(df_out, format = "html", caption = title, escape = TRUE)
  writeLines(html, out_file)
  invisible(df_out)
}

safe_se <- function(model, term) {
  out <- tryCatch(fixest::se(model)[[term]], error = function(e) NA_real_)
  if (is.null(out)) NA_real_ else out
}

safe_coef <- function(model, term) {
  out <- tryCatch(stats::coef(model)[[term]], error = function(e) NA_real_)
  if (is.null(out)) NA_real_ else out
}

term_stats <- function(model, term = "d_eav", label = NULL) {
  est <- safe_coef(model, term)
  se  <- safe_se(model, term)
  tibble(
    model = label %||% deparse(substitute(model)),
    N = tryCatch(stats::nobs(model), error = function(e) NA_integer_),
    estimate = est,
    std_error = se,
    upper_bound = est + 1.645 * se,
    p_value = tryCatch(2 * pnorm(abs(est / se), lower.tail = FALSE), error = function(e) NA_real_)
  )
}

p_equal_terms <- function(model, lhs = "neg_d_eav", rhs = "pos_d_eav") {
  tryCatch(fixest::wald(model, paste0(lhs, " = ", rhs))$p, error = function(e) NA_real_)
}

lincom_sum <- function(model, terms, label = NULL) {
  b <- stats::coef(model)
  V <- tryCatch(stats::vcov(model), error = function(e) NULL)
  if (is.null(V) || !all(terms %in% names(b)) || !all(terms %in% rownames(V))) {
    return(tibble(
      model = label %||% deparse(substitute(model)),
      N = tryCatch(stats::nobs(model), error = function(e) NA_integer_),
      lagged_magnitude = NA_real_,
      std_error = NA_real_,
      A_upper_bound = NA_real_,
      lagged_p = NA_real_
    ))
  }
  est <- sum(b[terms])
  Vsub <- V[terms, terms, drop = FALSE]
  se <- sqrt(sum(Vsub))
  tibble(
    model = label %||% deparse(substitute(model)),
    N = tryCatch(stats::nobs(model), error = function(e) NA_integer_),
    lagged_magnitude = est,
    std_error = se,
    A_upper_bound = est + 1.645 * se,
    lagged_p = 2 * pnorm(abs(est / se), lower.tail = FALSE)
  )
}

sample_index <- function(model, data) {
  idx <- tryCatch(fixest::obs(model), error = function(e) NULL)
  if (!is.null(idx)) return(idx)
  # fallback: mark complete cases for variables used in the model is not perfect,
  # but prevents hard failure if fixest::obs changes.
  seq_len(nrow(data))
}

safe_first_stage_f <- function(model) {
  # fixest exposes several IV fit statistics, but names differ across versions.
  out <- tryCatch(fixest::fitstat(model, "ivf1"), error = function(e) NULL)
  if (is.null(out)) return(NA_real_)
  as.numeric(unlist(out))[1]
}
```

```{r}
#| label: tbl-05-iv-type
#| results: asis
include_table("v22_table_05_IV_by_type_upper_bounds.html")
```

## Table 6. All agencies OLS with asymmetric effects

```{r}
#| label: tbl-06-asym-ols-all
#| results: asis
include_table("v22_table_06_OLS_all_agencies_asym.html")
```

## Table 6. OLS asymmetric upper-bound summary

```{r}
#| label: tbl-06-asym-ols-upper
#| results: asis
include_table("v22_table_06_OLS_all_agencies_asym_upper_bounds.html")
```

## Table 7. All agencies IV with asymmetric effects

```{r}
#| label: tbl-07-asym-iv-all
#| results: asis
include_table("v22_table_07_IV_all_agencies_asym.html")
```

## Table 7. IV asymmetric upper-bound summary

```{r}
#| label: tbl-07-asym-iv-upper
#| results: asis
include_table("v22_table_07_IV_all_agencies_asym_upper_bounds.html")
```

## Table 8. OLS by agency type with asymmetric effects

```{r}
#| label: tbl-08-asym-ols-type
#| results: asis
include_table("v22_table_08_OLS_by_type_asym_upper_bounds.html")
```

## Table 9. IV by agency type with asymmetric effects

```{r}
#| label: tbl-09-asym-iv-type
#| results: asis
include_table("v22_table_09_IV_by_type_asym_upper_bounds.html")
```

## Table 10. All agencies OLS with lagged EAV effects

```{r}
#| label: tbl-10-lag-ols-all
#| results: asis
include_table("v22_table_10_OLS_all_agencies_lagged.html")
```

## Table 10. Sum of current and lagged effects

```{r}
#| label: tbl-10-lag-sums
#| results: asis
include_table("v22_table_10_OLS_all_agencies_lagged_sums.html")
```

## Table 11. OLS by agency type with lagged EAV effects

```{r}
#| label: tbl-11-lag-ols-type
#| results: asis
include_table("v22_table_11_OLS_by_type_lagged_upper_bounds.html")
```

# Appendix tables


# A1. Instrument validity

```{r}
#| label: tbl-instrument-validity
#| results: asis
include_table("instrument_validity_checks.html")
```


## Table A2. OLS by agency type point estimates

```{r}
#| label: tbl-a2-ols-type-points
#| results: asis
include_table("v22_table_A2_OLS_by_type_point_estimates.html")
```

## Table A3. IV by agency type point estimates

```{r}
#| label: tbl-a3-iv-type-points
#| results: asis
include_table("v22_table_A3_IV_by_type_point_estimates.html")
```

## Table A4. OLS symmetry tests

```{r}
#| label: tbl-a4-ols-symmetry
#| results: asis
include_table("v22_table_A4_OLS_by_type_asym_p_equal.html")
```

## Table A5. OLS asymmetric point estimates

```{r}
#| label: tbl-a5-ols-asym-points
#| results: asis
include_table("v22_table_A5_OLS_by_type_asym_point_estimates.html")
```

## Table A6. IV symmetry tests

```{r}
#| label: tbl-a6-iv-symmetry
#| results: asis
include_table("v22_table_A6_IV_by_type_asym_p_equal.html")
```

## Table A7. IV asymmetric point estimates

```{r}
#| label: tbl-a7-iv-asym-points
#| results: asis
include_table("v22_table_A7_IV_by_type_asym_point_estimates.html")
```

## Table A8. Lagged model p-values

```{r}
#| label: tbl-a8-lag-pvalues
#| results: asis
include_table("v22_table_A8_OLS_by_type_lagged_p_values.html")
```

## Table A9. Lagged model point estimates

```{r}
#| label: tbl-a9-lag-points
#| results: asis
include_table("v22_table_A9_OLS_by_type_lagged_point_estimates.html")
```
