---
title: "Levy Elasticity Paper Tables"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

<style>
/* Notes created by modelsummary/tinytable */
table[id^="tinytable_"] tfoot td {
  text-align: left !important;
}

/* Notes created by save_df_table() */
.table-note {
  text-align: left !important;
  width: 100%;
}
</style>

```{r}
#| label: setup
#| include: false

library(htmltools)
library(fs)

table_dir <- fs::path("results", "tables_corrected_clustered_v7_4")

include_table <- function(file) {
  table_path <- fs::path(table_dir, file)

  if (!fs::file_exists(table_path)) {
    htmltools::HTML(
      paste0(
        '<div class="callout callout-style-default callout-warning">',
        '<div class="callout-header"><strong>Missing table</strong></div>',
        '<div class="callout-body"><code>',
        htmltools::htmlEscape(as.character(table_path)),
        '</code></div></div>'
      )
    )
  } else {
    htmltools::includeHTML(table_path)
  }
}
```



```{r}
#| eval: false
#| echo: true
source("scripts/descriptive_stats_22_lags_cluster_corrected_v7_4_1.R")
quarto::quarto_render("levy_paper_tables_v7_4.qmd")
```

# Main paper tables

## Table 2. All-agency OLS models

```{r}
#| label: tbl-02-ols-all
#| results: asis
include_table("v22_table_02_OLS_all_agencies.html")
```

### Table 2 upper-bound summary

```{r}
#| label: tbl-02-ols-upper
#| results: asis
include_table("v22_table_02_OLS_all_agencies_upper_bounds.html")
```

## Table 3. All-agency IV models

```{r}
#| label: tbl-03-iv-all
#| results: asis
include_table("v22_table_03_IV_all_agencies.html")
```

### Table 3 upper-bound and diagnostic summary

The coefficient test asks whether the IV estimate differs from zero.
p_exog asks whether OLS treatment of EAV growth as exogenous appears defensible.
The first-stage statistic asks whether reassessment year predicts EAV growth strongly enough to identify the IV coefficient.

Failure to reject exogeneity also does not prove exogeneity, especially when the instrument is weak

```{r}
#| label: tbl-03-iv-upper
#| results: asis
include_table("v22_table_03_IV_all_agencies_upper_bounds.html")
```

## Table 4. OLS models by agency type


> Comparing stars across columns does not show if agency types differ. It does not imply that the school and township coefficients differ significantly. A formal comparison requires a pooled interaction model or an appropriate cross-group Wald test. Text shouldn't say significant for schools and not significant for townships, for example.


### Wide upper-bound table

```{r}
#| label: tbl-04-ols-type-wide
#| results: asis
include_table("v22_table_04_OLS_by_type_upper_bounds.html")
```

### Long upper-bound table

```{r}
#| label: tbl-04-ols-type-long
#| results: asis
include_table("v22_table_04_OLS_by_type_upper_bounds_long.html")
```

## Table 5. IV models by agency type

Shows whether the IV coefficient differs from zero separately by agency type.


The table should report, for every model:

- a cluster-robust first-stage Wald/Kleibergen–Paap statistic;

- first-stage partial R2, if practical;

- a weak-IV-robust confidence interval or test when strength is questionable;

- optionally the exogeneity-test p-value.


### Wide upper-bound table

```{r}
#| label: tbl-05-iv-type-wide
#| results: asis
include_table("v22_table_05_IV_by_type_upper_bounds.html")
```

### Long upper-bound table

```{r}
#| label: tbl-05-iv-type-long
#| results: asis
include_table("v22_table_05_IV_by_type_upper_bounds_long.html")
```


### Table 5C. IV diagnostics by agency type

```{r}
#| label: tbl-05c-iv-type-diagnostics
#| results: asis
include_table(
  "v22_table_05_C_IV_by_type_diagnostics.html"
)
```


## Table 6. All-agency asymmetric OLS models

```{r}
#| label: tbl-06-asym-ols-all
#| results: asis
include_table("v22_table_06_OLS_all_agencies_asym.html")
```

### Table 6 positive and negative upper-bound summary

```{r}
#| label: tbl-06-asym-ols-upper
#| results: asis
include_table("v22_table_06_OLS_all_agencies_asym_upper_bounds.html")
```

### Table 6B. OLS upper bounds for positive and negative EAV changes

```{r}
#| label: tbl-06b-asym-ols-upper
#| results: asis
include_table("v22_table_06_B_OLS_all_agencies_asym_pos_neg_upper_bounds.html")
```

## Table 7. All-agency asymmetric IV models

```{r}
#| label: tbl-07-asym-iv-all
#| results: asis
include_table("v22_table_07_IV_all_agencies_asym.html")
```

### Table 7 positive and negative upper-bound summary

```{r}
#| label: tbl-07-asym-iv-upper
#| results: asis
include_table("v22_table_07_IV_all_agencies_asym_upper_bounds.html")
```

### Table 7B. IV upper bounds for positive and negative EAV changes

```{r}
#| label: tbl-07b-asym-iv-upper
#| results: asis
include_table("v22_table_07_B_IV_all_agencies_asym_pos_neg_upper_bounds.html")
```

### Table 7C. First-stage diagnostics

```{r}
#| label: tbl-07c-asym-iv-first-stage
#| results: asis
include_table("v22_table_07_C_IV_all_agencies_asym_first_stage.html")
```

### Table 7D. Alternative negative generated instrument

```{r}
#| label: tbl-07d-asym-iv-alt
#| results: asis
include_table("v22_table_07_D_IV_all_agencies_asym_alt_neg_instrument_pos_neg_upper_bounds.html")
```

## Table 8. Asymmetric OLS models by agency type

### Wide upper-bound table

```{r}
#| label: tbl-08-asym-ols-type-wide
#| results: asis
include_table("v22_table_08_OLS_by_type_asym_upper_bounds.html")
```

### Long upper-bound table

```{r}
#| label: tbl-08-asym-ols-type-long
#| results: asis
include_table("v22_table_08_OLS_by_type_asym_upper_bounds_long.html")
```

### Table 8B wide positive and negative upper-bound table

```{r}
#| label: tbl-08b-asym-ols-type-wide
#| results: asis
include_table("v22_table_08_B_OLS_by_type_asym_pos_neg_upper_bounds.html")
```

### Table 8B long positive and negative upper-bound table

```{r}
#| label: tbl-08b-asym-ols-type-long
#| results: asis
include_table("v22_table_08_B_OLS_by_type_asym_pos_neg_upper_bounds_long.html")
```

## Table 9. Asymmetric IV models by agency type

### Wide upper-bound table

```{r}
#| label: tbl-09-asym-iv-type-wide
#| results: asis
include_table("v22_table_09_IV_by_type_asym_upper_bounds.html")
```

### Long upper-bound table

```{r}
#| label: tbl-09-asym-iv-type-long
#| results: asis
include_table("v22_table_09_IV_by_type_asym_upper_bounds_long.html")
```

### Table 9B wide positive and negative upper-bound table

```{r}
#| label: tbl-09b-asym-iv-type-wide
#| results: asis
include_table("v22_table_09_B_IV_by_type_asym_pos_neg_upper_bounds.html")
```

### Table 9B long positive and negative upper-bound table

```{r}
#| label: tbl-09b-asym-iv-type-long
#| results: asis
include_table("v22_table_09_B_IV_by_type_asym_pos_neg_upper_bounds_long.html")
```

### Table 9C. First-stage diagnostics by agency type

```{r}
#| label: tbl-09c-asym-iv-type-first-stage
#| results: asis
include_table("v22_table_09_C_IV_by_type_asym_first_stage_long.html")
```

### Table 9D. Alternative negative generated instrument by agency type

```{r}
#| label: tbl-09d-asym-iv-type-alt
#| results: asis
include_table("v22_table_09_D_IV_by_type_asym_alt_neg_instrument_long.html")
```

## Table 10. All-agency OLS models with lagged EAV effects

```{r}
#| label: tbl-10-lag-ols-all
#| results: asis
include_table("v22_table_10_OLS_all_agencies_lagged.html")
```

### Table 10 cumulative current and lagged effects

```{r}
#| label: tbl-10-lag-sums
#| results: asis
include_table("v22_table_10_OLS_all_agencies_lagged_sums.html")
```

## Table 11. OLS models with lagged EAV effects by agency type

### Wide upper-bound table

```{r}
#| label: tbl-11-lag-ols-type-wide
#| results: asis
include_table("v22_table_11_OLS_by_type_lagged_upper_bounds.html")
```

### Long upper-bound table

```{r}
#| label: tbl-11-lag-ols-type-long
#| results: asis
include_table("v22_table_11_OLS_by_type_lagged_upper_bounds_long.html")
```

# Appendix and diagnostic tables

## Table A1. Instrument relevance

The excluded variable F-test (often called the first-stage F-test) in an Instrumental Variable (IV) model is a diagnostic test used to check the strength of your instruments. It determines if your excluded instruments are sufficiently correlated with the endogenous explanatory variables to avoid weak instrument bias

Interpreting the Test: 

The Null Hypothesis (\(H_{0}\)): The excluded instruments are irrelevant (i.e., they do not jointly predict the endogenous variable in the first stage).

Rule of Thumb: A standard rule of thumb is that the F-statistic should be greater than 10. If the F-test yields a value below 10, it generally indicates weak instruments, meaning your IV estimates may be biased and standard errors may be unreliable.

Modern Standards: Modern econometric guidance (such as Lee et al., 2022) suggests targeting higher F-statistics (e.g., >104.7) to guarantee robustness at a 5% significance level.

```{r}
#| label: tbl-a1-instrument-validity
#| results: asis
include_table("instrument_validity_checks.html")
```

## Table A2. OLS point estimates by agency type

### Wide point-estimate table

```{r}
#| label: tbl-a2-ols-type-points-wide
#| results: asis
include_table("v22_table_A2_OLS_by_type_point_estimates_wide.html")
```

### Long point-estimate table

```{r}
#| label: tbl-a2-ols-type-points-long
#| results: asis
include_table("v22_table_A2_OLS_by_type_point_estimates.html")
```

## Table A3. IV point estimates by agency type

### Wide point-estimate table

```{r}
#| label: tbl-a3-iv-type-points-wide
#| results: asis
include_table("v22_table_A3_IV_by_type_point_estimates_wide.html")
```

### Long point-estimate table

```{r}
#| label: tbl-a3-iv-type-points-long
#| results: asis
include_table("v22_table_A3_IV_by_type_point_estimates.html")
```

## Table A4. OLS symmetry tests

```{r}
#| label: tbl-a4-ols-symmetry
#| results: asis
include_table("v22_table_A4_OLS_by_type_asym_p_equal.html")
```

## Table A5. OLS asymmetric point estimates for positive EAV changes

### Wide point-estimate table

```{r}
#| label: tbl-a5-ols-asym-points-wide
#| results: asis
include_table("v22_table_A5_OLS_by_type_asym_point_estimates_wide.html")
```

### Long point-estimate table

```{r}
#| label: tbl-a5-ols-asym-points-long
#| results: asis
include_table("v22_table_A5_OLS_by_type_asym_point_estimates.html")
```

### Table A5B. OLS asymmetric point estimates for positive and negative EAV changes

#### Wide point-estimate table

```{r}
#| label: tbl-a5b-ols-asym-points-pos-neg-wide
#| results: asis
include_table("v22_table_A5_B_OLS_by_type_asym_point_estimates_pos_neg_wide.html")
```

#### Long point-estimate table

```{r}
#| label: tbl-a5b-ols-asym-points-pos-neg-long
#| results: asis
include_table("v22_table_A5_B_OLS_by_type_asym_point_estimates_pos_neg.html")
```

## Table A6. IV symmetry tests

```{r}
#| label: tbl-a6-iv-symmetry
#| results: asis
include_table("v22_table_A6_IV_by_type_asym_p_equal.html")
```

## Table A7. IV asymmetric point estimates for positive EAV changes

### Wide point-estimate table

```{r}
#| label: tbl-a7-iv-asym-points-wide
#| results: asis
include_table("v22_table_A7_IV_by_type_asym_point_estimates_wide.html")
```

### Long point-estimate table

```{r}
#| label: tbl-a7-iv-asym-points-long
#| results: asis
include_table("v22_table_A7_IV_by_type_asym_point_estimates.html")
```

### Table A7B. IV asymmetric point estimates for positive and negative EAV changes

#### Wide point-estimate table

```{r}
#| label: tbl-a7b-iv-asym-points-pos-neg-wide
#| results: asis
include_table("v22_table_A7_B_IV_by_type_asym_point_estimates_pos_neg_wide.html")
```

#### Long point-estimate table

```{r}
#| label: tbl-a7b-iv-asym-points-pos-neg-long
#| results: asis
include_table("v22_table_A7_B_IV_by_type_asym_point_estimates_pos_neg.html")
```

## Table A8. P-values for cumulative current and lagged effects

```{r}
#| label: tbl-a8-lag-pvalues
#| results: asis
include_table("v22_table_A8_OLS_by_type_lagged_p_values.html")
```

## Table A9. Cumulative current and lagged point estimates

### Wide point-estimate table

```{r}
#| label: tbl-a9-lag-points-wide
#| results: asis
include_table("v22_table_A9_OLS_by_type_lagged_point_estimates_wide.html")
```

### Long point-estimate table

```{r}
#| label: tbl-a9-lag-points-long
#| results: asis
include_table("v22_table_A9_OLS_by_type_lagged_point_estimates.html")
```
