---
title: "Levy Elasticity"
subtitle: "April 2024 Update"
author: "MVH & AWM"
format: 
  html:
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left-body
---

# Model Discussion

We believe [MODEL] represents the best model.

## Variables

[Mention grouping and how we'll move forward calling them municipalities or something.]

### Independent Variable

ln(levy) 

### Dependent Variables

ln(av) - natural log of the muni's levy. Used to reflect the tax base in lieu of EAV because it shows greater variation, lacks the EQ factor, doesn't include exemptions, [Alea add stuff].

## To (2W) Fixed or Not Fixed Effects

During an earlier iteration of our research design, we argued that two-way fixed effects were inappropriate given our use of a reassessment as the exogenous shock allowing us make a causal argument. Our current model neither makes a causal argument nor uses reassessment as a shock. Thus, the question is moot and we can use forward 

# Data Discussion

We are using the "gm_for_pivots.csv" file made in "models.qmd".

Creation of the data set can be replicated with the whatever.qmd file.

# Models

```{r setup, output = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = TRUE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(prediction)


set_summ_defaults(digits = 2, robust = "HC5")

gm <- read.csv("gm_for_pivots.csv")

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 
```

## Basic Models (e.g., ln(levy) \~ ln(av) + e)

```{r basic}

basic1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(basic1, basic2, basic3)

modnames <- list("No AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            AIC = "AIC",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

basic_table <- set_caption(ht, "Dependent Variable: ln(levy)")

print(basic_table)
```

## Reassessment Lag Dummy Variable

```{r reassess_lag_table_1}

relag1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

relag2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

relag3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(relag1, relag2, relag3)

modnames <- list("0 AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_lag_table <- set_caption(ht, "Dependent Variable: ln(levy); Interactions w/ lag(reassess_year)")

print(reassess_lag_table)
```

Let's try playing adding regular reassessment_year!

```{r reassess_table_1}

reass1_1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass1_2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass1_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(reass1_1, reass1_2, reass1_3)

modnames <- list("0 AV Lag", "1 AV Lag", "2 AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            "AIC" = "AIC",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_table_1 <- set_caption(ht, "Dependent Variable: ln(levy)")

print(reassess_table_1)

```
Crazy LSAT mix-and-match time!

```{r reassess_table_LSAT}

reass2_1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_2 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(reass2_1, reass2_2, reass2_3, reass2_4)

modnames <- list("Standard Model (2 AV Lags)", "ln(AV)", "1st AV Lag", "2nd AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

reassess_table_LSAT <- set_caption(ht, "Dependent Variable: ln(levy); Interactions w/ Reassessment Year")

print(reassess_table_LSAT)

```


## Polynomial Models

```{r polymodels}

poly1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly2 <- plm(log_levy ~ log_av + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(poly1, poly2, poly3, poly4)

modnames <- list("Standard Model (2 AV Lags)", "No Lag", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "hc5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-statistic" = "statistic",
                            "p-value" = "p.value"))

lag_table <- set_caption(ht, "Dependent Variable: ln(levy)")

print(lag_table)
```

# Goodness of Fit

[TBD]

```{r, eval = FALSE}


⁠sst <- with(panel.data, sum((lifeExp - mean(lifeExp))^2))

⁠m1.sse <- t(residuals(m1)) %*% residuals(m1)

⁠m1.r2 <- (sst - m1.sse) / sst

⁠N = dim(panel.data[1]

⁠1 - (1 - m1.r2)*((N - 1)/(N - length(coef(m1)) - 1))
```
