---
title: "Home Rule Municipalities' Levies' Responsiveness to the Tax Base"
subtitle: "April 2024 Update"
author: "MVH & AWM"
format: 
  html:
    theme: lumen
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 200px
---


# Model Decision

ln(levy) = ln(av) + lag(ln(av)) + lag(ln(av), 2) + lag(ln(av)\^2)

Plain language: regress the log of the levy on the log of av, two lags of the log of av, and a lagged binomial of logged av.

# Data and Variables Discussion

## Sample

Taxing agencies are grouped together if they share a geographic tax base with other taxing agencies. This allows ups to sum the amount levied against the taxable AV. The final version of the grouped labels were created manually, but they were largely based off of taxing agencies the shared taxable EAVs, or the first 6 digits of their agency number. `grouped_labels.csv` contains the names used for grouping taxing agencies that share a geographic location. It also helps address the concern of creation or ending of taxing agencies (e.g. specific taxing agencies for Libraries within a municipality).

## Variables

### Dependent Variable

ln(levy)

### Independent Variables

-   ln(av) - natural log of the municipalities taxable assessed value.
-   lag(ln(av)) - assessment years are 1 year before the tax year. There is also a 1 year delay where the AV declines slightly due to appeals.
-   lag(ln(av)\^2)

*Two reasons for the polynomial:*

1.  We hypothesize that the levy's responsiveness to the tax base's size is non-linear.
2.  Exploratory data analysis (visualizations) further suggested diminishing marginal returns in responsiveness to the tax base.

We *did not* try throwing this variable into the model first to see what happened second.

We *did* use a notepad, colored pens, and some pre-calc to verify where the exponent needed to go vis-a-vi the ln() operator.

## To (2W) Fixed or Not Fixed Effects

During an earlier iteration of our research design, we argued that two-way fixed effects were inappropriate given our use of a reassessment as the exogenous shock allowing us make a causal argument. Our current model neither makes a causal argument nor uses reassessment as a shock. Thus, the question is moot and we can move forward using 2WFE.

# Data Discussion

We are using the `gm_for_pivots.csv` and `gm_nochi_for_pivots.csv` file made in `models.qmd` & `panel_replication.qmd`.

Creation of the data set can be replicated with the `panel_replication.qmd` file.

## Outstanding Question

-   Our results are robust to Chicago's inclusion/exclusion from the model.

Which goes into the appendix?

::: {style="color:red"}
(Michael thinks Chicago inflates our standard errors and thus including it in our data is unsporting.)
:::

# Models

Load necessary packages, import data, convert to panel data.

```{r setup}
#| code-fold: false
#| output: false

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(prediction)


set_summ_defaults(digits = 2, robust = "HC5")

gm <- read.csv("gm_for_pivots.csv")

gm_nochi <- read.csv("gm_nochi_for_pivots.csv")

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year"))

nochi_pd <- pdata.frame(gm_nochi, 
                        index = c("uniqueid", "year"))
```


# Percent Change Over Time

```{r}



nochi_pd$av_pct_change = round((nochi_pd$av - lag(nochi_pd$av,1)) / (nochi_pd$av), digits = 4)

nochi_pd$levy_pct_change = round((nochi_pd$total_final_levy - lag(nochi_pd$total_final_levy,1)) / (nochi_pd$total_final_levy), digits = 4)

library(tidyverse)
```



```{r}
ggplot(data = nochi_pd %>% filter(av_pct_change > -.1 & av_pct_change < .1), 
aes(x=year, y = av_pct_change, group = grouped_label, color = Triad)) + geom_line() + labs(title="Obs between -.1 & +.1")
 
ggplot(data = nochi_pd %>% filter(av_pct_change > -.2 & av_pct_change < .2), 
aes(x=year, y = av_pct_change, group = grouped_label, color = Triad)) + geom_line() + labs(title="Obs between -.2 & +.2") 

# ggplot(data = nochi_pd %>% filter(av_pct_change < -.1 | av_pct_change > .1), 
#        aes(x=year, y = av_pct_change, group = grouped_label, color = Triad, label = grouped_label) ) + 
#   geom_line() + 
#   labs(title = "Above 10% or -10% yearly change. \nobs dropped from other graph")
```


```{r}

ggplot(data = nochi_pd %>% filter( levy_pct_change > -.5),
       aes(x=year, y = levy_pct_change, group = grouped_label, color = Triad)) +
  geom_line() +
  labs(title = "Levy Growth")


ggplot(data = nochi_pd %>% filter( levy_pct_change > -.2),
       aes(x=year, y = levy_pct_change, group = grouped_label, color = Triad)) +
  geom_line() +
  labs(title = "Levy Growth")

ggplot(data = nochi_pd,
       aes(x=year, y = total_final_levy, group = grouped_label, color = Triad)) +
  geom_line() +
  labs(title = "Levy Growth")

ggplot(data = nochi_pd %>% 
         filter(levy_pct_change > -.1 & levy_pct_change < .1), 
       aes(x=year, y = levy_pct_change, group = grouped_label, color = Triad)) +
  geom_line() +
 # geom_smooth() + 
  labs(title = "Levy Growth", subtitle = "Obs between -.1 & +.1")


ggplot(data = nochi_pd %>% filter(levy_pct_change > -.2 & levy_pct_change < .2), 
aes(x=year, y = levy_pct_change, group = grouped_label, color = Triad)) + geom_line() + labs(title = "Levy Growth", subtitle="Obs between -.2 & +.2")

ggplot(data = nochi_pd %>% filter(levy_pct_change < -.1 | av_pct_change > .1), 
aes(x=year, y = levy_pct_change, group = grouped_label, color = Triad)) + geom_line() +
  labs(title = "Levy Growth", subtitle = "Above 10% or -10% yearly change. \nobs dropped from other graph")
```

```{r}
gm_nochi <- read.csv("gm_nochi_for_pivots.csv")


gm_nochi <- gm_nochi %>% 
  group_by(grouped_label) %>% 
  # filter(year >= 2011) %>%
  mutate(
  levy_idx = total_final_levy / (total_final_levy[year == "2011"]),
  av_idx = av / (av[year == "2011"])) 

ggplot() +
  geom_line(data = gm_nochi %>% filter(year > 2011),
       aes(x=year, y = av_idx, group = grouped_label, color = Triad), alpha = .2) +
  geom_smooth(data = gm_nochi %>% filter(year > 2011), aes(x=year, y = av_idx, color = Triad)) + 
  labs(title = "Indexed Assessed Value")


gm_nochi %>% 
  group_by(grouped_label) %>% 
  summarize(
    #levy_cagr17 = round((((total_final_levy[year == 2022] / total_final_levy[year == 2006])^(1/17) - 1 ) * 100), digits = 3),
            
            
    #av_cagr17 = round((((av[year == 2022] / av[year == 2006])^(1/17) - 1 ) * 100), digits = 3),
            
            levy_cagr12 = round((((total_final_levy[year == 2022] / total_final_levy[year == 2011])^(1/12) - 1 ) * 100), digits = 3),
            
            av_cagr12 = round((((av[year == 2022] / av[year == 2011])^(1/12) - 1 ) * 100), digits = 3) ) %>% arrange(av_cagr12)

gm_nochi %>% 
  group_by(grouped_label) %>% 
  summarize(levy_cagr12 = round((((total_final_levy[year == 2022] / total_final_levy[year == 2011])^(1/12) - 1 ) * 100), digits = 3),
            
            av_cagr12 = round((((av[year == 2022] / av[year == 2011])^(1/12) - 1 ) * 100), digits = 3) ) %>% arrange(av_cagr12) %>%
  ggplot() + 
  geom_point(aes(x=levy_cagr12, y = av_cagr12, group = grouped_label) ) + 
  geom_text(aes(x=levy_cagr12, y = av_cagr12 + .5, label = grouped_label), size = 3) + theme_classic() + 
  labs(title = "12-year CAGR, 2011-2022", x = "Levy CAGR", y = "AV CAGR") + 
  scale_x_continuous(limits = c(-3, 9), breaks = c(-3, 0, 3, 6, 9) ) 



gm_nochi %>% 
  group_by(grouped_label) %>% 
  summarize(levy_cagr12 = round((((total_final_levy[year == 2022] / total_final_levy[year == 2011])^(1/12) - 1 ) * 100), digits = 3),
            
            av_cagr12 = round((((av[year == 2022] / av[year == 2011])^(1/12) - 1 ) * 100), digits = 3) ) %>% arrange(av_cagr12) %>%
  ggplot() + 
  geom_point(aes(y=levy_cagr12, x = av_cagr12, group = grouped_label) ) + 
  geom_text(aes(y=levy_cagr12, x = av_cagr12 + .5, label = grouped_label), size = 3) +  
  labs(title = "12-year CAGR, 2011-2022", y = "Levy CAGR", x = "AV CAGR") + 
  scale_y_continuous(limits = c(-3, 9), breaks = c(-3, 0, 3, 6, 9) ) 


# 
# gm_nochi %>% 
#   as.data.frame() %>% ungroup() %>%
#   reframe(levy_cagr12 = round((((total_final_levy[year == 2022] / total_final_levy[year == 2011])^(1/12) - 1 ) * 100), digits = 3),
#             
#             av_cagr12 = round((((av[year == 2022] / av[year == 2011])^(1/12) - 1 ) * 100), digits = 3), by = NULL )

```


## Basic Model: ln(levy) \~ ln(av)

::: callout-warning
Note: If you have tidyverse loaded from working on some other file in R, the output in all models will be WRONG because the lagged variable will not be calculated correctly. Either close R and open only this file and run it OR use \`detach("package:dplyr", unload = TRUE)\` and \`detach("package:dplyr", unload = TRUE )\`
:::

```{r}
#| label: tbl-basic_w_Chi
#| tbl-cap: Includes Chicago
# 
detach("package:dplyr", unload = TRUE)
detach("package:tidyverse", unload = TRUE)


basic1_1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic1_2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic1_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(basic1_1, basic1_2, basic1_3)

modnames <- list("No AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

basic_table <- set_caption(ht, "Dependent Variable: ln(levy)")

print(basic_table)
```

```{r}
#| label: tbl-basic-wo-chi
#| tbl-cap: Excludes Chicago


basic1_nochi <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

basic2_nochi <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

basic3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(basic1_nochi, basic2_nochi, basic3_nochi)

modnames <- list("No AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

basic_table_nochi <- set_caption(ht, "Dependent Variable: ln(levy) (Excludes Chicago)")

print(basic_table_nochi)
```

## Basic Model w/ Polynomial

```{r tbl-polymodels}

poly1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly2 <- plm(log_levy ~ log_av + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(poly1, poly2, poly3, poly4)

modnames <- list("Standard Model (2 AV Lags)", "No Lag", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-statistic" = "statistic",
                            "p-value" = "p.value"))

poly_table <- set_caption(ht, "Dependent Variable: ln(levy)")

print(poly_table)
```

```{r tbl-polymodels_nochi}

poly1_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

poly2_nochi <- plm(log_levy ~ log_av + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

poly3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

poly4_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(poly1_nochi, poly2_nochi, poly3_nochi, poly4_nochi)

modnames <- list("Standard Model (2 AV Lags)", "No Lag", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-statistic" = "statistic",
                            "p-value" = "p.value"))

poly_table_nochi <- set_caption(ht, "Dependent Variable: ln(levy) (Excludes Chicago)")

print(poly_table_nochi)

```

# Robustness Checks

## Plot Model Residuals

The best model appears to use 1 lag of ln(av) and the binomial lag(ln(av)\^2).

```{r }
#| label: graphresiduals

best_mod <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

best_mod_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

pred_best <- prediction(best_mod, data = gm_pd)

pred_best_nochi <- prediction(best_mod_nochi, data = nochi_pd)

```

```{r}
#| label: fig-residuals
#| layout-ncol: 2
#| fig-subcap: 
#|      - "Best Model Residuals (Includes Chicago)"
#|      - "Best Model Residuals (Excludes Chicago)"

library(tidyverse)

pred_best <- pred_best %>%
  mutate(resid = log_levy - fitted)

pred_best_nochi <- pred_best_nochi %>%
  mutate(resid = log_levy - fitted)

pred_best %>%
  ggplot(aes(x = log_levy, y = resid), alpha = .5) +
  geom_point() +
  theme_classic() #  + labs(title = "Best Model Residuals")

pred_best_nochi %>%
  ggplot(aes(x = log_levy, y = resid), alpha = .5) +
  geom_point() +
  theme_classic() # + labs(title = "Best Model Residuals (Excludes Chicago)" )

```

## Other models

### Reassessment Lag Dummy Interacted w/ ln(av)

```{r tbl-reassess_lag_table}
detach("package:dplyr", unload=TRUE)
relag1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

relag2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

relag3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(relag1, relag2, relag3)

modnames <- list("0 AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

ht
```

```{r tbl-reassess_lag_table_nochi}

relag1_nochi <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

relag2_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

relag3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(relag1_nochi, relag2_nochi, relag3_nochi)

modnames <- list("0 AV Lags", "1 AV Lag", "2 AV Lags")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

ht
```

### Reassment Dummy Interacted w/ ln(AV)

```{r reassess_table_1}

reass1_1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass1_2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass1_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(reass1_1, reass1_2, reass1_3)

modnames <- list("0 AV Lag", "1 AV Lag", "2 AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

ht

```

```{r reassess_table_1_nochi}

reass1_1_nochi <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass1_2_nochi <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass1_3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(reass1_1_nochi, reass1_2_nochi, reass1_3_nochi)

modnames <- list("0 AV Lag", "1 AV Lag", "2 AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            "AIC" = "AIC",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

ht
```

### Interact reassessment w/ each AV lag.

```{r reassess_table_LSAT}

reass2_1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_2 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

reass2_4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(reass2_1, reass2_2, reass2_3, reass2_4)

modnames <- list("Standard Model (2 AV Lags)", "ln(AV)", "1st AV Lag", "2nd AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))
ht

```

```{r reassess_table_LSAT_nochi}

reass2_1_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2),
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass2_2_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass2_3_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

reass2_4_nochi <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = nochi_pd)

mods <- list(reass2_1_nochi, reass2_2_nochi, reass2_3_nochi, reass2_4_nochi)

modnames <- list("Standard Model (2 AV Lags)", "ln(AV)", "1st AV Lag", "2nd AV Lag")

ht <- export_summs(mods,
             model.names = modnames,
             robust = "HC5",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared",
                            "F-stat" = "statistic",
                            "p-value" = "p.value"))

ht
```
