---
title: "Levy Elasticity"
subtitle: "April 2024 Update"
author: "MVH & AWM"
format: 
  docx:
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left-body
---

# Model Discussion

## Variables

### Independent Variable

### Dependent Variables

## To Fixed or Not Fixed Effects

# Data Discussion

We are using the "gm_for_pivots.csv" file made in "models.qmd".

Creation of the data set can be replicated with the whatever.qmd file.

# Models

```{r setup, output = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = TRUE)

library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(prediction)


set_summ_defaults(digits = 2, robust = "HC3")

gm <- read.csv("gm_for_pivots.csv")

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 
```

## Basic Models (e.g., ln(levy) \~ ln(av) + e)

```{r basic}

basic1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

basic3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

mods <- list(basic1, basic2, basic3)

modnames <- list("0 Lags", "1 Lag", "2 Lags")

#coefs = c("ln(av)" = log_av, "lag1(ln(av))", "lag2(ln(av))")

export_summs(mods,
             model.names = modnames,
             robust = "HC3",
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            AIC = "AIC",
                            "F-stat" = "statistic",
                            "p-value"))
```

## Inclusion of Reassessment Dummy Variable

```{r reassess_dummy}


```

## Polynomial Models

```{r polymodels}


```

# Goodness of Fit

```{r}


⁠sst <- with(panel.data, sum((lifeExp - mean(lifeExp))^2))

⁠m1.sse <- t(residuals(m1)) %*% residuals(m1)

⁠m1.r2 <- (sst - m1.sse) / sst

⁠N = dim(panel.data[1]

⁠1 - (1 - m1.r2)*((N - 1)/(N - length(coef(m1)) - 1))
```

# A Quick Note on Chicago
