---
title: "February 1 Update"
author: "MVH & AWM"
format: pptx
editor: visual
---

###

Two-way fixed effects (TWFE) does not work in the context of a staggered treatment DiD design. The control group has already been "contaminated." Thus, the "parallel lines" assumption is violated.

###

A variety of solutions to this problem have been proffered:

1.  List 1

2.  List 2

3.  List 3

None of them have been widely accepted, although some papers (e.g., \[cite\]) have compared the different estimators' RMSE and computational efficiency.

###

We propose using Callaway and Sant'Anna's (2021) model:

-   Lacks a "no anticipation" requirement.

-   Allows "stacking" treatment periods.

    -   Compare across Triads

    -   Compare across reassessment cycles

-   Allows conditional parallel trends.

**Bad News: There is an R package but no Stata package.**

###

TWFE Results

```{r, eval = F}


```

###

Group-Time ATE Results

```{r, eval = F}


```

###

Next steps:

1.  Add coviariates to facilitate absence of parallel trends assumption.

2.  Compare to other post-TWFE models.
