---
title: "Model Decisions, Discussions, & Output"
subtitle: "Responsiveness of the Levy to the Tax Base"
author: "Michael Van Hulle"
date: "March 26, 2024"
format: 
  html:
    code-folding: hide
    code-line-numbers: true
    toc: true
    toc-location: left-body
---

# Model parameters discussion.

1.  Which agencies in the data set? NOTEL ALL ITEMS EXCEPT d AND e are done.
    a.  Home rule ONLY (evaluate how home rule-y the non municipalities are. Are they just subdivisions of the munis? 63 for munis vs. \~90
    b.  Qual eval of those entities
    c.  Drop border crossers
    d.  Drop agencies w/ little prop tax rev.
        a.  Create variable to measure property tax dependence. should be (total_rev - total_final_levy)/total_rev (or similar)
    e.  Grouping --- it is a concern and should be done by agency digits and eav.
2.  Variables
    1.  DV - ln(total_levy) - allows calculation of elasticity, which economists \<3
        1.  We want the levy value requested by the muni/agency to capture the agency's responsiveness to the change in the tax base. That should be the same as they received since they are HR agencies.
            1.  Check this!
    2.  IV
        1.  ln(AV)
            1.  Change in AV better reflects the change in the tax base and our RQ is about the levy's responsiveness to the tax base. Thus, irrelevant whether we use AV or EAV.
            2.  Downside: Value of exemptions could be high causing a divergence?
                1.  Alea backs AV out of EAV.
        2.  lag(ln(AV)), ln2(log(AV))
            1.  Given 3 year reassessment cycle, we want to account for the effect of the prior reassessment...especially given the trend we see of the initial bump in AV followed by the decrease from appeals.
            2.  We do not need to log them since they are control variables.\*\*
            3.  YES WE DO NEED TO LOG THEM
            4.  WE DO NOT NEED TO LOG THE OTHER NUMERIC CONTROL VARIABLES
            5.  Scratch work supporting this conclusion is in the "log_scratchwork.R" file
        3.  (ln(av))\^2
            1.  In case it is a polynomial relationship
            2.  This shouldn't cause a problem like log(av\^2), which is just 2\*log(av), leading to an irritating coefficient to interpret.
            3.  But we need to check this variable improves our model fit
        4.  lag(Reassessment year) dummy (to use with interaction term)
        5.  log(AV)\*lag(Reassess)
            1.  check if responsiveness is related to it being an assessment year
            2.  NO
            3.  Only incorporated into the budget the year after reassessment -- hence description as "lag"
3.  Other model items:
    1.  Is "year" the calendar year or the tax year? Determines whether we want to lag the reassess variable.
        1.  Alea: Year in the agency_dt is the tax year. Reassessment year might be calendar year.
        2.  We should double check this item.
    2.  2WFE are OK because we, within each year, 1/3 of the county is reassessed; we are no longer using it as a "treatment" to make causal statements.
    3.  DOUBLE CHECK TO ASSUAGE ALEA'S FEARS RE: NOT LOGGING OTHER STUFF
        1.  Upon double checking, Alea was right. Damn.
    4.  No values we plan to log are currently zero (and we can add 1 with no serious problems)

# Models

We're using the "grouped_munis.csv" data set that Alea cleaned in "CookCounty_PanelData_TFL.rmd"

```{r setup, message = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = TRUE)

library(plm)
library(stargazer)

gm <- read.csv("grouped_munis.csv")

```

## AV lags, 2WFE

-   Note: lagged av variables have already been logged.

```{r}

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(log_levy ~ log_av + av_lag,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(log_levy ~ log_av + av_lag + av_lag2,
              model = "within",
              effect = "twoways",
              data = gm_pd)

summary(simple1)
summary(simple2)
summary(simple3)
```

## reassess_lag dummy, av lags, 2WFE

```{r}

med1 <- plm(log_levy ~ log_av + reassess_lag1 + log_av*reassess_lag1,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + av_lag + reassess_lag1 + log_av*reassess_lag1,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + av_lag + av_lag2 + reassess_lag1 + log_av*reassess_lag1,
              model = "within",
              effect = "twoways",
              data = gm_pd)

summary(med1)
summary(med2)
summary(med3)

stargazer(med1, type = "html")

```

## reassess_year dummy, av lags, 2WFE

```{r}

med1.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2.1 <- plm(log_levy ~ log_av + av_lag + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3.1 <- plm(log_levy ~ log_av + av_lag + av_lag2 + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

summary(med1.1)
summary(med2.1)
summary(med3.1)

```

The PD df has 8178 observations.

```{r pd_summary, eval=FALSE}

summary(pd)
```

The pd data frame has 8178 observations.

Step 1

Let's filter our data set down to reflect the comments above.

Here, we:

1.  Create lags for AV;
2.  Filter for HR;
3.  Group by first 6;
4.  Filter out munis without levies
5.  Visually evaluate the data for stuff that's broken.

I know you already did this step! Sorry!

I ended up with 1591 obs.

```{r grouping_and_lags, eval=FALSE}

table(pd$minor_type)

pd %>%
  group_by(clean_name) %>%
  filter(home_rule_ind == 1,
         is.na(clean_name)) %>%
  select(-clean_name) %>%
  group_by(agency_num) %>%
  summarize(year, agency_name, agency_num, av, total_levy)

lagged_pd_1 <- pd %>%
  arrange(year) %>%
  group_by(agency_num) %>%
  mutate(
    av_lag_1 = lag(av)) %>%
  ungroup()

lagged_pd_1 %>%
  select(year, agency_num, av, av_lag_1) %>%
  distinct()

lagged_pd_2 <- lagged_pd_1 %>%
  group_by(agency_num) %>%
  mutate(av_lag_2 = lag(av_lag_1)) %>%
  ungroup()

# Group by summed_levy_first6; use reframe because that's how you use it!
# Let's also take out those two taxing agencies
# 1591 obs (which is the same number as if we just filtered for HR == 1 earlier on)

lagged_pd_grouped_6 <- lagged_pd_2 %>%
  group_by(first6) %>%
  reframe(year, clean_name, levy = summed_levy_first6, av,
          av_lag_1, av_lag_2, home_rule_ind) %>%
  filter(home_rule_ind == 1,
         levy >= 1) %>%
  select(-home_rule_ind) %>%
  arrange(clean_name, desc(year))

lagged_pd_grouped_6  
```

Let's check a few other things:

1.  If we group by first_6, how many taxing districts fail to have a clean_name?
    1.  LAKE CO TAX OBJ CT ORD-220, 044030010; 2022 levy = 649k
    2.  SD 122 BOND / PART ANNEXED BY SD 127 1/2 2010, 040830001, 2022 levy = 0.
    3.  Will drop both these taxing agencies for now.
2.  Some munis have multiple obs/year
3.  Filter out places with levies of 1. Assume it was to prepare a log transform when making the summed levy amts.

```{r, eval=FALSE}

lagged_pd_grouped_6 %>%
  group_by(clean_name) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

# Let's kick out everything with 17 obs.

lagged_pd_grouped_6 %>%
  group_by(clean_name) %>%
  summarize(n = n()) %>%
  filter(n != 17) %>%
  arrange(desc(n))

# What if we brute force our way to success w/ distinct()?

lagged_pd_grouped_6 %>%
  group_by(clean_name) %>%
  distinct() %>%
  summarize(n = n()) %>%
  filter(n != 17) %>%
  arrange(desc(n))

# After deduping, only 2 munis have more obs. than years.
```

-   35 munis have wrong number of obs.

    -   Of those, 33 have more obs than years.

    -   3 have fewer obs than years

-   After deduping, the following munis are ALSO missing obs.

    -   Mt Prospect

    -   Wilmette

    -   Midlothian

    -   Northfield

    -   River Grove

    -   Melrose Park

    -   Palatine

-   After de-duping, Elk Grove Village and Chicago Heights still have too many obs.

```{r, eval=FALSE}

pd %>%
  filter(clean_name %in% c('Mt Prospect', 'Wilmette', 'Midlothian', 'Northfield', 'River Grove', 'Melrose Park', 'Palatine')) %>%
  group_by(clean_name) %>%
  summarize(clean_name, agency_name, agency_num, n= n()) %>%
  distinct()
```

-   Melrose Park and Midlothian have numbers consistent with 2x17, so we need to go back and check.

-   Mt Prospect - 2x16

-   River Grove and Northfield are fine

-   Need to investigate palatine and wilmette

```{r, eval=FALSE}

pd %>%
  filter(agency_num %in% c('030960000', '031330000')) %>%
  group_by(agency_num) %>%
  ungroup() %>%
  arrange(agency_num, year) %>%
  select(year, agency_name, agency_num, av)

```

Let's toss out Mt Prospect, Palatine and Wilmette as well as the obs. without a clean name.

Need to pull back in the dropped obs for: Melrose Park, Midlothian, River Grove, and Northfield.

Let's check out Chicago Heights and Elk Grove Village.

```{r, eval=FALSE}

pd %>%
  filter(clean_name %in% c('Chicago Heights', 'Elk Grove Village')) %>%
  group_by(agency_num) %>%
  mutate(n = n()) %>%
  ungroup() %>%
  select(clean_name, year, agency_name, agency_num, n, av)

```

We need to make sure we have the right number of CITY OF CHICAGO HEIGHTS obs.

Summary:

We need to retrieve data for the following entities: Melrose Park, Midlothian, River Grove, and Northfield, and Chicago Heights.

We need to remove Mt Prospect, Palatine and Wilmette as well as the obs. without a clean name, and Elk Grove Village

```{r merge_join}


```

Detach dplyr because it breaks shit.

```{r}

detach("package:dplyr", unload = TRUE)

library(plm)

pd_final <- pdata.frame(pd_final, index = c("agency_num", "year"))
```

Detach plm and reload tidyverse to look at data. (Models not initially running.)

```{r}

pd_final %>%
  select(agency_name, agency_num, clean_name, total_levy, av) %>%
  filter(total_levy == 0) %>%
  group_by(clean_name) %>%
  summarize(clean_name, agency_num, agency_name, n = n())

pd_final %>%
  select(agency_name, agency_num, clean_name, total_levy, av) %>%
  filter(av == 0) %>%
  group_by(clean_name) %>%
  summarize(clean_name, agency_name, n = n())

```

```{r}

detach("package:dplyr", unload = TRUE)

library(plm)

```

```{r}

uglm1 <- plm(total_levy ~ av, 
              index = c("agency_num", "year"), 
              model = "within", 
              effect= "twoways",   
              data = pd_final)

uglm2 <- plm(total_levy ~ av + lag_1_av,
             data = pd_final,
             na.action = na.omit,
              index = c("agency_num", "year"), 
              model = "within",
              effect= "twoways")

uglm3 <- plm(total_levy ~ av + lag_1_av + lag_2_av,
             data = pd_final,
             na.action = na.omit,
              index = c("agency_num", "year"), 
              model = "within",
              effect= "twoways")



export_summs(uglm1, uglm2, uglm3, 
             robust = "HC3", statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))
```

```{r}

luglm1 <- plm(log(total_levy+1) ~ log(av+1), 
              data = pd_final,
              na.action = na.omit,
              index = c("agency_num", "year"), 
              model = "within", 
              effect= "twoways")

luglm2 <- plm(log(total_levy + 1) ~ log(av + 1) + log(lag_1_av + 1),
              data = pd_final,
              na.action = na.omit,
              index = c("agency_num", "year"), 
              model = "within",
              effect= "twoways")

luglm3 <- plm(log(total_levy + 1) ~ log(av + 1) + 
                log(lag_1_av + 1) + log(lag_2_av + 1),
              data = pd_final,
              na.action = na.omit,
              index = c("agency_num", "year"), 
              model = "within",
              effect= "twoways")



export_summs(luglm1, luglm2, luglm3, 
             robust = "HC3", statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))

```
