---
title: "Model Decisions, Discussions, & Output"
subtitle: "Responsiveness of the Levy to the Tax Base"
author: "Michael Van Hulle"
date: "March 26, 2024"
format: 
  html:
    code-fold: true
    code-line-numbers: true
    code-overflow: wrap
    toc: true
---

# Model parameters discussion.

1.  Which agencies in the data set? NOTEL ALL ITEMS EXCEPT d AND e are done.
    a.  Home rule ONLY (evaluate how home rule-y the non municipalities are. Are they just subdivisions of the munis? 63 for munis vs. \~90
    b.  Qual eval of those entities
    c.  Drop border crossers
    d.  Drop agencies w/ little prop tax rev.
        a.  Create variable to measure property tax dependence. should be (total_rev - total_final_levy)/total_rev (or similar)
    e.  Grouping --- it is a concern and should be done by agency digits and eav.
2.  Variables
    1.  DV - ln(total_levy) - allows calculation of elasticity, which economists \<3
        1.  We want the levy value requested by the muni/agency to capture the agency's responsiveness to the change in the tax base. That should be the same as they received since they are HR agencies.
            1.  Check this!
    2.  IV
        1.  ln(AV)
            1.  Change in AV better reflects the change in the tax base and our RQ is about the levy's responsiveness to the tax base. Thus, irrelevant whether we use AV or EAV.
            2.  Downside: Value of exemptions could be high causing a divergence?
                1.  Alea backs AV out of EAV.
        2.  lag(ln(AV)), ln2(log(AV))
            1.  Given 3 year reassessment cycle, we want to account for the effect of the prior reassessment...especially given the trend we see of the initial bump in AV followed by the decrease from appeals.
            2.  We do not need to log them since they are control variables.\*\*
            3.  YES WE DO NEED TO LOG THEM
            4.  WE DO NOT NEED TO LOG THE OTHER NUMERIC CONTROL VARIABLES
            5.  Scratch work supporting this conclusion is in the "log_scratchwork.R" file
        3.  (ln(av))\^2
            1.  In case it is a polynomial relationship
            2.  This shouldn't cause a problem like log(av\^2), which is just 2\*log(av), leading to an irritating coefficient to interpret.
            3.  But we need to check this variable improves our model fit
        4.  lag(Reassessment year) dummy (to use with interaction term)
        5.  log(AV)\*lag(Reassess)
            1.  check if responsiveness is related to it being an assessment year
            2.  NO
            3.  Only incorporated into the budget the year after reassessment -- hence description as "lag"
3.  Other model items:
    1.  Is "year" the calendar year or the tax year? Determines whether we want to lag the reassess variable.
        1.  Alea: Year in the agency_dt is the tax year. Reassessment year might be calendar year.
        2.  We should double check this item.
    2.  2WFE are OK because we, within each year, 1/3 of the county is reassessed; we are no longer using it as a "treatment" to make causal statements.
    3.  DOUBLE CHECK TO ASSUAGE ALEA'S FEARS RE: NOT LOGGING OTHER STUFF
        1.  Upon double checking, Alea was right. Damn.
    4.  No values we plan to log are currently zero (and we can add 1 with no serious problems)

# 2WFE Models with Chicago

We're using the "grouped_munis.csv" data set that Alea cleaned in "CookCounty_PanelData_TFL.rmd". This has also been recreatd in the new chunk named "AWM-setup" that is set to eval=FALSE for non-Alea coders.

TL;DNR: THE BEST MODEL SEEMS TO BE ln(av) with one lag and lag(ln(av)^2)


```{r warning = FALSE, message=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = TRUE)

library(tidyverse)
library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(prediction)
library(modelsummary)


source("helper_recode_variables.R")

groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))

grouped_manual <- recoded_data %>% 
  left_join(groupies2,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP" ### |   major_type == "MISCELLANEOUS"
           & minor_type != "MISC"
           ) %>%
  filter(minor_type != "SSA") %>% 
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE)+1,
            cty_total_eav = first(cty_total_eav), 
            av = first(av),   # should be first() not sum() --- AWM 3/30/24
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind)) %>% 
   # left_join(muni_agency_names) %>% 
    #select(-c(Column1, `Most recent reassessed`)) %>% 
    mutate(
      log_eav = log(cty_total_eav),
      log_levy = log(total_final_levy),
      log_av = log(av),  # added AWM 3/25/2024
      bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything())

 grouped_manual %>%  # 236 nonHR and 68 HR
  ungroup() %>%
  filter(year == 2021) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
 
grouped_manual %>%  # 236 nonHR and 68 HR
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())



# 1552 obs
# 2278 obs after 2022 update
# 1122 homerule munis after adding home_rule_ind filter
grouped_manual_has16 <- grouped_manual %>%  # 124 nonHR and 69 HR
  ungroup() %>%
 # filter(year == 2021) %>%
  arrange(home_rule_ind) %>%
  group_by(uniqueid) %>%
  distinct() %>%
  mutate(count = n()) %>%
  filter(count == 17 & home_rule_ind == 1) %>% 
  ungroup()


gm <- grouped_manual_has16

write.csv(gm, "gm_for_pivots.csv")


grouped_manual_has16 %>% filter(grouped_label != "Chicago") %>%  write_csv("gm_nochi_for_pivots.csv")

```

We're going to look at some pivot tables... And we're back!

## AV lags, 2WFE

```{r}
detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

#summary(simple1)
#summary(simple2)
#summary(simple3)

export_summs(simple1, simple2,  simple3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

#### Goodness of Fit stuff

```{r}

laggedDV <- plm(log_levy ~  lag(log_levy) + log_av + lag(log_av, 1) + lag(log_av,2), 
             index = c("grouped_label", "year"),
             model = "within",
             effect = "twoways",
             data = gm_pd)

export_summs(laggedDV)

gm$e <- simple1$residuals
# test of rho hat
aux_1 <- lm(e~ -1 + lag(e), data = gm)
aux_1 %>% tidy()

aux_2 <- plm(e ~ lag(e), 
             index = c("grouped_label", "year"),
             model = "within",
             effect = "twoways",
             data = gm)

nR2 <- aux_2 %>% r.squared*aux_2$df.residual
nR2 %>% 
  pchisq(1, lower.tail = F)
```

Can not reject the null hypothesis that there is no autocorelation --> 
Therefore there is autocorrelation in our panel data. Use HC5 type erroro

The estimate for correcting the autocorrelation is 0.851...

```{r}
#detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(total_final_levy ~ av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(total_final_levy ~ av + lag(av, 1),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(total_final_levy ~ av + lag(av, 1) + lag(av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

#summary(simple1)
#summary(simple2)
#summary(simple3)

export_summs(simple1, simple2,  simple3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

## reassess_lag dummy, av lags, 2WFE

```{r}

med1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)
# 
# summary(med1)
# summary(med2)
# summary(med3)
# 

export_summs(med1, med2,  med3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

```

## reassess_year dummy, av lags, 2WFE

```{r}

ass.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.5 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

huxreg(ass.1, ass.2, ass.3, ass.4, ass.5,
       statistics = c(N = "nobs", 
                      R2 = "r.squared", 
                      adj.R2 = "adj.r.squared", 
                      F = "fstatistic", 
                      `Prob>F` = "fstatistic", 
                      AIC = "AIC", 
                      BIC = "BIC"),
       title = "Regression Summary"
)

```

## AV lags, Polynomial, 2WFE

```{r}

poly1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly5 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

model_list <- list(poly1, poly2, poly3, poly4, poly5)

clean_models <- sapply(model_list, broom::tidy)

export_summs(model_list,
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            F = "fstatistic", 
                            `Prob>F` = "fstatistic", 
                            AIC = "AIC", 
                            BIC = "BIC"),
             title = "Regression Summary"
)
```

```{r}

poly4_resids <- prediction(poly.4)

poly4_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

simple3_resids <- prediction(simple3)

simple3_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

```

::: aside
Why are the residuals changing so hard once we remove Chicago???
:::



# 2WFE Models Without Chicago

```{r eval = FALSE}

gm <- gm %>% filter(grouped_label!="Chicago")

```

## AV lags, 2WFE

```{r}
detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(simple1, simple2,  simple3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}


detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(total_final_levy ~ av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(total_final_levy ~ av + lag(av, 1),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(total_final_levy ~ av + lag(av, 1) + lag(av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(simple1, simple2,  simple3, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

## reassess_lag dummy, av lags, 2WFE

```{r}

med1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(med1, med2,  med3, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

```

## reassess_year dummy, av lags, 2WFE

```{r}

med1.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2.1 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3.1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(med1.1, med2.1,  med3.1, , 
          statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared")
          )

```

## AV lags, Polynomial, 2WFE

```{r}

poly.1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(poly.1, poly.2, poly.3, poly.4, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}

library(prediction)

poly4_resids <- prediction(poly.4)

poly4_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

simple3_resids <- prediction(simple3)

simple3_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

```

::: aside
Why are the residuals changing so hard once we remove Chicago???
:::

# Random Effects

## AV lags

```{r}

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

pool1 <- plm(log_levy ~ log_av,
              model = "random",
              effect = "twoways",
              data = gm_pd)

pool2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "random",
              effect = "twoways",
              data = gm_pd)

pool3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "random",
              effect = "twoways",
              data = gm_pd)

models <- list(pool1, pool2, pool3)

export_summs(models, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

```
## Reassessment Year Dummy

```{r}
med1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "random",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "random",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "random",
              effect = "twoways",
              data = gm_pd)

export_summs(med1, med2,  med3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

## Interacted with all the things.

```{r}

ass.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.5 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

huxreg(ass.1, ass.2, ass.3, ass.4, ass.5,
       statistics = c(N = "nobs", 
                      R2 = "r.squared", 
                      adj.R2 = "adj.r.squared", 
                      F = "fstatistic", 
                      `Prob>F` = "fstatistic", 
                      AIC = "AIC", 
                      BIC = "BIC"),
       title = "Regression Summary"
)

```

