---
title: "Replication Code for NTA Panel Data"
author: "AWM & MVH"
date: "October 13, 2024"
format: 
  html:
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left
    cap-location: margin
    df-print: default
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 200px
---

**Files needed for panel creation replication:**

-   agency_reassessmentyears.csv
-   cpi.csv
-   eq_factor.csv
-   panel_data_blindcoded.xlsx

## Code Cleaning Steps

-   90% within Cook County 
-   Does not change home rule status during sample years 

### Slightly more detail on cleaning process:

**Some taxing agencies are missing their cty_cook_eav & cty_total_eav even though they have a total_final_levy value** 

-   Using the logic that the tax rate = levy / taxable EAV, then we can back out the EAV by  using the total_final_levy and total_final_rate variables. 
-   Taxable EAV = total_final_levy / (total_final_rate) / 100 
- A Couple municipalities had missing levies and were manually entered by looking up the CAGR and historic levy amounts in the document

**Remove taxing agencies that had a levy = \$0 for any year. Drop values for all years.**  

-   Countryside, Deer Park, Homer Glen, ~~Norridge~~, Oak Brook, Schaumburg, Dixmoor (2011 only) are dropped using \`dropped_munis \<- c("030250000", "030270000", "030300000", "030585000", "030840000", "030890000", "031150000")\` 

  - Manually imputed Norridge Levy amounts from Norridge CAGR.

**Remove Municipalities that change home rule status:**

-   Midlothian, Northfield, River Grove became home rule in 2010.
-   Melrose Park became home rule in 2011.
-   South Chicago Heights became home rule in 2019.
-   Summit became home rule in 2016.
-   exclude_hr_change \<- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000")

**Keep taxing agencies that are within Cook County**

-   Create variable `pct_in_Cook` = cty_cook_eav / cty_total_eav. Keep all taxing agencies that are 90% or more in Cook County. Use cty_total_eav in the models since we are using the full levy amount in the models


```{r warning = FALSE, message=FALSE}
#| code-fold: true

#knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(stars)
library(modelsummary)
```

## Join initial data from CCAO package

```{r}
## Change database file path to match your computer's location 
## of the PTAXSIM database!


ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "./ptaxsim.db/ptaxsim-2023.0.0.db")
 
#ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2023.0.0.db")

agency_dt <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT *
  FROM agency
  "
) |>
  mutate(first6 = str_sub(agency_num,1,6)) 

all_taxing_agencies <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT agency_num, agency_name, major_type, minor_type
  FROM agency_info
  "
  ) |>
  mutate(first6 = str_sub(agency_num, 1, 6))

DBI::dbDisconnect(ptaxsim_db_conn)

```

```{r load_necessary_files}
#| message: false

# pulls in additional tables that exist in PTAXSIM database
# for calculating taxable AV: Taxable EAV / eq_factor for each year
cpi <- read_csv("./Necessary_Files/cpi.csv") 

eq_factor <- read_csv("./Necessary_Files/eq_factor.csv") |> 
  select(-eq_factor_tentative)

agency_triads <- read_csv("./Necessary_Files/agency_reassessmentyears.csv") 

```


```{r}
#| message: false

# Remove variables with data on EAV in other jurisdictions

raw_data_joined <- left_join(agency_dt, agency_triads) |> select(-c(cty_dupage_eav:cty_livingston_eav))

```


## Clean variables and filter observations from joined data


```{r}

# Start with 18649 obs.

raw_data_joined <- raw_data_joined |>
  rename(minor_type = agency_minor_type,
         major_type = agency_major_type) |>
  
  # Filter out SSAs
  # drops 5916 agency-year combos (updated for 2023 db)
  filter(minor_type != "SSA") |> 
  
  # fills in missing cty_cook_eav variables. 
  # uses logic that EAV = levy / tax rate = EAV
  mutate(total_final_levy = as.numeric(total_final_levy),
         cty_cook_eav = as.numeric(cty_cook_eav),
         cty_total_eav = as.numeric(cty_total_eav)) |>
  mutate(cty_cook_eav = ifelse(is.na(cty_cook_eav) & total_final_levy > 0, 
                               total_final_levy / (total_final_rate/100), cty_cook_eav),
         cty_total_eav = ifelse(is.na(cty_total_eav) & total_final_levy > 0 , 
                                total_final_levy / (total_final_rate/100), cty_total_eav))

## 12733 obs. (MVH w/ 2023 db)



exclude_hr_change <- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000" )


recoded_data <- raw_data_joined |> 
  left_join(cpi, by = c("year" = "levy_year")) |>
  left_join(eq_factor) |>
  # Excluding munis that change HR status removes 144 agency-year pairs.
  filter(!agency_num %in% exclude_hr_change) |>
  # 12589 obs.
  
  # Clean up data types
  mutate(
    agency_num = as.character(agency_num),            # change variable type
    agency_num = str_pad(agency_num, 9, "left", "0"), # add missing leading zeros
    first6 = str_pad(first6, 6, "left", "0"),
    home_rule_ind = as.character(home_rule_ind),      # change reference category
    reassess_year = as.character(reassess_year)       # change variable type
    ) |>
  
  # Calculate AV as a function of EAV and the EQ factor
  mutate(cty_total_eav = as.numeric(cty_total_eav),    # taxable eav in cook and neighboring counties
         cty_cook_eav = as.numeric(cty_cook_eav),      # taxable EAV in cook county only
         pct_in_Cook = cty_cook_eav / cty_total_eav,   # to identify taxing agencies that cross county lines
         total_final_levy = as.numeric(total_final_levy), 
         av = cty_cook_eav / eq_factor_final,          # backed out taxable Assessed Value of properties
         first6_w_hr = str_c(first6, "_", home_rule_ind),
         agency_w_hr = str_c(agency_num, "_", home_rule_ind)
         ) |> 
  
  # Keep only agencies greater than 95% in Cook
  # Drops 1608 obs.
  filter(pct_in_Cook > 0.90) 

# 10891 obs. in recoded_data

```

## Import grouping labels

```{r}

 # Read in grouped labels

groupies <- readxl::read_xlsx("panel_data_blindcoding.xlsx", sheet = "TFL manual code") |>
  select(first6, agency_num, agency_group, flag_drop, agency_name) |>
  
  # Change object types to facilitate merging.
  
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         agency_num = as.character(agency_num), 
         first6 = as.character(first6), # make character
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
  )
```


### Merge Grouped Labels, Recode Data & Summarize to Grouped Taxing Agency Level

```{r}
table(recoded_data$year, recoded_data$minor_type)

  
grouped_manual <- recoded_data |> 
  # 10981 obs.
  left_join(groupies,
            by = c("agency_name", "agency_num")
  ) |> 
  # Filter post-grouped agencies to munis, townships, schools and miscellaneous agencies such as Parks or Library Special Districts
  # 10,261 obs after filtering
  filter(
  (  (major_type == "MUNICIPALITY/TOWNSHIP" |  major_type == "MISCELLANEOUS" ) | (minor_type == "ELEMENTARY" |   minor_type == "SECONDARY") ) & 
      !minor_type %in% c("SANITARY", "WATER", "MOSQUITO", "COOK" )) 

table(grouped_manual$year, grouped_manual$minor_type)

grouped_manual <- grouped_manual |>
  
  arrange(agency_num, year) |>

    group_by(year, agency_group) |> 
  # Change dataframe to reflect grouped agencies
  # Consolidates 10261 obs. pre-grouping into 7614 obs.
  summarize(
    agency_name = first(agency_name),
    agency_num = first(agency_num),
    total_final_levy = sum(total_final_levy, na.rm=TRUE),
    total_final_levy = ifelse(total_final_levy == 0, NA, total_final_levy), # change 0's to NAs so ln() doesn't break it
    major_type = paste(list(unique(major_type)), sep = ", "),   
    minor_type = paste(list(unique(minor_type)), sep = ", "),

    cty_total_eav = mean(cty_total_eav, na.rm=TRUE), 
    av = first(av),   
    triad_name = first(triad_name), 
    agency_count = n(),
    reassess_year = first(reassess_year),
    home_rule_ind = first(home_rule_ind),
    flag_drop = first(flag_drop)
  ) |> 
  # Create variables to indicate bundling after grouping
  mutate(
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(agency_group, "_", home_rule_ind, "_", bundled),
    first2_dig = str_sub(agency_num, 1, 2),
    
    # Fix misclassification of Cicero, Evanston, and Chicago
    type = case_when(
      first2_dig == "03" ~ "Muni",
      agency_group == "Evanston" | agency_group == "Cicero" | agency_group == "Chicago" ~ "Muni",
      first2_dig == "04" ~ "School",
      first2_dig == "02"  ~ "Township", 
      TRUE ~ "Other"
      )) |>

  select(year, agency_group, everything()) # puts variables in useful order.


# Identify grouped agencies that do not exist across entire panel
# 7 agency groups will be dropped.
dropped_agencies <- grouped_manual |>
  group_by(agency_group) |> 
  summarize(n=n(),
            flag_drop = sum(flag_drop, na.rm=TRUE)) |>
  filter(n!=18 | flag_drop > 0)

dropped_agencies  # check what will be dropped

# Filter out observations from 7 agencies 
grouped_manual <- grouped_manual |>
  filter(!agency_group %in% dropped_agencies$agency_group)

```

```{r year_type_table}

table(grouped_manual$year, grouped_manual$type)

```


```{r}
grouped_manual |> 
  group_by(year, agency_group, triad_name)  |> 
  summarize(total_final_levy = sum(total_final_levy, na.rm = TRUE)) |> 
  filter(agency_group != "Chicago" & agency_group != "Chicago Park District") |> 
  ggplot() + 
  theme_classic() + 
  geom_line(aes(x=year, y = total_final_levy, group=agency_group) ) +
  facet_wrap(~triad_name)

grouped_manual |> 
  group_by(year, agency_group, triad_name, home_rule_ind)  |> 
  summarize(total_final_levy = sum(total_final_levy, na.rm = TRUE)) |> 
  filter(agency_group != "Chicago" & agency_group != "Chicago Park District") |> 
  ggplot() + 
  theme_classic() + 
  geom_line(aes(x=year, y = total_final_levy, group=agency_group) ) +
  facet_wrap(~home_rule_ind)
```


## Models

Create "true" AV variable
Assumes that taxed AV is accurate during assessment years and stays mostly flat until the next assessment year. The true market value is then smoothed between the assessment years.

```{r merriman_model_variable}

df <- grouped_manual |>
  ungroup() |>
  group_by(agency_group) |> 
  
  arrange(year)|> 
  # Assessment Year
  mutate(assess_year_av = ifelse(reassess_year == 1, av, NA)) |>
  
  fill(assess_year_av, .direction = "down") |>
  
  mutate(
    # 1 year after assessment:
    rate_smooth = if_else(lag(reassess_year, n=1) == 1 | lead(reassess_year, n=2) == 1, ((lead(av, 2) / assess_year_av)^(1/3)) - 1, 0),
    
     # 2 years after assessment:  
   rate_smooth = if_else(lag(reassess_year, n=2) == 1 | lead(reassess_year, n=1) == 1, (lead(assess_year_av, 1) / assess_year_av)^(1/2) - 1, rate_smooth),

  rate_smooth = if_else(reassess_year == 1, 0, rate_smooth),
  av_true = assess_year_av*(1+rate_smooth),
 ) |>
  arrange(agency_name, year) |>
  select(agency_group, year, av, assess_year_av, av_true, rate_smooth, everything()) |>
  ungroup()

```

```{r av_check}
#| eval: false

df |>
  filter(!(year %in% c("2006", "2007", "2022", "2023"))) |>
  select(av_true, av) |>
  ggplot() +
  geom_density(aes(log(av_true), color = "blue")) +
  geom_density(aes(log(av), color = "red")) +
  theme_classic()

df |>
  filter(!(year %in% c("2006", "2007", "2022", "2023"))) |>
  filter(is.na(av_true)) |>
  summarize(n = n())

df |>
  filter(!(year %in% c("2006", "2007", "2022", "2023"))) |>
  filter(is.na(av)) |>
  summarize(n = n())

```


> av_true is NOT fully checked. It is missing for some years in the beginning and the end depending on when their reassessment year was. Not all agencies are missing the same years of data. Different number of observations for av vs av_true variables.

### Models with "True AV"

```{r}
#| label: tbl-merriman_models-agency_group
#| tbl-cap: "agency_group fixed effects. Uses grouped and summed taxing agencies. Includes log(av) and log(av_true) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. Newey-West stand errors. "

library(fixest)
mods_1 <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) | agency_group + year,
               data = df,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                ),
  
    "2" = feols(log(total_final_levy) ~ log(av) + log(av_true) | agency_group + year,
               data = df,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                ),
  
     "3" = feols(log(total_final_levy) ~ log(av)*reassess_year + log(av_true)*reassess_year | agency_group + year,
               data = df,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                ),
  
    "4" = feols(log(total_final_levy) ~ log(av_true) | agency_group + year,
               data = df,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true) | agency_group + year,
               data = df,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                )
  )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

> Reassessment year interaction does not do what it was originally meant to do! av_true*reassess_year means means that when it is the reeassess_year, that it would use the av_true value, but av_true is the same as av at reassessment years.

Model comparison to check work. Agency Group fixed effects is what we want.


```{r}
#| label: tbl-merriman_models-iid
#| tbl-cap: "Model comparison using agency_name and then agency group fixed effects. Includes log(av) and log(av_true) in model. iid standard errors."

mods_iid <- list(
  
  "Agency Name 1" = feols(log(total_final_levy) ~ log(av) | agency_name + year,
               data = df,
               vcov = "iid",
               panel.id = c("agency_name", "year")
                ),
    "Agency Name 2" = feols(log(total_final_levy) ~ log(av) + log(av_true) | agency_name + year,
               data = df,
               vcov = "iid",
               panel.id = c("agency_name", "year")
                ),
  
  "Agency Name Interact" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true)| agency_name + year,
               data = df,
               vcov = "iid",
               panel.id = c("agency_name", "year")
                ),
    "Agency Group - 1" = feols(log(total_final_levy) ~ log(av) | agency_group + year,
               data = df,
               vcov = "iid",
               panel.id = c("agency_group", "year")
                ),
    "Agency Group 2" = feols(log(total_final_levy) ~ log(av) + log(av_true) | agency_group + year,
               data = df,
               vcov = "iid",
               panel.id = c("agency_group", "year")
                ),
  
  "Agency Group Interact" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true) | agency_group + year,
               data = df,
               vcov = "iid",
               panel.id = c("agency_group", "year")
                )
  )


modelsummary::modelsummary(
  mods_iid,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

### Old Models w/o "True AV"

```{r old_models}

library(fixest)

models <- list(
  "Plain TWFE" = feols(log(total_final_levy) ~ log(av)  | agency_group + year,  data = grouped_manual, vcov = "newey_west", panel.id = c("agency_group", "year")),
  
      "Homerule TWFE" = feols(log(total_final_levy) ~ log(av)  | agency_group + year,  data = grouped_manual |> filter(home_rule_ind == "1"), vcov = "newey_west", panel.id = c("agency_group", "year")),
      
  "Nonhomerule" = feols(log(total_final_levy)~ log(av)  | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual |> filter(home_rule_ind == "0")),
  
    "Nonhomerule - noschools" = feols(log(total_final_levy)~ log(av)  | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual |> filter(home_rule_ind == "0" & type != "School")),
  
  "TWFE w/ AV Lags" = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual),
  
  "Homerule TWFE" = feols(log(total_final_levy) ~ log(av) + l(log(av), 1) + l(log(av), 2 ) | agency_group + year,  data = grouped_manual |> filter(home_rule_ind == "1"), vcov = "newey_west", panel.id = c("agency_group", "year")),
      
  "Nonhomerule" = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual |> filter(home_rule_ind == "0"))
  
  )


modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)


```
