---
title: "Model Decisions, Discussions, & Output"
subtitle: "Responsiveness of the Levy to the Tax Base"
author: "Michael Van Hulle"
date: "March 26, 2024"
format: 
  html:
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    cap-location: margin
---

# Model parameters discussion.

1.  Which agencies in the data set? NOTE: ALL ITEMS EXCEPT d AND e are done.
    a.  Home rule ONLY (evaluate how home rule-y the non municipalities are. Are they just subdivisions of the munis? 63 for munis vs. \~90
    b.  Qual eval of those entities
    c.  Drop border crossers
    d.  Drop agencies w/ little prop tax rev.
        a.  Create variable to measure property tax dependence. should be (total_rev - total_final_levy)/total_rev (or similar)
    e.  Grouping --- it is a concern and should be done by agency digits and eav.
2.  Variables
    1.  DV - ln(total_levy) - allows calculation of elasticity, which economists \<3
        1.  We want the levy value requested by the muni/agency to capture the agency's responsiveness to the change in the tax base. That should be the same as they received since they are HR agencies.
            1.  Check this!
    2.  IV
        1.  ln(AV)
            1.  Change in AV better reflects the change in the tax base and our RQ is about the levy's responsiveness to the tax base. Thus, irrelevant whether we use AV or EAV.
            2.  Downside: Value of exemptions could be high causing a divergence?
                1.  Alea backs AV out of EAV.
        2.  lag(ln(AV)), ln2(log(AV))
            1.  Given 3 year reassessment cycle, we want to account for the effect of the prior reassessment...especially given the trend we see of the initial bump in AV followed by the decrease from appeals.
        4.  lag(Reassessment year) dummy (to use with interaction term)
        5.  log(AV)\*lag(Reassess)
            1.  check if responsiveness is related to it being an assessment year
            2.  NO
            3.  Only incorporated into the budget the year after reassessment -- hence description as "lag"
3.  Other model items:
    1.  Is "year" the calendar year or the tax year? Determines whether we want to lag the reassess variable.
        1.  Alea: Year in the agency_dt is the tax year. Reassessment year might be calendar year.
        2.  We should double check this item.
    2.  2WFE are OK because we, within each year, 1/3 of the county is reassessed; we are no longer using it as a "treatment" to make causal statements.



```{r warning = FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(plm)
library(stars)
library(lmtest)
library(huxtable)
library(jtools)
library(prediction)
library(modelsummary)
```

:::aside
If you do not want to deal with updating the ptaxsim database and trust our initial data joining process, you can view and use the `raw_agency_joined.csv` without running these lines. This chunk takes the `agency` data table from PTAXSIM, a csv file that contains an indicator for if a municipality was reassessed during a certain year, and a csv file containing different naming options for summarizing the taxing agencies. 
:::

```{r eval = FALSE}

## Change database file path to match your computer's location 
## of the PTAXSIM database!
ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), 
#  "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2022.0.0.db")
"./ptaxsim.db/ptaxsim-2022.0.0.db")

muni_agency_names <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT DISTINCT agency_num, agency_name, minor_type
  FROM agency_info
  WHERE minor_type = 'MUNI'
  OR agency_num = '020060000'
  "
  ) %>% 
  mutate(first6 = str_sub(agency_num,1,6)) %>%
  select(-minor_type)


agency_dt <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT *
  FROM agency
  "
) %>%
  mutate(first6 = str_sub(agency_num,1,6)) %>%
  mutate(year = as.character(year))


is.integer64 <- function(x){
  class(x)=="integer64"
}

agency_dt <- agency_dt %>%
  mutate_if(is.integer64, as.integer)


# has binary variable for if it was a reassessment year or not. 
# Manually created based on the 3 year rotation used for reassessments.
reassessment_years <- read_csv("./Necessary_Files/Triad_reassessment_years.csv")


reassessments_long <- reassessment_years %>% 
  pivot_longer(cols = c(`2006`:`2022`), names_to = "year", values_to = "reassess_year")


nicknames <- readxl::read_xlsx("./Necessary_Files/muni_shortnames.xlsx") %>% 
  select(-c(agency_number, short_name, `Column1`, `Most recent reassessed`))



all_taxing_agencies <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT agency_num, agency_name, major_type, minor_type
  FROM agency_info
  "
  ) %>%
  mutate(first6 = str_sub(agency_num,1,6)  )


muni_agency_names <- muni_agency_names %>% 
  left_join(nicknames)

all_taxing_agencies <- all_taxing_agencies %>%
  left_join(muni_agency_names, by = c("first6")) %>%
  rename(muni_name =  agency_name.y,
         muni_num = agency_num.y,
         agency_name = agency_name.x,
         agency_num = agency_num.x)

raw_data_joined <- left_join(agency_dt, all_taxing_agencies, by = c("agency_num", "first6"))

raw_data_joined <- left_join(raw_data_joined, reassessments_long, by = c("Triad", "year")) %>%
   # drop extra columns
  select(-c(cty_dupage_eav:cty_livingston_eav, clean_name_alt, shpfile_name, ORIGOID, township_code))   
  
# If manipulating in Stata or Excel, have NAs be blank:
#agency_dt %>% write_csv("agency_raw_joined.csv", na = "")


# exported file used in R code:
raw_data_joined %>% write_csv("agency_raw_joined.csv")

```


```{r}
raw_data_joined <- read_csv("agency_raw_joined.csv")    # 17,2294 obs

## Fill in missing data for taxable EAV variables
## uses logic that EAV = levy / tax rate = EAV
raw_data_joined <- raw_data_joined %>%
  
  # drops 5332 taxing agencies (agency-year combos)
  filter(minor_type != "SSA") %>% 
  
  # fills in missing cty_cook_eav variables. 
  mutate(cty_cook_eav = ifelse(is.na(cty_cook_eav) & total_final_levy > 0, 
                               total_final_levy / (total_final_rate/100), cty_cook_eav),
         cty_total_eav = ifelse(is.na(cty_total_eav) & total_final_levy > 0 , 
                                total_final_levy / (total_final_rate/100), cty_total_eav)) %>% 
  
  # then keeps only taxing agencies that have a taxable EAV > 0
  filter(cty_total_eav > 0 )

## 11,533 obs - AWM 3/31/2024



# pulls in additional tables that exist in PTAXSIM database
# for calculating taxable AV: Taxable EAV / 
cpi <- read_csv("./Necessary_Files/cpi.csv") #%>%

eq_factor <- read_csv("./Necessary_Files/eq_factor.csv") %>% 
  select(-eq_factor_tentative)

# Remove taxing agnecies that had a levy of $0 for any year. 
# drop all occurances of the taxing agency
# Countryside, Deer Park, Homer Glen, Norridge, Oak Brook, Schaumburg, Dixmoor (2011 only) are dropped using `dropped_munis 
dropped_munis <- c("030250000", "030270000", "030300000", "030585000", "030840000", "030890000", "031150000", "031230000")


exclude_hr_change <- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000" )


recoded_data <- raw_data_joined %>% 
  left_join(cpi, by = c("year" = "levy_year")) %>%
  left_join(eq_factor) %>%
  mutate(
    # year = as.factor(year) 
    agency_num = as.character(agency_num),
    
    agency_num = str_pad(agency_num, 9, "left", "0"), # add missing leading zeros
    first6 = str_pad(first6, 6, "left", "0"),
    home_rule_ind = as.character(home_rule_ind),      # change reference category
    minor_type = as.factor(minor_type),
    reassess_year = as.character(reassess_year)) %>%
  
  mutate(cty_total_eav = as.numeric(cty_total_eav),    # taxable eav in cook and neighboring counties
         cty_cook_eav = as.numeric(cty_cook_eav),      # taxable EAV in cook county only
         pct_in_Cook = cty_cook_eav / cty_total_eav,   # to identify taxing agencies that cross county lines
         total_final_levy = as.numeric(total_final_levy), 
         total_non_cap_ext = as.numeric(total_non_cap_ext),
        # total_capped_ext = ifelse(home_rule_ind == 0, (total_ext - total_non_cap_ext), NA),
        # total_non_cap_ext = ifelse(home_rule_ind == 1, total_ext, total_non_cap_ext),
         total_reduced_levy = as.numeric(total_reduced_levy), # for non-HR agencies that have their levy reduced
         av = cty_cook_eav / eq_factor_final,          # backed out taxable Assessed Value of properties
         first6_w_hr = str_c(first6, "_", home_rule_ind),
         agency_w_hr = str_c(agency_num, "_", home_rule_ind)
         ) # %>%
 # group_by(year, cty_total_eav, home_rule_ind) %>%
  #mutate(summed_levy_sharetaxbase = sum(total_final_levy)+1) %>% # grouped by tax base and year
  #ungroup() %>%
 # group_by(year, first6, home_rule_ind) %>%
  #mutate(summed_levy_first6 =sum(total_final_levy)+1) %>% # grouped by first 6 digits in agency number
 # ungroup()


recoded_data <- recoded_data %>% 
  
  filter(pct_in_Cook > 0.9) %>% #keep only agencies greater than 90% in Cook
  
  mutate(
    total_final_levy_4log = total_final_levy + 1,
    #Add 1 to total_final_levy to allow ln transformation.
    
    log_eav = log(cty_total_eav), # eav within Cook AND neighboring counties.
    log_levy = log(total_final_levy_4log),
   # log_capped = log(total_capped_ext),
   # log_noncapped = log(total_non_cap_ext),
    log_av = log(av),
    
    year = as.factor(year), # for plm()
    agency_num = as.factor(agency_num) # for plm()
    
  )
```

```{r warning = FALSE, message=FALSE}
source("helper_recode_variables.R")

groupies2 <- read_csv("grouped_labels.csv") %>%          
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         first6 = as.character(first6), # make character
        # home_rule_ind = as.character(home_rule_ind),
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
         first6_w_hr_ind = str_c(first6, "_", hr_ind))

grouped_manual <- recoded_data %>% 
  left_join(groupies2,
            by = c("agency_name", "agency_num")
            ) %>% 
    filter(major_type == "MUNICIPALITY/TOWNSHIP" ### |   major_type == "MISCELLANEOUS"
           & minor_type != "MISC"
           ) %>%
  filter(minor_type != "SSA") %>% 
  group_by(year, grouped_label, home_rule_ind, lim_rate) %>% 
  summarize(agency_name = first(agency_name),
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE)+1,
            cty_total_eav = first(cty_total_eav), 
            av = first(av),   # should be first() not sum() --- AWM 3/30/24
            Triad = first(Triad), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind)) %>% 
   # left_join(muni_agency_names) %>% 
    #select(-c(Column1, `Most recent reassessed`)) %>% 
    mutate(
      log_eav = log(cty_total_eav),
      log_levy = log(total_final_levy),
      log_av = log(av),  # added AWM 3/25/2024
      bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(grouped_label, "_", home_rule_ind, "_", bundled),
      panel_id = str_c(grouped_label, "_", home_rule_ind, "_", bundled, "_", lim_rate),
    first2_dig = str_sub(agency_num, 1,2),
    town = ifelse(first2_dig == "02" | agency_name == "TOWN CICERO", "Town", "Muni")) %>% 
  filter(total_final_levy > 1) %>%
  select(year, uniqueid, everything())

 grouped_manual %>%  # 236 nonHR and 68 HR
  ungroup() %>%
  filter(year == 2021) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())
 
grouped_manual %>%  # 236 nonHR and 68 HR
  ungroup() %>%
  filter(year == 2022) %>%
  group_by(home_rule_ind) %>%
  summarize(count = n())



# 1552 obs
# 2278 obs after 2022 update
# 1122 homerule munis after adding home_rule_ind filter
grouped_manual_has16 <- grouped_manual %>%  # 124 nonHR and 69 HR
  ungroup() %>%
 # filter(year == 2021) %>%
  arrange(home_rule_ind) %>%
  group_by(uniqueid) %>%
  distinct() %>%
  mutate(count = n()) %>%
  filter(count == 17 & home_rule_ind == 1) %>% 
  ungroup()


gm <- grouped_manual_has16

write.csv(gm, "gm_for_pivots.csv")


grouped_manual_has16 %>% filter(grouped_label != "Chicago") %>%  write_csv("gm_nochi_for_pivots.csv")

```

We're going to look at some pivot tables... And we're back!

## AV lags, 2WFE

```{r}
detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

#summary(simple1)
#summary(simple2)
#summary(simple3)

export_summs(simple1, simple2,  simple3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

#### Goodness of Fit stuff

```{r}

laggedDV <- plm(log_levy ~  lag(log_levy) + log_av + lag(log_av, 1) + lag(log_av,2), 
             index = c("grouped_label", "year"),
             model = "within",
             effect = "twoways",
             data = gm_pd)

export_summs(laggedDV)

gm$e <- simple1$residuals
# test of rho hat
aux_1 <- lm(e~ -1 + lag(e), data = gm)
aux_1 %>% tidy()

aux_2 <- plm(e ~ lag(e), 
             index = c("grouped_label", "year"),
             model = "within",
             effect = "twoways",
             data = gm)

nR2 <- aux_2 %>% r.squared*aux_2$df.residual
nR2 %>% 
  pchisq(1, lower.tail = F)
```

Can not reject the null hypothesis that there is no autocorelation --> 
Therefore there is autocorrelation in our panel data. Use HC5 type erroro

The estimate for correcting the autocorrelation is 0.851...

```{r}
#detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(total_final_levy ~ av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(total_final_levy ~ av + lag(av, 1),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(total_final_levy ~ av + lag(av, 1) + lag(av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

#summary(simple1)
#summary(simple2)
#summary(simple3)

export_summs(simple1, simple2,  simple3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

## reassess_lag dummy, av lags, 2WFE

```{r}

med1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)
# 
# summary(med1)
# summary(med2)
# summary(med3)
# 

export_summs(med1, med2,  med3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

```

## reassess_year dummy, av lags, 2WFE

```{r}

ass.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.5 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

huxreg(ass.1, ass.2, ass.3, ass.4, ass.5,
       statistics = c(N = "nobs", 
                      R2 = "r.squared", 
                      adj.R2 = "adj.r.squared", 
                      F = "fstatistic", 
                      `Prob>F` = "fstatistic", 
                      AIC = "AIC", 
                      BIC = "BIC"),
       title = "Regression Summary"
)

```

## AV lags, Polynomial, 2WFE

```{r}

poly1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly5 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

model_list <- list(poly1, poly2, poly3, poly4, poly5)

clean_models <- sapply(model_list, broom::tidy)

export_summs(model_list,
             statistics = c(N = "nobs", 
                            R2 = "r.squared", 
                            adj.R2 = "adj.r.squared", 
                            F = "fstatistic", 
                            `Prob>F` = "fstatistic", 
                            AIC = "AIC", 
                            BIC = "BIC"),
             title = "Regression Summary"
)
```

```{r}

poly4_resids <- prediction(poly.4)

poly4_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

simple3_resids <- prediction(simple3)

simple3_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

```

::: aside
Why are the residuals changing so hard once we remove Chicago???
:::



# 2WFE Models Without Chicago

```{r eval = FALSE}

gm <- gm %>% filter(grouped_label!="Chicago")

```

## AV lags, 2WFE

```{r}
detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(simple1, simple2,  simple3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}


detach("package:dplyr", unload = TRUE)


gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

simple1 <- plm(total_final_levy ~ av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple2 <- plm(total_final_levy ~ av + lag(av, 1),
              model = "within",
              effect = "twoways",
              data = gm_pd)

simple3 <- plm(total_final_levy ~ av + lag(av, 1) + lag(av,2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(simple1, simple2,  simple3, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

## reassess_lag dummy, av lags, 2WFE

```{r}

med1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(med1, med2,  med3, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

```

## reassess_year dummy, av lags, 2WFE

```{r}

med1.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med2.1 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

med3.1 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(med1.1, med2.1,  med3.1, , 
          statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared")
          )

```

## AV lags, Polynomial, 2WFE

```{r}

poly.1 <- plm(log_levy ~ log_av,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

poly.4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av^2),
              model = "within",
              effect = "twoways",
              data = gm_pd)

export_summs(poly.1, poly.2, poly.3, poly.4, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

```{r}

library(prediction)

poly4_resids <- prediction(poly.4)

poly4_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

simple3_resids <- prediction(simple3)

simple3_resids %>%
  ggplot(aes(fitted)) +
  geom_density()

```

::: aside
Why are the residuals changing so hard once we remove Chicago???
:::

# Random Effects

## AV lags

```{r}

gm_pd <- pdata.frame(gm, index = c("uniqueid", "year")) 

pool1 <- plm(log_levy ~ log_av,
              model = "random",
              effect = "twoways",
              data = gm_pd)

pool2 <- plm(log_levy ~ log_av + lag(log_av),
              model = "random",
              effect = "twoways",
              data = gm_pd)

pool3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av,2),
              model = "random",
              effect = "twoways",
              data = gm_pd)

models <- list(pool1, pool2, pool3)

export_summs(models, 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))

```
## Reassessment Year Dummy

```{r}
med1 <- plm(log_levy ~ log_av + lag(reassess_year) + log_av*lag(reassess_year),
              model = "random",
              effect = "twoways",
              data = gm_pd)

med2 <- plm(log_levy ~ log_av + lag(log_av) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "random",
              effect = "twoways",
              data = gm_pd)

med3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + lag(reassess_year) + log_av*lag(reassess_year),
              model = "random",
              effect = "twoways",
              data = gm_pd)

export_summs(med1, med2,  med3, robust = "HC3", 
             statistics = c(N = "nobs", R2 = "r.squared", adj.R2 = "adj.r.squared"))
```

## Interacted with all the things.

```{r}

ass.1 <- plm(log_levy ~ log_av + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.2 <- plm(log_levy ~ log_av + lag(log_av) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.3 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + log_av*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.4 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

ass.5 <- plm(log_levy ~ log_av + lag(log_av) + lag(log_av, 2) + reassess_year + lag(log_av, 2)*reassess_year,
              model = "within",
              effect = "twoways",
              data = gm_pd)

huxreg(ass.1, ass.2, ass.3, ass.4, ass.5,
       statistics = c(N = "nobs", 
                      R2 = "r.squared", 
                      adj.R2 = "adj.r.squared", 
                      F = "fstatistic", 
                      `Prob>F` = "fstatistic", 
                      AIC = "AIC", 
                      BIC = "BIC"),
       title = "Regression Summary"
)

```

