---
title: "Replication Code for NTA Panel Data"
author: "AWM & MVH"
date: "October 13, 2024"
format: 
  html:
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    code-fold: true
    toc-location: left
    cap-location: margin
    df-print: default
    # grid:
    #   sidebar-width: 200px
    #   body-width: 900px
    #   margin-width: 200px
---

**Files needed for panel creation replication:**

-   agency_reassessmentyears.csv
-   cpi.csv
-   eq_factor.csv
-   panel_data_blindcoded.xlsx

# Code Cleaning Steps

-   90% within Cook County 
-   Does not change home rule status during sample years 

### Slightly more detail on cleaning process:

**Some taxing agencies are missing their cty_cook_eav & cty_total_eav even though they have a total_final_levy value** 

-   Using the logic that the tax rate = levy / taxable EAV, then we can back out the EAV by  using the total_final_levy and total_final_rate variables. 
-   Taxable EAV = total_final_levy / (total_final_rate) / 100 
-   A Couple municipalities had missing levies and were manually entered by looking up the CAGR and historic levy amounts in the document

**Remove taxing agencies that had a levy = \$0 for any year. Drop values for all years.**  

-   Countryside, Deer Park, Homer Glen, ~~Norridge~~, Oak Brook, Schaumburg, Dixmoor (2011 only) are dropped using \`dropped_munis \<- c("030250000", "030270000", "030300000", "030585000", "030840000", "030890000", "031150000")\` 

-   Manually imputed Norridge Levy amounts from Norridge CAGR.

**Remove Municipalities that change home rule status:**

-   Midlothian, Northfield, River Grove became home rule in 2010.
-   Melrose Park became home rule in 2011.
-   South Chicago Heights became home rule in 2019.
-   Summit became home rule in 2016.
-   exclude_hr_change \<- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000")

**Keep taxing agencies that are within Cook County**

-   Create variable `pct_in_Cook` = cty_cook_eav / cty_total_eav. Keep all taxing agencies that are 90% or more in Cook County. Use cty_total_eav in the models since we are using the full levy amount in the models

```{r setup, warning = FALSE, message=FALSE}
#| code-fold: true

#knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(stars)
library(modelsummary)
library(fixest)
library(tinytable)

```

## Join initial data from CCAO package

```{r}
## Change database file path to match your computer's location 
## of the PTAXSIM database!

file_path <- "C:/Users/aleaw/" 

if (file.exists(file_path)){
   ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2023.0.0.db")
} else {
    ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "./ptaxsim.db/ptaxsim-2023.0.0.db")

}
# ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "./ptaxsim.db/ptaxsim-2023.0.0.db")
 
#ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/aleaw/OneDrive/Documents/PhD Fall 2021 - Spring 2022/Merriman RA/ptax/ptaxsim.db/ptaxsim-2023.0.0.db")

agency_dt <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT *
  FROM agency
  "
) |>
  mutate(first6 = str_sub(agency_num,1,6)) 

all_taxing_agencies <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT agency_num, agency_name, major_type, minor_type
  FROM agency_info
  "
  ) |>
  mutate(first6 = str_sub(agency_num, 1, 6))

DBI::dbDisconnect(ptaxsim_db_conn)

```

```{r load_necessary_files}
#| message: false

# pulls in additional tables that exist in PTAXSIM database
# for calculating taxable AV: Taxable EAV / eq_factor for each year
cpi <- read_csv("./Necessary_Files/cpi.csv") 

eq_factor <- read_csv("./Necessary_Files/eq_factor.csv") |> 
  select(-eq_factor_tentative)

agency_triads <- read_csv("./Necessary_Files/agency_reassessmentyears.csv") 

agency_sum_file <- read_csv("./Necessary_files/ptaxsim_taxing_agency_summaries_2006to2023.csv")  %>% select(-c(agency_minor_type, agency_major_type))


```

```{r}
#| message: false

# Remove variables with data on EAV in other jurisdictions

raw_data_joined <- left_join(agency_dt, agency_triads) |> select(-c(cty_dupage_eav:cty_livingston_eav)) %>% 
   left_join(agency_sum_file, by = c("year", "agency_num", "agency_name"))

 

```

 ## Clean variables and filter observations from joined data

```{r}

# Start with 18649 obs.

raw_data_joined <- raw_data_joined |>
  rename(minor_type = agency_minor_type,
         major_type = agency_major_type) |>
  
  # Filter out SSAs
  # drops 5916 agency-year combos (updated for 2023 db)
  filter(minor_type != "SSA") |> 
  
  # fills in missing cty_cook_eav variables. 
  # uses logic that EAV = levy / tax rate = EAV
  mutate(total_final_levy = as.integer(total_final_levy),
         cty_cook_eav = as.integer(cty_cook_eav),
         cty_total_eav = as.integer(cty_total_eav)) |>
  mutate(cty_cook_eav = ifelse(is.na(cty_cook_eav) & total_final_levy > 0, 
                               total_final_levy / (total_final_rate/100), cty_cook_eav),
         cty_total_eav = ifelse(is.na(cty_total_eav) & total_final_levy > 0 , 
                                total_final_levy / (total_final_rate/100), cty_total_eav))

## 12733 obs. (MVH w/ 2023 db)



exclude_hr_change <- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000" )


recoded_data <- raw_data_joined |> 
  left_join(cpi, by = c("year" = "levy_year")) |>
  left_join(eq_factor) |>
  # Excluding munis that change HR status removes 144 agency-year pairs.
  filter(!agency_num %in% exclude_hr_change) |>
  # 12589 obs.
  
  # Clean up data types
  mutate(
    agency_num = as.character(agency_num),            # change variable type
    agency_num = str_pad(agency_num, 9, "left", "0"), # add missing leading zeros
    first6 = str_pad(first6, 6, "left", "0"),
    home_rule_ind = as.character(home_rule_ind),      # change reference category
    reassess_year = as.character(reassess_year)       # change variable type
    ) |>
  
  # Calculate AV as a function of EAV and the EQ factor
  mutate(cty_total_eav = as.numeric(cty_total_eav),    # taxable eav in cook and neighboring counties
         cty_cook_eav = as.numeric(cty_cook_eav),      # taxable EAV in cook county only
         pct_in_Cook = cty_cook_eav / cty_total_eav,   # to identify taxing agencies that cross county lines
         total_final_levy = as.numeric(total_final_levy), 
         av = cty_cook_eav / eq_factor_final,          # backed out taxable Assessed Value of properties
         first6_w_hr = str_c(first6, "_", home_rule_ind),
         agency_w_hr = str_c(agency_num, "_", home_rule_ind)
         ) |> 
  
  # Keep only agencies greater than 95% in Cook
  # Drops 1608 obs.
  filter(pct_in_Cook > 0.90) 

# 10891 obs. in recoded_data

```

## Import grouping labels

```{r}

 # Read in grouped labels

groupies <- readxl::read_xlsx("panel_data_blindcoding.xlsx", sheet = "TFL manual code") |>
  select(first6, agency_num, agency_group, flag_drop, agency_name) |>
  
  # Change object types to facilitate merging.
  
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         agency_num = as.character(agency_num), 
         first6 = as.character(first6), # make character
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
  )
```

## Merge Grouped Labels, Recode Data & Summarize to Grouped Taxing Agency Level

```{r}
table(recoded_data$minor_type, recoded_data$year)


  
grouped_manual <- recoded_data |> 
  # 10981 obs.
  left_join(groupies,
            by = c("agency_name", "agency_num")
  ) |> 
  # Filter post-grouped agencies to munis, townships, schools and miscellaneous agencies such as Parks or Library Special Districts
  # 10,261 obs after filtering
  filter(
  (  (major_type == "MUNICIPALITY/TOWNSHIP" |  major_type == "MISCELLANEOUS" ) | (minor_type == "ELEMENTARY" |   minor_type == "SECONDARY") ) & 
      !minor_type %in% c("SANITARY", "WATER", "MOSQUITO", "COOK" )) 

table(grouped_manual$year, grouped_manual$minor_type)
```


```{r}
#| include: false
grouped_manual %>% filter(is.na(agency_group))

grouped_manual <- grouped_manual |> 
  mutate(agency_group = ifelse(is.na(agency_group), agency_name, agency_group))
```


```{r}
grouped_manual <- grouped_manual |>
  
  arrange(agency_num, year) |>

    group_by(year, agency_group) |> 
  # Change dataframe to reflect grouped agencies
  # Consolidates 10261 obs. pre-grouping into 7614 obs.
  summarize(
    agency_name = first(agency_name),
    agency_num = first(agency_num),
    total_final_levy = sum(total_final_levy, na.rm=TRUE),
    total_final_levy = ifelse(total_final_levy == 0, NA, total_final_levy), # change 0's to NAs so ln() doesn't break it
    major_type = paste(list(unique(major_type)), sep = ", "),   
    minor_type = paste(list(unique(minor_type)), sep = ", "),
    cty_cook_eav = first(cty_cook_eav),
    cty_total_eav = first(cty_total_eav), 

    total_fmv = sum(fmv, na.rm=TRUE),
    taxed_fmv = sum(fmv_taxed, na.rm=TRUE),
    taxed_eav = first(eav_taxed),
    total_eav = first(eav),
    av = first(av),
    triad_name = first(triad_name), 
    agency_count = n(),
    reassess_year = first(reassess_year),
    home_rule_ind = first(home_rule_ind),
    flag_drop = first(flag_drop)
  ) |> 
  ungroup() |>
  # Create variables to indicate bundling after grouping
  mutate(
    bundled = ifelse(agency_count > 1, 1, 0),
    uniqueid = str_c(agency_group, "_", home_rule_ind, "_", bundled),
    first2_dig = str_sub(agency_num, 1, 2),
    
    # Fix misclassification of Cicero, Evanston, and Chicago
    type = case_when(
      first2_dig == "03" ~ "Muni",
      agency_group == "Evanston" | agency_group == "Cicero" | agency_group == "Chicago" ~ "Muni",
      first2_dig == "04" ~ "School",
      first2_dig == "02"  ~ "Township", 
      TRUE ~ "Other"
      )) |>
  select(year, agency_group, everything()) # puts variables in useful order.


# Identify grouped agencies that do not exist across entire panel
# 7 agency groups will be dropped.
dropped_agencies <- grouped_manual |>
  group_by(agency_group) |> 
  summarize(n=n(),
            flag_drop = sum(flag_drop, na.rm=TRUE)) |>
  filter(n!=18 | flag_drop > 0)

dropped_agencies  # check what will be dropped

# Filter out observations from 7 agencies 
grouped_manual <- grouped_manual |>
  filter(!agency_group %in% dropped_agencies$agency_group) 
# if using taxedeav from the agency dt


grouped_manual <- grouped_manual |> filter(#year >= 2007 & 
                     triad_name != "City"
                   )

```

```{r bundlecoded-not-summed}

table(recoded_data$minor_type, recoded_data$year)
```


```{r}
#| label: tbl-beforetable-forpresentation
#| tbl-cap: "Minor Types of Taxing Agencies before they are grouped. Data from CCAO PTAXSIM package."


before_table <- recoded_data |>
  left_join(groupies,
            by = c("agency_name", "agency_num")
  ) |> 
  filter(
  (  (major_type == "MUNICIPALITY/TOWNSHIP" |  major_type == "MISCELLANEOUS" ) | (minor_type == "ELEMENTARY" |   minor_type == "SECONDARY") ) & 
      !minor_type %in% c("SANITARY", "WATER", "MOSQUITO", "COOK" )) |>
  arrange(agency_num, year) |>

    group_by(year, agency_group) |> 
  mutate(
    major_type = major_type,
    minor_type = minor_type,
    agency_group_name = first(agency_name),
    agency_group_num = first(agency_num),

    major_type_group = paste(list(unique(major_type)), sep = ", "),   
    minor_type_group = paste(list(unique(minor_type)), sep = ", "),
    agency_count = n(),
  ) |> 
  mutate(
    first2_dig = str_sub(agency_num, 1, 2),
    # Fix misclassification of Cicero, Evanston, and Chicago
    type = case_when(
      first2_dig == "03" ~ "Muni",
      agency_group == "Evanston" | agency_group == "Cicero" | agency_group == "Chicago" ~ "Muni",
      first2_dig == "04" ~ "School",
      first2_dig == "02"  ~ "Township", 
      TRUE ~ "Other"
      )) |>
ungroup() |>
  select(year, agency_group, everything()) %>%
  filter(!agency_group %in% dropped_agencies$agency_group)

library(modelsummary)

before_table_pre_format <- before_table |>
  mutate(minor_type = case_when(minor_type == "BOND" ~ "Bond Fund",
                                minor_type == "ELEMENTARY" ~ "Elementary School District",
                                minor_type == "FIRE" ~ "Fire District",
                                minor_type == "GEN ASST" ~ "General Assistance Fund",
                                minor_type == "HEALTH" ~ "Health Services",
                                minor_type == "INFRA" ~ "Infrastructure Fund",
                                minor_type == "LIBRARY" ~ "Library District",
                                minor_type == "MISC" ~ "Miscellaneous District (e.g., mosquito abatement)",
                                minor_type == "MUNI" ~ "Municipality",
                                minor_type == "PARK" ~ "Park District",
                                minor_type == "SECONDARY" ~ "Secondary School District",
                                minor_type == "TOWNSHIP" ~ "Township",
                                minor_type == "POLICE" ~ "Police District",
                                TRUE ~ minor_type
                                 )) #|>
  # rename("Agency Minor Type" = minor_type) |>
  # rename("Agency Major Type" = type) |>
  # mutate(type = case_when(type == "Muni" ~ "Municipality",
  #                         type == "School" ~ "School District",
  #                         TRUE ~ type))

datasummary_crosstab(minor_type~type,  
                     statistic = 1~1+N, 
                     data = before_table_pre_format |>
                            filter(year == 2022))
                      

```

```{r year_type_table, include=FALSE}

table(grouped_manual$year, grouped_manual$type)


datasummary_crosstab(minor_type~type, data = grouped_manual %>% filter(year==2022),  statistic = 1~1+N, output = "flextable")

```

```{r}
#| layout-ncol: 2

grouped_manual |> 
  group_by(year, agency_group, triad_name)  |> 
  summarize(total_final_levy = sum(total_final_levy, na.rm = TRUE)) |> 
 # filter(agency_group != "Chicago" & agency_group != "Chicago Park District") |> 
  ggplot(aes(x=year, y = total_final_levy, group=agency_group)) + 
  theme_classic() + 
  geom_line() +
  facet_wrap(~triad_name) +
    labs(title = "Levy by Triad")


grouped_manual |> 
  group_by(year, agency_group, triad_name, home_rule_ind)  |> 
  summarize(cty_cook_eav = sum(cty_cook_eav, na.rm = TRUE)) |> 
#  filter(agency_group != "Chicago" & agency_group != "Chicago Park District") |> 
  ggplot(aes(x=year, y = cty_cook_eav, group=agency_group, color = triad_name) ) + 
  theme_classic() + 
  geom_line() +
  facet_wrap(~home_rule_ind) +
    labs(title = "Taxed EAV by Triad & Homerule Status")

grouped_manual |> 
  group_by(year, agency_group, triad_name)  |> 
  summarize(taxed_eav = sum(taxed_eav, na.rm = TRUE)) |> 
  ggplot() + 
  theme_classic() + 
  geom_line(aes(x=year, y = taxed_eav, group=agency_group) ) +
  facet_wrap(~triad_name) + 
  labs(title = "Taxed EAV by Triad", 
       caption = "Taxed EAV from backing out final_tax_to_dist variable")

grouped_manual |> 
  group_by(year, agency_group, triad_name, home_rule_ind)  |> 
  summarize(total_eav = sum(total_eav, na.rm = TRUE)) |> 
  ggplot() + 
  theme_classic() + 
  geom_line(aes(x=year, y = total_eav, group=agency_group, color = triad_name) ) +
  facet_wrap(~home_rule_ind)+
  labs(title = "Total Value by Triad & Home Rule Status")

```

Create estimated or "true" taxbase variable: The estimated market value is smoothed between the assessment years.

```{r}
#| label: fig-alt-attempt-estimate-smoothed-value
#| warning: false
#| message: false
#| layout-ncol: 2


df <- grouped_manual |>
  ungroup() |>
    mutate(assess_year_eav = ifelse(reassess_year == 1, cty_cook_eav, NA)) |>

  group_by(agency_group) |> 
  
  arrange(agency_group, year)|> 
  # Assessment Year
  
  fill(assess_year_eav, .direction = "down") |> 
  mutate(
   est_value = if_else(reassess_year == 1, cty_cook_eav, NA),
   r = if_else(reassess_year == 1, (lead(cty_cook_eav, 3)/cty_cook_eav )^ (1/(4-1))-1, NA)
  ) %>%
    fill(r, .direction = "down") |>
  mutate(r = ifelse(reassess_year == 0 & (year == 2022 & year == 2023), NA, r)) |> 
  mutate(est_value = if_else(is.na(est_value), lag(est_value, 1)*(1 + r), est_value),
         est_value = if_else(is.na(est_value), lag(est_value, 1)*(1 + r), est_value),
         est_value = if_else(year==2023 & reassess_year == 0, NA, est_value),
         est_value = if_else(year == 2022 & triad_name == "City", NA, est_value)
         ) |> 
  ungroup()




graphmunis <- c("Arlington Heights", "Alsip", "Dolton", "Cicero", "Evanston")

for(i in graphmunis){

 df %>%
    mutate(i=i) %>%
  mutate(across(.cols = c(est_value, cty_cook_eav, assess_year_eav), ~.x/1000000) ) %>%
 # filter(year>2010) %>%
  filter(agency_group == i) %>%
  ggplot() +

   # geom_line(aes(x=year, y = assess_year_eav), alpha = .5, color = "gray50")+
   # geom_point(aes(x=year, y = assess_year_eav), fill  = "gray50", alpha = .5) +

  geom_line(aes(x=year, y = cty_cook_eav), color = "black", lty = 3) + 
  geom_point(aes(x=year, y = cty_cook_eav), 
                 fill  = "black", alpha = .5) +
  
      geom_line(aes(x=year, y = est_value), alpha = .5, color = "red", lty = 2)+
    geom_point(aes(x=year, y = est_value), 
                 fill  = "red", alpha = .5) +
  scale_x_continuous(breaks = seq(ceiling(min(2006)), floor(max(2022)), by = 2)) +
  scale_y_continuous(labels = scales::dollar_format()) + 
    theme_classic() + 
    labs(title = paste(i), y= "Tax Base (in Millions)", x = "") -> graph

  print(graph)
}
```



```{r }
#| warning: false
#| message: false
#| label: fig-linegraph-triads-avg-growth


df %>% ungroup() |>
  mutate(across(.cols = c(est_value, cty_cook_eav, assess_year_eav), ~.x/1000000) ) %>%

  group_by(year, triad_name) %>%
  summarize(assess_year_eav = sum(assess_year_eav),
            cty_cook_eav =sum(cty_cook_eav),
            est_value = sum(est_value)) %>%
  ggplot() +

    geom_line(aes(x=year, y = assess_year_eav, group = triad_name))+

  geom_line(aes(x=year, y = cty_cook_eav, group = triad_name)) + 

      geom_line(aes(x=year, y = est_value, group = triad_name, color = triad_name), alpha = .5)+
    geom_point(aes(x=year, y = est_value, fill = triad_name, group = triad_name), alpha = .5) +
  scale_x_continuous(breaks = seq(ceiling(min(2006)), floor(max(2022)), by = 2)) +
  scale_y_continuous(labels = scales::dollar_format()) + 
  labs(title = "Summed Value by Triad (in Taxed EAV)", y = "Value ($1000)", x = "")
```


```{r flip_assessmentyear}
df <- df %>% 
  ungroup() %>%
  mutate(flip_assess = ifelse(reassess_year == 1, "0", "1"),
        # eav = cty_cook_eav,  # NOTE that eav was for total EAV in the agency summary file. Here it is the taxed EAV
         ln_av = log(av),
         ln_eav = log(cty_cook_eav),
         ln_taxed_eav = log(taxed_eav),
         ln_taxed_fmv = log(taxed_fmv),
         ln_fmv = log(total_fmv),
         ln_levy = log(total_final_levy),
         ln_est_v = log(est_value),
          ) %>%
  group_by(agency_group) %>%
  arrange(agency_group, year) %>%
  mutate(
        lag_eav = lag(cty_cook_eav, 1),
         ln_lag_av = log(lag(av, 1)),
         ln_lag_eav = log(lag(cty_cook_eav)),
         eav_updown= ifelse(lag(cty_cook_eav, 1) < cty_cook_eav, "Up", "Down"),
         ass = ifelse(lag(assess_year_eav,1) < assess_year_eav, "Up", "Down"),
         ass2 = ifelse(lag(cty_cook_eav,1) < cty_cook_eav, "Up", "Down")) %>% 
  ungroup() 
```

```{r}
#| include: false

df %>% filter(is.na(agency_group))
df %>% filter(is.na(triad_name))

# one school didn't have an agency group name, so give it a name.
df <- df %>% 
  mutate(agency_group = ifelse(is.na(agency_group), agency_name, agency_group))
```

#### Export CSV

```{r exportCSV}
df |> write_csv("NTA_data_2024_11_06.csv")
```

```{r}
#| layout-ncol: 2
#| warning: false
#| message: false

df %>% 
  filter(is.na(assess_year_eav)) %>% 
  group_by(year) %>%
  summarize(count = n()) %>% arrange(desc(count))


df %>% 
  filter(is.na(est_value)) %>% 
  group_by(year) %>%
  summarize(count = n()) %>% arrange(desc(count))

```

If we drop Chicago, we get to keep another year of data for all of the other munis in North and South triads. 

# NTA Descriptive Statistics

## Tables

Exported as Word Documents. 

```{r}
#| label: model-vars-continuous-notlogged2
#| warning: false
#| message: false

crosstable::crosstable(data = df, cols = c(type, total_final_levy, cty_total_eav, av, taxed_fmv))


```


```{r}
#| label: model-vars-continuous-notlogged
#| warning: false
#| message: false

cont_var <- df |>
  select(type, cty_cook_eav, total_final_levy, est_value, ln_lag_eav) |>
  group_by(type) |>
  reframe(n = n(), 
          "Min TEAV" = min(cty_cook_eav, na.rm = T), 
          "Mas TEAV" = max(cty_cook_eav, na.rm = T), 
          "Mean TEAV" = mean(cty_cook_eav, na.rm = T), 
          "Median TEAV" = median(cty_cook_eav, na.rm = T),
          "SD TEAV" = sd(cty_cook_eav, na.rm = T),
          "Min Levy" = min(total_final_levy, na.rm = T), 
          "Max Levy" = max(total_final_levy, na.rm = T), 
          "Mean Levy" = mean(total_final_levy, na.rm = T), 
          "Median Levy" = median(total_final_levy, na.rm = T),
          "SD Levy" = sd(total_final_levy, na.rm = T),
          "Min Est. Value" = min(est_value, na.rm = T), 
          "Max Est. Value" = max(est_value, na.rm = T), 
          "Mean Est. Value" = mean(est_value, na.rm = T), 
          "Median Est. Value" = median(est_value, na.rm=TRUE),
          "SD Est. Value" = sd(est_value, na.rm = T)
  ) |>
  pivot_longer(
    cols = -type,
    names_to = c("variable", "statistic"), 
    names_sep = " " 
  ) |>
  unite(col = "var_stat", variable, statistic, sep = " ") |>
  pivot_wider(
    id_cols = var_stat, 
    names_from = type, 
    values_from = value
  ) 

cont_var %>% flextable::flextable() 
tt_cont_var <- tt(cont_var)
         
tt_cont_var |>
  save_tt("cont_descr_stats_11_5_24.docx",
          overwrite = TRUE)

```


```{r}
#| label: model-vars-continuous-descr
#| warning: false
#| message: false

tt_cont_var <- df |>
  select(type, ln_eav, ln_levy, ln_est_v, ln_lag_eav) |>
  group_by(type) |>
  reframe(n = n(), 
          "min ln(eav)" = min(ln_eav, na.rm = T), 
          "max ln(eav)" = max(ln_eav, na.rm = T), 
          "mean ln(eav)" = mean(ln_eav, na.rm = T), 
          "median ln(eav)" = median(ln_eav, na.rm = T),
          "sd ln(eav)" = sd(ln_eav, na.rm = T),
          "min ln(levy)" = min(ln_levy, na.rm = T), 
          "max ln(levy)" = max(ln_levy, na.rm = T), 
          "mean ln(levy)" = mean(ln_levy, na.rm = T), 
          "median ln(levy)" = median(ln_levy, na.rm = T),
          "sd ln(levy)" = sd(ln_levy, na.rm = T),
          "min ln(lag eav)" = min(ln_lag_eav, na.rm = T), 
          "max ln(lag eav)" = max(ln_lag_eav, na.rm = T), 
          "mean ln(lag eav)" = mean(ln_lag_eav, na.rm = T), 
          "median ln(lag eav)" = median(ln_lag_eav, na.rm = T),
          "sd ln(lag eav)" = sd(ln_lag_eav, na.rm = T),
          "min ln(estV)" = min(ln_est_v, na.rm = T), 
          "max ln(estV)" = max(ln_est_v, na.rm = T), 
          "mean ln(estV)" = mean(ln_est_v, na.rm = T), 
          "median ln(estV)" = median(ln_est_v),
          "sd ln(estV)" = sd(ln_est_v, na.rm = T)
  ) |>
  pivot_longer(
    cols = -type, 
    names_to = c("variable", "statistic"), 
    names_sep = " " 
  ) |>
  unite(col = "var_stat", variable, statistic, sep = " ") |>
  pivot_wider(
    id_cols = var_stat, 
    names_from = type, 
    values_from = value,
    values_fn = function(x) format(x, digits = 2, nsmall = 2)
  ) |>
  tt()
          
tt_cont_var |>
  save_tt("cont_descr_stats_11_5_24.docx",
          overwrite = TRUE)

```

```{r}
#| label: model-vars-cat

tt_cat_vars <- df |>
  select(type, year) |>
  group_by(type, year) |>
  summarize(n = n()) |> 
  pivot_wider(
    names_from = type,  # Use 'type' as columns
    values_from = n,     # Use 'n' as values
    id_cols = year      # Use 'year' as rows 
  ) |>
  tt()

tt_cat_vars |>
  save_tt("cat_descr_stats_11_5_24.docx",
          overwrite = TRUE)


```

## Visualizations

### Time Trends


```{r}
#| label: levies_over_time_by_type


df |> 
  group_by(year) |> 
  summarize(median_levy = median(total_final_levy/1000000, na.rm = TRUE)) |> 
  ggplot(aes(x = year, y = median_levy), lwd = 2) + 
  geom_line() +
  labs(
    title = "Median Levy Over Time - for All Agencies in Models",
    x = "Year",
    y = "Millions of Dollars"
  )+
  scale_x_continuous(breaks = seq(min(df$year), max(df$year), by = 2)) +  # Adjust x-axis breaks 
  theme_minimal()

df |> 
  group_by(year, type) |> 
  summarize(median_levy = median(total_final_levy/1000000, na.rm = TRUE)) |> 
  ggplot() + 
  geom_line(aes(x = year, y = median_levy, color = type), lwd =2) +
  labs(
    title = "Median Levy Over Time by Taxing Agency Type",
    x = "Year",
    y = "Millions of Dollars",
    color = "Agency Type"
  ) +
  scale_color_brewer(palette = "Reds", direction = -1) +
  scale_x_continuous(breaks = seq(min(df$year), max(df$year), by = 2)) +  # Adjust x-axis breaks 
  theme_minimal()
  


```


```{r}
#| label: levies_over_time_by_type_hrind
#| layout-ncol: 2


df |> 
  group_by(year, home_rule_ind) |> 
  summarize(median_levy = median(total_final_levy/1000000, na.rm = TRUE)) |> 
  ggplot(aes(x = year, y = median_levy, group = home_rule_ind, lty = home_rule_ind)) + 
  geom_line(lwd = 1) +
  labs(
    title = "Median Levy Over Time - for All Agencies in Models",
    x = "Year",
    y = "Millions of Dollars", caption = ""
  )+
  scale_x_continuous(breaks = seq(min(df$year), max(df$year), by = 2)) +  # Adjust x-axis breaks 
  theme_minimal()

df |> 
  group_by(year, type, home_rule_ind) |> 
  summarize(median_levy = median(total_final_levy/1000000, na.rm = TRUE)) |> 
  ggplot(aes(x = year, y = median_levy, color = type, lty = home_rule_ind)) + 
  geom_line(lwd =1  ) +
  labs(
    title = "Median Levy Over Time by Taxing Agency Type",
    x = "Year",
    y = "Millions of Dollars",
    color = "Agency Type"
  ) +
  scale_color_brewer(palette = "Reds", direction = -1) +
  scale_x_continuous(breaks = seq(min(df$year), max(df$year), by = 2)) +  # Adjust x-axis breaks 
  theme_minimal()
  


```

```{r}
#| label: tax-base-over-time

df |> 
  filter(type != "Township")  |>
  group_by(year, type) |> 
  summarize(median_eav = median(taxed_eav, na.rm = TRUE)/1000000) |> 
  ggplot(aes(x = year, y = median_eav, color = type)) + 
  geom_line(lwd = 1.5) +
  labs(
    title = "Median EAV Over Time by Taxing Agency Type",
    x = "Year",
    y = "EAV (Millions)",
    color = "Agency Type"
  ) +
  scale_color_brewer(palette = "Blues", direction = -1) + 
  scale_x_continuous(breaks = seq(min(df$year), max(df$year), by = 2)) +  # Adjust x-axis breaks 
  theme_minimal()

```


```{r }
#| warning: false
#| message: false
#| label: fig-linegraph-triads-loggedtaxbase_estvalue
  
df %>% ungroup() |>
 # mutate(across(.cols = c(ln_av, ln_est_v), ~.x/1000000) ) %>%
  group_by(year, triad_name) %>%
  summarize(
            eav = sum(cty_cook_eav),
            est_value = sum(est_value)) %>%
 # filter(year > 2008 & year < 2021) %>%
  ggplot() +

  geom_line(aes(x=year, y = log(eav), group = triad_name)) + 

      geom_line(aes(x=year, y = log(est_value), group = triad_name, color = triad_name), alpha = .5)+
    geom_point(aes(x=year, y = log(est_value), fill = triad_name, group = triad_name), alpha = .5) +
  scale_x_continuous(breaks = seq(ceiling(min(2006)), floor(max(2022)), by = 2)) +
  labs(title = "Summed Value by Triad", y = "Logged Value", x = "")
```

### Bar Charts/Histograms

```{r}
#| label: fig-bar_chart_all_agencies_stacked
#| column: margin

library(RColorBrewer)
df |>
  filter(year == 2022) |>
  mutate(type = ifelse(type == "Muni", "Municipality", type)) |>
  group_by(type, home_rule_ind) |>
  ggplot(aes(x=type, fill = home_rule_ind)) +
  geom_bar() +
    geom_text(stat = 'count', aes(label = ..count.., y = ..count..), vjust = -0.5, color = "black") +
  labs(
    title = "Taxing Agency Count by Agency Type",
    caption = "Agency counts are consistent across all years",
    x = "Agency Type",
    y = "N"
  ) +
  theme_classic() +
  scale_fill_manual(values = brewer.pal(n = 6, "Blues")[3:6]) +
  theme(legend.position = "none",
        axis.title.y = element_text(angle = 0))

```


```{r}
#| label: bar_chart_all_agencies

library(RColorBrewer)
df |>
  filter(year == 2022) |>
  mutate(type = ifelse(type == "Muni", "Municipality", type)) |>
  ggplot(aes(x = type, fill = type)) +
  geom_bar() +
  geom_text(stat = 'count', aes(label = ..count.., y = ..count..), vjust = -0.5, color = "black") +
  labs(
    title = "Taxing Agency Count by Agency Type",
    subtitle = "Values Are Consistent Across All Years",
    x = "Agency Type",
    y = "N"
  ) +
  theme_classic() +
  scale_fill_manual(values = brewer.pal(n = 6, "Blues")[3:6]) +
  theme(legend.position = "none",
        axis.title.y = element_text(angle = 0))

```

```{r}
#| label: bar_chart_schools

df |>
  filter(year == 2022) |>
  filter(type == "School") |>
  filter(minor_type %in% c("ELEMENTARY", "SECONDARY")) |>
  ggplot(aes(x = minor_type, fill = minor_type)) +
  geom_bar() +
  geom_text(stat = 'count', aes(label = ..count.., y = ..count..), vjust = -0.5, color = "black") +
  labs(
    title = "School Districts: Primary and Secondary",
    subtitle = "Values Are Consistent Across All Years",
    x = "School Agency Type",
    y = "N"
  ) +
  theme_classic() +
  scale_fill_manual(values = c(brewer.pal(n = 6, "Blues")[3], brewer.pal(n = 6, "Blues")[5])) +  # Specify colors individually
  theme(legend.position = "none",
        axis.title.y = element_text(angle = 0))

```

```{r}
#| label: bar_chart_homerule

df |>
  filter(year == 2022) |>
  filter(type == "Muni") |>
  mutate(home_rule = ifelse(home_rule_ind == 1, "Yes", "No")) |>  # Create a new column for home rule status
  ggplot(aes(x = home_rule, fill = home_rule)) +
  geom_bar() +
  geom_text(stat = 'count', aes(label = ..count.., y = ..count..), vjust = -0.5, color = "black") +
  labs(
    title = "Municipalities by Home Rule Status",
    subtitle = "Values Are Consistent Across All Years",
    x = "Home Rule Status",
    y = "N"
  ) +
  theme_classic() +
  scale_fill_manual(values = brewer.pal(n = 5, "Blues")[3:4]) +  # Use 2 colors from the Blues palette
  theme(legend.position = "none",
        axis.title.y = element_text(angle = 0)) 

```

```{r}
df %>% ungroup() |>
  mutate(across(.cols = c(taxed_eav, total_eav, cty_cook_eav, est_value), ~.x/1000000) ) %>%
  group_by(year, triad_name) %>%
  summarize(
          eav_total = sum(total_eav),
          eav_taxed = sum(taxed_eav),

            eav = sum(cty_cook_eav),
            est_value = sum(est_value)) %>%
  ggplot(lwd = 3) +

  geom_line(aes(x=year, y = eav, group = triad_name)) + 
      geom_line(aes(x=year, y = eav_total, group = triad_name, color = triad_name), alpha = .5, , color = "gray")+

      geom_line(aes(x=year, y = est_value, group = triad_name, color = triad_name), alpha = .5)+
        geom_line(aes(x=year, y = eav_taxed, group = triad_name, color = triad_name), alpha = .5)+

    geom_point(aes(x=year, y = est_value, fill = triad_name, group = triad_name), alpha = .5) +
  scale_x_continuous(breaks = seq(ceiling(min(2006)), floor(max(2023)), by = 2)) +
    scale_y_continuous(labels = scales::dollar) +

  labs(title = "Summed Value by Triad", y = "Tax Base (in Millions)", x = "", 
       caption = "Light Gray line is total Value instead of Taxed Value") + theme_classic()
```


# Models

## NTA Models

```{r}
#| column: page
#| label: tbl-main-models
#| tbl-cap: "Uses estimated value of EAV and current tax year EAV"


df <- df |> mutate(eav = cty_cook_eav)
  
  all_models <- list(
    
    "All Agencies" = list(
    
    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
                data = df,
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) +  log(eav)  | agency_group + year,
                data = df,
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),
    
    "Municipalities" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "Muni"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) +  log(eav) | agency_group + year,
                data = df |> filter(type == "Muni"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),      
    
    "Schools" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "School"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) +  log(eav) | agency_group + year,
                data = df |> filter(type == "School"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),
    
  "Townships" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "Township"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(eav) + log(est_value) | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),
    "Special Districts" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "Other"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) +  log(eav) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    )
    )
  
all_models_formatted <- modelsummary(all_models,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

all_models_formatted

save_tt(all_models_formatted,
        "all_models_2024_11_6.docx",
        overwrite = TRUE)

```


```{r}
#| column: page
#| label: tbl-main-models-laggedeav
#| tbl-cap: "Uses estimated value of EAV and lagged EAV"
#| include: false
#| eval: false

df <- df |> mutate(eav = cty_cook_eav)
  
  all_models <- list(
    
    "All Agencies" = list(
    
    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
                data = df,
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) + l(log(eav)) | agency_group + year,
                data = df,
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),
    
    "Municipalities" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "Muni"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) + l(log(eav)) | agency_group + year,
                data = df |> filter(type == "Muni"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),      
    
    "Schools" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "School"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) +  l(log(eav)) | agency_group + year,
                data = df |> filter(type == "School"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),
    
  "Townships" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "Township"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) + l(log(eav)) | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    ),
    "Special Districts" = list(

    "I" = feols(log(total_final_levy) ~ log(est_value) | agency_group + year,
          data = df |> filter(type == "Other"),
          vcov = ~agency_group,
          panel.id = c("agency_group", "year"),
          ),
    
    "II" = feols(log(total_final_levy) ~ log(est_value) +  l(log(eav)) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year"),
                )
    )
    )
  
all_models_formatted <- modelsummary(all_models,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

all_models_formatted

```


```{r}
#| label: munis_and_schools_models
#| column: page


munis_and_schools <- list(
  
  "Municipalities" = list(
    
    "All Municipalities" = feols(log(total_final_levy) ~ log(est_value) + log(eav) | agency_group + year,
                data = df |> filter(type == "Muni"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Homerule" = feols(log(total_final_levy) ~ log(est_value) + log(eav) | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ log(est_value) + log(eav) | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(
    
    "All Schools" = feols(log(total_final_levy) ~ log(est_value) + log(eav)| agency_group + year,
                data = df |> filter(type == "School"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Elementary" = feols(log(total_final_levy) ~ log(est_value) + log(eav) | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ log(est_value) + log(eav)
                        | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ), 
  
  "Other" = list(
    
    "Townships" = feols(log(total_final_levy) ~ log(est_value) + log(eav)
                        | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Special District" = feols(log(total_final_levy) ~ log(est_value) + log(eav) 
                         | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

save_tt(munis_and_schools_formatted,
        "munis_and_schools_formatted_2024_11_6.docx",
        overwrite = TRUE)

```

```{r}
#| label: munis_and_schools_robustness-lags
#| column: page
#| tbl-cap: "Robustness Check Slide: Has est_value with eav and lagged eav. "


munis_and_schools <- list(
  
  "Municipalities" = list(
    
    "All Municipalities" = feols(log(total_final_levy) ~ log(est_value) + log(eav) + 
                         l(log(eav), 1)  | agency_group + year,
                data = df |> filter(type == "Muni"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Homerule" = feols(log(total_final_levy) ~ log(est_value) + log(eav) + 
                         l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ log(est_value) + log(eav) +  
                             l(log(eav), 1)  | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(
    
    "All Schools" = feols(log(total_final_levy) ~ log(est_value) + log(eav) +  
                            l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "School"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Elementary" = feols(log(total_final_levy) ~ log(est_value) + log(eav) +  
                           l(log(eav), 1)| agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ log(est_value) + log(eav) +  
                          l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ), 
  
  "Other" = list(
    
    "Townships" = feols(log(total_final_levy) ~ log(est_value) + log(eav) +  
                          l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Special District" = feols(log(total_final_levy) ~ log(est_value) + log(eav) +  
                                 l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

save_tt(munis_and_schools_formatted,
        "munis_and_schools_robustness_2024_11_6.docx",
        overwrite = TRUE)

```


## Variations

```{r}
#| label: munis_and_schools_nolags
#| column: page
#| warning: false
#| message: false


munis_and_schools <- list(
  
  "Municipalities" = list(
    # 
    # "All Municipalities" = feols(log(total_final_levy) ~ log(eav)  | agency_group + year,
    #             data = df |> filter(type == "Muni"),
    #             vcov = ~agency_group,
    #             panel.id = c("agency_group", "year")
    #             ),
    
    "Homerule" = feols(log(total_final_levy) ~ log(eav)  | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ log(eav)  | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(
    
    # "All Schools" = feols(log(total_final_levy) ~ log(eav)  | agency_group + year,
    #             data = df |> filter(type == "School"),
    #             vcov = ~agency_group,
    #             panel.id = c("agency_group", "year")
    #             ),
    # 
    "Elementary" = feols(log(total_final_levy) ~ log(eav)  | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ log(eav)  | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Other" = list(    
    "Special District" = feols(log(total_final_levy) ~  log(eav) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
      "Townships" = feols(log(total_final_levy) ~  log(eav) | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
    )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

```


```{r}
#| label: munis_and_schools_lagsonly
#| column: page
#| warning: false
#| message: false

munis_and_schools <- list(
  
  "Municipalities" = list(

    "Homerule" = feols(log(total_final_levy) ~  l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(

    
    "Elementary" = feols(log(total_final_levy) ~  l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ), 
  
  "Other" = list(    
    "Special District" = feols(log(total_final_levy) ~  l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
      "Townships" = feols(log(total_final_levy) ~  l(log(eav), 1) | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
    )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

```



```{r}
#| include: false
#| eval: false
#| label: munis_and_schools_lags_reassess

munis_and_schools <- list(
  
  "Municipalities" = list(

    "Homerule" = feols(log(total_final_levy) ~  l(log(est_value), 1)*reassess_year | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ l(log(est_value), 1)*reassess_year | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(

    "Elementary" = feols(log(total_final_levy) ~  l(log(est_value), 1)*reassess_year | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ l(log(est_value), 1)*reassess_year | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

```


```{r}
#| include: false
#| eval: false
#| label: munis_and_schools_models_flipassess

munis_and_schools <- list(
  
  "Municipalities" = list(

    "Homerule" = feols(log(total_final_levy) ~ log(est_value)*flip_assess  + log(eav)*flip_assess
                       | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ log(est_value)*flip_assess  + log(eav)*flip_assess
                           | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(
  
    "Elementary" = feols(log(total_final_levy) ~ log(est_value)*flip_assess  + log(eav)*flip_assess
                         | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ log(est_value)*flip_assess  + log(eav)*flip_assess 
                           | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

```


```{r}
#| label: munis_and_schools_models_assymmetric 
#| warning: false
#| message: false


munis_and_schools <- list(
  
  "Municipalities" = list(
    
    "Homerule" = feols(log(total_final_levy) ~ log(eav)*eav_updown + 
                         log(est_value)*eav_updown | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ log(eav)*eav_updown + 
                         log(est_value)*eav_updown | agency_group + year,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(
    
    # "All Schools" = feols(log(total_final_levy) ~ log(eav)*eav_updown + 
    #                      l(log(eav), 1)*eav_updown | agency_group + year,
    #             data = df |> filter(type == "School"),
    #             vcov = ~agency_group,
    #             panel.id = c("agency_group", "year")
    #             ),
    
    "Elementary" = feols(log(total_final_levy) ~ log(eav)*eav_updown + 
                         log(est_value)*eav_updown  | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ log(eav)*eav_updown + 
                        log(est_value)*eav_updown | agency_group + year,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted

```

```{r}
#| label: tbl-munis_and_schools_models_adddedtriadFE
#| tbl-cap: "Has Year-Triad and agency_group FE"
#| message: false
#| warning: false

munis_and_schools <- list(
  
  "Municipalities" = list(
    
    # "All Municipalities" = feols(log(total_final_levy) ~ log(eav) + 
    #                      l(log(eav), 1) | agency_group + year^triad_name,
    #             data = df |> filter(type == "Muni"),
    #             vcov = ~agency_group,
    #             panel.id = c("agency_group", "year")
    #             ),
    
    "Homerule" = feols(log(total_final_levy) ~ log(eav) + 
                         l(log(eav), 1) | agency_group + year^triad_name,
                data = df |> filter(type == "Muni" & home_rule_ind == 1),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Non-Homerule" = feols(log(total_final_levy) ~ log(eav) + 
                         l(log(eav), 1) | agency_group + year^triad_name,
                data = df |> filter(type == "Muni" & home_rule_ind == 0),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  ),
  
  "Schools" = list(
    # 
    # "All Schools" = feols(log(total_final_levy) ~ log(eav) + 
    #                      l(log(eav), 1) | agency_group + year^triad_name,
    #             data = df |> filter(type == "School"),
    #             vcov = ~agency_group,
    #             panel.id = c("agency_group", "year")
    #             ),
    
    "Elementary" = feols(log(total_final_levy) ~ log(eav) + 
                         l(log(eav), 1) | agency_group + year^triad_name,
                data = df |> filter(type == "School" & minor_type == "ELEMENTARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Secondary" = feols(log(total_final_levy) ~ log(eav) + 
                         l(log(eav), 1) | agency_group + year^triad_name,
                data = df |> filter(type == "School" & minor_type == "SECONDARY"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  )
)

munis_and_schools_formatted <- modelsummary(munis_and_schools,
             shape = "cbind",                                  
             #coef_map = name_map,
             fmt = function(x) round(x, 2),
             #gof_omit = "AIC|BIC|RMSE|Std.Errors|FE",
             stars = TRUE)

munis_and_schools_formatted


```



```{r}
#| label: export_fes
#| eval: false

feols_test <- feols(log(total_final_levy) ~  log(est_value)  | agency_group + year,
               data = df,
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                )

FEs <- fixef(feols_test)

FE_agencies <- as.list(FEs$agency_group[1])

FE_vals <- as.list(FEs$agency_group[3])

FE_agencies_df <- as.data.frame(FE_agencies)

FE_agencies_df <- FE_agencies_df |>
  pivot_longer()


```

```{r}
#| label: tbl-modelsbytype4
#| tbl-cap: "Uses agency_group fixed effects with grouped and summed taxing agencies. Compares models with log(eav), lagged log(eav), and log(est_value) in model. SEs clustered by taxing agency. "

mods_1 <- list(
  
    "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)*eav_updown  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
      "Homerule" = feols(log(total_final_levy) ~  log(est_value)*eav_updown  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)*eav_updown | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~  log(est_value)*eav_updown | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)*eav_updown  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ) ,
  
    "Schools" = feols(log(total_final_levy) ~ log(est_value)*eav_updown  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                )      )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 ##gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

```{r}
#| label: tbl-models-MVHAWM
#| tbl-cap: "Combo Tables Nov. 7th"
#| column: page

mods_1 <- list(
  
    "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)  + log(l(est_value, 1))  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
        "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value)  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
            "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value) + log(l(est_value, 1))  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
      "Homerule" = feols(log(total_final_levy) ~  log(est_value)  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)  | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
         "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value)  | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~  log(est_value) | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
         "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value)  + log(l(est_value, 1)) | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
  
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ) ,
    
        "Schools" = feols(log(total_final_levy) ~ log(est_value)  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ) ,
  
  
    "Schools" = feols(log(total_final_levy) ~ log(est_value) + ln_lag_eav + log(eav)  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
      
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value) + log(l(est_value, 1))  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
        "Townships" = feols(log(total_final_levy) ~  ln_lag_eav + log(eav) + log(est_value) + log(l(est_value,1)) | agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Special District" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value) + log(l(est_value,1)) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  
    )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 ##gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```


```{r}
#| label: tbl-models-MVHAWMhybrid-withFMV
#| tbl-cap: "Fair Market Value (FMV) and the Tax Base (TEAV) Nov. 7th"
#| column: page

mods_1 <- list(
  
    "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav)  + log(l(est_value, 1)) + log(total_fmv)  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  

      "Homerule" = feols(log(total_final_levy) ~  log(est_value)  | agency_group + year,
               data = df |> filter(home_rule_ind == 1 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(total_fmv) + log(taxed_fmv)  | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
         "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value)   | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~  log(est_value) | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
         "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value)  + log(l(est_value, 1)) | agency_group + year,
               data = df |> filter(home_rule_ind == 0 & type == "Muni"),
             vcov  = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
  
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(total_fmv)+ log(taxed_fmv) | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ) ,
    
        "Schools" = feols(log(total_final_levy) ~ log(est_value)  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ) ,
  
  
    "Schools" = feols(log(total_final_levy) ~ log(est_value) + ln_lag_eav + log(eav)  | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
      
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value) + log(l(est_value,1)) | agency_group + year,
               data = df |> filter(type == "School"),
               vcov = ~ agency_group,
               panel.id = c("agency_group", "year")
                ),
    
        "Townships" = feols(log(total_final_levy) ~  ln_lag_eav + log(eav) + log(est_value) + log(l(est_value,1)) + log(total_fmv) + log(taxed_fmv)| agency_group + year,
                data = df |> filter(type == "Township"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                ),
    
    "Special District" = feols(log(total_final_levy) ~ ln_lag_eav + log(eav) + log(est_value) + log(l(est_value,1)) + log(total_fmv) + log(taxed_fmv) | agency_group + year,
                data = df |> filter(type == "Other"),
                vcov = ~agency_group,
                panel.id = c("agency_group", "year")
                )
  
    )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 ##gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```


```{r}
#| label: tbl-merriman_models_start2011
#| tbl-cap: "**2011-2020. All Agencies (after Grouping and Cleaning)** Agency_group and year fixed effects. Uses grouped and summed taxing agencies. Includes lagged log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. HC1 standard errors as is the default for Stata. "


df2011 <- df |> filter(year > 2010 & year <= 2020)

mods_1 <- list(
  
  "1" = feols(log(total_final_levy) ~ ln_eav | agency_group + year,
               data = df2011,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                ),
  
    "2" = feols(log(total_final_levy) ~ ln_est_v | agency_group + year,
               data = df2011,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                ),
  
      "3" = feols(log(total_final_levy) ~ ln_lag_eav  | agency_group + year,
               data = df2011,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                ),
  
     "4A. HC1" = feols(log(total_final_levy) ~ ln_lag_eav + ln_est_v | agency_group + year,
               data = df2011,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                       ),
  
     "4B. Twoway FE" = feols(log(total_final_levy) ~ ln_lag_eav + ln_est_v | agency_group + year,
               data = df2011,
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                       )
)

modelsummary::modelsummary(
  mods_1,
  output = "flextable",
# gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```
```{r}
#| label: tbl-merriman_models_start2014
#| tbl-cap: "**2014-2020. All Agencies (after Grouping and Cleaning)** Agency_group and year fixed effects. Uses grouped and summed taxing agencies. Includes lagged log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. HC1 standard errors as is the default for Stata. "


df2014 <- df |> filter(year > 2013 & year <= 2020)

mods_1 <- list(
  
  "1" = feols(log(total_final_levy) ~ ln_eav | agency_group + year,
               data = df2014,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                ),
  
    "2" = feols(log(total_final_levy) ~ ln_est_v | agency_group + year,
               data = df2014,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                ),
  
      "3" = feols(log(total_final_levy) ~ ln_lag_eav  | agency_group + year,
               data = df2014,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                ),
  
     "4A. HC1" = feols(log(total_final_levy) ~ ln_lag_eav + ln_est_v | agency_group + year,
               data = df2014,
               vcov = "hc1",
               panel.id = c("agency_group", "year")
                       ),
  
     "4B. Twoway FE" = feols(log(total_final_levy) ~ ln_lag_eav + ln_est_v | agency_group + year,
               data = df2014,
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                       )
)

modelsummary::modelsummary(
  mods_1,
  output = "flextable",
# gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

```{r}
#| label: tbl-modelsbytype_start2011
#| tbl-cap: "2011-2020. Uses agency_group fixed effects with grouped and summed taxing agencies. Includes log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. Hc1 standard errors. "

mods_1 <- list(
  
  "All Types" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess  | agency_group + year,
               data = df2011,
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                ),
  
    "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess  | agency_group + year,
               data = df2011 |> filter(home_rule_ind == 1 & type == "Muni"),
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess | agency_group + year,
               data = df2011 |> filter(home_rule_ind == 0 & type == "Muni"),
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                ),
  
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess  | agency_group + year,
               data = df2011 |> filter(type == "School"),
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                )        )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 ##gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

```{r}
#| label: tbl-modelsbytype_start2014
#| tbl-cap: "2014-2020. Uses agency_group fixed effects with grouped and summed taxing agencies. Includes log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. Hc1 standard errors. "

mods_1 <- list(
  
  "All Types" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess  | agency_group + year,
               data = df2014,
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                ),
  
    "Homerule" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess  | agency_group + year,
               data = df2014 |> filter(home_rule_ind == 1 & type == "Muni"),
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                ),
  
     "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess | agency_group + year,
               data = df2014 |> filter(home_rule_ind == 0 & type == "Muni"),
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                ),
  
    "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess  | agency_group + year,
               data = df2014 |> filter(type == "School"),
               vcov = "twoway",
               panel.id = c("agency_group", "year")
                )        )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 ##gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```


<!-- ## Matching Merriman's Stata Output -->

<!-- ```{r} -->
<!-- #| label: tbl-merriman_models-agency_group -->
<!-- #| tbl-cap: "**2010 to 2020. All Agencies (after Grouping and Cleaning)** Agency_group and year fixed effects. Uses grouped and summed taxing agencies. Includes lagged log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. HC1 standard errors as is the default for Stata. " -->


<!-- df <- df |> filter(year >= 2010 & year <= 2020) -->

<!-- mods_1 <- list( -->

<!--   "1" = feols(log(total_final_levy) ~ ln_eav | agency_group + year, -->
<!--                data = df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--     "2" = feols(log(total_final_levy) ~ ln_est_v | agency_group + year, -->
<!--                data = df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--       "3" = feols(log(total_final_levy) ~ ln_lag_eav  | agency_group + year, -->
<!--                data = df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--      "4A. HC1" = feols(log(total_final_levy) ~ ln_lag_eav + ln_est_v | agency_group + year, -->
<!--                data = df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                        ), -->

<!--      "4B. Twoway FE" = feols(log(total_final_levy) ~ ln_lag_eav + ln_est_v | agency_group + year, -->
<!--                data = df, -->
<!--                vcov = "twoway", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                        ) -->
<!-- ) -->

<!-- modelsummary::modelsummary( -->
<!--   mods_1, -->
<!--   output = "flextable", -->
<!-- # gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"), -->
<!--               stars = TRUE -->
<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- #| label: tbl-homerule-agency_group -->
<!-- #| tbl-cap: "**Home Rule Agencies only!** Uses agency_group fixed effects with grouped and summed taxing agencies. Includes log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. Twoway clustered standard errors. " -->

<!-- library(fixest) -->

<!-- hr_df = df %>% filter(home_rule_ind == 1) -->
<!-- mods_1 <- list( -->

<!--       "1" = feols(log(total_final_levy) ~  log(est_value) | agency_group + year, -->
<!--                data = hr_df, -->
<!--                vcov = "twoway", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--   "2" = feols(log(total_final_levy) ~ ln_lag_eav | agency_group + year, -->
<!--                data = hr_df, -->
<!--                vcov = "twoway", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->



<!--      "3" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) + flip_assess | agency_group + year, -->
<!--                data = hr_df, -->
<!--                vcov = "twoway", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--     "4" = feols(log(total_final_levy) ~ log(est_value) + ln_lag_eav | agency_group + year, -->
<!--                data = hr_df, -->
<!--                vcov = "twoway", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--   "Interact" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) + log(est_value)*flip_assess | agency_group + year, -->
<!--                data = hr_df, -->
<!--                vcov = "twoway", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ) -->
<!--   ) -->


<!-- modelsummary::modelsummary( -->
<!--   mods_1, -->
<!--   output = "flextable", -->
<!--  #gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"), -->
<!--               stars = TRUE -->
<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- #| label: tbl-NONhomerule-agency_group -->
<!-- #| tbl-cap: "**Non-Home Rule Municipalities only** Uses agency_group fixed effects with grouped and summed taxing agencies. Includes log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. HC1 standard errors. " -->

<!-- library(fixest) -->

<!-- nonhr_df = df %>%  -->
<!--   filter(home_rule_ind == 0 & type == "Muni") -->

<!-- mods_1 <- list( -->


<!--     "1" = feols(log(total_final_levy) ~  log(est_value) | agency_group + year, -->
<!--                data = nonhr_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->


<!--   "2" = feols(log(total_final_levy) ~ ln_lag_eav | agency_group + year, -->
<!--                data = nonhr_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--      "3" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess | agency_group + year, -->
<!--                data = nonhr_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--     "4" = feols(log(total_final_levy) ~ log(est_value) + ln_lag_eav | agency_group + year, -->
<!--                data = nonhr_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->
<!--       "4" = feols(log(total_final_levy) ~ log(est_value) + ln_eav  | agency_group + year, -->
<!--                data = nonhr_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--   "Interact" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) + log(est_value)*flip_assess | agency_group + year, -->
<!--                data = nonhr_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ) -->
<!--   ) -->


<!-- modelsummary::modelsummary( -->
<!--   mods_1, -->
<!--   output = "flextable", -->
<!-- # gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"), -->
<!--               stars = TRUE -->
<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- #| label: tbl-school-hc1 -->
<!-- #| tbl-cap: "**Schools only** Uses agency_group fixed effects with grouped and summed taxing agencies. Includes log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. HC1 standard errors. " -->

<!-- library(fixest) -->

<!-- school_df = df %>%  -->
<!--   filter(type == "School") -->

<!-- mods_1 <- list( -->


<!--     "1" = feols(log(total_final_levy) ~  log(est_value) | agency_group + year, -->
<!--                data = school_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->


<!--   "2" = feols(log(total_final_levy) ~ ln_lag_eav | agency_group + year, -->
<!--                data = school_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--      "3" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)*flip_assess | agency_group + year, -->
<!--                data = school_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--     "4" = feols(log(total_final_levy) ~ log(est_value) + ln_lag_eav | agency_group + year, -->
<!--                data = school_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->
<!--       "4" = feols(log(total_final_levy) ~ log(est_value) + ln_eav  | agency_group + year, -->
<!--                data = school_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--   "Interact" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) + log(est_value)*flip_assess | agency_group + year, -->
<!--                data = school_df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ) -->
<!--   ) -->


<!-- modelsummary::modelsummary( -->
<!--   mods_1, -->
<!--   output = "flextable", -->
<!-- # gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"), -->
<!--               stars = TRUE -->
<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- #| label: tbl-modelsbytype -->
<!-- #| tbl-cap: "Uses agency_group fixed effects with grouped and summed taxing agencies. Includes log(eav) and log(est_value) in model. Uses Ptaxsim 2023.0.0. and necessary files edited last on Oct. 12th. HC1 standard errors. " -->

<!-- library(fixest) -->

<!-- mods_1 <- list( -->

<!--   "All Types" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)  | agency_group + year, -->
<!--                data = df, -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->

<!--       "Homerule Munis" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value)  | agency_group + year, -->
<!--                data = df |> filter(home_rule_ind == 1 & type == "Muni"), -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->
<!--      "NonHR" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) | agency_group + year, -->
<!--                data = df |> filter(home_rule_ind == 0 & type != "School"), -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->
<!--        "NonHR Munis" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) | agency_group + year, -->
<!--                data = df |> filter(home_rule_ind == 0 & type == "Muni"), -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->
<!--                 ), -->
<!--     "Schools" = feols(log(total_final_levy) ~ ln_lag_eav + log(est_value) | agency_group + year, -->
<!--                data = df |> filter(type == "School"), -->
<!--                vcov = "hc1", -->
<!--                panel.id = c("agency_group", "year") -->

<!--                 ) -->
<!--   ) -->


<!-- modelsummary::modelsummary( -->
<!--   mods_1, -->
<!--   output = "flextable", -->
<!--  #gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"), -->
<!--               stars = TRUE -->
<!-- ) -->

<!-- ``` -->

<!-- ## Old -->

<!-- ### Old Models w/o "Estimated Value" -->

<!-- ```{r old_models} -->

<!-- library(fixest) -->

<!-- models <- list( -->
<!--   "Plain TWFE" = feols(log(total_final_levy) ~ log(cty_cook_eav)  | agency_group + year,  data = grouped_manual, vcov = "newey_west", panel.id = c("agency_group", "year")), -->

<!--       "Homerule TWFE" = feols(log(total_final_levy) ~ log(cty_cook_eav)  | agency_group + year,  data = grouped_manual |> filter(home_rule_ind == "1"), vcov = "newey_west", panel.id = c("agency_group", "year")), -->

<!--   "Nonhomerule" = feols(log(total_final_levy)~ log(cty_cook_eav)  | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual |> filter(home_rule_ind == "0")), -->

<!--     "Nonhomerule - noschools" = feols(log(total_final_levy)~ log(cty_cook_eav)  | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual |> filter(home_rule_ind == "0" & type != "School")), -->

<!--   "TWFE w/ AV Lags" = feols(log(total_final_levy)~ log(cty_cook_eav) + l(log(cty_cook_eav), 1) + l(log(cty_cook_eav), 2 ) | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual), -->

<!--   "Homerule TWFE" = feols(log(total_final_levy) ~ log(cty_cook_eav) + l(log(cty_cook_eav), 1) + l(log(cty_cook_eav), 2 ) | agency_group + year,  data = grouped_manual |> filter(home_rule_ind == "1"), vcov = "newey_west", panel.id = c("agency_group", "year")), -->

<!--   "Nonhomerule" = feols(log(total_final_levy)~ log(cty_cook_eav) + l(log(cty_cook_eav), 1) + l(log(cty_cook_eav), 2 ) | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = grouped_manual |> filter(home_rule_ind == "0")) -->

<!--   ) -->


<!-- modelsummary( -->
<!--   models, -->
<!--   output = "flextable", -->
<!--               stars = TRUE -->
<!-- ) -->


<!-- ``` -->
