---
title: "Replication Code for NTA Panel Data"
author: "AWM & MVH"
date: "October 13, 2024"
format: 
  html:
    code-line-numbers: true
    code-overflow: wrap
    toc: true
    toc-location: left
    cap-location: margin
    df-print: default
    grid:
      sidebar-width: 200px
      body-width: 900px
      margin-width: 200px
---

**Files needed for panel creation replication:**

-   Triad_reassessment_years.csv
-   muni_shortnames.xlsx
-   cpi.csv
-   eq_factor.csv
-   agency_groups.csv

## Code Cleaning Steps

**After the tables from PTAXSIM are joined together (saved as “agency_raw_joined.csv”) observations are filtered out based on our desired sample criteria.** 

-   90% within Cook County 
-   Does not change home rule status during sample years 

### Slightly more detail on cleaning process:

**Some taxing agencies are missing their cty_cook_eav & cty_total_eav even though they have a total_final_levy value** 

-   Using the logic that the tax rate = levy / taxable EAV, then we can back out the EAV by  using the total_final_levy and total_final_rate variables. 
-   Taxable EAV = total_final_levy / (total_final_rate) / 100 
- A Couple municipalities had missing levies and were manually entered by looking up the CAGR and historic levy amounts in the document

**Remove taxing agencies that had a levy = \$0 for any year. Drop values for all years.**  

-   Countryside, Deer Park, Homer Glen, ~~Norridge~~, Oak Brook, Schaumburg, Dixmoor (2011 only) are dropped using \`dropped_munis \<- c("030250000", "030270000", "030300000", "030585000", "030840000", "030890000", "031150000")\` 

**Remove Municipalities that change home rule status:**

-   Midlothian, Northfield, River Grove became home rule in 2010.
-   Melrose Park became home rule in 2011.
-   South Chicago Heights became home rule in 2019.
-   Summit became home rule in 2016.
-   exclude_hr_change \<- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000"

**Keep taxing agencies that are within Cook County**

-   Create variable `pct_in_Cook` = cty_cook_eav / cty_total_eav. Keep all taxing agencies that are 95% or more in Cook County. Use cty_total_eav in the models since we are using the full levy amount in the models


```{r warning = FALSE, message=FALSE}
#| code-fold: true

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(stars)
library(modelsummary)
```

## Join initial data from CSVs

```{r}
## Change database file path to match your computer's location 
## of the PTAXSIM database!


ptaxsim_db_conn <- DBI::dbConnect(RSQLite::SQLite(), "./ptaxsim.db/ptaxsim-2023.0.0.db")

agency_dt <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT *
  FROM agency
  "
) |>
  mutate(first6 = str_sub(agency_num,1,6)) 

all_taxing_agencies <- DBI::dbGetQuery(
  ptaxsim_db_conn,
  "SELECT agency_num, agency_name, major_type, minor_type
  FROM agency_info
  "
  ) |>
  mutate(first6 = str_sub(agency_num, 1, 6))

DBI::dbDisconnect(ptaxsim_db_conn)

```

```{r load_necessary_files}
#| message: false

nicknames <- readxl::read_xlsx("./Necessary_Files/muni_shortnames.xlsx") |> 
  select(-c(agency_number, short_name, `Column1`, `Most recent reassessed`))

# pulls in additional tables that exist in PTAXSIM database
# for calculating taxable AV: Taxable EAV / 
cpi <- read_csv("./Necessary_Files/cpi.csv") 

eq_factor <- read_csv("./Necessary_Files/eq_factor.csv") |> 
  select(-eq_factor_tentative)

agency_triads <- read_csv("./Necessary_Files/agency_reassessmentyears.csv") 

```


```{r}
#| message: false

# Remove variables with data on EAV in other jurisdictions

raw_data_joined <- left_join(agency_dt, agency_triads) |> select(-c(cty_dupage_eav:cty_livingston_eav))

```


## Clean variables and filter observations from joined data


```{r}

# Start with 18649 obs.

raw_data_joined <- raw_data_joined |>
  rename(minor_type = agency_minor_type,
         major_type = agency_major_type) |>
  
  # Filter out SSAs
  # drops 5916 agency-year combos (updated for 2023 db)
  filter(minor_type != "SSA") |> 
  
  # fills in missing cty_cook_eav variables. 
  # uses logic that EAV = levy / tax rate = EAV
  mutate(cty_cook_eav = ifelse(is.na(cty_cook_eav) & total_final_levy > 0, 
                               total_final_levy / (total_final_rate/100), cty_cook_eav),
         cty_total_eav = ifelse(is.na(cty_total_eav) & total_final_levy > 0 , 
                                total_final_levy / (total_final_rate/100), cty_total_eav))

## 12733 obs. (MVH w/ 2023 db)



exclude_hr_change <- c("030770000", "030800000","030880000", "031070000", "031190000", "031250000" )


recoded_data <- raw_data_joined |> 
  left_join(cpi, by = c("year" = "levy_year")) |>
  left_join(eq_factor) |>
  # Excluding munis that change HR status removes 144 agency-year pairs.
  filter(!agency_num %in% exclude_hr_change) |>
  # 12589 obs.
  
  # Clean up data types
  mutate(
    agency_num = as.character(agency_num),            # change variable type
    agency_num = str_pad(agency_num, 9, "left", "0"), # add missing leading zeros
    first6 = str_pad(first6, 6, "left", "0"),
    home_rule_ind = as.character(home_rule_ind),      # change reference category
    reassess_year = as.character(reassess_year)       # change variable type
    ) |>
  
  # Calculate AV as a function of EAV and the EQ factor
  mutate(cty_total_eav = as.numeric(cty_total_eav),    # taxable eav in cook and neighboring counties
         cty_cook_eav = as.numeric(cty_cook_eav),      # taxable EAV in cook county only
         pct_in_Cook = cty_cook_eav / cty_total_eav,   # to identify taxing agencies that cross county lines
         total_final_levy = as.numeric(total_final_levy), 
         av = cty_cook_eav / eq_factor_final,          # backed out taxable Assessed Value of properties
         first6_w_hr = str_c(first6, "_", home_rule_ind),
         agency_w_hr = str_c(agency_num, "_", home_rule_ind)
         ) |> 
  
  # Keep only agencies greater than 95% in Cook
  # Drops 1608 obs.
  filter(pct_in_Cook > 0.95) 

# 10891 obs. in recoded_data

```

## Import grouping labels

```{r}

 # Read in grouped labels

groupies <- readxl::read_xlsx("panel_data_blindcoding.xlsx", sheet = "TFL manual code") |>
  select(first6, agency_num, agency_group, flag_drop, agency_name) |>
  
 # Change object types to facilitate merging.
  
  mutate(agency_num = str_pad(agency_num, 9, "left", "0"),
         agency_num = as.character(agency_num), 
         first6 = as.character(first6), # make character
         first6 = str_pad(first6, 6, "left", "0"), # add leading zeros
        )
```


### Merge Grouped Labelsm, Recode Data & Summarize to Grouped Taxing Agency Level

```{r}


grouped_manual <- recoded_data |> 
  # 10981 obs.
  left_join(groupies,
            by = c("agency_name", "agency_num")
            ) |> 
  # Filter post-grouped agencies to munis, townships, schools and miscellaneous agencies such as TIFs.
  # Drops 345 obs.
    filter(major_type == "MUNICIPALITY/TOWNSHIP" | major_type == "SCHOOL" |   major_type == "MISCELLANEOUS"
      & minor_type != "SANITARY"
           ) |>
  # 10546 obs.
  group_by(year, agency_group) |> 
  # Change dataframe to reflect grouped agencies
  # Consolidates 10546 obs. pre-grouping into 7679 obs.
  reframe(agency_name = first(agency_name), # changed to reframe to make grouping more conspicuous
            agency_num = first(agency_num),
            total_final_levy = sum(total_final_levy, na.rm=TRUE) + 1, # Add 1 to avoid ln(0)
            cty_total_eav = first(cty_total_eav), 
            av = first(av),   # should be first() not sum() --- AWM 3/30/24
            triad_name = first(triad_name), 
            agency_count = n(),
            reassess_year = first(reassess_year),
            home_rule_ind = first(home_rule_ind),
            flag_drop = first(flag_drop)
            ) |> 
  # Create variables to indicate bundling  
  mutate(
      bundled = ifelse(agency_count > 1, 1, 0),
      uniqueid = str_c(agency_group, "_", home_rule_ind, "_", bundled),
     first2_dig = str_sub(agency_num, 1, 2),
    
    # Fix ptaxsim.db misclassification of Cicero, Evanston, and Chicago
    type = case_when(
      first2_dig == "02"  ~ "Township", 
      first2_dig == "03" | agency_group == "Evanston" | 
        agency_group == "Cicero" | agency_group == "Chicago" ~ "Muni",
      first2_dig == "04" ~ "School",
      TRUE ~ "Other"
      )) |>
  select(year, uniqueid, everything()) # puts variables in useful order.


# Identify grouped agencies that do not exist across entire panel
# 9 agency groups will be dropped.
dropped_agencies <- grouped_manual |>
  group_by(agency_group) |> 
  summarize(n=n()) |>
  filter(n!=18)

# Filter out observations from 9 agencies (65 agency_group-year obs.)
# 7614 remaining obs.

grouped_manual <- grouped_manual |>
  filter(!agency_group %in% dropped_agencies$agency_group)

```

```{r year_type_table}

table(grouped_manual$year, grouped_manual$type)

```

```{r}
grouped_manual |> 
  group_by(year, agency_group, triad_name)  |> 
  summarize(total_final_levy = sum(total_final_levy, na.rm = TRUE)) |> 
  filter(agency_group != "Chicago") |> 
  ggplot() + 
  theme_classic() + 
  geom_line(aes(x=year, y = total_final_levy, group=agency_group) ) +
  facet_wrap(~triad_name)

grouped_manual |> 
  group_by(year, agency_group, triad_name, home_rule_ind)  |> 
  summarize(total_final_levy = sum(total_final_levy, na.rm = TRUE)) |> 
  filter(agency_group != "Chicago") |> 
  ggplot() + 
  theme_classic() + 
  geom_line(aes(x=year, y = total_final_levy, group=agency_group) ) +
  facet_wrap(~home_rule_ind)
```


## Models


```{r}
library(fixest)
df <- grouped_manual

models <- list(
  "Plain TWFE" = feols(log(total_final_levy) ~ log(av)  | agency_group + year,  data = df, vcov = "newey_west", panel.id = c("agency_group", "year")),
  
      "Homerule TWFE" = feols(log(total_final_levy) ~ log(av)  | agency_group + year,  data = df |> filter(home_rule_ind == "1"), vcov = "newey_west", panel.id = c("agency_group", "year")),
      
  "Nonhomerule" = feols(log(total_final_levy)~ log(av)  | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = df |> filter(home_rule_ind == "0")),
  
    "Nonhomerule - noschools" = feols(log(total_final_levy)~ log(av)  | agency_group + year, vcov = "newey_west", panel.id = c("agency_group", "year"), data = df |> filter(home_rule_ind == "0" & type != "School")),
  
  "TWFE w/ AV Lags" = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | agency_name + year, vcov = "newey_west", panel.id = c("agency_name", "year"), data = df),
  
  "Homerule TWFE" = feols(log(total_final_levy) ~ log(av) + l(log(av), 1) + l(log(av), 2 ) | agency_name + year,  data = df |> filter(home_rule_ind == "1"), vcov = "newey_west", panel.id = c("agency_name", "year")),
      
  "Nonhomerule" = feols(log(total_final_levy)~ log(av) + l(log(av), 1) + l(log(av), 2 ) | agency_name + year, vcov = "newey_west", panel.id = c("agency_name", "year"), data = df |> filter(home_rule_ind == "0"))
  
  )


modelsummary(
  models,
  output = "flextable",
              stars = TRUE
)
```



```{r}
df_formodels <- df |>
  ungroup() |>
  group_by(agency_group) |> 
  
  arrange(year)|> 
  mutate(
    #reassess_year=as.numeric(reassess_year),
    assess_year_av = ifelse(reassess_year == 1, av, NA)) |>
  
  fill(assess_year_av, .direction = "down") |>
  
  mutate(
    # rate of growth in assessment year is 0

    # rate of growth from point A to point B = 3-year CAGR 
    
    # Alea's math: Do year after the assessment:
    # rate_smooth_2 = if_else(lag(reassess_year) == 1 | lead(reassess_year, n=2) == 1, (lead(av, 3) / av)^(1/4) - 1, 0),
    # av_stair_2 = if_else(lag(reassess_year, n=1) == 1 | lead(reassess_year, n = 2) == 1, assess_year_av*(1+rate_smooth_2), assess_year_av),
    # 
 #    # Alea's math: Do 2 years afer the assessment using previous predicted value:
 #    rate_smooth_2 = if_else(lag(reassess_year) == 1 | lead(reassess_year, n=2) ==1, ((lead(av, 2) / av_stair_2)^(1/3)) - 1, rate_smooth_2),
 #    av_stair_2 = ifelse(lead(reassess_year) == 1 | lag(reassess_year, n = 2) == 1, lag(av_stair_2)*(1+lag(rate_smooth_2)), av_stair_2),
 #   # rate_smooth_2 = if_else(lag(reassess_year, n=2) == 1, ((lead(av, 1) / av_stair_2)^(1/2)) - 1, rate_smooth_2),
 #   av_smooth_2 = av_stair_2 * (1+rate_smooth_2),
 # av_true = av_stair_2,
    
    # Merriman's math
    # 1 year after assessment:
    rate_smooth = if_else(lag(reassess_year, n=1) == 1 | lead(reassess_year, n=2) == 1, ((lead(av, 2) / assess_year_av)^(1/3)) - 1, 0),
    
     # 2 years after assessment:  
   rate_smooth = if_else(lag(reassess_year, n=2) == 1 | lead(reassess_year, n=1) == 1, (lead(assess_year_av, 1) / assess_year_av)^(1/2) - 1, rate_smooth),

  rate_smooth = if_else(reassess_year == 1, 0, rate_smooth),
  av_stair = assess_year_av*(1+rate_smooth),
  av_true = av_stair
 ) |>
  
  select(year, reassess_year, agency_name, av, rate_smooth, everything()) |> 
  arrange(agency_name, year) |>
  select(agency_group, year, av, assess_year_av, av_true, 
         av_stair, rate_smooth, everything()) |>
  ungroup()

```

```{r}
#| label: tbl-merriman_models-agency_group
#| tbl-cap: "agency_group fixed effects and sums. Includes log(av) and log(av_true in model). Uses September 21st 2024 csv file."

library(fixest)
mods_1 <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) + log(av_true) | agency_group + year,
               data = df_formodels,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true) | agency_group + year,
               data = df_formodels,
               vcov = "newey_west",
               panel.id = c("agency_group", "year")
                )
  )


modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```




```{r}
#| label: tbl-merriman_models
#| tbl-cap: "Includes log(av) and log(av_true in model). Uses September 21st 2024 csv file."

library(fixest)
mods_1 <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) + log(av_true) | agency_name + year,
               data = df_formodels,
               vcov = "newey_west",
               panel.id = c("agency_name", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + log(av_true) + log(av)*log(av_true) | agency_name + year,
               data = df_formodels,
               vcov = "newey_west",
               panel.id = c("agency_name", "year")
                )
  )

modelsummary::modelsummary(
  mods_1,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

mods_iid <- list(
  
  "1" = feols(log(total_final_levy) ~ log(av) + log(av_true) | agency_name + year,
               data = df_formodels,
               vcov = "iid",
               panel.id = c("agency_name", "year")
                ),
  
  "Interact" = feols(log(total_final_levy) ~ log(av) + av_true + log(av)*av_true | agency_name + year,
               data = df_formodels,
               vcov = "iid",
               panel.id = c("agency_name", "year")
                )
  )


modelsummary::modelsummary(
  mods_iid,
  output = "flextable",
 gof_map = c("nobs", "f",  "r2.within","r2.within.adjusted","complete.obs","std.error.type", "rmse"),
              stars = TRUE
)

```

